---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Bivariate Regression Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Bivariate Regression Tutorial with Summary Statistics

### Data Management

This code inputs the variable summaries and creates a summary table.
```{r}
Predictor <- c(N=4,M=2.000,SD=2.449)
Criterion <- c(N=4,M=7.000,SD=2.449)
BivariateSummary <- rbind(Predictor,Criterion)
class(BivariateSummary) <- "wss"
```

This code creates a correlation matrix, enters just the top triangle, and then uses a function to fill in the whole matrix.
```{r}
RegressionCorr <- declareCorrelations("Predictor","Criterion")
RegressionCorr["Predictor","Criterion"] <- .056
RegressionCorr <- fillCorrelations(RegressionCorr)
```

This code creates new tables that identify the specific variables used in the regression model.
```{r}
PredictorSummary <- rbind(Predictor)
class(PredictorSummary) <- "wss"
CriterionSummary <- rbind(Criterion)
```

### Analyses of Overall Model Fit

This section produces analyses of the overall fit of the model.

#### Confidence Interval

This code will calculate R Squared and Adjusted R Squared for the regression model.
```{r}
describeRegressionEffect(PredictorSummary,CriterionSummary,RegressionCorr)
```

This code will produce the confidence interval for R Squared.
```{r}
estimateRegressionEffect(PredictorSummary,CriterionSummary,RegressionCorr)
```

The code defaults to 90% confidence intervals. This can be changed if desired.
```{r}
estimateRegressionEffect(PredictorSummary,CriterionSummary,RegressionCorr,conf.level=.95)
```

#### Significance Test

This code will produce a source table associated with the regression model.
```{r}
describeRegressionOmnibus(PredictorSummary,CriterionSummary,RegressionCorr)
```

This code will calculate NHST for the regression model.
```{r}
testRegressionOmnibus(PredictorSummary,CriterionSummary,RegressionCorr)
```

### Analyses of the Regression Coefficients

This section analyses the regression coefficients obtained from the overall model.

#### Confidence Intervals 

This code will provide a table of confidence intervals for each of the regression coefficients.
```{r}
estimateRegressionCoefficients(PredictorSummary,CriterionSummary,RegressionCorr)
```

This code will produce a graph of the confidence intervals for each of the regression coefficients.
```{r,Regression-BivariateCoeffA}
plotRegressionCoefficients(PredictorSummary,CriterionSummary,RegressionCorr)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateRegressionCoefficients(PredictorSummary,CriterionSummary,RegressionCorr,conf.level=.99)
```

For the graph, it is possible to plot just coefficients for the predictors (minus the intercept) in addition to changing the confidence level. A comparison line and region of practical equivalence can also be added.
```{r,Regression-BivariateCoeffB}
plotRegressionCoefficients(PredictorSummary,CriterionSummary,RegressionCorr,conf.level=.99,mu=0,rope=c(-2,2),intercept=FALSE)
```

#### Significance Tests

This code will produce a table of NHST separately for each of the regression coefficients. In this case, all the coefficients are tested against a value of zero.
```{r}
testRegressionCoefficients(PredictorSummary,CriterionSummary,RegressionCorr)
```

#### Standardized Coefficient

This code will provide a table of confidence intervals for the standardized coefficient.
```{r}
estimateStandardizedRegressionCoefficients(PredictorSummary,CriterionSummary,RegressionCorr)
```

This code will produce a graph of the confidence intervals for the standardized coefficient.
```{r,Regression-BivariateStandardA}
plotStandardizedRegressionCoefficients(PredictorSummary,CriterionSummary,RegressionCorr)
```

As in other places, the code defaults to a 95% confidence interval. This can be changed if desired.
```{r}
estimateStandardizedRegressionCoefficients(PredictorSummary,CriterionSummary,RegressionCorr,conf.level=.99)
```

For the graph, it is possible to change the confidence level.
```{r,Regression-BivariateStandardB}
plotStandardizedRegressionCoefficients(PredictorSummary,CriterionSummary,RegressionCorr,conf.level=.99)
```

### Analyses of Regression Values

This section provides analyses of individual predicted values.

#### Regression Line

This code produces a plot of the regression line (with confidence and prediction intervals suppressed).
```{r,Regression-BivariateLineA}
plotRegression(PredictorSummary,CriterionSummary,RegressionCorr,interval="none")
```

#### Confidence and Prediction Intervals

This code provides estimates confidence and prediction limits for a specific value of the Predictor (value=4).
```{r}
estimateRegression(PredictorSummary,CriterionSummary,RegressionCorr,value=4)
```

This code plots the confidence interval associated with the regression line and labels the interval for the specific value of the Predictor.
```{r,Regression-BivariateConfA}
plotRegression(PredictorSummary,CriterionSummary,RegressionCorr,value=4,interval="confidence")
```

This code plots the prediction interval associated with the regression line and labels the interval for the specific value of the Predictor.
```{r,Regression-BivariateConfB}
plotRegression(PredictorSummary,CriterionSummary,RegressionCorr,value=4,interval="prediction")
```
