---
subtitle: "Bivariate Regression Data Tutorial"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Bivariate Regression Data Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7",filename='revised_toc.R')
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Bivariate Regression Data Tutorial

### Data Management

This page analyzes bivariate regression models using raw data input.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile,base_level=3,toc_depth=4)
```

---

#### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Predictor <- c(0,0,3,5)
Criterion <- c(9,6,4,9)
BivariateData <- data.frame(Predictor,Criterion)
```

#### Descriptive Statistics

This code obtains the descriptive statistics for the data frame.
```{r}
describeMeans(BivariateData)
describeCorrelations(BivariateData)
```

### Analyses of the Overall Model

This section produces analyses of the overall regression model.

#### Confidence Interval

This code will produce the confidence interval for R Squared.
```{r}
estimateRegressionOmnibus(BivariateData)
```

The code defaults to 90% confidence intervals. This can be changed if desired.
```{r}
estimateRegressionOmnibus(BivariateData,conf.level=.95)
```

#### Significance Test

This code will produce a source table associated with the regression model.
```{r}
describeRegressionOmnibus(BivariateData)
```

This code will calculate NHST for the regression model.
```{r}
testRegressionOmnibus(BivariateData)
```

### Analyses of the Regression Coefficients

This section analyses the regression coefficients obtained from the overall model.

#### Confidence Intervals 

This code will provide a table of confidence intervals for each of the regression coefficients.
```{r}
estimateRegressionCoefficients(BivariateData)
```

This code will produce a graph of the confidence intervals for each of the regression coefficients.
```{r,Bivariate-Data-CoefficientsA}
plotRegressionCoefficients(BivariateData)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateRegressionCoefficients(BivariateData,conf.level=.99)
```

For the graph, it is possible to plot just coefficients for the predictors (minus the intercept) in addition to changing the confidence level. A comparison line and region of practical equivalence can also be added.
```{r,Bivariate-Data-CoefficientsB}
plotRegressionCoefficients(BivariateData,conf.level=.99,line=0,rope=c(-2,2),intercept=FALSE)
```

#### Significance Tests

This code will produce a table of NHST separately for each of the regression coefficients. In this case, all the coefficients are tested against a value of zero.
```{r}
testRegressionCoefficients(BivariateData)
```

#### Standardized Coefficient

This code will provide a table of confidence intervals for the standardized coefficient.
```{r}
estimateStandardizedRegressionCoefficients(BivariateData)
```

This code will produce a graph of the confidence intervals for the standardized coefficient.
```{r,Bivariate-Data-StandardizedA}
plotStandardizedRegressionCoefficients(BivariateData)
```

As in other places, the code defaults to a 95% confidence interval. This can be changed if desired.
```{r}
estimateStandardizedRegressionCoefficients(BivariateData,conf.level=.99)
```

For the graph, it is possible to change the confidence level.
```{r,Bivariate-Data-StandardizedB}
plotStandardizedRegressionCoefficients(BivariateData,conf.level=.99)
```

### Analyses of Regression Values

This section provides analyses of individual predicted values.

#### Regression Line

This code produces a plot of the regression line (with confidence and prediction intervals suppressed).
```{r,Bivariate-Data-LineA}
plotRegression(BivariateData,interval="none")
```

This code adds a scatter of data points to the regression plot.
```{r,Bivariate-Data-LineB}
plotRegression(BivariateData,interval="none",points=TRUE)
```

#### Confidence and Prediction Intervals

This code provides estimates confidence and prediction limits for a specific value of the Predictor (value=4).
```{r}
estimateRegression(BivariateData,value=4)
```

This code plots the confidence interval associated with the regression line and labels the interval for the specific value of the Predictor.
```{r,Bivariate-Data-ConfidenceA}
plotRegression(BivariateData,value=4,interval="confidence")
```

This code plots the prediction interval associated with the regression line and labels the interval for the specific value of the Predictor.
```{r,Bivariate-Data-ConfidenceB}
plotRegression(BivariateData,value=4,interval="prediction")
```
