---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Mixed Design Correlations Data Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## Mixed Design Correlations Data Tutorial

### Data Management

#### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Factor <- c(1,1,1,1,2,2,2,2)
Outcome1 <- c(0,0,3,5,9,4,6,9)
Outcome2 <- c(4,7,4,9,6,3,3,8)
Outcome3 <- c(4,9,6,9,5,3,8,8)
Factor <- factor(Factor,levels=c(1,2),labels=c("Level1","Level2"))
MixedData <- data.frame(Factor,Outcome1,Outcome2,Outcome3)
```

This code subsets the data into two different data frames (for simple effects analysis).
```{r}
MixedDataL1 <- subset(MixedData,Factor=="Level1")
MixedDataL2 <- subset(MixedData,Factor=="Level2")
```

#### Descriptive Statistics

This code obtains the descriptive statistics for the two data frames.
```{r}
with(MixedDataL1,describeMeans(cbind(Outcome1,Outcome2,Outcome3)))
with(MixedDataL2,describeMeans(cbind(Outcome1,Outcome2,Outcome3)))
```

This code obtains a table of correlations for the two data frames.
```{r}
with(MixedDataL1,describeCorrelations(cbind(Outcome1,Outcome2,Outcome3)))
with(MixedDataL2,describeCorrelations(cbind(Outcome1,Outcome2,Outcome3)))
```

### Analyses of a Correlation

This section produces analyses of a single correlation in each of the frames.

#### Confidence Intervals

This code will provide the confidence interval for the correlation.
```{r}
with(MixedDataL1,estimateCorrelations(cbind(Outcome1,Outcome2)))
with(MixedDataL2,estimateCorrelations(cbind(Outcome1,Outcome2)))
```

This code will produce a graph of the confidence interval for the correlation.
```{r,MixedCorrelation-A}
with(MixedDataL1,plotCorrelations(cbind(Outcome1,Outcome2)))
with(MixedDataL2,plotCorrelations(cbind(Outcome1,Outcome2)))
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
with(MixedDataL1,estimateCorrelations(cbind(Outcome1,Outcome2),conf.level=.99))
with(MixedDataL2,estimateCorrelations(cbind(Outcome1,Outcome2),conf.level=.99))
```

Of course, it is possible to change from the default confidence level in the graph. It is also possible to add a comparison value and a region of practical equivalence.
```{r,MixedCorrelation-B}
with(MixedDataL1,plotCorrelations(cbind(Outcome1,Outcome2),conf.level=.99,line=0,rope=c(-.2,.2)))
with(MixedDataL2,plotCorrelations(cbind(Outcome1,Outcome2),conf.level=.99,line=0,rope=c(-.2,.2)))
```

#### Significance Tests

This code will produce a table of NHST for the correlation (against a value of zero).
```{r}
with(MixedDataL1,testCorrelations(cbind(Outcome1,Outcome2)))
with(MixedDataL2,testCorrelations(cbind(Outcome1,Outcome2)))
```

### Analyses of Several Correlations

This section analyzes the correlations among multiple variables.

#### Confidence Intervals

This code will provide the confidence intervals for the correlations.
```{r}
with(MixedDataL1,estimateCorrelations(cbind(Outcome1,Outcome2,Outcome3)))
with(MixedDataL2,estimateCorrelations(cbind(Outcome1,Outcome2,Outcome3)))
```

This code will produce a graph of the confidence intervals for the correlations.
```{r,MixedCorrelations-A}
with(MixedDataL1,plotCorrelations(cbind(Outcome1,Outcome2,Outcome3)))
with(MixedDataL2,plotCorrelations(cbind(Outcome1,Outcome2,Outcome3)))
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
with(MixedDataL1,estimateCorrelations(cbind(Outcome1,Outcome2,Outcome3),conf.level=.99))
with(MixedDataL2,estimateCorrelations(cbind(Outcome1,Outcome2,Outcome3),conf.level=.99))
```

Of course, it is possible to change from the default confidence level in the graph. It is also possible to add a comparison value and a region of practical equivalence.
```{r,MixedCorrelations-B}
with(MixedDataL1,plotCorrelations(cbind(Outcome1,Outcome2,Outcome3),conf.level=.99,line=0,rope=c(-.2,.2)))
with(MixedDataL2,plotCorrelations(cbind(Outcome1,Outcome2,Outcome3),conf.level=.99,line=0,rope=c(-.2,.2)))
```

#### Significance Tests

This code will produce a table of NHST for the correlations (against a value of zero).
```{r}
with(MixedDataL1,testCorrelations(cbind(Outcome1,Outcome2,Outcome3)))
with(MixedDataL2,testCorrelations(cbind(Outcome1,Outcome2,Outcome3)))
```

### Analyses of a Correlation Difference

This section analyzes the difference in the correlations from the two frames.

#### Confidence Intervals

First it is necessary to estimate the confidence intervals for each of the correlations.
```{r}
CorrEstimateL1 <- with(MixedDataL1,estimateCorrelations(cbind(Outcome1,Outcome2)))
CorrEstimateL2 <- with(MixedDataL2,estimateCorrelations(cbind(Outcome1,Outcome2)))
```

Then we can estimate the difference in the correlations and get its confidence interval.
```{r}
estimateCorrelationDifference(CorrEstimateL1,CorrEstimateL2)
```

Of course, it is also possible to the plot this estimate.
```{r,MixedCorrDifference-A}
plotCorrelationDifference(CorrEstimateL1,CorrEstimateL2)
```

The code defaults to 95% confidence intervals. This can be changed if desired by first re-estimating the confidence intervals for each correlation.
```{r}
CorrEstimateL1 <- with(MixedDataL1,estimateCorrelations(cbind(Outcome1,Outcome2),conf.level=.99))
CorrEstimateL2 <- with(MixedDataL2,estimateCorrelations(cbind(Outcome1,Outcome2),conf.level=.99))
```

Then we can estimate the difference in the correlations and get its confidence interval.
```{r}
estimateCorrelationDifference(CorrEstimateL1,CorrEstimateL2)
```

Finally, we can re-plot the estimate.
```{r,MixedCorrDifference-B}
plotCorrelationDifference(CorrEstimateL1,CorrEstimateL2)
```

If you wish, you can get the confidence intervals for the correlations and the correlation difference combined.

First it is necessary to estimate the confidence intervals for each of the correlations.
```{r}
CorrEstimateL1 <- with(MixedDataL1,estimateCorrelations(cbind(Outcome1,Outcome2)))
CorrEstimateL2 <- with(MixedDataL2,estimateCorrelations(cbind(Outcome1,Outcome2)))
```

Then we can estimate the correlations and the difference in the correlations.
```{r}
estimateCorrelationComparison(CorrEstimateL1,CorrEstimateL2)
```

This code produces a difference plot using the confidence intervals for the correlations and the correlation difference.
```{r,MixedCorrComparison-A}
plotCorrelationComparison(CorrEstimateL1,CorrEstimateL2)
```

The code defaults to 95% confidence intervals. This can be changed if desired by first re-estimating the confidence intervals for each correlation.
```{r}
CorrEstimateL1 <- with(MixedDataL1,estimateCorrelations(cbind(Outcome1,Outcome2),conf.level=.99))
CorrEstimateL2 <- with(MixedDataL2,estimateCorrelations(cbind(Outcome1,Outcome2),conf.level=.99))
```

Then we can estimate the correlations and the difference in the correlations.
```{r}
estimateCorrelationComparison(CorrEstimateL1,CorrEstimateL2)
```

Finally, we can re-plot the comparison.
```{r,MixedCorrComparison-B}
plotCorrelationComparison(CorrEstimateL1,CorrEstimateL2)
```
