---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Mixed Design Correlations Summary Statistics Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Mixed Design Correlations Summary Statistics Tutorial

### Data Management

This code inputs the variable summaries and creates a summary table.
```{r}
Outcome1 <- c(N=4,M=2.000,SD=2.449)
Outcome2 <- c(N=4,M=6.000,SD=2.449)
Outcome3 <- c(N=4,M=7.000,SD=2.449)
MixedSummaryL1 <- rbind(Outcome1,Outcome2,Outcome3)
class(MixedSummaryL1) <- "wss"
```

This code creates a correlation matrix, enters just the top triangle, and then uses a function to fill in the whole matrix.
```{r}
MixedCorrL1 <- declareCorrelations("Outcome1","Outcome2","Outcome3")
MixedCorrL1["Outcome1",] <- c(1.000,.500,.389)
MixedCorrL1["Outcome2",] <- c(.500,1.000,.889)
MixedCorrL1["Outcome3",] <- c(.389,.889,1.000)
```

And repeat the process to create the second subset.
```{r}
Outcome1 <- c(N=4,M=7.000,SD=2.449)
Outcome2 <- c(N=4,M=5.000,SD=2.449)
Outcome3 <- c(N=4,M=6.000,SD=2.449)
MixedSummaryL2 <- rbind(Outcome1,Outcome2,Outcome3)
class(MixedSummaryL2) <- "wss"
```

And for the correlation matrix of the second subset.
```{r}
MixedCorrL2 <- declareCorrelations("Outcome1","Outcome2","Outcome3")
MixedCorrL2["Outcome1",] <- c(1.000,.889,.500)
MixedCorrL2["Outcome2",] <- c(.889,1.000,.389)
MixedCorrL2["Outcome3",] <- c(.500,.389,1.000)
```

### Analyses of a Correlation

This section produces analyses of a single correlation in each of the subsets.

This code creates a new table that identifies the two levels for comparison and repeats for the second subset.
```{r}
CompSummaryL1 <- MixedSummaryL1[c("Outcome1","Outcome2"),]
class(CompSummaryL1) <- "wss"
CompSummaryL2 <- MixedSummaryL2[c("Outcome1","Outcome2"),]
class(CompSummaryL2) <- "wss"
```

This creates a separate correlation matrix for each of the two subsets of data.
```{r}
CompCorrL1 <- MixedCorrL1[c("Outcome1","Outcome2"),c("Outcome1","Outcome2")]
CompCorrL2 <- MixedCorrL2[c("Outcome1","Outcome2"),c("Outcome1","Outcome2")]
```

#### Confidence Intervals

This code will provide the confidence interval for the correlation.
```{r}
estimateCorrelations(CompSummaryL1,CompCorrL1)
estimateCorrelations(CompSummaryL2,CompCorrL2)
```

This code will produce a graph of the confidence interval for the correlation.
```{r,MixedCorrelation-A}
plotCorrelations(CompSummaryL1,CompCorrL1)
plotCorrelations(CompSummaryL2,CompCorrL2)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateCorrelations(CompSummaryL1,CompCorrL1,conf.level=.99)
estimateCorrelations(CompSummaryL2,CompCorrL2,conf.level=.99)
```

Of course, it is possible to change from the default confidence level in the graph. It is also possible to add a comparison value and a region of practical equivalence.
```{r,MixedCorrelation-B}
plotCorrelations(CompSummaryL1,CompCorrL1,conf.level=.99,line=0,rope=c(-.2,.2))
plotCorrelations(CompSummaryL2,CompCorrL2,conf.level=.99,line=0,rope=c(-.2,.2))
```

#### Significance Tests

This code will produce a table of NHST for the correlation (against a value of zero).
```{r}
testCorrelations(CompSummaryL1,CompCorrL1)
testCorrelations(CompSummaryL2,CompCorrL2)
```

### Analyses of Several Correlations

This section analyzes the correlations among multiple variables in each of the subsets.

#### Confidence Intervals

This code will provide the confidence intervals for the correlations.
```{r}
estimateCorrelations(MixedSummaryL1,MixedCorrL1)
estimateCorrelations(MixedSummaryL2,MixedCorrL2)
```

This code will produce a graph of the confidence intervals for the correlations.
```{r,MixedCorrelations-A}
plotCorrelations(MixedSummaryL1,MixedCorrL1)
plotCorrelations(MixedSummaryL2,MixedCorrL2)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateCorrelations(MixedSummaryL1,MixedCorrL1,conf.level=.99)
estimateCorrelations(MixedSummaryL2,MixedCorrL2,conf.level=.99)
```

Of course, it is possible to change from the default confidence level in the graph. It is also possible to add a comparison value and a region of practical equivalence.
```{r,MixedCorrelations-B}
plotCorrelations(MixedSummaryL1,MixedCorrL1,conf.level=.99,line=0,rope=c(-.2,.2))
plotCorrelations(MixedSummaryL2,MixedCorrL2,conf.level=.99,line=0,rope=c(-.2,.2))
```

#### Significance Tests

This code will produce a table of NHST for the correlations (against a value of zero).
```{r}
testCorrelations(MixedSummaryL1,MixedCorrL1)
testCorrelations(MixedSummaryL2,MixedCorrL2)
```

### Analyses of a Correlation Difference

This section analyzes the difference in the correlations from the two subsets.

#### Confidence Intervals

First it is necessary to estimate the confidence intervals for each of the correlations.
```{r}
CorrEstimateL1 <- estimateCorrelations(CompSummaryL1,CompCorrL1)
CorrEstimateL2 <- estimateCorrelations(CompSummaryL2,CompCorrL2)
```

Then we can estimate the difference in the correlations and get its confidence interval.
```{r}
estimateCorrelationDifference(CorrEstimateL1,CorrEstimateL2)
```

Of course, it is also possible to the plot this estimate.
```{r,MixedCorrDifference-A}
plotCorrelationDifference(CorrEstimateL1,CorrEstimateL2)
```

The code defaults to 95% confidence intervals. This can be changed if desired by first re-estimating the confidence intervals for each correlation.
```{r}
CorrEstimateL1 <- estimateCorrelations(CompSummaryL1,CompCorrL1,conf.level=.99)
CorrEstimateL2 <- estimateCorrelations(CompSummaryL2,CompCorrL2,conf.level=.99)
```

Then we can estimate the difference in the correlations and get its confidence interval.
```{r}
estimateCorrelationDifference(CorrEstimateL1,CorrEstimateL2)
```

Finally, we can re-plot the estimate.
```{r,MixedCorrDifference-B}
plotCorrelationDifference(CorrEstimateL1,CorrEstimateL2)
```

If you wish, you can get the confidence intervals for the correlations and the correlation difference combined.

First it is necessary to estimate the confidence intervals for each of the correlations.
```{r}
CorrEstimateL1 <- estimateCorrelations(CompSummaryL1,CompCorrL1)
CorrEstimateL2 <- estimateCorrelations(CompSummaryL2,CompCorrL2)
```

Then we can estimate the correlations and the difference in the correlations.
```{r}
estimateCorrelationComparison(CorrEstimateL1,CorrEstimateL2)
```

This code produces a difference plot using the confidence intervals for the correlations and the correlation difference.
```{r,MixedCorrComparison-A}
plotCorrelationComparison(CorrEstimateL1,CorrEstimateL2)
```

The code defaults to 95% confidence intervals. This can be changed if desired by first re-estimating the confidence intervals for each correlation.
```{r}
CorrEstimateL1 <- estimateCorrelations(CompSummaryL1,CompCorrL1,conf.level=.99)
CorrEstimateL2 <- estimateCorrelations(CompSummaryL2,CompCorrL2,conf.level=.99)
```

Then we can estimate the correlations and the difference in the correlations.
```{r}
estimateCorrelationComparison(CorrEstimateL1,CorrEstimateL2)
```

Finally, we can re-plot the comparison.
```{r,MixedCorrComparison-B}
plotCorrelationComparison(CorrEstimateL1,CorrEstimateL2)
```
