---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Multiple Regression Summary Statistics Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Multiple Regression Summary Statistics Tutorial

This page analyzes multiple regression models using summary statistics input.

### Data Management

This code inputs the variable summaries and creates a summary table.
```{r}
Predictor1 <- c(N=4,M=2.000,SD=2.449)
Predictor2 <- c(N=4,M=6.000,SD=2.449)
Criterion <- c(N=4,M=7.000,SD=2.449)
RegressionSummary <- rbind(Predictor1,Predictor2,Criterion)
class(RegressionSummary) <- "wss"
```

This code creates a correlation matrix, enters just the top triangle, and then uses a function to fill in the whole matrix.
```{r}
RegressionCorr <- declareCorrelations("Predictor1","Predictor2","Criterion")
RegressionCorr["Predictor1","Predictor2"] <- .500
RegressionCorr["Predictor1","Criterion"] <- .056
RegressionCorr["Predictor2","Criterion"] <- .389
RegressionCorr <- fillCorrelations(RegressionCorr)
```

### Analyses of the Overall Model

This section produces analyses of the overall regression model.

#### Confidence Interval

This code will produce the confidence interval for R Squared.
```{r}
estimateRegressionOmnibus(RegressionSummary,RegressionCorr)
```

The code defaults to 90% confidence intervals. This can be changed if desired.
```{r}
estimateRegressionOmnibus(RegressionSummary,RegressionCorr,conf.level=.95)
```

#### Significance Test

This code will produce a source table associated with the regression model.
```{r}
describeRegressionOmnibus(RegressionSummary,RegressionCorr)
```

This code will calculate NHST for the regression model.
```{r}
testRegressionOmnibus(RegressionSummary,RegressionCorr)
```

### Analyses of the Regression Coefficients

This section analyses the regression coefficients obtained from the overall model.

#### Confidence Intervals

This code will provide a table of confidence intervals for each of the regression coefficients.
```{r}
estimateRegressionCoefficients(RegressionSummary,RegressionCorr)
```

This code will produce a graph of the confidence intervals for each of the regression coefficients.
```{r,Multiple-Summary-CoefficientsA}
plotRegressionCoefficients(RegressionSummary,RegressionCorr)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateRegressionCoefficients(RegressionSummary,RegressionCorr,conf.level=.99)
```

For the graph, it is possible to plot just coefficients for the predictors (minus the intercept) in addition to changing the confidence level.
```{r,Multiple-Summary-CoefficientsB}
plotRegressionCoefficients(RegressionSummary,RegressionCorr,conf.level=.99,line=0,intercept=FALSE)
```

#### Significance Tests

This code will produce a table of NHST separately for each of the regression coefficients. In this case, all the coefficients are tested against a value of zero.
```{r}
testRegressionCoefficients(RegressionSummary,RegressionCorr)
```

#### Standardized Coefficient

This code will provide a table of confidence intervals for each of the standardized coefficients.
```{r}
estimateStandardizedRegressionCoefficients(RegressionSummary,RegressionCorr)
```

This code will produce a graph of the confidence intervals for each of the standardized coefficients.
```{r,Multiple-Summary-StandardizedA}
plotStandardizedRegressionCoefficients(RegressionSummary,RegressionCorr)
```

As in other places, the code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateStandardizedRegressionCoefficients(RegressionSummary,RegressionCorr,conf.level=.99)
```

For the graph, it is possible to change the confidence level.
```{r,Multiple-Summary-StandardizedB}
plotStandardizedRegressionCoefficients(RegressionSummary,RegressionCorr,conf.level=.99)
```
