---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Multiple Regression Tutorial with Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Multiple Regression Tutorial with Data

### Data Management

#### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Predictor1 <- c(0,0,3,5)
Predictor2 <- c(4,7,4,9)
Criterion <- c(9,6,4,9)
RegressionData <- data.frame(Predictor1,Predictor2,Criterion)
```

#### Descriptive Statistics

This code obtains the descriptive statistics for the data frame.
```{r}
describeMeans(Predictor1,Predictor2,Criterion)
```

### Analyses of the Overall Model

This section produces analyses of the overall regression model.

#### Confidence Interval

This code will produce the confidence interval for R Squared.
```{r}
estimateRegressionOmnibus(cbind(Predictor1,Predictor2),Criterion)
```

The code defaults to 90% confidence intervals. This can be changed if desired.
```{r}
estimateRegressionOmnibus(cbind(Predictor1,Predictor2),Criterion,conf.level=.95)
```

#### Significance Test

This code will produce a source table associated with the regression model.
```{r}
describeRegressionOmnibus(cbind(Predictor1,Predictor2),Criterion)
```

This code will calculate NHST for the regression model.
```{r}
testRegressionOmnibus(cbind(Predictor1,Predictor2),Criterion)
```

### Analyses of the Regression Coefficients

This section analyses the regression coefficients obtained from the overall model.

#### Confidence Intervals 

This code will provide a table of confidence intervals for each of the regression coefficients.
```{r}
estimateRegressionCoefficients(cbind(Predictor1,Predictor2),Criterion)
```

This code will produce a graph of the confidence intervals for each of the regression coefficients.
```{r,Regression-MultipleA}
plotRegressionCoefficients(cbind(Predictor1,Predictor2),Criterion)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateRegressionCoefficients(cbind(Predictor1,Predictor2),Criterion,conf.level=.99)
```

For the graph, it is possible to plot just coefficients for the predictors (minus the intercept) in addition to changing the confidence level.
```{r,Regression-MultipleB}
plotRegressionCoefficients(cbind(Predictor1,Predictor2),Criterion,conf.level=.99,line=0,intercept=FALSE)
```

#### Significance Tests

This code will produce a table of NHST separately for each of the regression coefficients. In this case, all the coefficients are tested against a value of zero.
```{r}
testRegressionCoefficients(cbind(Predictor1,Predictor2),Criterion)
```

#### Standardized Coefficients

This code will provide a table of confidence intervals for each of the standardized coefficients.
```{r}
estimateStandardizedRegressionCoefficients(cbind(Predictor1,Predictor2),Criterion)
```

This code will produce a graph of the confidence intervals for each of the standardized coefficients.
```{r,Regression-MultipleStandardA}
plotStandardizedRegressionCoefficients(cbind(Predictor1,Predictor2),Criterion)
```

As in other places, the code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateStandardizedRegressionCoefficients(cbind(Predictor1,Predictor2),Criterion,conf.level=.99)
```

For the graph, it is possible to change the confidence level.
```{r,Regression-MultipleStandardB}
plotStandardizedRegressionCoefficients(cbind(Predictor1,Predictor2),Criterion,conf.level=.99)
```
