---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{One Correlation Data Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## One Correlation Data Tutorial

### Data Management

#### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Outcome1 <- c(0,0,3,5)
Outcome2 <- c(4,7,4,9)
PairedData <- data.frame(Outcome1,Outcome2)
```

#### Descriptive Statistics

This code will produce raincloud plots for better understanding of the distributions.
```{r,PairedCorrelation-Rainclouds}
plotRainclouds(PairedData)
```

This code obtains the descriptive statistics for the data frame.
```{r}
describeMeans(PairedData)
describeCorrelations(PairedData)
```

This code provides a scatterplot for the bivariate relationship.
```{r,PairedCorrelation-ScatterA}
plotScatter(PairedData)
```

This code provides a scatterplot along with a 95% confidence ellipse for the data.
```{r,PairedCorrelation-ScatterB}
plotScatter(PairedData,ellipse=TRUE)
```

The ellipse can be altered for different confidence levels.
```{r,PairedCorrelation-ScatterC}
plotScatter(PairedData,ellipse=TRUE,conf.level=.99)
```

### Analyses of a Correlation

This section produces analyses of the correlation.

#### Confidence Interval

This code will provide the confidence interval for the correlation.
```{r}
estimateCorrelations(PairedData)
```

This code will produce a graph of the confidence interval for the correlation.
```{r,PairedCorrelation-A}
plotCorrelations(PairedData)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateCorrelations(PairedData,conf.level=.99)
```

Of course, it is possible to change from the default confidence level and to add a comparison line and a region of practical equivalence to the graph.
```{r,PairedCorrelation-B}
plotCorrelations(PairedData,conf.level=.99,line=0,rope=c(-.2,.2))
```

#### Significance Test

This code will produce a table of NHST for the correlation (against a value of zero).
```{r}
testCorrelations(PairedData)
```
