---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{One Sample Summary Statistics Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## One Sample Summary Statistics Tutorial

### Data Management

This code inputs the variable and creates a single summary table.
```{r}
Outcome <- c(N=8,M=4.000,SD=3.117)
OneSampleSummary <- rbind(Outcome)
class(OneSampleSummary) <- "wss"
```

### Analyses of the Mean

This section produces analyses that are equivalent to one-sample analyses for the variable.

#### Confidence Interval

This code will provide a confidence interval for the variable.
```{r}
estimateMeans(OneSampleSummary)
```

This code will produce a graph of the confidence interval for the variable.
```{r,OneSample-Summary-MeansA}
plotMeans(OneSampleSummary)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateMeans(OneSampleSummary,conf.level=.99)
```

For the graph, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence in addition to changing the confidence level.
```{r,OneSample-Summary-MeansB}
plotMeans(OneSampleSummary,conf.level=.99,line=5,rope=c(3,7))
```

#### Significance Test

This code will produce a table of NHST for the variable. In this case, the mean is tested against a value of zero.
```{r}
testMeans(OneSampleSummary)
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
testMeans(OneSampleSummary,mu=5)
```

#### Standardized Effect Size

This code will provide the standardized mean difference for the variable. In this case, the mean is compared to zero to form the effect size.
```{r}
estimateStandardizedMeans(OneSampleSummary)
```

Here too it is possible to alter the width of the confidence interval and to establish a more plausible comparison value for the mean.
```{r}
estimateStandardizedMeans(OneSampleSummary,mu=5,conf.level=.99)
```
