---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "2020-11-20"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Relational Repeated Measures (Within-Subjects) Tutorial with Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Relational Repeated Measures (Within-Subjects) Tutorial with Data

### Data Management

#### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Outcome1 <- c(0,0,3,5)
Outcome2 <- c(4,7,4,9)
Outcome3 <- c(9,6,4,9)
RepeatedData <- data.frame(Outcome1,Outcome2,Outcome3)
```

#### Plot of the Data

```{r,Repeated-Violins}
plotViolins(Outcome1,Outcome2,Outcome3,main="Summaries of the Variables")
plotBoxes(Outcome1,Outcome2,Outcome3,add=TRUE)
plotData(Outcome1,Outcome2,Outcome3,add=TRUE,method="stack",pch=16)
```

#### Descriptive Statistics

This code obtains the descriptive statistics for the data frame.
```{r}
describeMeans(Outcome1,Outcome2,Outcome3)
```

### Analyses of the Omnibus Effect

This section produces analyses that are the traditional way to represent and test overall variable differences.

#### Confidence Intervals

This code will provide a table of confidence intervals for each of the variables.
```{r}
estimateMeans(Outcome1,Outcome2,Outcome3)
```

This code will produce a graph of the confidence intervals for each of the variables.
```{r,RelationalRepeated-Means}
plotMeans(Outcome1,Outcome2,Outcome3)
```

#### Significance Test

This code provides an ANOVA source table for the omnibus effect.
```{r}
describeMeansOmnibus(Outcome1,Outcome2,Outcome3)
testMeansOmnibus(Outcome1,Outcome2,Outcome3)
```

### Analyses of the Pairwise Comparisons

This section provides analyses of all possible pairwise comparisons among the variables.

#### Confidence Intervals

This code will provide a table of descriptive statistics and confidence intervals for each pairwise comparison.

```{r}
estimateMeansPairwise(Outcome1,Outcome2,Outcome3)
```

This code will produce a graph of the confidence intervals for each of the pairwise comparisons.
```{r,RelationalRepeated-Pairwise}
plotMeansPairwise(Outcome1,Outcome2,Outcome3,mu=0)
```

#### Significance Tests

This code will produce a table of NHST for each of the pairwise comparisons. In this case, all the comparisons are tested against a value of zero.
```{r}
testMeansPairwise(Outcome1,Outcome2,Outcome3)
```

### Analyses of the Pairwise Comparisons Using Relational Intervals

This section provides analyses of all possible pairwise comparisons among the variables using relational intervals.

#### Confidence and Relational Intervals

This code will provide a table of confidence and relational intervals for each pairwise comparison.
```{r}
estimateMeansRelational(Outcome1,Outcome2,Outcome3)
```

This code will produce a graph of the confidence and relational intervals for each of the pairwise comparisons.
```{r,RelationalRepeated-RelationalA}
plotMeansRelational(Outcome1,Outcome2,Outcome3)
```

The code defaults to 95% confidence and relational intervals. This can be changed if desired.
```{r}
estimateMeansRelational(Outcome1,Outcome2,Outcome3,conf.level=.99)
```

For the graph, it is possible to change the confidence level.
```{r,RelationalRepeated-RelationalB}
plotMeansRelational(Outcome1,Outcome2,Outcome3,conf.level=.99)
```
