---
subtitle: "Repeated Measures (Within-Subjects) Data Tutorial"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Repeated Measures (Within-Subjects) Data Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Repeated Measures (Within-Subjects) Data Tutorial

This page analyzes a single-factor within-subjects (repeated measures) design using raw data input.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

#### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Outcome1 <- c(0, 0, 3, 5)
Outcome2 <- c(4, 7, 4, 9)
Outcome3 <- c(9, 6, 4, 9)
RepeatedData <- data.frame(Outcome1, Outcome2, Outcome3)
```

#### Descriptive Statistics

This code obtains the descriptive statistics for the data frame.
```{r}
describeMeans(RepeatedData)
```

### Analyses of the Means

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

#### Confidence Intervals

This code will provide a table of confidence intervals for each level of the factor.
```{r}
estimateMeans(RepeatedData)
```

This code will produce a graph of the confidence intervals for each level of the factor.
```{r,Repeated-Data-MeansA}
plotMeans(RepeatedData)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateMeans(RepeatedData, conf.level = .99)
```

For the graph, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence in addition to changing the confidence level.
```{r,Repeated-Data-MeansB}
plotMeans(RepeatedData, conf.level = .99, line = 5, rope = c(3, 7))
```

#### Significance Tests

This code will produce a table of NHST separately for each level of the factor. In this case, all the means are tested against a value of zero.
```{r}
testMeans(RepeatedData)
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
testMeans(RepeatedData, mu = 5)
```

#### Standardized Effect Sizes

This code will produce a table of standardized mean differences separately for each level of the factor. In this case, the mean is compared to zero to form the effect size.
```{r}
estimateStandardizedMeans(RepeatedData)
```

Here too it is possible to alter the width of the confidence intervals and to establish a more plausible comparison value for the mean.
```{r}
estimateStandardizedMeans(RepeatedData, mu = 5, conf.level = .99)
```

### Analyses of a Comparison

This section produces analyses that are equivalent to comparisons of two levels of a factor.

```{r}
ComparisonData <- cbind(Outcome1, Outcome2)
```

#### Confidence Intervals

This code identifies the two levels for comparison and estimates the confidence interval of the difference.
```{r}
estimateMeanDifference(ComparisonData)
```

This code obtains and plots the confidence intervals for the mean difference in the identified comparison.
```{r,Repeated-Data-DifferenceA}
plotMeanDifference(ComparisonData)
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
estimateMeanDifference(ComparisonData, conf.level = .99)
```

Once again, the confidence levels can be changed away from the default and a comparison line to represent a population (or test) value and a region of practical equivalence can be added to the graph..
```{r,Repeated-Data-DifferenceB}
plotMeanDifference(ComparisonData, conf.level = .99, line = 0, rope = c(-2, 2))
```

If you wish, you can get the confidence intervals for the means and the mean difference in one command.
```{r}
estimateMeanComparison(ComparisonData)
```

This code produces a difference plot using the confidence intervals for the means and the mean difference.
```{r,Repeated-Data-ComparisonA}
plotMeanComparison(ComparisonData)
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
estimateMeanComparison(ComparisonData, conf.level = .99)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r,Repeated-Data-ComparisonB}
plotMeanComparison(ComparisonData, conf.level = .99, rope = c(-2, 2))
```

#### Significance Test

This code produces NHST for the identified comparison (using a default test value of zero).
```{r}
testMeanDifference(ComparisonData)
```

If the default value of zero is not plausible, it too can be changed.
```{r}
testMeanDifference(ComparisonData, mu = -2)
```

#### Standardized Effect Size

This code calculates a standardized mean difference for the comparison and its confidence interval.
```{r}
estimateStandardizedMeanDifference(ComparisonData)
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
estimateStandardizedMeanDifference(ComparisonData, conf.level = .99)
```

### Analyses of a Contrast

This section produces analyses that are equivalent to analyses involving multiple levels of a factor.

This code identifies a contrast among the levels.
```{r}
O1vsOthers <- c(-1, .5, .5)
```

#### Confidence Intervals

This code produces a confidence interval for that contrast.
```{r}
estimateMeanContrast(RepeatedData, contrast = O1vsOthers)
```

This code obtains and plots the confidence intervals for the mean difference in the identified contrast.
```{r,Repeated-Data-ContrastA}
plotMeanContrast(RepeatedData, contrast = O1vsOthers)
```

As in all other cases, the default value of the confidence interval can be changed.
```{r}
estimateMeanContrast(RepeatedData, contrast = O1vsOthers, conf.level = .99)
```

The width of the confidence interval for the contrast can be altered and a comparison line to represent a population (or test) value and a region of practical equivalence can be added to the graph.
```{r,Repeated-Data-ContrastB}
plotMeanContrast(RepeatedData, contrast = O1vsOthers, conf.level = .99, line = 0, rope = c(-2, 2))
```

If you wish, you can get the confidence intervals for the mean subsets and the mean contrast in one command.
```{r}
estimateMeanSubsets(RepeatedData, contrast = O1vsOthers)
```

This code produces a difference plot using the confidence intervals for the mean subsets and the mean contrast.
```{r,Repeated-Data-SubsetsA}
plotMeanSubsets(RepeatedData, contrast = O1vsOthers)
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
estimateMeanSubsets(RepeatedData, contrast = O1vsOthers, conf.level = .99)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r,Repeated-Data-SubsetsB}
plotMeanSubsets(RepeatedData, contrast = O1vsOthers, labels = c("Outcome1", "Others"), conf.level = .99, rope = c(-2, 2))
```

#### Significance Test

This code produces a NHST for the identified contrast. It tests the contrast against a value of zero by default.
```{r}
testMeanContrast(RepeatedData, contrast = O1vsOthers)
```

If desired, the contrast can be tested against other values.
```{r}
testMeanContrast(RepeatedData, contrast = O1vsOthers, mu = 4)
```

#### Standardized Effect Size

This code calculates a standardized contrast and its confidence interval.
```{r}
estimateStandardizedMeanContrast(RepeatedData, contrast = O1vsOthers)
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
estimateStandardizedMeanContrast(RepeatedData, contrast = O1vsOthers, conf.level = .99)
```
