---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Set of Correlations Data Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## Set of Correlations Data Tutorial

### Data Management

#### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Outcome1 <- c(0,0,3,5)
Outcome2 <- c(4,7,4,9)
Outcome3 <- c(9,6,4,9)
RepeatedData <- data.frame(Outcome1,Outcome2,Outcome3)
```

#### Descriptive Statistics

This code will produce raincloud plots for better understanding of the distributions.
```{r,RepeatedCorrelation-Rainclouds}
plotRainclouds(RepeatedData)
```

This code obtains the descriptive statistics for the data frame.
```{r}
describeMeans(RepeatedData)
describeCorrelations(RepeatedData)
```

### Analyses of a Correlation

This section produces analyses of a single correlation.

```{r}
ComparisonData <- cbind(Outcome1,Outcome2)
```

#### Confidence Interval

This code will provide the confidence interval for the correlation.
```{r}
estimateCorrelations(ComparisonData)
```

This code will produce a graph of the confidence interval for the correlation.
```{r,RepeatedCorrelation-A}
plotCorrelations(ComparisonData)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateCorrelations(ComparisonData,conf.level=.99)
```

Of course, it is possible to change from the default confidence level in the graph. It is also possible to add a comparison value and a region of practical equivalence.
```{r,RepeatedCorrelation-B}
plotCorrelations(ComparisonData,conf.level=.99,line=0,rope=c(-.2,.2))
```

#### Significance Test

This code will produce a table of NHST for the correlation (against a value of zero).
```{r}
testCorrelations(ComparisonData)
```

### Analyses of Several Correlations

This section analyzes the correlations among multiple variables.

#### Confidence Intervals

This code will provide the confidence intervals for the correlations.
```{r}
estimateCorrelations(RepeatedData)
```

This code will produce a graph of the confidence intervals for the correlations.
```{r,RepeatedCorrelations-A}
plotCorrelations(RepeatedData)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateCorrelations(RepeatedData,conf.level=.99)
```

Of course, it is possible to change from the default confidence level in the graph. It is also possible to add a comparison value and a region of practical equivalence.
```{r,RepeatedCorrelations-B}
plotCorrelations(RepeatedData,conf.level=.99,line=0,rope=c(-.2,.2))
```

#### Significance Tests

This code will produce a table of NHST for the correlations (against a value of zero).
```{r}
testCorrelations(RepeatedData)
```
