---
subtitle: "Single Correlation Data Tutorial"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Single Correlation Data Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7",filename='revised_toc.R')
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Single Correlation Data Tutorial

This page analyzes a single correlation between two variables using raw data input.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile,base_level=3,toc_depth=4)
```

---

### Data Management

#### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Outcome1 <- c(0,0,3,5)
Outcome2 <- c(4,7,4,9)
PairedData <- data.frame(Outcome1,Outcome2)
```

#### Plot of the Data

This code provides a scatterplot for the bivariate relationship.
```{r,SingleCorrelation-Data-ScatterA}
plotScatter(PairedData)
```

This code provides a scatterplot along with a 95% confidence ellipse for the data.
```{r,SingleCorrelation-Data-ScatterB}
plotScatter(PairedData,ellipse=TRUE)
```

The ellipse can be altered for different confidence levels.
```{r,SingleCorrelation-Data-ScatterC}
plotScatter(PairedData,ellipse=TRUE,conf.level=.99)
```

#### Descriptive Statistics

This code obtains the descriptive statistics for the data frame.
```{r}
describeMeans(PairedData)
describeCorrelations(PairedData)
```

### Analyses of a Correlation

This section produces analyses of the correlation.

#### Confidence Interval

This code will provide the confidence interval for the correlation.
```{r}
estimateCorrelations(PairedData)
```

This code will produce a graph of the confidence interval for the correlation.
```{r,SingleCorrelation-Data-IntervalsA}
plotCorrelations(PairedData)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateCorrelations(PairedData,conf.level=.99)
```

Of course, it is possible to change from the default confidence level and to add a comparison line and a region of practical equivalence to the graph.
```{r,SingleCorrelation-Data-IntervalsB}
plotCorrelations(PairedData,conf.level=.99,line=0,rope=c(-.2,.2))
```

#### Significance Test

This code will produce a table of NHST for the correlation (against a value of zero).
```{r}
testCorrelations(PairedData)
```
