---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Analyze One Way Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Analyze One Way Data Application

This page provides basic analyses using one-way (between-subjects) data.

### Data Management

Enter the data.
```{r}
Factor <- c(rep(1,4),rep(2,4),rep(3,4))
Outcome <- c(0,0,3,5,4,7,4,9,9,6,4,9)
Factor <- factor(Factor,levels=c(1,2,3),labels=c("Level1","Level2","Level3"))
OneWayData <- data.frame(Factor,Outcome)
```

### Analyze the Means

Estimate, test, and standardized the means, including altering the confidence level and setting a population value.
```{r}
(Outcome~Factor) |> analyzeMeans()
(Outcome~Factor) |> analyzeMeans(conf.level=.99,mu=5)
```

### Analyze a Mean Difference

Determine and then estimate, test, and standardize a mean difference.
```{r}
Comparison <- factor(Factor,c("Level1","Level2"))
(Outcome~Comparison) |> analyzeMeanDifference()
(Outcome~Comparison) |> analyzeMeanDifference(conf.level=.99)
```

### Analyze a Mean Contrast

Determine and then estimate, test, and standardize a mean contrast.
```{r}
L1vsOthers <- c(-1,.5,.5)
(Outcome~Factor) |> analyzeMeanContrast(contrast=L1vsOthers)
(Outcome~Factor) |> analyzeMeanContrast(contrast=L1vsOthers,conf.level=.99)
```

### Analyze the Omnibus Effect

Obtain a ANOVA source table, test for significance, and estimate the proportion of variance accounted for.
```{r}
(Outcome~Factor) |> analyzeMeansOmnibus()
(Outcome~Factor) |> analyzeMeansOmnibus(conf.level=.99)
```

### Analyze Pairwise Comparisons

Estimate, test, and standardize all pairwise mean comparisons.
```{r}
(Outcome~Factor) |> analyzeMeansPairwise()
(Outcome~Factor) |> analyzeMeansPairwise(conf.level=.99)
```
