---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Analyze Meta Functions Repeated Measures Data Applications}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## Analyze Meta Functions - Repeated Measures Data Applications

### Data Management

Enter the data.
```{r}
Outcome1 <- c(0,0,3,5)
Outcome2 <- c(4,7,4,9)
Outcome3 <- c(9,6,4,9)
RepeatedData <- data.frame(Outcome1,Outcome2,Outcome3)
```

### Analyze the Means

Estimate, test, and standardized the means, including altering the confidence level and setting a population value.
```{r}
analyzeMeans(RepeatedData)
analyzeMeans(RepeatedData,conf.level=.99,mu=5)
```

### Analyze a Mean Difference

Determine and then estimate, test, and standardize a mean difference.
```{r}
analyzeMeanDifference(cbind(Outcome1,Outcome2))
analyzeMeanDifference(cbind(Outcome1,Outcome2),conf.level=.99)
```

### Analyze a Mean Contrast

Determine and then estimate, test, and standardize a mean contrast.
```{r}
O1vsOthers <- c(-1,.5,.5)
analyzeMeanContrast(RepeatedData,contrast=O1vsOthers)
analyzeMeanContrast(RepeatedData,contrast=O1vsOthers,conf.level=.99)
```

### Analyze the Omnibus Effect

Obtain a ANOVA source table, test for significance, and estimate the proportion of variance accounted for.
```{r}
analyzeMeansOmnibus(RepeatedData)
analyzeMeansOmnibus(RepeatedData,conf.level=.99)
```

### Analyze the Pairwise Comparisons

Estimate, test, and standardize all pairwise mean comparisons.
```{r}
analyzeMeansPairwise(RepeatedData)
analyzeMeansPairwise(RepeatedData,conf.level=.99)
```
