---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{By Factorial Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## By Factorial Data Application

This page analyzes simple effects using factorial (between-subjects) data.

### Data Management

Simulate some data.
```{r}
FactorA <- c(rep(1,30),rep(2,30),rep(3,30),rep(1,30),rep(2,30),rep(3,30))
FactorB <- c(rep(1,90),rep(2,90))
FactorA <- factor(FactorA,levels=c(1,2,3),labels=c("A1","A2","A3"))
FactorB <- factor(FactorB,levels=c(1,2),labels=c("B1","B2"))
Outcome <- c(rnorm(30,mean=8,sd=2),rnorm(30,mean=11,sd=4),rnorm(30,mean=12,sd=4),rnorm(30,mean=8,sd=2),rnorm(30,mean=8,sd=3),rnorm(30,mean=7,sd=4))
FactorialData <- data.frame(FactorA,FactorB,Outcome)
```

### Descriptive Statistics

Get descriptive statistics separately for each simple effect.
```{r}
(Outcome~FactorA) |> describeMeansBy(by=FactorB)
```

### Analyses of the Means

Estimate, plot, test, and standardize the means separately for each simple effect.
```{r,By-Factorial-Means}
(Outcome~FactorA) |> estimateMeansBy(by=FactorB)
(Outcome~FactorA) |> plotMeansBy(by=FactorB)
(Outcome~FactorA) |> testMeansBy(by=FactorB)
(Outcome~FactorA) |> estimateStandardizedMeansBy(by=FactorB)
```

### Analyses of a Comparison

Specify a comparison separately for each simple effect.
```{r}
Comparison=factor(FactorB,c("A1","A2"))
```

Analyze the specified comparison separately for each simple effect.
```{r,By-Factorial-Comparison}

(Outcome~FactorA) |> estimateMeanDifferenceBy(by=FactorB)
(Outcome~FactorA) |> plotMeanDifferenceBy(by=FactorB)
(Outcome~FactorA) |> testMeanDifferenceBy(by=FactorB)
(Outcome~FactorA) |> estimateStandardizedMeanDifferenceBy(by=FactorB)
```

### Analyses of a Contrast

Specify a contrast for a factor.
```{r}
A1vsOthers <- c(-1,.5,.5)
```

Analyze the specified contrast separately for each simple effect.
```{r,By-Factorial-Contrast}
(Outcome~FactorA) |> estimateMeanContrastBy(by=FactorB,contrast=A1vsOthers)
(Outcome~FactorA) |> plotMeanContrastBy(by=FactorB,contrast=A1vsOthers)
(Outcome~FactorA) |> testMeanContrastBy(by=FactorB,contrast=A1vsOthers)
(Outcome~FactorA) |> estimateStandardizedMeanContrastBy(by=FactorB,contrast=A1vsOthers)
```
