---
subtitle: "By Mixed Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{By Mixed Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## By Mixed Data Application

This page analyzes simple effects using mixed design (between-subjects and within-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

This code inputs the variable names and creates a viewable data frame.
```{r}
Factor <- c(rep(1, 10), rep(2, 10))
Factor <- factor(Factor, levels = c(1, 2), labels = c("Level1", "Level2"))
Outcome1 <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7, 5, 9, 10, 9, 11, 4, 11, 7, 6, 8)
Outcome2 <- c(7, 13, 11, 10, 13, 8, 11, 14, 12, 11, 7, 8, 7, 11, 10, 7, 8, 4, 8, 10)
Outcome3 <- c(9, 16, 11, 12, 15, 13, 9, 14, 11, 10, 8, 6, 8, 11, 5, 7, 9, 3, 6, 7)
MixedData <- construct(Factor, Outcome1, Outcome2, Outcome3)
```

### Summary Statistics

Get the descriptive statistics separately for each simple effect.
```{r}
construct(Outcome1, Outcome2, Outcome3) |> describeSummaryBy(by = Factor)
```

### Analyses of the Means

Estimate, plot, test, and standardize the means separately for each simple effect.
```{r, By-Mixed-Means}
construct(Outcome1, Outcome2, Outcome3) |> estimateMeansBy(by = Factor)
construct(Outcome1, Outcome2, Outcome3) |> plotMeansBy(by = Factor)
construct(Outcome1, Outcome2, Outcome3) |> testMeansBy(by = Factor)
construct(Outcome1, Outcome2, Outcome3) |> estimateStandardizedMeansBy(by = Factor)
```

### Analyses of a Comparison

Analyze the specified comparison separately for each simple effect.
```{r, By-Mixed-Comparison}
construct(Outcome1, Outcome2) |> estimateMeanDifferenceBy(by = Factor)
construct(Outcome1, Outcome2) |> plotMeanDifferenceBy(by = Factor)
construct(Outcome1, Outcome2) |> testMeanDifferenceBy(by = Factor)
construct(Outcome1, Outcome2) |> estimateStandardizedMeanDifferenceBy(by = Factor)
```

### Analyses of a Contrast

Analyze the specified contrast separately for each simple effect.
```{r, By-Mixed-Contrast}
construct(Outcome1, Outcome2, Outcome3) |> estimateMeanContrastBy(by = Factor, contrast = c(-1, .5, .5))
construct(Outcome1, Outcome2, Outcome3) |> plotMeanContrastBy(by = Factor, contrast = c(-1, .5, .5))
construct(Outcome1, Outcome2, Outcome3) |> testMeanContrastBy(by = Factor, contrast = c(-1, .5, .5))
construct(Outcome1, Outcome2, Outcome3) |> estimateStandardizedMeanContrastBy(by = Factor, contrast = c(-1, .5, .5))
```
