---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Combination OneWay Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Combination OneWay Data Application

This page adds data, plausibility curves, and other information to confidence interval plots using one-way (between-subjects) data.

### Data Management

Simulate some data.
```{r}
Factor <- c(rep(1,50),rep(2,50),rep(3,50))
Factor <- factor(Factor,levels=c(1,2,3),labels=c("Group1","Group2","Group3"))
Group1 <- round(rnorm(50,mean=7,sd=2),0)
Group2 <- round(rnorm(50,mean=11,sd=4),0)
Group3 <- round(rnorm(50,mean=12,sd=4),0)
Outcome <- c(Group1,Group2,Group3)
```

### Analyses of the Means

Estimate and get a simple plot of the confidence intervals.
```{r,Combination-OneWay-ConfidenceA}
(Outcome~Factor) |> estimateMeans()
(Outcome~Factor) |> plotMeans()
```

Get an enhanced plot of data and confidence intervals.
```{r,Combination-OneWay-ConfidenceB}
customTheme <- c("darkred","darkblue","darkgoldenrod")
(Outcome~Factor) |> plotData(main="Data and Confidence Intervals",method="jitter",col=customTheme)
(Outcome~Factor) |> plotMeans(add=TRUE,values=FALSE,line=10,col=customTheme)
```

### Analyses of a Comparison

Create a comparison and get a simple plot of the confidence intervals.
```{r,Combination-OneWay-ComparisonA}
Comparison <- factor(Factor,c("Group1","Group2"))
(Outcome~Comparison) |> estimateMeanComparison()
(Outcome~Comparison) |> plotMeanComparison()
```

Get an enhanced plot of data and confidence intervals with a plausibility curve.
```{r,Combination-OneWay-ComparisonB}
comparisonTheme <- c("darkred","darkblue","black")
(Outcome~Comparison) |> plotMeanComparison(main="Data, Confidence Intervals, and a Plausibility Curve",ylim=c(0,20),values=FALSE,col=comparisonTheme)
(Outcome~Comparison) |> plotPlausible(add=TRUE,type=c("none","none","right"),col=comparisonTheme)
(Outcome~Comparison) |> plotData(add=TRUE,method="jitter",col=comparisonTheme)
```

### Analyses of a Mean Contrast

Create a contrast and get a plot of the mean subsets and the contrast.
```{r,Combination-OneWay-ContrastA}
G1vsOthers <- c(-1,.5,.5)
(Outcome~Factor) |> estimateMeanSubsets(contrast=G1vsOthers,labels=c("Group1","Others"))
(Outcome~Factor) |> plotMeanSubsets(contrast=G1vsOthers,labels=c("Group1","Others"))
```

Create side-by-side enhanced plots of the means and the mean subsets.
```{r,Combination-OneWay-ContrastB}
contrastTheme <- c("darkred","darkblue","darkblue")
par(mfrow=c(1,2),mar=c(1,1,1,0))
(Outcome~Factor) |> plotMeans(col=contrastTheme,ylim=c(0,20),values=FALSE,main="")
(Outcome~Factor) |> plotData(add=TRUE,method="jitter",col=contrastTheme)
(Outcome~Factor) |> plotMeanSubsets(contrast=G1vsOthers,labels=c("Group1","Others"),col=comparisonTheme,ylim=c(0,20),ylab="",values=FALSE,main="")
(Outcome~Factor) |> plotPlausible(contrast=G1vsOthers,add=TRUE,type=c("none","none","right"),col=comparisonTheme)
```
