---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Complex Contrasts Repeated Measures Data Applications}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## Complex Contrasts Repeated Measures Data Applications

### Data Management

Set up for analyses of the raw data
```{r}
Outcome1 <- c(0,0,3,5)
Outcome2 <- c(4,7,4,9)
Outcome3 <- c(9,6,4,9)
RepeatedData <- data.frame(Outcome1,Outcome2,Outcome3)
```

### Analyses of a Complex Mean Contrast

Set two contrasts - One for the Grand Mean and One for Outcome 2
```{r}
c1=c(1/3,1/3,1/3)
c2=c(0,1,0)
```

Estimate and plot the confidence intervals for each contrast and the difference between contrasts
```{r,Repeated-ComplexA}
estimateMeanComplex(RepeatedData,contrast1=c1,contrast2=c2,labels=c("GrandMean","Level2"))
plotMeanComplex(RepeatedData,contrast1=c1,contrast2=c2,labels=c("GrandMean","Level2"))
```

Change confidence Level for the intervals and re-estimate
```{r,Repeated-ComplexB}
estimateMeanComplex(RepeatedData,contrast1=c1,contrast2=c2,labels=c("GrandMean","Level2"),conf.level=.99)
plotMeanComplex(RepeatedData,contrast1=c1,contrast2=c2,labels=c("GrandMean","Level2"),conf.level=.99,rope=c(-2,2))
```
