---
subtitle: "Complex OneWay Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Complex OneWay Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Complex OneWay Data Application

This page analyzes differences between two contrasts using one-way (between-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

Simulate some data.
```{r}
Factor <- c(rep(1, 50), rep(2, 50), rep(3, 50))
Factor <- factor(Factor, levels = c(1, 2, 3), labels = c("Level1", "Level2", "Level3"))
Level1 <- round(rnorm(50, mean = 7, sd = 2), 0)
Level2 <- round(rnorm(50, mean = 11, sd = 4), 0)
Level3 <- round(rnorm(50, mean = 12, sd = 4), 0)
Outcome <- c(Level1, Level2, Level3)
```

### Analyses of a Complex Mean Contrast

Estimate and plot the means for examination.
```{r,Complex-OneWay-Means}
(Outcome ~ Factor) |> estimateMeans()
(Outcome ~ Factor) |> plotMeans()
```

Create a single contrast to compare the first group to the grand mean (which requires some arithmetic). Then esimate and plot the contrast.
```{r,Complex-OneWay-Contrast}
L1vsGrand <- c(.6667, -.3333, -.3333)
(Outcome ~ Factor) |> estimateMeanContrast(contrast = L1vsGrand)
(Outcome ~ Factor) |> plotMeanContrast(contrast = L1vsGrand)
```

### Analysis of a Difference Between Two Contrasts

Rather than setting just one contrast, set two contrasts: one for the Grand Mean and one for Level 1.
```{r}
GrandMean <- c(1/3, 1/3, 1/3)
L1Only <- c(1, 0, 0)
```

Estimate and plot the confidence intervals for each contrast and the difference between contrasts.
```{r,Complex-OneWay-ComplexA}
(Outcome ~ Factor) |> estimateMeanComplex(contrast1 = GrandMean, contrast2 = L1Only, labels = c("GrandMean", "L1Only"))
(Outcome ~ Factor) |> plotMeanComplex(contrast1 = GrandMean, contrast2 = L1Only, labels = c("GrandMean", "L1Only"))
```

Enhance the plot by adding colors and removing value labels.
```{r,Complex-OneWay-ComplexB}
comparisonTheme <- c("darkred", "darkblue", "black")
(Outcome ~ Factor) |> plotMeanComplex(contrast1 = GrandMean, contrast2 = L1Only, labels = c("GrandMean", "L1Only"), values = FALSE, col = comparisonTheme)
```
