---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Complex Repeated Measures Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## Complex Repeated Measures Data Application

### Data Management

Simulate some data.
```{r}
Outcome1 <- round(rnorm(50,mean=7,sd=2),0)
Outcome2 <- round(rnorm(50,mean=11,sd=4),0)
Outcome3 <- round(rnorm(50,mean=12,sd=4),0)
RepeatedData <- data.frame(Outcome1,Outcome2,Outcome3)
```

### Analyses of a Complex Mean Contrast

Estimate and plot the means for examination.
```{r,Complex-Repeated-Means}
(RepeatedData) |> estimateMeans()
(RepeatedData) |> plotMeans()
```

Create a single contrast to compare the first variable to the grand mean (which requires some arithmetic). Then esimate and plot the contrast.
```{r,Complex-Repeated-Contrast}
O1vsGrand <- c(.6667,-.3333,-.3333)
(RepeatedData) |> estimateMeanContrast(contrast=O1vsGrand)
(RepeatedData) |> plotMeanContrast(contrast=O1vsGrand)
```

### Analysis of a Difference Between Two Contrasts

Rather than setting just one contrast, set two contrasts: one for the Grand Mean and one for Level 1.
```{r}
GrandMean <- c(1/3,1/3,1/3)
O1Only <- c(1,0,0)
```

Estimate and plot the confidence intervals for each contrast and the difference between contrasts.
```{r,Complex-Repeated-ComplexA}
(RepeatedData) |> estimateMeanComplex(contrast1=GrandMean,contrast2=O1Only,labels=c("GrandMean","O1Only"))
(RepeatedData) |> plotMeanComplex(contrast1=GrandMean,contrast2=O1Only,labels=c("GrandMean","O1Only"))
```

Enhance the plot by adding colors and removing value labels.
```{r,Complex-Repeated-ComplexB}
comparisonTheme <- c("darkred","darkblue","black")
(RepeatedData) |> plotMeanComplex(contrast1=GrandMean,contrast2=O1Only,labels=c("GrandMean","O1Only"),values=FALSE,col=comparisonTheme)
```
