---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Complex OneWay Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## Complex OneWay Data Application

### Data Management

Simulate some data.
```{r}
Factor <- c(rep(1,50),rep(2,50),rep(3,50))
Factor <- factor(Factor,levels=c(1,2,3),labels=c("Group1","Group2","Group3"))
Group1 <- round(rnorm(50,mean=7,sd=2),0)
Group2 <- round(rnorm(50,mean=11,sd=4),0)
Group3 <- round(rnorm(50,mean=12,sd=4),0)
Outcome <- c(Group1,Group2,Group3)
```

### Analyses of a Complex Mean Contrast

Estimate and plot the means for examination.
```{r,Complex-OneWay-Means}
(Outcome~Factor) |> estimateMeans()
(Outcome~Factor) |> plotMeans()
```

Create a single contrast to compare the first group to the grand mean (which requires some arithmetic). Then esimate and plot the contrast.
```{r,Complex-OneWay-Contrast}
L1vsGrand <- c(.6667,-.3333,-.3333)
(Outcome~Factor) |> estimateMeanContrast(contrast=L1vsGrand)
(Outcome~Factor) |> plotMeanContrast(contrast=L1vsGrand)
```

### Analysis of a Difference Between Two Contrasts

Rather than setting just one contrast, set two contrasts: one for the Grand Mean and one for Level 1.
```{r}
GrandMean <- c(1/3,1/3,1/3)
Level1 <- c(1,0,0)
```

Estimate and plot the confidence intervals for each contrast and the difference between contrasts.
```{r,Complex-OneWay-ComplexA}
(Outcome~Factor) |> estimateMeanComplex(contrast1=GrandMean,contrast2=Level1,labels=c("GrandMean","Level1"))
(Outcome~Factor) |> plotMeanComplex(contrast1=GrandMean,contrast2=Level1,labels=c("GrandMean","Level1"))
```

Enhance the plot by adding colors and removing value labels.
```{r,Complex-OneWay-ComplexB}
comparisonTheme <- c("darkred","darkblue","black")
(Outcome~Factor) |> estimateMeanComplex(contrast1=GrandMean,contrast2=Level1,labels=c("GrandMean","Level1"))
(Outcome~Factor) |> plotMeanComplex(contrast1=GrandMean,contrast2=Level1,labels=c("GrandMean","Level1"),values=FALSE,col=comparisonTheme)
```
