---
subtitle: "Complex Repeated Measures Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Complex Repeated Measures Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Complex Repeated Measures Data Application

This page analyzes differences between two contrasts on the same measures using repeated-measures (within-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

Simulate some data.
```{r}
Outcome1 <- round(rnorm(50, mean = 7, sd = 2), 0)
Outcome2 <- round(rnorm(50, mean = 11, sd = 4), 0)
Outcome3 <- round(rnorm(50, mean = 12, sd = 4), 0)
RepeatedData <- data.frame(Outcome1, Outcome2, Outcome3)
```

### Analyses of a Complex Mean Contrast

Estimate and plot the means for examination.
```{r,Complex-Repeated-Means}
(RepeatedData) |> estimateMeans()
(RepeatedData) |> plotMeans()
```

Create a single contrast to compare the first variable to the grand mean (which requires some arithmetic). Then esimate and plot the contrast.
```{r,Complex-Repeated-Contrast}
O1vsGrand <- c(.6667, -.3333, -.3333)
(RepeatedData) |> estimateMeanContrast(contrast = O1vsGrand)
(RepeatedData) |> plotMeanContrast(contrast = O1vsGrand)
```

### Analysis of a Difference Between Two Contrasts

Rather than setting just one contrast, set two contrasts: one for the Grand Mean and one for Level 1.
```{r}
GrandMean <- c(1/3, 1/3, 1/3)
O1Only <- c(1, 0, 0)
```

Estimate and plot the confidence intervals for each contrast and the difference between contrasts.
```{r,Complex-Repeated-ComplexA}
(RepeatedData) |> estimateMeanComplex(contrast1 = GrandMean, contrast2 = O1Only, labels = c("GrandMean", "O1Only"))
(RepeatedData) |> plotMeanComplex(contrast1 = GrandMean, contrast2 = O1Only, labels = c("GrandMean", "O1Only"))
```

Enhance the plot by adding colors and removing value labels.
```{r,Complex-Repeated-ComplexB}
comparisonTheme <- c("darkred", "darkblue", "black")
(RepeatedData) |> plotMeanComplex(contrast1 = GrandMean, contrast2 = O1Only, labels = c("GrandMean", "O1Only"), values = FALSE, col = comparisonTheme)
```
