---
subtitle: "Contrasts OneWay Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Contrasts OneWay Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Contrasts OneWay Data Application

This page adds data, plausibility curves, and other information to confidence interval plots of contrasts using one-way (between-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

Simulate some data.
```{r}
Factor <- c(rep(1, 50), rep(2, 50), rep(3, 50))
Factor <- factor(Factor, levels = c(1, 2, 3), labels = c("Group1", "Group2", "Group3"))
Group1 <- round(rnorm(50, mean = 7, sd = 2), 0)
Group2 <- round(rnorm(50, mean = 11, sd = 4), 0)
Group3 <- round(rnorm(50, mean = 12, sd = 4), 0)
Outcome <- c(Group1, Group2, Group3)
```

### Analyses of the Means

Estimate and get a simple plot of the confidence intervals.
```{r,Contrasts-OneWay-ConfidenceA}
(Outcome ~ Factor) |> estimateMeans()
(Outcome ~ Factor) |> plotMeans()
```

Get an enhanced plot of data and confidence intervals.
```{r,Contrasts-OneWay-ConfidenceB}
customTheme <- c("darkred", "darkblue", "darkgoldenrod")
(Outcome ~ Factor) |> plotData(main = "Data and Confidence Intervals", method = "jitter", col = customTheme)
(Outcome ~ Factor) |> plotMeans(add = TRUE, values = FALSE, line = 10, col = customTheme)
```

### Analyses of a Comparison

Create a comparison and get a simple plot of the confidence intervals.
```{r,Contrasts-OneWay-ComparisonA}
Comparison <- factor(Factor, c("Group1", "Group2"))
(Outcome ~ Comparison) |> estimateMeanComparison()
(Outcome ~ Comparison) |> plotMeanComparison()
```

Get an enhanced plot of data and confidence intervals with a plausibility curve.
```{r,Contrasts-OneWay-ComparisonB}
comparisonTheme <- c("darkred", "darkblue", "black")
(Outcome ~ Comparison) |> plotMeanComparison(main = "Data, Confidence Intervals, and a Plausibility Curve", ylim = c(0, 20), values = FALSE, col = comparisonTheme)
(Outcome ~ Comparison) |> plotPlausible(add = TRUE, type = c("none", "none", "right"), col = comparisonTheme)
(Outcome ~ Comparison) |> plotData(add = TRUE, method = "jitter", col = comparisonTheme)
```

### Analyses of a Mean Contrast

Create a contrast and get a plot of the mean subsets and the contrast.
```{r,Contrasts-OneWay-ContrastA}
G1vsOthers <- c(-1, .5, .5)
(Outcome ~ Factor) |> estimateMeanSubsets(contrast = G1vsOthers, labels = c("Group1", "Others"))
(Outcome ~ Factor) |> plotMeanSubsets(contrast = G1vsOthers, labels = c("Group1", "Others"))
```

Create side-by-side enhanced plots of the means and the mean subsets.
```{r,Contrasts-OneWay-ContrastB}
contrastTheme <- c("darkred", "darkblue", "darkblue")
par(mfrow = c(1, 2))
(Outcome ~ Factor) |> plotMeans(col = contrastTheme, ylim = c(0, 20), values = FALSE, main = "")
(Outcome ~ Factor) |> plotData(add = TRUE, method = "jitter", col = contrastTheme)
(Outcome ~ Factor) |> plotMeanSubsets(contrast = G1vsOthers, labels = c("Group1", "Others"), col = comparisonTheme, ylim = c(0, 20), ylab = "", values = FALSE, main = "")
(Outcome ~ Factor) |> plotPlausible(contrast = G1vsOthers, add = TRUE, type = c("none", "none", "right"), col = comparisonTheme)
par(mfrow = c(1, 1))
```
