---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Contrasts Repeated Measures Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## Contrasts Repeated Measures Data Application

### Data Management

Simulate some data.
```{r}
Outcome1 <- round(rnorm(50,mean=7,sd=2),0)
Outcome2 <- round(rnorm(50,mean=11,sd=4),0)
Outcome3 <- round(rnorm(50,mean=12,sd=4),0)
RepeatedData <- data.frame(Outcome1,Outcome2,Outcome3)
```

### Analyses of the Means

Get a simple plot of the confidence intervals.
```{r,Repeated-ConfidenceA}
(RepeatedData) |> estimateMeans()
(RepeatedData) |> plotMeans()
```

Get an enhanced plot of data and confidence intervals.
```{r,Repeated-ConfidenceB}
colorTheme <- c("darkred","darkblue","darkgoldenrod")
(RepeatedData) |> plotData(main="Data and Confidence Intervals",method="jitter",col=colorTheme)
(RepeatedData) |> plotMeans(add=TRUE,values=FALSE,line=10,col=colorTheme)
```

### Analyses of a Comparison

Create a comparison and get a simple plot of the confidence intervals.
```{r,Repeated-ConfidenceC}
ComparisonData <- data.frame(Outcome1,Outcome2)
(ComparisonData) |> estimateMeanComparison()
(ComparisonData) |> plotMeanComparison()
```

Get an enhanced plot of data and confidence intervals with a plausibility curve.
```{r,Repeated-ConfidenceD}
comparisonTheme <- c("darkred","darkblue","black")
(ComparisonData) |> plotMeanComparison(main="Data, Confidence Intervals, and a Plausibility Curve",ylim=c(0,20),values=FALSE,col=comparisonTheme)
(ComparisonData) |> plotPlausible(add=TRUE,type=c("none","none","right"),col=comparisonTheme)
(ComparisonData) |> plotData(add=TRUE,method="jitter",col=comparisonTheme)
```

### Analyses of a Mean Contrast

Create a contrast and get a plot of the mean subsets and the contrast.
```{r,Contrasts-OneWay-ContrastA}
L1vsOthers <- c(-1,.5,.5)
(RepeatedData) |> estimateMeanSubsets(contrast=L1vsOthers,labels=c("Level1","Others"))
(RepeatedData) |> plotMeanSubsets(contrast=L1vsOthers,labels=c("Level1","Others"))
```

Create side-by-side plots of the means and the mean subsets and enhance the plots by adding colors.
```{r,Contrasts-OneWay-ContrastB}
contrastTheme <- c("darkred","darkblue","darkblue")
par(mfrow=c(1,2))
(RepeatedData) |> plotMeans(col=contrastTheme,ylim=c(0,20),values=FALSE,main="")
(RepeatedData) |> plotData(add=TRUE,col=contrastTheme)
(RepeatedData) |> plotMeanSubsets(contrast=L1vsOthers,labels=c("Level1","Others"),col=comparisonTheme,ylim=c(0,20),ylab="",values=FALSE,main="")
(RepeatedData) |> plotPlausible(contrast=L1vsOthers,add=TRUE,type=c("none","none","right"),col=comparisonTheme)
par(mfrow=c(1,1))
```
