---
subtitle: "Contrasts Repeated Measures Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Contrasts Repeated Measures Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7",filename='revised_toc.R')
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Contrasts Repeated Measures Data Application

This page adds data, plausibility curves, and other information to confidence interval plots of contrasts using repeated-measures (within-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile,base_level=3,toc_depth=4)
```

---

### Data Management

Simulate some data.
```{r}
Outcome1 <- round(rnorm(50,mean=7,sd=2),0)
Outcome2 <- round(rnorm(50,mean=11,sd=4),0)
Outcome3 <- round(rnorm(50,mean=12,sd=4),0)
RepeatedData <- data.frame(Outcome1,Outcome2,Outcome3)
```

### Analyses of the Means

Get a simple plot of the confidence intervals.
```{r,Contrasts-Repeated-ConfidenceA}
(RepeatedData) |> estimateMeans()
(RepeatedData) |> plotMeans()
```

Get an enhanced plot of data and confidence intervals.
```{r,Contrasts-Repeated-ConfidenceB}
customTheme <- c("darkred","darkblue","darkgoldenrod")
(RepeatedData) |> plotData(main="Data and Confidence Intervals",method="jitter",col=customTheme)
(RepeatedData) |> plotMeans(add=TRUE,values=FALSE,line=10,col=customTheme)
```

### Analyses of a Comparison

Create a comparison and get a simple plot of the confidence intervals.
```{r,Contrasts-Repeated-ComparisonA}
ComparisonData <- data.frame(Outcome1,Outcome2)
(ComparisonData) |> estimateMeanComparison()
(ComparisonData) |> plotMeanComparison()
```

Get an enhanced plot of data and confidence intervals with a plausibility curve.
```{r,Contrasts-Repeated-ComparisonB}
comparisonTheme <- c("darkred","darkblue","black")
(ComparisonData) |> plotMeanComparison(main="Data, Confidence Intervals, and a Plausibility Curve",ylim=c(0,20),values=FALSE,col=comparisonTheme)
(ComparisonData) |> plotPlausible(add=TRUE,type=c("none","none","right"),col=comparisonTheme)
(ComparisonData) |> plotData(add=TRUE,method="jitter",col=comparisonTheme)
```

### Analyses of a Mean Contrast

Create a contrast and get a plot of the mean subsets and the contrast.
```{r,Contrasts-Repeated-ContrastA}
O1vsOthers <- c(-1,.5,.5)
(RepeatedData) |> estimateMeanSubsets(contrast=O1vsOthers,labels=c("Outcome1","Others"))
(RepeatedData) |> plotMeanSubsets(contrast=O1vsOthers,labels=c("Outcome1","Others"))
```

Create side-by-side enhanced plots of the means and the mean subsets.
```{r,Contrasts-Repeated-ContrastB}
contrastTheme <- c("darkred","darkblue","darkblue")
par(mfrow=c(1,2))
(RepeatedData) |> plotMeans(col=contrastTheme,ylim=c(0,20),values=FALSE,main="")
(RepeatedData) |> plotData(add=TRUE,method="jitter",col=contrastTheme)
(RepeatedData) |> plotMeanSubsets(contrast=O1vsOthers,labels=c("Outcome1","Others"),col=comparisonTheme,ylim=c(0,20),ylab="",values=FALSE,main="")
(RepeatedData) |> plotPlausible(contrast=O1vsOthers,add=TRUE,type=c("none","none","right"),col=comparisonTheme)
par(mfrow=c(1,1))
```
