---
subtitle: "Effects Mixed Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Effects Mixed Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7",filename='revised_toc.R')
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Effects Mixed Data Application

This page implements a exposition pipe operator to analyze simple effects using mixed design (between-subjects and within-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile,base_level=3,toc_depth=4)
```

---

### Data Management

Simulate some data.
```{r}
Factor <- c(rep(1,30),rep(2,30))
Outcome1 <- c(round(rnorm(30,mean=8,sd=2),0),round(rnorm(30,mean=8,sd=2),0))
Outcome2 <- c(round(rnorm(30,mean=11,sd=4),0),round(rnorm(30,mean=8,sd=3),0))
Outcome3 <- c(round(rnorm(30,mean=12,sd=4),0),round(rnorm(30,mean=7,sd=4),0))
Factor <- factor(Factor,levels=c(1,2),labels=c("Level1","Level2"))
MixedData <- data.frame(Factor,Outcome1,Outcome2,Outcome3)
```
Subset the data for each simple effect.
```{r}
MixedB1 <- subset(MixedData,Factor=="Level1")
MixedB2 <- subset(MixedData,Factor=="Level2")
```

### Descriptive Statistics

Get the descriptive statistics separately for each simple effect.
```{r}
(MixedB1) %$>% cbind(Outcome1,Outcome2,Outcome3) |> describeMeans()
(MixedB2) %$>% cbind(Outcome1,Outcome2,Outcome3) |> describeMeans()
```

### Analyses of the Means

Use a similar process to obtain the tables of confidence interval estimates.
```{r,Effects-Mixed-Means}
(MixedB1) %$>% cbind(Outcome1,Outcome2,Outcome3) |> estimateMeans()
(MixedB2) %$>% cbind(Outcome1,Outcome2,Outcome3) |> estimateMeans()
(MixedB1) %$>% cbind(Outcome1,Outcome2,Outcome3) |> plotMeans()
(MixedB2) %$>% cbind(Outcome1,Outcome2,Outcome3) |> plotMeans()
(MixedB1) %$>% cbind(Outcome1,Outcome2,Outcome3) |> testMeansOmnibus()
(MixedB2) %$>% cbind(Outcome1,Outcome2,Outcome3) |> testMeansOmnibus()
(MixedB1) %$>% cbind(Outcome1,Outcome2,Outcome3) |> estimateStandardizedMeans()
(MixedB2) %$>% cbind(Outcome1,Outcome2,Outcome3) |> estimateStandardizedMeans()
```

### Analyses of a Comparison

Analyze the specified comparison separately for each simple effect.
```{r,Effects-Mixed-Comparison}
(MixedB1) %$>% cbind(Outcome1,Outcome2) |> estimateMeanDifference()
(MixedB2) %$>% cbind(Outcome1,Outcome2) |> estimateMeanDifference()
(MixedB1) %$>% cbind(Outcome1,Outcome2) |> plotMeanDifference()
(MixedB2) %$>% cbind(Outcome1,Outcome2) |> plotMeanDifference()
(MixedB1) %$>% cbind(Outcome1,Outcome2) |> testMeanDifference()
(MixedB2) %$>% cbind(Outcome1,Outcome2) |> testMeanDifference()
(MixedB1) %$>% cbind(Outcome1,Outcome2) |> estimateStandardizedMeanDifference()
(MixedB2) %$>% cbind(Outcome1,Outcome2) |> estimateStandardizedMeanDifference()
```

### Analyses of a Contrast

Specify a contrast for a factor.
```{r}
O1vsOthers <- c(-1,.5,.5)
```

Analyze the specified contrast separately for each simple effect.
```{r,Effects-Mixed-Contrast}
(MixedB1) %$>% cbind(Outcome1,Outcome2,Outcome3) |> estimateMeanContrast(contrast=O1vsOthers)
(MixedB2) %$>% cbind(Outcome1,Outcome2,Outcome3) |> estimateMeanContrast(contrast=O1vsOthers)
(MixedB1) %$>% cbind(Outcome1,Outcome2,Outcome3) |> plotMeanContrast(contrast=O1vsOthers)
(MixedB2) %$>% cbind(Outcome1,Outcome2,Outcome3) |> plotMeanContrast(contrast=O1vsOthers)
(MixedB1) %$>% cbind(Outcome1,Outcome2,Outcome3) |> testMeanContrast(contrast=O1vsOthers)
(MixedB2) %$>% cbind(Outcome1,Outcome2,Outcome3) |> testMeanContrast(contrast=O1vsOthers)
(MixedB1) %$>% cbind(Outcome1,Outcome2,Outcome3) |> estimateStandardizedMeanContrast(contrast=O1vsOthers)
(MixedB2) %$>% cbind(Outcome1,Outcome2,Outcome3) |> estimateStandardizedMeanContrast(contrast=O1vsOthers)
```
