---
subtitle: "Effects Factorial Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Effects Factorial Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7",filename='revised_toc.R')
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Effects Factorial Data Application

This page implements a exposition pipe operator to analyze simple effects using factorial (between-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile,base_level=3,toc_depth=4)
```

---

### Data Management

Simulate some data.
```{r}
FactorA <- c(rep(1,30),rep(2,30),rep(3,30),rep(1,30),rep(2,30),rep(3,30))
FactorB <- c(rep(1,90),rep(2,90))
FactorA <- factor(FactorA,levels=c(1,2,3),labels=c("A1","A2","A3"))
FactorB <- factor(FactorB,levels=c(1,2),labels=c("B1","B2"))
Outcome <- c(rnorm(30,mean=8,sd=2),rnorm(30,mean=11,sd=4),rnorm(30,mean=12,sd=4),rnorm(30,mean=8,sd=2),rnorm(30,mean=8,sd=3),rnorm(30,mean=7,sd=4))
FactorialData <- data.frame(FactorA,FactorB,Outcome)
```
Subset the data for each simple effect.
```{r}
FactorialB1 <- subset(FactorialData,FactorB=="B1")
FactorialB2 <- subset(FactorialData,FactorB=="B2")
```

### Descriptive Statistics

Get descriptive statistics separately for each simple effect.
```{r}
(FactorialB1) %$>% (Outcome~FactorA) |> describeMeans()
(FactorialB2) %$>% (Outcome~FactorA) |> describeMeans()
```

### Analyses of the Means

Estimate, plot, test, and standardize the means separately for each simple effect.
```{r,Effects-Factorial-Means}
(FactorialB1) %$>% (Outcome~FactorA) |> estimateMeans()
(FactorialB2) %$>% (Outcome~FactorA) |> estimateMeans()
(FactorialB1) %$>% (Outcome~FactorA) |> plotMeans()
(FactorialB2) %$>% (Outcome~FactorA) |> plotMeans()
(FactorialB1) %$>% (Outcome~FactorA) |> testMeansOmnibus()
(FactorialB2) %$>% (Outcome~FactorA) |> testMeansOmnibus()
(FactorialB1) %$>% (Outcome~FactorA) |> estimateStandardizedMeans()
(FactorialB2) %$>% (Outcome~FactorA) |> estimateStandardizedMeans()
```

### Analyses of a Comparison

Specify a comparison separately for each simple effect.
```{r}
ComparisonB1 <- (FactorialB1) %$>% factor(FactorA,c("A1","A2"))
ComparisonB2 <- (FactorialB2) %$>% factor(FactorA,c("A1","A2"))
```

Estimate, plot, test, and standardize the comparison separately for each simple effect.
```{r,Effects-Factorial-Comparison}
(FactorialB1) %$>% (Outcome~ComparisonB1) |> estimateMeanDifference()
(FactorialB2) %$>% (Outcome~ComparisonB2) |> estimateMeanDifference()
(FactorialB1) %$>% (Outcome~ComparisonB1) |> plotMeanDifference()
(FactorialB2) %$>% (Outcome~ComparisonB2) |> plotMeanDifference()
(FactorialB1) %$>% (Outcome~ComparisonB1) |> testMeanDifference()
(FactorialB2) %$>% (Outcome~ComparisonB2) |> testMeanDifference()
(FactorialB1) %$>% (Outcome~ComparisonB1) |> estimateStandardizedMeanDifference()
(FactorialB2) %$>% (Outcome~ComparisonB2) |> estimateStandardizedMeanDifference()
```

### Analyses of a Contrast

Specify a contrast for a factor.
```{r}
A1vsOthers <- c(-1,.5,.5)
```

Estimate, plot, test, and standardize the contrast separately for each simple effect.
```{r,Effects-Factorial-Contrast}
(FactorialB1) %$>% (Outcome~FactorA) |> estimateMeanContrast(contrast=A1vsOthers)
(FactorialB2) %$>% (Outcome~FactorA) |> estimateMeanContrast(contrast=A1vsOthers)
(FactorialB1) %$>% (Outcome~FactorA) |> plotMeanContrast(contrast=A1vsOthers)
(FactorialB2) %$>% (Outcome~FactorA) |> plotMeanContrast(contrast=A1vsOthers)
(FactorialB1) %$>% (Outcome~FactorA) |> testMeanContrast(contrast=A1vsOthers)
(FactorialB2) %$>% (Outcome~FactorA) |> testMeanContrast(contrast=A1vsOthers)
(FactorialB1) %$>% (Outcome~FactorA) |> estimateStandardizedMeanContrast(contrast=A1vsOthers)
(FactorialB2) %$>% (Outcome~FactorA) |> estimateStandardizedMeanContrast(contrast=A1vsOthers)
```
