---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Enhanced Plots Repeated Measures Data Applications}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## Enhanced Plots Repeated Measures Data Applications

### Data Management

Enter the data.
```{r}
Outcome1 <- rnorm(50,mean=7,sd=2.5)
Outcome2 <- rnorm(50,mean=11,sd=2.5)
Outcome3 <- rnorm(50,mean=12,sd=2.5)
RepeatedData <- data.frame(Outcome1,Outcome2,Outcome3)
```

### Analyses of the Means

Create a color theme for the plots.
```{r}
colorTheme <- c("darkred","darkblue","darkgoldenrod")
```

#### Diamond Plots

Get a simple diamond plots of the confidence intervals.
```{r,Repeated-DiamondA}
RepeatedData |> plotDiamonds()
```

Get an enhanced plot combining data and diamond plots.
```{r,Repeated-DiamondB}
RepeatedData |> plotData(main="Data and Diamond Plots",offset=0,method="jitter",col=colorTheme)
RepeatedData |> plotDiamonds(add=TRUE,line=10,rope=c(8,12),col=colorTheme)
```

#### Confidence Interval Plots

Get a simple plot of the confidence intervals.
```{r,Repeated-ConfidenceA}
RepeatedData |> plotIntervals()
```

Get an enhanced plot of data and confidence intervals with plausibility curves.
```{r,Repeated-ConfidenceB}
RepeatedData |> plotData(main="Data and Confidence Intervals with Plausibility Curves",offset=-.15,method="jitter",col=colorTheme)
RepeatedData |> plotIntervals(add=TRUE,values=FALSE,line=10,rope=c(8,12),col=colorTheme)
RepeatedData |> plotPlausible(add=TRUE,col=colorTheme)
```

### Analyses of a Comparison

Create a comparison and its color theme.
```{r}
ComparisonData <- data.frame(Outcome1,Outcome2)
comparisonTheme <- c("darkred","darkblue","black")
```

#### Diamond Plots

Get a simple diamond plots of the confidence intervals.
```{r,Repeated-DiamondC}
ComparisonData |> plotDiamonds(conf.level=.99)
```

Get an enhanced plot combining data and diamond plots.
```{r,Repeated-DiamondD}
ComparisonData |> plotDiamonds(main="Data and Diamond Plots",conf.level=.99,ylim=c(-5,25),rope=c(-2,2),col=comparisonTheme)
ComparisonData |> plotData(add=TRUE,offset=0,method="jitter",col=comparisonTheme)
```

#### Confidence Interval Plots

Get a simple plot of the confidence intervals.
```{r,Repeated-ConfidenceC}
ComparisonData |> plotIntervals(conf.level=.99)
```

Get an enhanced plot of data and confidence intervals with plausibility curves.
```{r,Repeated-ConfidenceD}
ComparisonData |> plotIntervals(main="Data and Confidence Intervals with Plausibility Curves",conf.level=.99,ylim=c(-5,25),values=FALSE,rope=c(-2,2),col=comparisonTheme)
ComparisonData |> plotPlausible(add=TRUE,conf.level=.99,type=c("none","none","right"),col=comparisonTheme)
ComparisonData |> plotData(add=TRUE,method="jitter",col=comparisonTheme)
```
