---
subtitle: "Exploratory OneWay Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Exploratory OneWay Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Exploratory OneWay Data Application

This page provides violin plots, beanplots, and raincloud plots using one-way (between-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

Simulate some data with various distributional shapes.
```{r}
Factor <- c(rep(1, 100), rep(2, 100), rep(3, 100))
Factor <- factor(Factor, levels = c(1, 2, 3), labels = c("Level1", "Level2", "Level3"))
Level1 <- round(rnorm(100, 10, 2), 0)
Level2 <- c(round(rnorm(50, 7, 1), 0), round(rnorm(50, 13, 1), 0))
Level3 <- c(round(rnorm(25, 7, 1), 0), round(rnorm(75, 11, 1), 0))
Outcome <- c(Level1, Level2, Level3)
```

### Violin Plots

Build violin plots using multiple basic plot calls.
```{r,Exploratory-OneWay-ViolinsA}
(Outcome ~ Factor) |> plotBoxes(values = FALSE, main = "Violin Plots")
(Outcome ~ Factor) |> plotDensity(add = TRUE, offset = 0, type = "full")
```

Obtain violin plots using one call (and enhance the plot).
```{r,Exploratory-OneWay-ViolinsB}
(Outcome ~ Factor) |> plotViolins(col = c("darkred", "darkblue", "darkgoldenrod"))
```

### Bean Plots

Build bean plots using multiple basic plot calls.
```{r,Exploratory-OneWay-BeansA}
(Outcome ~ Factor) |> plotDensity(type = "full", offset = 0, main = "Bean Plots")
(Outcome ~ Factor) |> plotData(add = TRUE, offset = 0, pch = 95, method = "overplot")
```

Obtain bean plots using one call (and enhance the plot).
```{r,Exploratory-OneWay-BeansB}
(Outcome ~ Factor) |> plotBeans(col = c("darkred", "darkblue", "darkgoldenrod"))
```

### Raincloud Plots

Build raincloud plots using multiple basic plot calls.
```{r,Exploratory-OneWay-RaincloudsA}
(Outcome ~ Factor) |> plotBoxes(values = FALSE, main = "Raincloud Plots")
(Outcome ~ Factor) |> plotDensity(add = TRUE, offset = .1)
(Outcome ~ Factor) |> plotData(add = TRUE, method = "jitter", offset = -.15)
```

Obtain raincloud plots using one call (and enhance the plot).
```{r,Exploratory-OneWay-RaincloudsB}
(Outcome ~ Factor) |> plotRainclouds(col = c("darkred", "darkblue", "darkgoldenrod"))
```
