---
subtitle: "Exploratory Repeated Measures Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Exploratory Repeated Measures Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Exploratory Analyses Repeated Measures Data Application

This page utilize advnaced methods to build plots that combine various elements using repeated measures (within-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

This code inputs the variable names and creates a viewable data frame.
```{r}
Outcome1 <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7)
Outcome2 <- c(7, 13, 11, 10, 13, 8, 11, 14, 12, 11)
Outcome3 <- c(9, 16, 11, 12, 15, 13, 9, 14, 11, 10)
RepeatedData <- construct(Outcome1, Outcome2, Outcome3)
```

### Building Layers

The typical way to build a plot is to use sepearate calls for each plotting elements (e.g., data, boxplots) and using the "add" parameter to put them on the same plot.
```{r, Exploratory-Repeated-Traditional}
(RepeatedData) |> plotData()
(RepeatedData) |> plotBoxes(add = TRUE)
```

This can be simplified by using an "add" version of the function call instead of using the longer "add" parameter for the function call.
```{r, Exploratory-Repeated-Add}
(RepeatedData) |> plotData()
(RepeatedData) |> addBoxes()
```

Rather than separate lines for function calls, all plotting elements have passthrough capabilities that allow the them to be placed on the same line.
```{r, Exploratory-Repeated-Passthrough}
(RepeatedData) |>  plotData() |>  addBoxes()
```

### Common Layered Plots

Obtain violin plots using one call (and enhance the plot).
```{r, Exploratory-Repeated-Violins}
(RepeatedData) |> plotViolins(col = c("darkred", "darkblue", "darkgoldenrod"))
```

Obtain bean plots using one call (and enhance the plot).
```{r, Exploratory-Repeated-Beans}
(RepeatedData) |> plotBeans(col = c("darkred", "darkblue", "darkgoldenrod"))
```

Obtain raincloud plots using one call (and enhance the plot).
```{r, Exploratory-Repeated-Rainclouds}
(RepeatedData) |> plotRainclouds(col = c("darkred", "darkblue", "darkgoldenrod"))
```
