---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Exploratory Repeated Measures Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## Exploratory Analyses Repeated Measures Data Application

### Data Management

Simulate some data with various distributional shapes.
```{r}
Outcome1 <- round(rnorm(100,10,2),0)
Outcome2 <- c(round(rnorm(50,7,1),0),round(rnorm(50,13,1),0))
Outcome3 <- c(round(rnorm(25,7,1),0),round(rnorm(75,11,1),0))
RepeatedData <- data.frame(Outcome1,Outcome2,Outcome3)
```

### Violin Plots

Build violin plots using multiple basic plot calls.
```{r,Exploratory-Repeated-ViolinsA}
(RepeatedData) |> plotBoxes(values=FALSE,main="Violin Plots")
(RepeatedData) |> plotDensity(add=TRUE,offset=0,type="full")
```

Obtain violin plots using one call (and enhance the plot).
```{r,Exploratory-Repeated-ViolinsB}
(RepeatedData) |> plotViolins(col=c("darkred","darkblue","darkgoldenrod"))
```

### Bean Plots

Build bean plots using multiple basic plot calls.
```{r,Exploratory-Repeated-BeansA}
(RepeatedData) |> plotDensity(type="full",offset=0,main="Bean Plots")
(RepeatedData) |> plotData(add=TRUE,offset=0,pch=95,method="overplot")
```

Obtain bean plots using one call (and enhance the plot).
```{r,Exploratory-Repeated-BeansB}
(RepeatedData) |> plotBeans(col=c("darkred","darkblue","darkgoldenrod"))
```

### Raincloud Plots

Build raincloud plots using multiple basic plot calls.
```{r,Exploratory-Repeated-RaincloudsA}
(RepeatedData) |> plotBoxes(values=FALSE,main="Raincloud Plots")
(RepeatedData) |> plotDensity(add=TRUE,offset=.1)
(RepeatedData) |> plotData(add=TRUE,method="jitter",offset=-.15)
```

Obtain raincloud plots using one call (and enhance the plot).
```{r,Exploratory-Repeated-RaincloudsB}
(RepeatedData) |> plotRainclouds(col=c("darkred","darkblue","darkgoldenrod"))
```
