---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Exposition Factorial Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## Exposition Factorial Data Application

### Data Management

Simulate some data.
```{r}
FactorA <- c(rep(1,30),rep(2,30),rep(3,30),rep(1,30),rep(2,30),rep(3,30))
FactorB <- c(rep(1,90),rep(2,90))
FactorA <- factor(FactorA,levels=c(1,2,3),labels=c("A1","A2","A3"))
FactorB <- factor(FactorB,levels=c(1,2),labels=c("B1","B2"))
Outcome <- c(rnorm(30,mean=8,sd=2),rnorm(30,mean=11,sd=4),rnorm(30,mean=12,sd=4),rnorm(30,mean=8,sd=2),rnorm(30,mean=8,sd=3),rnorm(30,mean=7,sd=4))
FactorialData <- data.frame(FactorA,FactorB,Outcome)
```
Subset the data for each simple effect.
```{r}
FactorialB1 <- subset(FactorialData,FactorB=="B1")
FactorialB2 <- subset(FactorialData,FactorB=="B2")
```

### Analyses of the Means

Use the exposition pipe (%$>%) to identify the subset of interest, select the variables to analyzed, and use the native pipe to plot the means and the data.
```{r,Exposition-Factorial}
(FactorialB1) %$>% (Outcome~FactorA) |> plotData(main="Confidence Intervals and Data",ylim=c(-5,25),offset=-.05,method="overplot",col="darkblue")
(FactorialB2) %$>% (Outcome~FactorA) |> plotData(add=TRUE,offset=.05,method="overplot",col="darkred")
(FactorialB1) %$>% (Outcome~FactorA) |> plotMeans(add=TRUE,offset=-.15,col="darkblue",values=FALSE)
(FactorialB2) %$>% (Outcome~FactorA) |> plotMeans(add=TRUE,offset=.15,col="darkred",values=FALSE)
legend("topleft",inset=.01,box.lty=0,pch=16,legend=c("B1","B2"),col=c("darkblue","darkred"))
```

Use a similar process to obtain the tables of confidence interval estimates.
```{r}
(FactorialB1) %$>% (Outcome~FactorA) |> estimateMeans()
(FactorialB2) %$>% (Outcome~FactorA) |> estimateMeans()
```
### Analyses of the Simple Effects

Using the pipe operators, get the source table for each simple effect.
```{r}
(FactorialB1) %$>% (Outcome~FactorA) |> describeMeansOmnibus()
(FactorialB2) %$>% (Outcome~FactorA) |> describeMeansOmnibus()
```
Test each simple effect for statistical significance.
```{r}
(FactorialB1) %$>% (Outcome~FactorA) |> testMeansOmnibus()
(FactorialB2) %$>% (Outcome~FactorA) |> testMeansOmnibus()
```
Obtain the proportion of variance accounted for by each simple effect.
```{r}
(FactorialB1) %$>% (Outcome~FactorA) |> estimateMeansOmnibus()
(FactorialB2) %$>% (Outcome~FactorA) |> estimateMeansOmnibus()
```
