---
subtitle: "Exposition OneWay Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Exposition OneWay Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7",filename='revised_toc.R')
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Exposition OneWay Data Application

This page explains the use of the exposition operator in analyzing defined data frames using one-way (between-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile,base_level=3,toc_depth=4)
```

---

### Data Management

Simulate some data, placing it directly into a data frame (as opposed to declaring the variables separately).
```{r}
OneWayData <- data.frame(Factor = rep(factor(c("Group 1","Group 2","Group 3")),each=50),
                        Outcome=c(round(rnorm(50,mean=7,sd=2),0),
                        round(rnorm(50,mean=11,sd=4),0),
                        round(rnorm(50,mean=12,sd=4),0)))
```

### Using the Exposition Operator

When larger or predefined data sets are used, it is necessary to identify the data first and then select the variables from within the data set. In base R, this is accomplished using a `with` command (or built in data identification parameters). Note that this syntax does permit the use of pipe operators to work with individual variables (not that the data set contains more variables in this example).
```{r}
with(OneWayData,estimateMeans(Outcome~Factor))
```

In EASI, this is accomplished more efficiently and flexibly by using an exposition operator (such as the included `%$>%`). This is particularly useful in cases where there is a desire to focus on specific variables (though again, not present in this data set).
```{r,Exposition-OneWay-Basic}
OneWayData %$>% (Outcome~Factor) |> estimateMeans()
OneWayData %$>% (Outcome~Factor) |> plotMeans()
```
