---
subtitle: "Exposition OneWay Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Exposition OneWay Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7",filename='revised_toc.R')
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Exposition OneWay Data Application

This page explains the use of the exposition operator in analyzing defined data frames using one-way (between-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile,base_level=3,toc_depth=4)
```

---

### Data Management

Simulate some data, placing it directly into a data frame (as opposed to declaring the variables separately).
```{r}
OneWayData <- data.frame(Factor = rep(factor(c("Group 1","Group 2","Group 3")),each=50),
                        Outcome=c(round(rnorm(50,mean=7,sd=2),0),
                        round(rnorm(50,mean=11,sd=4),0),
                        round(rnorm(50,mean=12,sd=4),0)))
```

### Using an Exposition Operator

When larger or predefined data sets are used, it is necessary to identify the data and the selected variables. In base R, this is accomplished using a `with` command.
```{r}
with(OneWayData,estimateMeans(Outcome~Factor))
```

In EASI, this is accomplished more efficiently and flexibly by using an exposition operator (such as the included `%$>%`). Here, the data is identified first, then variables are selected and all levels are piped to the desired analyses.
```{r,Exposition-OneWay-Basic}
OneWayData %$>% (Outcome~Factor) |> estimateMeans()
OneWayData %$>% (Outcome~Factor) |> plotMeans()
```

### Advanced Uses of the Operator

This approach is particularly useful in cases where there is a desire to focus on specific variables. In this case, two specific levels are chosen for the sake of making a comparison.
```{r,Exposition-OneWay-Comparison}
OneWayData %$>% (Outcome~factor(Factor,c("Group 1","Group 2"))) |> estimateMeanComparison()
OneWayData %$>% (Outcome~factor(Factor,c("Group 1","Group 2"))) |> plotMeanComparison()
OneWayData %$>% (Outcome~factor(Factor,c("Group 1","Group 2"))) |> estimateStandardizedMeanDifference()
```
