---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{FactorialBy Data Applications}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## FactorialBy Data Applications

### Data Management

#### Data Entry

Enter the data.
```{r}
FactorA <- c(1,1,1,1,2,2,2,2,3,3,3,3,1,1,1,1,2,2,2,2,3,3,3,3)
FactorB <- c(1,1,1,1,1,1,1,1,1,1,1,1,2,2,2,2,2,2,2,2,2,2,2,2)
Outcome <- c(0,0,3,5,4,7,4,9,4,9,6,9,3,1,6,6,2,2,5,7,2,4,7,7)
FactorA <- factor(FactorA,levels=c(1,2,3),labels=c("A1","A2","A3"))
FactorB <- factor(FactorB,levels=c(1,2),labels=c("B1","B2"))
FactorialData <- data.frame(FactorA,FactorB,Outcome)
```

#### Descriptive Statistics

Get descriptive statistics separately for each simple effect.
```{r}
(Outcome~FactorA) |> describeMeansBy(by=FactorB)
```

### Analyses of the Omnibus and Simple Effects

Get an ANOVA for the design as a whole.
```{r}
(Outcome~FactorA) |> describeMeansOmnibusMultifactor(by=FactorB)
(Outcome~FactorA) |> testMeansOmnibusMultifactor(by=FactorB)
(Outcome~FactorA) |> estimateMeansOmnibusMultifactor(by=FactorB)
```

Get an ANOVA separately for each simple effect.
```{r}
(Outcome~FactorA) |> describeMeansOmnibusBy(by=FactorB)
(Outcome~FactorA) |> testMeansOmnibusBy(by=FactorB)
(Outcome~FactorA) |> estimateMeansOmnibusBy(by=FactorB)
```

### Analyses of the Means

Plot the means and confidence intervals for the design as a whole.
```{r,FactorialBy-Multifactor}
(Outcome~FactorA) |> plotMeansMultifactor(by=FactorB,col=c("black","gray60"))
legend("topleft",inset=.01,box.lty=0,pch=16,legend=c("B1","B2"),col=c("black","gray60"))
```

Estimate, plot, test, and standardize the means separately for each simple effect.
```{r,FactorialBy-Means}
(Outcome~FactorA) |> estimateMeansBy(by=FactorB)
(Outcome~FactorA) |> plotMeansBy(by=FactorB)
(Outcome~FactorA) |> testMeansBy(by=FactorB)
(Outcome~FactorA) |> estimateStandardizedMeansBy(by=FactorB)
```

### Analyses of a Comparison

Analyze the specified comparison separately for each simple effect.
```{r,FactorialBy-Comparison}
Comparison=factor(FactorB,c("Level1","Level2"))
(Outcome~FactorA) |> estimateMeanDifferenceBy(by=FactorB)
(Outcome~FactorA) |> plotMeanDifferenceBy(by=FactorB)
(Outcome~FactorA) |> testMeanDifferenceBy(by=FactorB)
(Outcome~FactorA) |> estimateStandardizedMeanDifferenceBy(by=FactorB)
```

### Analyses of a Contrast

Analyze the specified contrast separately for each simple effect.
```{r,FactorialBy-Contrast}
L1vsOthers <- c(-1,.5,.5)
(Outcome~FactorA) |> estimateMeanContrastBy(by=FactorB,contrast=L1vsOthers)
(Outcome~FactorA) |> plotMeanContrastBy(by=FactorB,contrast=L1vsOthers)
(Outcome~FactorA) |> testMeanContrastBy(by=FactorB,contrast=L1vsOthers)
(Outcome~FactorA) |> estimateStandardizedMeanContrastBy(by=FactorB,contrast=L1vsOthers)
```
