---
subtitle: "Frequencies Repeated Measures Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Frequencies Repeated Measures Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7",filename='revised_toc.R')
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Frequencies Repeated Measures Data Application

This page provides basic data plots and frequency distributions using repeated-measures (within-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile,base_level=3,toc_depth=4)
```

---

### Data Management

Simulate some data.
```{r}
Outcome1 <- round(rnorm(50,mean=7,sd=2),0)
Outcome2 <- round(rnorm(50,mean=11,sd=4),0)
Outcome3 <- round(rnorm(50,mean=12,sd=4),0)
RepeatedData <- data.frame(Outcome1,Outcome2,Outcome3)
```

### Data Plots

Plot the data and enhance with color.
```{r,Frequencies-Repeated-Data}
(RepeatedData) |> plotData(offset=0,method="overplot",connect=TRUE,col="darkblue")
```

### Frequency Distributions

Describe the frequency distributions.
```{r}
(RepeatedData) |> describeFrequencies()
```

Plot the frequency distributions and enhance with color.
```{r,Frequencies-Repeated-Frequencies}
(RepeatedData) |> plotFrequencies(offset=0,col="darkblue")
```
