---
subtitle: "Frequencies Repeated Measures Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Frequencies Repeated Measures Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Frequencies Repeated Measures Data Application

This page provides basic data plots and frequency distributions using repeated-measures (within-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

This code inputs the variable names and creates a viewable data frame.
```{r}
Outcome1 <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7)
Outcome2 <- c(7, 13, 11, 10, 13, 8, 11, 14, 12, 11)
Outcome3 <- c(9, 16, 11, 12, 15, 13, 9, 14, 11, 10)
RepeatedData <- construct(Outcome1, Outcome2, Outcome3)
```

### Frequency Distributions

Frequency distributions and data plots are often a first step in analyzing data.

Describe the frequency distributions.
```{r}
(RepeatedData) |> describeFrequencies()
```

Plot the frequencies as data points and enhance with color. Data points obtained from the same individuals are connected.
```{r, Frequencies-Repeated-Data}
(RepeatedData) |> plotData(offset = 0, method = "swarm", connect = TRUE, col = "darkblue")
```

### Summary Statistics

It is often helpful to view the summary statistics in conjunction with the frequency distributions.

Describe the summary statistics.
```{r}
(RepeatedData) |> describeSummary()
```

Plot the frequency distributions as histograms and add the summary statistics. The bars represent standard deviations, with dotted lines as the default but solid lines representing the sides with more skew.
```{r, Frequencies-Repeated-Frequencies}
(RepeatedData) |> plotFrequencies(main = "Frequencies and Summary Statistics for the Data", col = "darkblue")
(RepeatedData) |> plotSummary(add = TRUE, col = "darkblue")
```
