---
subtitle: "Layers OneWay Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Layers OneWay Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7",filename='revised_toc.R')
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Layers One Way Data Application

This page utilize advanced methods to build plots that combine various elements using one-way (between-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile,base_level=3,toc_depth=4)
```

---

### Data Management

Simulate some data.
```{r}
Factor <- c(rep(1,50),rep(2,50),rep(3,50))
Factor <- factor(Factor,levels=c(1,2,3),labels=c("Level1","Level2","Level3"))
Level1 <- round(rnorm(50,mean=7,sd=2),0)
Level2 <- round(rnorm(50,mean=11,sd=4),0)
Level3 <- round(rnorm(50,mean=12,sd=4),0)
Outcome <- c(Level1,Level2,Level3)
```

### Using the "add" Functions

The typical way to build a plot is to use sepearate calls for each plotting elements (e.g., data, boxplots) and using the "add" parameter to put them on the same plot.
```{r, Passthrough-OneWay-Traditional}
(Outcome~Factor) |> plotData() 
(Outcome~Factor) |> plotBoxes(add=TRUE)
```

This can be simplified by using an "add" version of the function call instead of using the longer "add" parameter for the function call.
```{r, Passthrough-OneWay-Add}
(Outcome~Factor) |> plotData() 
(Outcome~Factor) |> addBoxes()
```

### Using Passthrough Abilities

Rather than separate lines for function calls, all plotting elements have passthrough capabilites that allow the them to be placed on the same line.
```{r, Passthrough-OneWay-PassthroughA}
(Outcome~Factor) |> plotData() |> addBoxes()
```

As another example, diamond plots (which represent confidence intervals) can be combined with a jittered plot of data.
```{r, Passthrough-OneWay-PassthroughB}
(Outcome~Factor) |> plotData(offset=0,method="jitter") |> addDiamonds()
```

As a third example, plausibility curves can be used in conjunction with confidence intervals for the means.
```{r, Passthrough-OneWay-PassthroughC}
(Outcome~Factor) |> plotPlausible(main="Confidence Intervals and Plausibilty Curves",offset=0) |> addIntervals(values=FALSE)
```
