---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Mixed Design (Between-Subjects and Within-Subjects) Data Applications}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## Mixed Design (Between-Subjects and Within-Subjects) Data Applications

### Data Management

Enter the data.
```{r}
Factor <- c(1,1,1,1,2,2,2,2)
Outcome1 <- c(0,0,3,5,1,3,6,6)
Outcome2 <- c(4,7,4,9,3,1,6,6)
Outcome3 <- c(4,9,6,9,3,3,6,8)
Factor <- factor(Factor,levels=c(1,2),labels=c("Level1","Level2"))
MixedData <- data.frame(Factor,Outcome1,Outcome2,Outcome3)
MixedData
```

#### Descriptive Statistics

Get the descriptive statistics separately for each simple effect.
```{r}
describeMeansBy(cbind(Outcome1,Outcome2,Outcome3),by=Factor)
```

### Analyses of the Means

Estimate, plot, test, and standardize the means separately for each simple effect.
```{r,MixedBy-Means}
estimateMeansBy(cbind(Outcome1,Outcome2,Outcome3),by=Factor)
plotMeansBy(cbind(Outcome1,Outcome2,Outcome3),by=Factor)
testMeansBy(cbind(Outcome1,Outcome2,Outcome3),by=Factor)
estimateStandardizedMeansBy(cbind(Outcome1,Outcome2,Outcome3),by=Factor)
```

### Analyses of a Comparison

Analyze the specified comparison separately for each simple effect.
```{r,MixedBy-Comparison}
estimateMeanDifferenceBy(cbind(Outcome1,Outcome2),by=Factor)
testMeanDifferenceBy(cbind(Outcome1,Outcome2),by=Factor)
plotMeanDifferenceBy(cbind(Outcome1,Outcome2),by=Factor)
estimateStandardizedMeanDifferenceBy(cbind(Outcome1,Outcome2),by=Factor)
```

### Analyses of a Contrast

Analyze the specified contrast separately for each simple effect.
```{r,MixedBy-Contrast}
O1vsOthers <- c(-1,.5,.5)
estimateMeanContrastBy(cbind(Outcome1,Outcome2,Outcome3),by=Factor,contrast=O1vsOthers)
testMeanContrastBy(cbind(Outcome1,Outcome2,Outcome3),by=Factor,contrast=O1vsOthers)
plotMeanContrastBy(cbind(Outcome1,Outcome2,Outcome3),by=Factor,contrast=O1vsOthers)
estimateStandardizedMeanContrastBy(cbind(Outcome1,Outcome2,Outcome3),by=Factor,contrast=O1vsOthers)
```

### Analyses of the Omnibus Effect

Get an ANOVA separately for each simple effect.
```{r}
describeMeansOmnibusBy(cbind(Outcome1,Outcome2,Outcome3),by=Factor)
testMeansOmnibusBy(cbind(Outcome1,Outcome2,Outcome3),by=Factor)
estimateMeansOmnibusBy(cbind(Outcome1,Outcome2,Outcome3),by=Factor)
```

Get an ANOVA for the design as a whole.
```{r}
describeMeansOmnibusMultifactor(cbind(Outcome1,Outcome2,Outcome3),by=Factor)
testMeansOmnibusMultifactor(cbind(Outcome1,Outcome2,Outcome3),by=Factor)
estimateMeansOmnibusMultifactor(cbind(Outcome1,Outcome2,Outcome3),by=Factor)
```
