---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{MixedBy Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## MixedBy Data Application

This page analyzes simple effects using mixed design (between-subjects and within-subjects) data.

### Data Management

Enter the data.
```{r}
Factor <- c(1,1,1,1,2,2,2,2)
Outcome1 <- c(0,0,3,5,1,3,6,6)
Outcome2 <- c(4,7,4,9,3,1,6,6)
Outcome3 <- c(4,9,6,9,3,3,6,8)
Factor <- factor(Factor,levels=c(1,2),labels=c("Level1","Level2"))
MixedData <- data.frame(Factor,Outcome1,Outcome2,Outcome3)
```

#### Descriptive Statistics

Get the descriptive statistics separately for each simple effect.
```{r}
cbind(Outcome1,Outcome2,Outcome3) |> describeMeansBy(by=Factor)
```

### Analyses of the Omnibus and Simple Effects

Get an ANOVA for the design as a whole.
```{r}
cbind(Outcome1,Outcome2,Outcome3) |> describeMeansOmnibusMultifactor(by=Factor)
cbind(Outcome1,Outcome2,Outcome3) |> testMeansOmnibusMultifactor(by=Factor)
cbind(Outcome1,Outcome2,Outcome3) |> estimateMeansOmnibusMultifactor(by=Factor)
```

Get an ANOVA separately for each simple effect.
```{r}
cbind(Outcome1,Outcome2,Outcome3) |> describeMeansOmnibusBy(by=Factor)
cbind(Outcome1,Outcome2,Outcome3) |> testMeansOmnibusBy(by=Factor)
cbind(Outcome1,Outcome2,Outcome3) |> estimateMeansOmnibusBy(by=Factor)
```

### Analyses of the Means

Plot the means and confidence intervals for the design as a whole.
```{r,MixedBy-Multifactor}
cbind(Outcome1,Outcome2,Outcome3) |> plotMeansMultifactor(by=Factor,col=c("black","gray60"))
legend("topleft",inset=.01,box.lty=0,pch=16,legend=c("Level1","Level2"),col=c("black","gray60"))
```

Estimate, plot, test, and standardize the means separately for each simple effect.
```{r,MixedBy-Means}
cbind(Outcome1,Outcome2,Outcome3) |> estimateMeansBy(by=Factor)
cbind(Outcome1,Outcome2,Outcome3) |> plotMeansBy(by=Factor)
cbind(Outcome1,Outcome2,Outcome3) |> testMeansBy(by=Factor)
cbind(Outcome1,Outcome2,Outcome3) |> estimateStandardizedMeansBy(by=Factor)
```

### Analyses of a Comparison

Analyze the specified comparison separately for each simple effect.
```{r,MixedBy-Comparison}
cbind(Outcome1,Outcome2) |> estimateMeanDifferenceBy(by=Factor)
cbind(Outcome1,Outcome2) |> testMeanDifferenceBy(by=Factor)
cbind(Outcome1,Outcome2) |> plotMeanDifferenceBy(by=Factor)
cbind(Outcome1,Outcome2) |> estimateStandardizedMeanDifferenceBy(by=Factor)
```

### Analyses of a Contrast

Analyze the specified contrast separately for each simple effect.
```{r,MixedBy-Contrast}
O1vsOthers <- c(-1,.5,.5)
cbind(Outcome1,Outcome2,Outcome3) |> estimateMeanContrastBy(by=Factor,contrast=O1vsOthers)
cbind(Outcome1,Outcome2,Outcome3) |> testMeanContrastBy(by=Factor,contrast=O1vsOthers)
cbind(Outcome1,Outcome2,Outcome3) |> plotMeanContrastBy(by=Factor,contrast=O1vsOthers)
cbind(Outcome1,Outcome2,Outcome3) |> estimateStandardizedMeanContrastBy(by=Factor,contrast=O1vsOthers)
```
