---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{MixedBy Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## MixedBy Data Application

This page analyzes simple effects using mixed design (between-subjects and within-subjects) data.

### Data Management

Enter the data.
```{r}
Factor <- c(rep(1,30),rep(2,30))
Outcome1 <- c(round(rnorm(30,mean=8,sd=2),0),round(rnorm(30,mean=8,sd=2),0))
Outcome2 <- c(round(rnorm(30,mean=11,sd=4),0),round(rnorm(30,mean=8,sd=3),0))
Outcome3 <- c(round(rnorm(30,mean=12,sd=4),0),round(rnorm(30,mean=7,sd=4),0))
Factor <- factor(Factor,levels=c(1,2),labels=c("Level1","Level2"))
MixedData <- data.frame(Factor,Outcome1,Outcome2,Outcome3)
```

#### Descriptive Statistics

Get the descriptive statistics separately for each simple effect.
```{r}
cbind(Outcome1,Outcome2,Outcome3) |> describeMeansBy(by=Factor)
```

### Analyses of the Means

Estimate, plot, test, and standardize the means separately for each simple effect.
```{r,MixedBy-Means}
cbind(Outcome1,Outcome2,Outcome3) |> estimateMeansBy(by=Factor)
cbind(Outcome1,Outcome2,Outcome3) |> plotMeansBy(by=Factor)
cbind(Outcome1,Outcome2,Outcome3) |> testMeansBy(by=Factor)
cbind(Outcome1,Outcome2,Outcome3) |> estimateStandardizedMeansBy(by=Factor)
```

### Analyses of a Comparison

Analyze the specified comparison separately for each simple effect.
```{r,MixedBy-Comparison}
cbind(Outcome1,Outcome2) |> estimateMeanDifferenceBy(by=Factor)
cbind(Outcome1,Outcome2) |> plotMeanDifferenceBy(by=Factor)
cbind(Outcome1,Outcome2) |> testMeanDifferenceBy(by=Factor)
cbind(Outcome1,Outcome2) |> estimateStandardizedMeanDifferenceBy(by=Factor)
```

### Analyses of a Contrast

Specify a contrast for a factor.
```{r}
O1vsOthers <- c(-1,.5,.5)
```

Analyze the specified contrast separately for each simple effect.
```{r,MixedBy-Contrast}
cbind(Outcome1,Outcome2,Outcome3) |> estimateMeanContrastBy(by=Factor,contrast=O1vsOthers)
cbind(Outcome1,Outcome2,Outcome3) |> plotMeanContrastBy(by=Factor,contrast=O1vsOthers)
cbind(Outcome1,Outcome2,Outcome3) |> testMeanContrastBy(by=Factor,contrast=O1vsOthers)
cbind(Outcome1,Outcome2,Outcome3) |> estimateStandardizedMeanContrastBy(by=Factor,contrast=O1vsOthers)
```
