---
subtitle: "Omnibus Factorial Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Omnibus Factorial Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Omnibus Factorial Data Application

This page provides an omnibus analysis using factorial (between-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

Simulate some data.
```{r}
FactorA <- c(rep(1, 30), rep(2, 30), rep(3, 30), rep(1, 30), rep(2, 30), rep(3, 30))
FactorB <- c(rep(1, 90), rep(2, 90))
FactorA <- factor(FactorA, levels = c(1, 2, 3), labels = c("A1", "A2", "A3"))
FactorB <- factor(FactorB, levels = c(1, 2), labels = c("B1", "B2"))
Outcome <- c(rnorm(30, mean = 8, sd = 2), rnorm(30, mean = 11, sd = 4), rnorm(30, mean = 12, sd = 4), rnorm(30, mean = 8, sd = 2), rnorm(30, mean = 8, sd = 3), rnorm(30, mean = 7, sd = 4))
FactorialData <- data.frame(FactorA, FactorB, Outcome)
```

### Analyses of the Means

Plot the means and confidence intervals for the design as a whole.
```{r,FactorialBy-Multifactor}
(Outcome ~ FactorA) |> plotMeansMultifactor(by = FactorB, col = c("darkred", "darkblue"))
legend("topleft", inset = .01, box.lty = 0, pch = 16, legend = c("B1", "B2"), col = c("darkred", "darkblue"))
```

### Analyses of the Omnibus and Simple Effects

Get an ANOVA for the design as a whole.
```{r}
(Outcome ~ FactorA) |> describeMeansOmnibusMultifactor(by = FactorB)
(Outcome ~ FactorA) |> estimateMeansOmnibusMultifactor(by = FactorB)
(Outcome ~ FactorA) |> testMeansOmnibusMultifactor(by = FactorB)
```

Get an ANOVA separately for each simple effect.
```{r}
(Outcome ~ FactorA) |> describeMeansOmnibusBy(by = FactorB)
(Outcome ~ FactorA) |> estimateMeansOmnibusBy(by = FactorB)
(Outcome ~ FactorA) |> testMeansOmnibusBy(by = FactorB)
```
