---
subtitle: "Omnibus Mixed Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Omnibus Mixed Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Omnibus Mixed Data Application

This page provides an omnibus analysis using mixed design (between-subjects and within-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

Simulate some data.
```{r}
Factor <- c(rep(1, 30), rep(2, 30))
Outcome1 <- c(round(rnorm(30, mean = 8, sd = 2), 0), round(rnorm(30, mean = 8, sd = 2), 0))
Outcome2 <- c(round(rnorm(30, mean = 11, sd = 4), 0), round(rnorm(30, mean = 8, sd = 3), 0))
Outcome3 <- c(round(rnorm(30, mean = 12, sd = 4), 0), round(rnorm(30, mean = 7, sd = 4), 0))
Factor <- factor(Factor, levels = c(1, 2), labels = c("Level1", "Level2"))
MixedData <- data.frame(Factor, Outcome1, Outcome2, Outcome3)
```

### Analyses of the Means

Plot the means and confidence intervals for the design as a whole.
```{r,MixedBy-Multifactor}
cbind(Outcome1, Outcome2, Outcome3) |> plotMeansMultifactor(by = Factor, col = c("darkred", "darkblue"))
legend("topleft", inset = .01, box.lty = 0, pch = 16, legend = c("Level1", "Level2"), col = c("darkred", "darkblue"))
```

### Analyses of the Omnibus and Simple Effects

Get an ANOVA for the design as a whole.
```{r}
cbind(Outcome1, Outcome2, Outcome3) |> describeMeansOmnibusMultifactor(by = Factor)
cbind(Outcome1, Outcome2, Outcome3) |> estimateMeansOmnibusMultifactor(by = Factor)
cbind(Outcome1, Outcome2, Outcome3) |> testMeansOmnibusMultifactor(by = Factor)
```

Get an ANOVA separately for each simple effect.
```{r}
cbind(Outcome1, Outcome2, Outcome3) |> describeMeansOmnibusBy(by = Factor)
cbind(Outcome1, Outcome2, Outcome3) |> estimateMeansOmnibusBy(by = Factor)
cbind(Outcome1, Outcome2, Outcome3) |> testMeansOmnibusBy(by = Factor)
```
