---
subtitle: "Omnibus Factorial Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Omnibus Factorial Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Omnibus Factorial Data Application

This page provides an omnibus analysis using factorial (between-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

This code inputs the variable names and creates a viewable data frame.
```{r}
FactorA <- c(rep(1, 20), rep(2, 20), rep(3, 20))
FactorA <- factor(FactorA, levels = c(1, 2, 3), labels = c("A1", "A2", "A3"))
FactorB <- c(rep(1, 10), rep(2, 10), rep(1, 10), rep(2, 10), rep(1, 10), rep(2, 10))
FactorB <- factor(FactorB, levels = c(1, 2), labels = c("B1", "B2"))
Outcome <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7, 5, 9, 10, 9, 11, 4, 11, 7, 6, 8, 7, 13, 11, 10, 13, 8, 11, 14, 12, 11, 7, 8, 7, 11, 10, 7, 8, 4, 8, 10, 9, 16, 11, 12, 15, 13, 9, 14, 11, 10, 8, 6, 8, 11, 5, 7, 9, 3, 6, 7)
FactorialData <- construct(FactorA, FactorB, Outcome)
```

### Analyses of the Means

Plot the means and confidence intervals for the design as a whole.
```{r, Omnibus-Factorial}
(Outcome ~ FactorA) |> plotMeansFactorial(by = FactorB, col = c("darkred", "darkblue"))
legend("topleft", inset = .01, box.lty = 0, pch = 16, legend = c("B1", "B2"), col = c("darkred", "darkblue"))
```

### Analyses of the Omnibus and Simple Effects

Get an ANOVA for the design as a whole.
```{r}
(Outcome ~ FactorA) |> describeMeansFactorial(by = FactorB)
(Outcome ~ FactorA) |> estimateMeansFactorial(by = FactorB)
(Outcome ~ FactorA) |> testMeansFactorial(by = FactorB)
```

Get an ANOVA separately for each simple effect.
```{r}
(Outcome ~ FactorA) |> describeMeansEffectBy(by = FactorB)
(Outcome ~ FactorA) |> estimateMeansEffectBy(by = FactorB)
(Outcome ~ FactorA) |> testMeansEffectBy(by = FactorB)
```
