---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Pairwise Repeated Data Applications}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## Pairwise Repeated Data Applications

### Data Management

```{r}
Outcome1 <- c(0,0,3,5)
Outcome2 <- c(4,7,4,9)
Outcome3 <- c(9,6,4,9)
RepeatedData <- data.frame(Outcome1,Outcome2,Outcome3)
```

### Descriptive Statistics

Provide descriptive statistics for the variables.
```{r}
(RepeatedData) |> describeMeans()
```

### Analyses of Pairwise Comparisons

The analyses for the pairwise comparisons do not assume homogeneity of variance and do not make adjustments for multiple comparisons (and are therefore effectively equivalent to a series of paired samples t tests).

Provide a diffogram (plot of means and the confidence intervals for the pairwise comparisons)and specify colors for intervals that do not include zero (darkblue) and those that do include zero (darkred).
```{r,Repeated-PairwiseA}
(RepeatedData) |> plotMeansPairwiseDiffogram(col=c("darkblue","darkred"))
```

Provide a traditional plot of the confidence intervals for the pairwise comparisons (including a line that represents no difference for the comparisons).
```{r}
(RepeatedData) |> plotMeansPairwise(line=0)
```

Obtain a table of the point and interval estimates for the pairwise comparisons.
```{r,Repeated-PairwiseB}
(RepeatedData) |> estimateMeansPairwise()
```
Test the pairwise comparisons for statistical significance.
```{r}
(RepeatedData) |> testMeansPairwise()
```
Obtain standardized mean difference and their confidence intervals for the pairwise comparisons.
```{r}
(RepeatedData) |> estimateStandardizedMeansPairwise()
```

### Analyses of Post Hoc Comparisons

The analyses for the post hoc comparisons do assume homogeneity of variance and do make adjustments for multiple comparisons (based on Tukey HSD procedures).

Provide a diffogram (plot of means and the confidence intervals for the post hoc comparisons) and specify colors for intervals that do not include zero (darkblue) and those that do include zero (darkred).
```{r,Repeated-PosthocA}
(RepeatedData) |> plotMeansPosthocDiffogram(col=c("darkblue","darkred"))
```

Provide a traditional plot of the confidence intervals for the post hoc comparisons (including a line that represents no difference for the comparisons).
```{r,Repeated-PosthocB}
(RepeatedData) |> plotMeansPosthoc(line=0)
```

Obtain a table of the point and interval estimates for the post hoc comparisons.
```{r}
(RepeatedData) |> estimateMeansPosthoc()
```
Test the post hoc comparisons for statistical significance.
```{r}
(RepeatedData) |> testMeansPairwise()
```
Obtain standardized mean difference and their confidence intervals for the post hoc comparisons.
```{r}
(RepeatedData) |> estimateStandardizedMeansPosthoc()
```
