---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Passthrough Repeated Measures Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Passthrough Repeated Measures Data Application

This page utilizes passthrough capabilities and pipe operators to build plots that combine various elements using repeated measures (within-subjects) data.

### Data Management

Simulate some data.
```{r}
Outcome1 <- round(rnorm(50,mean=7,sd=2),0)
Outcome2 <- round(rnorm(50,mean=11,sd=4),0)
Outcome3 <- round(rnorm(50,mean=12,sd=4),0)
RepeatedData <- data.frame(Outcome1,Outcome2,Outcome3)
```

### Using the "add" Functions

The typical way to build a plot is to use sepearate calls for each plotting elements (e.g., data, boxplots) and using the "add" parameter to put them on the same plot.
```{r, Passthrough-Repeated-Traditional}
(RepeatedData) |> plotData() 
(RepeatedData) |> plotBoxes(add=TRUE)
```

This can be simplified by using an "add" version of the function call instead of using the longer "add" parameter for the function call.
```{r, Passthrough-Repeated-Add}
(RepeatedData) |> plotData() 
(RepeatedData) |> addBoxes()
```

### Using Passthrough Abilities

Rather than separate lines for function calls, all plotting elements have passthrough capabilites that allow the them to be placed on the same line.
```{r, Passthrough-Repeated-PassthroughA}
(RepeatedData) |> plotData() |> addBoxes()
```

As another example, diamond plots (which represent confidence intervals) can be combined with a jittered plot of data.
```{r, Passthrough-Repeated-PassthroughB}
(RepeatedData) |> plotData(offset=0,method="jitter") |> addDiamonds()
```

As a third example, plausibility curves can be used in conjunction with confidence intervals for the means.
```{r, Passthrough-Repeated-PassthroughC}
(RepeatedData) |> plotPlausible(main="Confidence Intervals and Plausibilty Curves",offset=0) |> addIntervals(values=FALSE)
```
