---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Pipes OneWay Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Pipes One Way Data Application

This page introduces a variety of native and simple pipe operators to implement basic analysis functions using one-way (between-subjects) data.

### Data Management

Simulate some data.
```{r}
Factor <- c(rep(1,50),rep(2,50),rep(3,50))
Factor <- factor(Factor,levels=c(1,2,3),labels=c("Level1","Level2","Level3"))
Level1 <- round(rnorm(50,mean=7,sd=2),0)
Level2 <- round(rnorm(50,mean=11,sd=4),0)
Level3 <- round(rnorm(50,mean=12,sd=4),0)
Outcome <- c(Level1,Level2,Level3)
```

### Using the Native and Dot Pipes

In R versions 4.1 and greater, the native pipe operator can be used instead of standard syntax. Here, the variable (or data frame or formula) is included first, followed by the pipe operator, and then the function call (with any relevant additional parameters in parentheses). 
```{r}
(Outcome~Factor) |> estimateMeans()
(Outcome~Factor) |> estimateMeans(conf.level=.99)
```

However, the native pipe operator does not easily permit the piping of the variable, data frame, or formula to multiple functions on the ride-hand side of the call simultaneously. EASI contains a very simple pipe operator that uses a period as a placeholder, permitting more advanced piping options.
```{r}
(Outcome~Factor) %.>% estimateMeans(.)
(Outcome~Factor) %.>% c(estimateMeans(.),testMeans(.))
(Outcome~Factor) %.>% c(estimateMeans(.,conf.level=.99),testMeans(.,mu=5))
```

### Using Passthrough Pipes

Traditionally, a pipe operator sends the results (not the input) of each operation in sequence to the next operation. Sometimes, it is useful to implement a "pass though" instead, where the input for the first call is piped to the second call.
```{r}
(Outcome~Factor) %.>>% estimateMeans(.) %.>>% testMeans(.)
(Outcome~Factor) %.>>% estimateMeans(.,conf.level=.99) %.>>% testMeans(.,mu=5)
```

In these examples, the passthrough pipe is only required prior to the first analysis because the second one is the terminal call and thus nothing needs to "pass though". As a result, the second pipe operator could be the dot or the native pipe operator instead.
```{r}
(Outcome~Factor) %.>>% describeMeans(.) %.>% estimateMeans(.)
(Outcome~Factor) %.>>% describeMeans(.) |> estimateMeans()
```
