---
subtitle: "Plausible Repeated Measures Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Plausible Repeated Measures Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Plausible Repeated Measures Data Application

This page adds data and plausibility curves to confidence interval plots of comparisons and contrasts using repeated-measures (within-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

This code inputs the variable names and creates a viewable data frame.
```{r}
Outcome1 <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7)
Outcome2 <- c(7, 13, 11, 10, 13, 8, 11, 14, 12, 11)
Outcome3 <- c(9, 16, 11, 12, 15, 13, 9, 14, 11, 10)
RepeatedData <- construct(Outcome1, Outcome2, Outcome3)
```

### Analyses of the Means

Get a simple plot of the confidence intervals.
```{r, Plausible-Repeated-ConfidenceA}
(RepeatedData) |> estimateMeans()
(RepeatedData) |> plotMeans()
```

Get an enhanced plot of data and confidence intervals.
```{r, Plausible-Repeated-ConfidenceB}
(RepeatedData) |> plotData(main = "Data and Confidence Intervals", method = "stack", col = c("darkred", "darkblue", "darkgoldenrod"))
(RepeatedData) |> addMeans(values = FALSE, line = 9, col = c("darkred", "darkblue", "darkgoldenrod"))
```

### Analyses of a Comparison

Create a comparison and get a simple plot of the confidence intervals.
```{r, Plausible-Repeated-ComparisonA}
(RepeatedData) |> pick(Outcome1, Outcome2) |> estimateMeanComparison()
(RepeatedData) |> pick(Outcome1, Outcome2) |> plotMeanComparison()
```

Get an enhanced plot of data and confidence intervals with a plausibility curve.
```{r, Plausible-Repeated-ComparisonB}
(RepeatedData) |> pick(Outcome1, Outcome2) |> plotMeanComparison(main = "Data, Confidence Intervals, and a Plausibility Curve", ylim = c(0, 20), values = FALSE, col = c("darkred", "darkblue", "black"))
(RepeatedData) |> pick(Outcome1, Outcome2) |> addPlausible(type = c("none", "none", "right"), col = c("darkred", "darkblue", "black"))
(RepeatedData) |> pick(Outcome1, Outcome2) |> addData(method = "stack", col = c("darkred", "darkblue", "black"))
```

### Analyses of a Mean Contrast

Create a contrast and get a plot of the mean subsets and the contrast.
```{r, Plausible-Repeated-ContrastA}
(RepeatedData) |> estimateMeanSubsets(contrast = c(-1, .5, .5), labels = c("Outcome1", "Others"))
(RepeatedData) |> plotMeanSubsets(contrast = c(-1, .5, .5), labels = c("Outcome1", "Others"))
```

Create an enhanced plot of the means and the mean subsets with a plausibility curve.
```{r, Plausible-Repeated-ContrastB}
(RepeatedData) |> plotMeanSubsets(contrast = c(-1, .5, .5), labels = c("Outcome1", "Others"), main = "Confidence Intervals and a Plausibility Curve", ylim = c(0, 20), values = FALSE, col = c("darkred", "darkblue", "black"))
(RepeatedData) |> addPlausible(contrast = c(-1, .5, .5), type = c("none", "none", "right"), col = c("darkred", "darkblue", "black"))
```
