---
subtitle: "Relational Repeated Measures Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Relational Repeated Measures Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Relational Repeated Measures Data Application

This page examines means and mean differences with relational and arelational intervals using repeated-measures (within-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

Enter the data.
```{r}
Outcome1 <- c(61, 64, 72, 64, 64, 70, 73, 65, 65, 72)
Outcome2 <- c(69, 74, 79, 69, 64, 64, 69, 69, 74, 79)
Outcome3 <- c(70, 75, 80, 80, 70, 65, 70, 75, 70, 70)
Outcome4 <- c(70, 80, 85, 75, 70, 65, 75, 75, 85, 80)
Outcome5 <- c(65, 55, 70, 65, 65, 70, 70, 60, 65, 70)
RepeatedData <- data.frame(Outcome1, Outcome2, Outcome3, Outcome4, Outcome5)
```

### Omnibus Analyses

Provide descriptive statistics and an ANOVA source table.
```{r}
(RepeatedData) |> describeMeans()
(RepeatedData) |> describeMeansOmnibus()
(RepeatedData) |> testMeansOmnibus()
```

### Analyses of Relational Intervals

Provide estimates of the arelational and relational intervals.
```{r,Relational-Repeated-RelationalA}
(RepeatedData) |> estimateMeansRelational()
```

Plot the intervals and enhance with color.
```{r,Relational-Repeated-RelationalB}
(RepeatedData) |> plotMeansRelational(col = c("darkred", "darkblue", "darkgoldenrod", "darkgreen", "darkviolet"))
```
