---
subtitle: "Themes OneWay Data Application"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Themes OneWay Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7",filename='revised_toc.R')
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Themes OneWay Data Application

This page shows how to enhance different types of plots with color themes using one-way (between-subjects) data.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile,base_level=3,toc_depth=4)
```

---

### Data Management

Simulate some data.
```{r}
Factor <- c(rep(1,10),rep(2,10),rep(3,10),rep(4,10),rep(5,10))
Outcome <- c(61,64,72,64,64,70,73,65,65,72,69,74,79,69,64,64,69,69,74,79,70,75,80,80,70,65,70,75,70,70,70,80,85,75,70,65,75,75,85,80,65,55,70,65,65,70,70,60,65,70)
Factor <- factor(Factor,levels=c(1,2,3,4,5),labels=c("Level1","Level2","Level3","Level4","Level5"))
```

### Analyses of the Means

In plotting a main effect, the classic method for specifying colors is to identify either a single color for all elements of the plot or to directly specify the color for each level.
```{r,Themes-OneWay-MeansA}
(Outcome~Factor) |> plotMeans(col="darkblue")
(Outcome~Factor) |> plotMeans(col=c("darkred","darkblue","darkgoldenrod","darkgreen","darkviolet"))
```

Rather than directly specifying colors for each level, simply specify a pre-determined color theme (like the "muted" theme).
```{r,Themes-OneWay-MeansB}
(Outcome~Factor) |> plotMeans(col=theme("muted"))
(Outcome~Factor) |> plotMeans(col=theme("muted","main"))
```

### Analyses of a Comparison

In plotting a comparison, the classic method would again directly specify the levels for each element of the graph.
```{r,Themes-OneWay-ComparisonA}
Comparison <- factor(Factor,c("Level1","Level2"))
(Outcome~Comparison) |> plotMeanComparison(col=c("red3","blue3","black"))
(Outcome~Comparison) |> plotPlausible(col=c("red3","blue3","black"),add=TRUE)
```

It may be preferable to use a theme for the main elements (using the "vibrant" theme), but use a set color for the comparison portion of the graph. To do this, use the "comp" parameter (instead of "main").
```{r,Themes-OneWay-ComparisonB}
(Outcome~Comparison) |> plotMeanComparison(col=theme("vibrant","comp"))
(Outcome~Comparison) |> plotPlausible(col=theme("vibrant","comp"),add=TRUE)
```
