---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Theme OneWay Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Theme OneWay Data Application

This page shows how to enhance different types of plots with EASI color themes using one-way (between-subjects) data.

### Data Management

Simulate some data.
```{r}
Factor <- c(rep(1,10),rep(2,10),rep(3,10),rep(4,10),rep(5,10))
Outcome <- c(61,64,72,64,64,70,73,65,65,72,69,74,79,69,64,64,69,69,74,79,70,75,80,80,70,65,70,75,70,70,70,80,85,75,70,65,75,75,85,80,65,55,70,65,65,70,70,60,65,70)
Factor <- factor(Factor,levels=c(1,2,3,4,5),labels=c("Level1","Level2","Level3","Level4","Level5"))
```

### Analyses of the Means

Rather than directly specifying colors for each level, simply specify a built-in color theme (like EASI's "muted" theme, which is the default if "theme" is used).
```{r,Theme-OneWay-MeansA}
(Outcome~Factor) |> plotMeans(col=theme())
(Outcome~Factor) |> plotData(col=theme(),add=TRUE)
```

For larger number of levels, it may be preferably to use colors along a spectrum (similar to the vibrant or muted themes, though with the color orders determined mathematically) and have R determine the number of levels across the main effect.
```{r,Theme-OneWay-MeansB}
(Outcome~Factor) |> plotMeans(col=theme("muted","main",nlevels(Factor)))
(Outcome~Factor) |> plotData(col=theme("muted","main",nlevels(Factor)),add=TRUE)
```

### Analyses of a Comparison

In plotting a comparison, it may be preferable to use a theme for the main elements (like the confidence intervals and plausibility curves), but use a set color for the comparison portion of the graph. To do this, use the "comp" parameter (instead of "main").
```{r,Theme-OneWay-Comparison}
Comparison = factor(Factor,c("Level1","Level2"))
(Outcome~Comparison) |> plotMeanComparison(col=theme("vibrant","comp"))
(Outcome~Comparison) |> plotPlausible(col=theme("vibrant","comp"),add=TRUE)
```
