---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Themes Repeated Measures Data Application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Themes Repeated Measures Data Application

This page shows how to enhance different types of plots with color themes using repeated-measures (within-subjects) data.

### Data Management

Simulate some data.
```{r}
Outcome1 <-c(61,64,72,64,64,70,73,65,65,72)
Outcome2 <- c(69,74,79,69,64,64,69,69,74,79)
Outcome3 <- c(70,75,80,80,70,65,70,75,70,70)
Outcome4 <- c(70,80,85,75,70,65,75,75,85,80)
Outcome5 <- c(65,55,70,65,65,70,70,60,65,70)
RepeatedData <- data.frame(Outcome1,Outcome2,Outcome3,Outcome4,Outcome5)
```

### Analyses of the Means

In plotting a main effect, the classic method for specifying colors is to identify either a single color for all elements of the plot or to directly specify the color for each level.
```{r,Themes-Repeated-MeansA}
(RepeatedData) |> plotMeans(col="darkblue")
(RepeatedData) |> plotMeans(col=c("darkred","darkblue","darkgoldenrod","darkgreen","darkviolet"))
```

Rather than directly specifying colors for each level, simply specify a pre-determined color theme (like the "muted" theme).
```{r,Themes-Repeated-MeansB}
(RepeatedData) |> plotMeans(col=theme("muted"))
(RepeatedData) |> plotMeans(col=theme("muted","main"))
```

### Analyses of a Comparison

In plotting a comparison, the classic method would again directly specify the levels for each element of the graph.
```{r,Themes-Repeated-ComparisonA}
ComparisonData <- cbind(Outcome1,Outcome2)
(ComparisonData) |> plotMeanComparison(col=c("red3","blue3","black"))
(ComparisonData) |> plotPlausible(col=c("red3","blue3","black"),add=TRUE)
```

It may be preferable to use a theme for the main elements (using the "vibrant" theme), but use a set color for the comparison portion of the graph. To do this, use the "comp" parameter (instead of "main").
```{r,Themes-Repeated-ComparisonB}
(ComparisonData) |> plotMeanComparison(col=theme("vibrant","comp"))
(ComparisonData) |> plotPlausible(col=theme("vibrant","comp"),add=TRUE)
```
