---
title: "Estimation Approach to Statistical Inference"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Paired Samples Correlation Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Paired Samples Correlation Tutorial with Summary Statistics

### Data Management

This code inputs the variable summaries and creates a summary table.
```{r}
Outcome1 <- c(N=4,M=2.000,SD=2.449)
Outcome2 <- c(N=4,M=6.000,SD=2.449)
PairedSummary <- rbind(Outcome1,Outcome2)
class(PairedSummary) <- "wss"
```

This code creates a correlation matrix and enters single correlation.
```{r}
PairedCorr <- declareCorrelations("Outcome1","Outcome2")
PairedCorr["Outcome1","Outcome2"] <- .500
```
 
### Analyses of a Correlation

This section produces analyses of the correlation.

#### Confidence Interval

This code will provide the confidence interval for the correlation.
```{r}
estimateCorrelations(PairedSummary,PairedCorr)
```

This code will produce a graph of the confidence interval for the correlation.
```{r,PairedCorrelation-A}
plotCorrelations(PairedSummary,PairedCorr)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateCorrelations(PairedSummary,PairedCorr,conf.level=.99)
```

Of course, it is possible to change from the default confidence level in the graph.
```{r,PairedCorrelation-B}
plotCorrelations(PairedSummary,PairedCorr,conf.level=.99)
```

#### Significance Test

This code will produce a table of NHST for the correlation (against a value of zero).
```{r}
testCorrelations(PairedSummary,PairedCorr)
```
