---
title: "Estimation Approach to Statistical Inference"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{OneWay (Relational Between-Subjects) Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Relational OneWay (Between-Subjects) Tutorial with Summary Statistics

### Data Management

This code inputs the group summaries and creates a single summary table.
```{r}
Level1 <- c(N=4,M=2.000,SD=2.449)
Level2 <- c(N=4,M=6.000,SD=2.449)
Level3 <- c(N=4,M=7.000,SD=2.449)
OneWaySummary <- rbind(Level1,Level2,Level3)
class(OneWaySummary) <- "bss"
```

### Analyses of the Omnibus Effect

This section produces analyses that are the traditional way to represent and test overall group differences.

#### Confidence Intervals

This code will provide a table of confidence intervals for each level of the factor.
```{r}
estimateMeans(OneWaySummary)
```

This code will produce a graph of the confidence intervals for each level of the factor.
```{r,RelationalOneWay-Means}
plotMeans(OneWaySummary)
```

#### Significance Tests for the Omnibus Effect

This code provides an ANOVA source table for the omnibus effect.
```{r}
describeMeansOmnibus(OneWaySummary)
testMeansOmnibus(OneWaySummary)
```

### Analyses of the Pairwise Comparisons

This section provides analyses of all possible pairwise comparisons among the levels of the factor.

#### Confidence Intervals

This code will provide a table of descriptive statistics and confidence intervals for each pairwise comparison.

```{r}
estimateMeansPairwise(OneWaySummary)
```

This code will produce a graph of the confidence intervals for each of the pairwise comparisons.
```{r,RelationalOneWay-Pairwise}
plotMeansPairwise(OneWaySummary,mu=0)
```

#### Significance Tests

This code will produce a table of NHST for each of the pairwise comparisons. In this case, all the comparisons are tested against a value of zero.
```{r}
testMeansPairwise(OneWaySummary)
```

### Analyses of the Pairwise Comparisons Using Relational Intervals

This section provides analyses of all possible pairwise comparisons among the levels of the factor using relational intervals.

#### Confidence and Relational Intervals

This code will provide a table of confidence and relational intervals for each pairwise comparison.
```{r}
estimateMeansRelational(OneWaySummary)
```

This code will produce a graph of the confidence and relational intervals for each of the pairwise comparisons.
```{r,RelationalOneWay-RelationalA}
plotMeansRelational(OneWaySummary)
```

The code defaults to 95% confidence and relational intervals. This can be changed if desired.
```{r}
estimateMeansRelational(OneWaySummary,conf.level=.99)
```

For the graph, it is possible to change the confidence level.
```{r,RelationalOneWay-RelationalB}
plotMeansRelational(OneWaySummary,conf.level=.99)
```
