---
title: "Correlation Example with BodyWell Two Sample Data"
author: "Craig A. Wendorf"
date: "2020-10-20"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Correlation Example with BodyWell Two Sample Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8",filename="render_toc.R")
```

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Correlation Example with BodyWell Two Sample Data

### Table of Contents

```{r toc, echo=FALSE}
sourceDir <- getSrcDirectory(function(dummy) {dummy})
setwd(sourceDir)
render_toc("BodyWellTwoDataExample.Rmd")
```

### Analyses of the Correlation

#### Data Entry

First, enter the data.
```{r}
Gender <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2)
BodySatisfaction <- c(4,2.4,3,3,3.1,2.4,2.9,3.1,3,3.3,2,3.1,2.4,3.1,3.3,3.4,3.3,3.6,2.7,3.3,3.6,2.3,3.7,4,2.7,3.1,3.3,3.4,4.4,3.3,3.3,4,4.1,3.3,3.6,3.9,4,5,3,3,3.3,3.9,3.9,4.7,5,2.6,2.9,3.4,3.4,3.9,4.3,2.6,3.1,3.4,3.7,4,4.1,4,5,4,2.4,3.7,3,3.6,2.9,2.7,3.3,4.3,3.1,4.3,4.4,4,3.3,3.7,2.9,3.4,3.6,4.7,4.1,3,4.1,3.7,4.1,4,3.1,3.7,3.3,4.4,4.3,4,4,4,3.4,4.9,3.7,3.3,3.9,4.6,4,3.9,4.7,4.3,4.4,4.4,4.6,4.3)
Wellbeing <- c(1,2.4,2.3,2.4,2.8,3.2,3.4,3.4,3.6,3.6,3.8,3.8,4,4,4.2,4.2,4.4,4.4,4.6,4.6,4.6,4.8,4.8,4.8,5,5,5,5,5,5.2,5.3,5.2,5.2,5.6,5.6,5.6,5.6,5.6,5.8,5.7,5.8,5.8,5.9,5.8,5.8,6,6,6,6.1,6,6,6.2,6.2,6.2,6.4,6.4,6.4,6.6,7,2.8,3,3.2,3.2,3.4,3.4,3.8,4.2,4.4,4.4,4.6,4.6,4.6,4.8,4.8,4.8,5,5,5.2,5.2,5.4,5.6,5.6,5.5,5.6,5.6,5.7,5.6,5.6,5.6,5.8,5.8,6,6,6,6,6,6,6,6.1,6.2,6.2,6.2,6.2,6.4,6.6,7)
BodyWellTwoData <- data.frame(Gender,BodySatisfaction,Wellbeing)
```

This code subsets the data into two different data frames for use in analyzing the two Gender groups separately.
```{r}
BodyWellTwoDataL1 <- subset(BodyWellTwoData,Gender=="1")
BodyWellTwoDataL2 <- subset(BodyWellTwoData,Gender=="2")
```

#### Descriptive Statistics

This code obtains the descriptive statistics for the Gender groups.
```{r}
with(BodyWellTwoDataL1,describeMeans(BodySatisfaction,Wellbeing))
with(BodyWellTwoDataL2,describeMeans(BodySatisfaction,Wellbeing))
```

This code obtains a table of correlations for the two groups.
```{r}
with(BodyWellTwoDataL1,describeCorrelations(BodySatisfaction,Wellbeing))
with(BodyWellTwoDataL2,describeCorrelations(BodySatisfaction,Wellbeing))
```

### Analyses of a Correlation Comparison

The main question is whether the correlation between Body Satisfaction and Wellbeing is different in the two groups.

First it is necessary to estimate the confidence intervals for each of the correlations.
```{r}
CorrEstimateL1 <- with(BodyWellTwoDataL1,estimateCorrelations(BodySatisfaction,Wellbeing))
CorrEstimateL2 <- with(BodyWellTwoDataL2,estimateCorrelations(BodySatisfaction,Wellbeing))
```

Then we can estimate the correlations and the difference in the correlations.
```{r}
estimateCorrelationComparison(CorrEstimateL1,CorrEstimateL2,main="Correlations for the Gender Groups",labels=c("Females","Males"))
```

Finally, we get a difference plot using the confidence intervals for the correlations and the correlation difference.
```{r,BodyWellTwo-Comparison}
plotCorrelationComparison(CorrEstimateL1,CorrEstimateL2,main="Correlations for the Gender Groups",labels=c("Females","Males"),ylim=c(-1,1))
```
