---
title: "Correlation Example with BodyWell One Sample Summary Statistics"
author: "Craig A. Wendorf"
date: "2020-10-20"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Correlation Example with BodyWell One Sample Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8",filename="render_toc.R")
```

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Correlation Example with BodyWell One Sample Summary Statistics

### Table of Contents

```{r toc, echo=FALSE}
sourceDir <- getSrcDirectory(function(dummy) {dummy})
setwd(sourceDir)
render_toc("BodyWellOneSummaryExample.Rmd")
```

### Data Management

This code inputs the variable summaries and creates a summary table.
```{r}
BodySatisfaction <- c(N=106,M=3.605,SD=0.659)
Wellbeing <- c(N=106,M=5.055,SD=1.162)
BodyWellOneSummary <- rbind(BodySatisfaction,Wellbeing)
class(BodyWellOneSummary) <- "wss"
```

This code creates a correlation matrix and enters single correlation.
```{r}
BodyWellOneCorr <- declareCorrelations("BodySatisfaction","Wellbeing")
BodyWellOneCorr["BodySatisfaction","Wellbeing"] <- .467
```

### Analyses of the Correlation

More importantly, we can get the confidence interval for the correlation.
```{r}
estimateCorrelations(BodyWellOneSummary,BodyWellOneCorr)
```

This is the plot of correlation and its confidence interval.
```{r,BodyWellOne-Correlation}
plotCorrelations(BodyWellOneSummary,BodyWellOneCorr,main="Correlation for the Entire Sample",ylim=c(-1,1))
```
