---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "2020-06-20"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Repeated Measures (Within-Subjects) Example with Donohue Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8",filename="render_toc.R")
```

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Repeated Measures (Within-Subjects) Example with Donohue Summary Statistics

### Table of Contents

```{r toc, echo=FALSE}
sourceDir <- getSrcDirectory(function(dummy) {dummy})
setwd(sourceDir)
render_toc("DonohueSummaryExample.Rmd")
```

### Data Management

Prior to analyses, enter the tables of summary statistics.

```{r}
Pretest <- c(N=20,M=19.300,SD=5.904)
Posttest <- c(N=20,M=23.600,SD=4.762)
Followup <- c(N=20,M=23.400,SD=4.616)
DonohueSummary <- rbind(Pretest,Posttest,Followup)
class(DonohueSummary) <- "wss"

DonohueCorr <- declareCorrelations("Pretest","Posttest","Followup")
DonohueCorr["Pretest","Posttest"] <- .493
DonohueCorr["Pretest","Followup"] <- .536
DonohueCorr["Posttest","Followup"] <- .743
DonohueCorr <- fillCorrelations(DonohueCorr)
```

### Analyses of the Different Variables

With multiple variables, it is useful to get descriptive statistics and confidence intervals for each variable.

```{r}
estimateMeans(DonohueSummary)
```

It is also useful to view the means and confidence intervals of the groups in a plot.

```{r,Donohue-Means}
plotMeans(DonohueSummary,main="Critical Thinking Scores at Pretest, Posttest, and Followup")
```
 
### Analysis of a Variable Difference

The first research question is whether there is a difference between the posttest and followup occasions.

First, set the comparison and get an estimate of the difference and its confidence interval.

```{r}
PostvsFollowup <- DonohueSummary[c(2,3),]
class(PostvsFollowup) <- "wss"
estimateDifference(PostvsFollowup,DonohueCorr)
```

Then, obtain the difference plot for that comparison.

```{r,Donohue-Difference}
plotDifference(PostvsFollowup,DonohueCorr,main="Critical Thinking Scores of Posttest vs Followup")
```

Finally, obtain the standardized effect size for that comparison.

```{r}
standardizeDifference(PostvsFollowup,DonohueCorr)
```

### Analysis of a Variable Contrast

The second research question is whether the pretest differs from the posttest and followup combined.

First, set the contrast and get an estimate of the contrast and its confidence interval.

```{r}
PrevsPostFollow <- c(-1,.5,.5)
estimateContrast(DonohueSummary,DonohueCorr,contrast=PrevsPostFollow)
```

Then, obtain a difference plot for the contrast.

```{r,Donohue-Contrast}
plotContrast(DonohueSummary,DonohueCorr,contrast=PrevsPostFollow,labels=c("Pretest","Post&Follow"),main="Critical Thinking Scores of Prestest vs Posttest and Followup Combined",ylab="Critical Thinking")
```

Finally, estimate the standardized contrast.

```{r}
standardizeContrast(DonohueSummary,DonohueCorr,contrast=PrevsPostFollow)
```
