---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Repeated Measures (Within-Subjects) Example with Donohue Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Repeated Measures (Within-Subjects) Example with Donohue Data

### Enter Data

Prior to analyses, enter the data.

```{r}
Pretest <- c(7,11,11,13,15,17,18,18,19,19,19,19,21,22,25,25,25,26,27,29)
Posttest <- c(16,20,25,22,28,12,16,26,21,22,26,30,23,27,23,27,28,24,28,28)
Followup <- c(16,18,23,21,27,21,18,21,24,21,27,28,18,27,23,28,31,18,31,27)
DonohueData <- data.frame(Pretest,Posttest,Followup)
```
### Analyses of the Different Variables

With multiple variables, it is useful to get descriptive statistics and confidence intervals for each variable.

```{r}
estimateMeans(Pretest,Posttest,Followup)
```

It is also useful to view the means and confidence intervals of the groups in a plot.

```{r,Donohue-Means}
plotMeans(Pretest,Posttest,Followup,ylab="Critical Thinking")
```
 
### Analysis of a Variable Difference

The first research question is whether there is a difference between the posttest and followup occasions.

First, set the comparison and get an estimate of the difference and its confidence interval.

```{r}
estimateDifference(Posttest,Followup)
```

Then, obtain the difference plot for that comparison.

```{r,Donohue-Difference}
plotDifference(Posttest,Followup,ylab="Critical Thinking")
```

Finally, obtain the standardized effect size for that comparison.

```{r}
standardizeDifference(Posttest,Followup)
```

### Analysis of a Variable Contrast

The second research question is whether the pretest differs from the posttest and followup combined.

First, set the contrast and get an estimate of the contrast and its confidence interval.

```{r}
PrevsPostFollow <- c(-1,.5,.5)
estimateContrast(Pretest,Posttest,Followup,contrast=PrevsPostFollow)
```

Then, obtain a difference plot for the contrast.

```{r,Donohue-Contrast}
plotContrast(Pretest,Posttest,Followup,contrast=PrevsPostFollow,labels=c("Pretest","Post&Follow"),ylab="Critical Thinking")
```

Finally, estimate the standardized contrast.

```{r}
standardizeContrast(Pretest,Posttest,Followup,contrast=PrevsPostFollow)
```
