---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Factorial Between-Subjects Example with Frenda Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Factorial Between-Subjects Example with Frenda Summary Statistics

### Enter Summary Statistics

```{r}
EveningSleep <- c(N=26,M=1.50,SD=1.38)
EveningNosleep <- c(N=26,M=1.14,SD=0.96)
MorningSleep <- c(N=25,M=1.38,SD=1.50)
MorningNosleep <- c(N=26,M=2.22,SD=1.68)
FrendaSummary <- rbind(EveningSleep,EveningNosleep,MorningSleep,MorningNosleep)
class(FrendaSummary) <- "bss"
```

### Analyses of the Different Groups

```{r}
estimateMeans(FrendaSummary)
```

```{r,Frenda-Means}
plotMeans(FrendaSummary,ylab="False Memory")
```

### Analyses of the Marginal Means

```{r}
Evening <- c(.5,.5,0,0)
estimateContrast(FrendaSummary,contrast=Evening)
```

```{r}
Morning <- c(0,0,.5,.5)
estimateContrast(FrendaSummary,contrast=Morning)
```

```{r}
Sleep <- c(.5,0,.5,0)
estimateContrast(FrendaSummary,contrast=Sleep)
```

```{r}
Nosleep <- c(0,.5,0,.5)
estimateContrast(FrendaSummary,contrast=Nosleep)
```

### Analyses of the Factor A (Evening vs Morning) Main Effect

```{r}
mainFactorA <- c(-.5,-.5,.5,.5)
estimateContrast(FrendaSummary,contrast=mainFactorA)
```

```{r,Frenda-MainA}
plotContrast(FrendaSummary,contrast=mainFactorA,labels=c("Evening","Morning"),ylab="False Memory")
```

```{r}
testContrast(FrendaSummary,contrast=mainFactorA)
```

```{r}
standardizeContrast(FrendaSummary,contrast=mainFactorA)
```


### Analyses of the Factor B (Sleep vs NoSleep) Main Effect

```{r}
mainFactorB <- c(-.5,.5,-.5,.5)
estimateContrast(FrendaSummary,contrast=mainFactorB)
```

```{r,Frenda-MainB}
plotContrast(FrendaSummary,contrast=mainFactorB,labels=c("Sleep","NoSleep"),ylab="False Memory")
```

```{r}
testContrast(FrendaSummary,contrast=mainFactorB)
```

```{r}
standardizeContrast(FrendaSummary,contrast=mainFactorB)
```


### Analyses of the Factor A x B Interaction

```{r}
Interaction <- c(1,-1,-1,1)
estimateContrast(FrendaSummary,contrast=Interaction)
```

```{r}
testContrast(FrendaSummary,contrast=Interaction)
```

### Analyses of the Factor B (Sleep vs NoSleep) at A1 (Evening) Simple Effect

```{r}
simpleBatEvening <- c(-1,1,0,0)
estimateContrast(FrendaSummary,contrast=simpleBatEvening)
```

```{r,Frenda-SimpleA1}
plotContrast(FrendaSummary,contrast=simpleBatEvening,labels=c("Sleep","NoSleep"),ylab="False Memory")
```

```{r}
testContrast(FrendaSummary,contrast=simpleBatEvening)
```

```{r}
standardizeContrast(FrendaSummary,contrast=simpleBatEvening)
```


### Analyses of the Factor B (Sleep vs NoSleep) at A2 (Morning) Simple Effect

```{r}
simpleBatMorning <- c(0,0,-1,1)
estimateContrast(FrendaSummary,contrast=simpleBatMorning)
```

```{r,Frenda-SimpleA2}
plotContrast(FrendaSummary,contrast=simpleBatMorning,labels=c("Sleep","NoSleep"),ylab="False Memory")
```

```{r}
testContrast(FrendaSummary,contrast=simpleBatMorning)
```

```{r}
standardizeContrast(FrendaSummary,contrast=simpleBatMorning)
```
