---
title: "Mixed Design Example with Holzel Summary Statistics"
author: "Craig A. Wendorf"
date: "2020-10-20"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Mixed Design Example with Holzel Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8",filename="render_toc.R")
```

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Mixed Design Example with Holzel Summary Statistics

### Table of Contents

```{r toc, echo=FALSE}
sourceDir <- getSrcDirectory(function(dummy) {dummy})
setwd(sourceDir)
render_toc("HolzelSummaryExample.Rmd")
```

### Data Management

Create two tables of summary statistics for the first simple effect of interest.

```{r}
PretestControl <- c(N=17,M=43.815,SD=4.910)
PosttestControl <- c(N=17,M=43.932,SD=5.507)
HolzelSummaryControl <- rbind(PretestControl,PosttestControl)
class(HolzelSummaryControl) <- "wss"

HolzelCorrControl <- declareCorrelations("PretestControl","PosttestControl")
HolzelCorrControl["PretestControl","PosttestControl"] <- .970
HolzelCorrControl <- fillCorrelations(HolzelCorrControl)
```

Create two tables of summary statistics for the second simple effect of interest.

```{r}
PretestMeditation <- c(N=16,M=43.705,SD=6.427)
PosttestMeditation <- c(N=16,M=44.666,SD=6.303)
HolzelSummaryMeditation <- rbind(PretestMeditation,PosttestMeditation)
class(HolzelSummaryMeditation) <- "wss"

HolzelCorrMeditation <- declareCorrelations("PretestMeditation","PosttestMeditation")
HolzelCorrMeditation["PretestMeditation","PosttestMeditation"] <- .993
HolzelCorrMeditation <- fillCorrelations(HolzelCorrMeditation)
```

### Analyses of the Differences within Conditions

For each subset, obtain a difference plot comparing pretest and posttest.

```{r,Holzel-Comparison}
plotMeanComparison(HolzelSummaryControl,HolzelCorrControl,main="Pretest vs Posttest for the Control Group",ylab="Gray Matter")
plotMeanComparison(HolzelSummaryMeditation,HolzelCorrMeditation,main="Pretest vs Posttest for the Meditation Group",ylab="Gray Matter")
```

Then for each subset, obtain the standardized effect size comparing pretest to posttest.

```{r}
estimateStandardizedMeanDifference(HolzelSummaryControl,HolzelCorrControl)
estimateStandardizedMeanDifference(HolzelSummaryMeditation,HolzelCorrMeditation)
```
