---
title: "OneWay (Between-Subjects) Example with Rattan Summary Statistics"
author: "Craig A. Wendorf"
date: "2020-10-20"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{OneWay (Between-Subjects) Example with Rattan Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8",filename="render_toc.R")
```

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## OneWay (Between-Subjects) Example with Rattan Summary Statistics

### Table of Contents

```{r toc, echo=FALSE}
sourceDir <- getSrcDirectory(function(dummy) {dummy})
setwd(sourceDir)
render_toc("RattanSummaryExample.Rmd")
```

### Data Management

Prior to analyses, enter a table of summary statistics.

```{r}
Comfort <- c(N=18,M=3.333,SD=1.917)
Challenge <- c(N=17,M=5.265,SD=1.448)
Control <- c(N=19,M=4.447,SD=1.433)
RattanSummary <- rbind(Comfort,Challenge,Control)
class(RattanSummary) <- "bss"
```

### Analyses of the Different Groups

With multiple groups, it is useful to get descriptive statistics and confidence intervals for each group.

```{r}
estimateMeans(RattanSummary)
```

It is also useful to view the means and confidence intervals of the groups in a plot.

```{r,Rattan-Means}
plotMeans(RattanSummary,main="Motivation as a Function of Feedback Type",ylab="Motivation")
```

### Analysis of a Group Difference

The first research question is whether there is a difference between the two non-control groups.

First, set the comparison and obtain the difference plot for that comparison.

```{r,Rattan-Comparison}
ComfortvsChallenge <- rbind(Comfort,Challenge)
class(ComfortvsChallenge) <- "bss"
plotMeanComparison(ComfortvsChallenge,main="Influence of Comfort vs Challenge Feedback on Motivation",ylab="Motivation")
```

Then, obtain the standardized effect size for that comparison.

```{r}
estimateStandardizedMeanDifference(ComfortvsChallenge)
```

### Analysis of a Group Contrast

The second research question is whether the Comfort group differs from the other two groups.

First, set the contrast and obtain a difference plot for the contrast.

```{r,Rattan-Contrast}
ComfortvsOthers <- c(-1,.5,.5)
plotMeanSubsets(RattanSummary,contrast=ComfortvsOthers,labels=c("Comfort","Others"),main="Influence of Comfort Feedback vs Other Types of Feedback on Motivation",ylab="Motivation")
```

Then, estimate the standardized contrast.

```{r}
estimateStandardizedMeanContrast(RattanSummary,contrast=ComfortvsOthers)
```
