---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "2020-06-20"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{OneWay (Between-Subjects) Example with Rattan Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8",filename="render_toc.R")
```

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## OneWay (Between-Subjects) Example with Rattan Data

### Table of Contents

```{r toc, echo=FALSE}
sourceDir <- getSrcDirectory(function(dummy) {dummy})
setwd(sourceDir)
render_toc("RattanDataExample.Rmd")
```

### Data Management

Prior to analyses, enter the data.

```{r}
Feedback <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3)
Motivation <- c(5.5,5,5.5,6,1,2.5,4.5,1,3.5,1.5,5.5,6,1.5,1,3.5,2.5,3,1,2,6,4.5,4.5,6,7,3,7,3.5,5,4.5,5.5,6.5,6,6,7,5.5,6,2.5,4.5,3.5,6,5,6,3.5,4,3,5.5,3,6,3,5,6,6.5,3.5,2)
Feedback <- factor(Feedback,levels=c(1,2,3),labels=c("Comfort","Challenge","Control"))
RattanData <- data.frame(Feedback,Motivation)
```

### Analyses of the Different Groups

With multiple groups, it is useful to get descriptive statistics and confidence intervals for each group.

```{r}
estimateMeans(Motivation~Feedback)
```

It is also useful to view the means and confidence intervals of the groups in a plot.

```{r,Rattan-Means}
plotMeans(Motivation~Feedback,main="Motivation as a Function of Feedback Type",ylab="Motivation")
```

### Analysis of a Group Difference

The first research question is whether there is a difference between the two non-control groups.

First, set the comparison and get an estimate of the difference and its confidence interval.

```{r}
Comparison <- factor(Feedback,c("Comfort","Challenge"))
estimateDifference(Motivation~Comparison)
```

Then, obtain the difference plot for that comparison.

```{r,Rattan-Difference}
plotDifference(Motivation~Comparison,main="Influence of Comfort vs Challenge Feedback on Motivation",ylab="Motivation")
```

Finally, obtain the standardized effect size for that comparison.

```{r}
standardizeDifference(Motivation~Comparison)
```

### Analysis of a Group Contrast

The second research question is whether the Comfort group differs from the other two groups.

First, set the contrast and get an estimate of the contrast and its confidence interval.

```{r}
ComfortvsOthers <- c(-1,.5,.5)
estimateContrast(Motivation~Feedback,contrast=ComfortvsOthers)
```

Then, obtain a difference plot for the contrast.

```{r,Rattan-Contrast}
plotContrast(Motivation~Feedback,contrast=ComfortvsOthers,labels=c("Comfort","Others"),main="Influence of Comfort Feedback vs Other Types of Feedback on Motivation",ylab="Motivation")
```

Finally, estimate the standardized contrast.

```{r}
standardizeContrast(Motivation~Feedback,contrast=ComfortvsOthers)
```
