---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{OneWay (Between-Subjects) Example with Rattan Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## OneWay (Between-Subjects) Example with Rattan Summary Statistics

### Enter Summary Statistics

Prior to analyses, enter a table of summary statistics.

```{r}
Comfort <- c(N=18,M=3.333,SD=1.917)
Challenge <- c(N=17,M=5.265,SD=1.448)
Control <- c(N=19,M=4.447,SD=1.433)
RattanSummary <- rbind(Comfort,Challenge,Control)
class(RattanSummary) <- "bss"
```

### Analyses of the Different Groups

With multiple groups, it is useful to get descriptive statistics and confidence intervals for each group.

```{r}
estimateMeans(RattanSummary)
```

It is also useful to view the means and confidence intervals of the groups in a plot.

```{r,Rattan-Means}
plotMeans(RattanSummary,ylab="Motivation")
```

### Analysis of a Group Difference

The first research question is whether there is a difference between the two non-control groups.

First, set the comparison and get an estimate of the difference and its confidence interval.

```{r}
ComfortvsChallenge <- rbind(Comfort,Challenge)
class(ComfortvsChallenge) <- "bss"
estimateDifference(ComfortvsChallenge)
```

Then, obtain the difference plot for that comparison.

```{r,Rattan-Difference}
plotDifference(ComfortvsChallenge,ylab="Motivation")
```

Finally, obtain the standardized effect size for that comparison.

```{r}
standardizeDifference(ComfortvsChallenge)
```

### Analysis of a Group Contrast

The second research question is whether the Comfort group differs from the other two groups.

First, set the contrast and get an estimate of the contrast and its confidence interval.

```{r}
ComfortvsOthers <- c(-1,.5,.5)
estimateContrast(RattanSummary,contrast=ComfortvsOthers)
```

Then, obtain a difference plot for the contrast.

```{r,Rattan-Contrast}
plotContrast(RattanSummary,contrast=ComfortvsOthers,labels=c("Comfort","Others"),ylab="Motivation")
```

Finally, estimate the standardized contrast.

```{r}
standardizeContrast(RattanSummary,contrast=ComfortvsOthers)
```
