---
title: "Paired Samples Example with Thomason Summary Statistics"
author: "Craig A. Wendorf"
date: "2020-10-20"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Paired Samples Example with Thomason Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8",filename="render_toc.R")
```

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Paired Samples Example with Thomason Summary Statistics

### Table of Contents

```{r toc, echo=FALSE}
sourceDir <- getSrcDirectory(function(dummy) {dummy})
setwd(sourceDir)
render_toc("ThomasonSummaryExample.Rmd")
```

### Thomason1 Example

Thomason1 focuses on the difference between pretest and postest in the first sample. First, create the tables of summary statistics.

```{r}
Pretest <- c(N=12,M=11.583,SD=3.315)
Posttest <- c(N=12,M=13.250,SD=2.896)
Thomason1Summary <- rbind(Pretest,Posttest)
class(Thomason1Summary) <- "wss"
Thomason1Corr <- data.frame()
Thomason1Corr["Pretest","Posttest"] <- .892
```

The primary emphasis of the analysis is to estimate and represent the difference between the two conditions.

```{r,Thomason1-Comparison}
plotMeanComparison(Thomason1Summary,Thomason1Corr,main="LSAT Score Before and After Mapping",ylab="LSAT Score")
```

The secondary emphasis of the analysis is provide a standardized effect size for the difference.

```{r}
estimateStandardizedMeanDifference(Thomason1Summary,Thomason1Corr)
```

### Thomason2 Example

Thomason2 focuses on the difference between pretest and postest in the second sample. Thus, create the tables of summary statistics.

```{r}
Pretest <- c(N=16,M=12.875,SD=3.403)
Posttest <- c(N=16,M=14.250,SD=4.282)
Thomason2Summary <- rbind(Pretest,Posttest)
class(Thomason2Summary) <- "wss"
Thomason2Corr <- data.frame()
Thomason2Corr["Pretest","Posttest"] <- .871
```

The primary emphasis of the analysis is to estimate and represent the difference between the two conditions.

```{r,Thomason2-Comparison}
plotMeanComparison(Thomason2Summary,Thomason2Corr,main="LSAT Score Before and After Mapping",ylab="LSAT Score")
```

The secondary emphasis of the analysis is provide a standardized effect size for the difference.

```{r}
estimateStandardizedMeanDifference(Thomason2Summary,Thomason2Corr)
```

### Thomason3 Example

Thomason3 focuses on the difference between pretest and postest in the third sample. Thus, create the tables of summary statistics.

```{r}
Pretest <- c(N=39,M=67.410,SD=7.419)
Posttest <- c(N=39,M=71.769,SD=5.851)
Thomason3Summary <- rbind(Pretest,Posttest)
class(Thomason3Summary) <- "wss"
Thomason3Corr <- data.frame()
Thomason3Corr["Pretest","Posttest"] <- .601
```

The primary emphasis of the analysis is to estimate and represent the difference between the two conditions.

```{r,Thomason3-Comparison}
plotMeanComparison(Thomason3Summary,Thomason3Corr,main="LSAT Score Before and After Mapping",ylab="LSAT Score")
```

The secondary emphasis of the analysis is provide a standardized effect size for the difference.

```{r}
estimateStandardizedMeanDifference(Thomason3Summary,Thomason3Corr)
```
