---
title: "Bivariate Regression Summary Statistics Example"
output:
  github_document:
    preserve_yaml: FALSE
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page analyzes bivariate regression models using summary statistics input.

## Data Management

### Data Entry

This code inputs the variable summaries and creates a summary table.
```{r}
Predictor <- c(N = 10, M = 8.000, SD = 1.414)
Criterion <- c(N = 10, M = 11.000, SD = 2.211)
BivariateSummary <- construct(Predictor, Criterion, class = "wss")
```

This code creates a correlation matrix.
```{r}
Predictor <- c(1.000, .533)
Criterion <- c(.533, 1.000)
BivariateCorr <- construct(Predictor, Criterion, class = "corr")
```

### Summary Statistics

This code confirms the descriptive statistics from the summary tables.
```{r}
(BivariateSummary) |> describeSummary()
(BivariateCorr) |> describeCorrelations()
```

## Analyses of Overall Model

This section produces analyses of the overall regression model.

This code will produce a source table associated with the regression model.
```{r}
(BivariateSummary) |> describeModel(BivariateCorr)
```

### Confidence Interval

This code will produce the confidence interval for R Squared.
```{r}
(BivariateSummary) |> estimateModel(BivariateCorr)
```

The code defaults to 90% confidence intervals. This can be changed if desired.
```{r}
(BivariateSummary) |> estimateModel(BivariateCorr, conf.level = .95)
```

### Significance Test

This code will calculate NHST for the regression model.
```{r}
(BivariateSummary) |> testModel(BivariateCorr)
```

## Analyses of the Regression Coefficients

This section analyses the regression coefficients obtained from the overall model.

### Confidence Intervals 

This code will provide a table of confidence intervals for each of the regression coefficients.
```{r}
(BivariateSummary) |> estimateCoefficients(BivariateCorr)
```

This code will produce a graph of the confidence intervals for each of the regression coefficients.
```{r, Bivariate-Summary-CoefficientsA}
(BivariateSummary) |> plotCoefficients(BivariateCorr)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(BivariateSummary) |> estimateCoefficients(BivariateCorr, conf.level = .99)
```

For the graph, it is possible to plot just coefficients for the predictors (minus the intercept) in addition to changing the confidence level. A comparison line and region of practical equivalence can also be added.
```{r, Bivariate-Summary-CoefficientsB}
(BivariateSummary) |> plotCoefficients(BivariateCorr, conf.level = .99, line = 0, rope = c(-.5, .5), intercept = FALSE)
```

### Significance Tests

This code will produce a table of NHST separately for each of the regression coefficients. In this case, all the coefficients are tested against a value of zero.
```{r}
(BivariateSummary) |> testCoefficients(BivariateCorr)
```

### Standardized Coefficient

This code will provide a table of confidence intervals for the standardized coefficient.
```{r}
(BivariateSummary) |> standardizeCoefficients(BivariateCorr)
```

As in other places, the code defaults to a 95% confidence interval. This can be changed if desired.
```{r}
(BivariateSummary) |> standardizeCoefficients(BivariateCorr, conf.level = .99)
```

## Analyses of Regression Values

This section provides analyses of individual predicted values.

### Regression Line

This code produces a plot of the regression line (with confidence and prediction intervals suppressed).
```{r, Bivariate-Summary-LineA}
(BivariateSummary) |> plotRegression(BivariateCorr, interval = "none")
```

### Confidence and Prediction Intervals

This code provides estimates confidence and prediction limits for a specific value of the Predictor (value=4).
```{r}
(BivariateSummary) |> estimateRegression(BivariateCorr, value = 8)
```

This code plots the confidence interval associated with the regression line and labels the interval for the specific value of the Predictor.
```{r, Bivariate-Summary-ConfidenceA}
(BivariateSummary) |> plotRegression(BivariateCorr, value = 8, interval = "confidence")
```

This code plots the prediction interval associated with the regression line and labels the interval for the specific value of the Predictor.
```{r, Bivariate-Summary-ConfidenceB}
(BivariateSummary) |> plotRegression(BivariateCorr, value = 8, interval = "prediction")
```
