---
title: "Bivariate Regression Data Example"
description: >
  This page analyzes bivariate regression models using raw data input.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page analyzes bivariate regression models using raw data input.

## Preliminary Tasks

### Data Entry

This code inputs the variable names and creates a viewable data frame. Note that analyses assume that the second variable is the criterion and the first variable the predictors.
```{r}
Predictor <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7)
Criterion <- c(7, 13, 11, 10, 13, 8, 11, 14, 12, 11)
BivariateData <- construct(Predictor, Criterion)
```

### Summary Statistics

This code obtains the descriptive statistics for the data frame.
```{r}
(BivariateData) |> describeSummary()
(BivariateData) |> describeCorrelations()
```

## Analyses of the Overall Model

This section produces analyses of the overall regression model.

This code will produce a source table associated with the regression model.
```{r}
(BivariateData) |> describeModel()
```

### Confidence Interval

This code will produce the confidence interval for R Squared.
```{r}
(BivariateData) |> estimateModel()
```

The code defaults to 90% confidence intervals. This can be changed if desired.
```{r}
(BivariateData) |> estimateModel(conf.level = .95)
```

### Significance Test

This code will calculate NHST for the regression model.
```{r}
(BivariateData) |> testModel()
```

## Analyses of the Regression Coefficients

This section analyses the regression coefficients obtained from the overall model.

### Confidence Intervals 

This code will provide a table of confidence intervals for each of the regression coefficients.
```{r}
(BivariateData) |> estimateCoefficients()
```

This code will produce a graph of the confidence intervals for each of the regression coefficients.
```{r, Bivariate-Data-CoefficientsA}
(BivariateData) |> plotCoefficients()
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(BivariateData) |> estimateCoefficients(conf.level = .99)
```

For the graph, it is possible to plot just coefficients for the predictors (minus the intercept) in addition to changing the confidence level. A comparison line and region of practical equivalence can also be added.
```{r, Bivariate-Data-CoefficientsB}
(BivariateData) |> plotCoefficients(conf.level = .99, line = 0, rope = c(-.5, .5), intercept = FALSE)
```

### Significance Tests

This code will produce a table of NHST separately for each of the regression coefficients. In this case, all the coefficients are tested against a value of zero.
```{r}
(BivariateData) |> testCoefficients()
```

### Standardized Coefficient

This code will provide a table of confidence intervals for the standardized coefficient.
```{r}
(BivariateData) |> standardizeCoefficients()
```

As in other places, the code defaults to a 95% confidence interval. This can be changed if desired.
```{r}
(BivariateData) |> standardizeCoefficients(conf.level = .99)
```

## Analyses of Regression Values

This section provides analyses of individual predicted values.

### Regression Line

This code produces a plot of the regression line (with confidence and prediction intervals suppressed).
```{r, Bivariate-Data-LineA}
(BivariateData) |> plotRegression(interval = "none")
```

This code adds a scatter of data points to the regression plot.
```{r, Bivariate-Data-LineB}
(BivariateData) |> plotRegression(interval = "none", points = TRUE)
```

### Confidence and Prediction Intervals

This code provides estimates confidence and prediction limits for a specific value of the Predictor (value=4).
```{r}
(BivariateData) |> estimateRegression(value = 8)
```

This code plots the confidence interval associated with the regression line and labels the interval for the specific value of the Predictor.
```{r, Bivariate-Data-ConfidenceA}
(BivariateData) |> plotRegression(value = 8, interval = "confidence")
```

This code plots the prediction interval associated with the regression line and labels the interval for the specific value of the Predictor.
```{r, Bivariate-Data-ConfidenceB}
(BivariateData) |> plotRegression(value = 8, interval = "prediction")
```
