---
title: "Complex Repeated Measures Data Application"
description: >
  This page analyzes differences between two contrasts on the same measures using repeated-measures (within-subjects) data.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page analyzes differences between two contrasts on the same measures using repeated-measures (within-subjects) data.

## Data Management

This code inputs the variable names and creates a viewable data frame.
```{r}
Outcome1 <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7)
Outcome2 <- c(7, 13, 11, 10, 13, 8, 11, 14, 12, 11)
Outcome3 <- c(9, 16, 11, 12, 15, 13, 9, 14, 11, 10)
RepeatedData <- construct(Outcome1, Outcome2, Outcome3)
```

## Analyses of a Complex Contrast of Means

Estimate and plot the means for examination.
```{r, Complex-Repeated-Means}
(RepeatedData) |> estimateMeans()
(RepeatedData) |> plotMeans()
```

Create a single contrast to compare the first variable to the grand mean (which requires some arithmetic). Then esimate and plot the contrast.
```{r, Complex-Repeated-Contrast}
(RepeatedData) |> estimateContrast(contrast = c(2/3, -1/3, -1/3))
(RepeatedData) |> plotContrast(contrast = c(2/3, -1/3, -1/3))
```

## Analysis of a Difference Between Two Contrasts

Rather than setting just one contrast, set two contrasts: one for the Grand Mean and one for Level 1. Estimate and plot the confidence intervals for each contrast and the difference between contrasts.
```{r, Complex-Repeated-ComplexA}
(RepeatedData) |> estimateComplex(contrast1 = c(1/3, 1/3, 1/3), contrast2 = c(1, 0, 0), labels = c("GrandMean", "O1Only"))
(RepeatedData) |> plotComplex(contrast1 = c(1/3, 1/3, 1/3), contrast2 = c(1, 0, 0), labels = c("GrandMean", "O1Only"))
```

Enhance the plot by adding colors and removing value labels.
```{r, Complex-Repeated-ComplexB}
(RepeatedData) |> plotComplex(contrast1 = c(1/3, 1/3, 1/3), contrast2 = c(1, 0, 0), labels = c("GrandMean", "O1Only"), values = FALSE, col = c("darkred", "darkblue", "black"))
```
