---
title: "Effects Mixed Data Application"
description: >
  This page analyzes simple effects using mixed design (between-subjects and within-subjects) data.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page analyzes simple effects using mixed design (between-subjects and within-subjects) data.

## Data Management

This code inputs the variable names and creates a viewable data frame.
```{r}
Factor <- c(rep(1, 10), rep(2, 10))
Factor <- factor(Factor, levels = c(1, 2), labels = c("Level1", "Level2"))
Outcome1 <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7, 5, 9, 10, 9, 11, 4, 11, 7, 6, 8)
Outcome2 <- c(7, 13, 11, 10, 13, 8, 11, 14, 12, 11, 7, 8, 7, 11, 10, 7, 8, 4, 8, 10)
Outcome3 <- c(9, 16, 11, 12, 15, 13, 9, 14, 11, 10, 8, 6, 8, 11, 5, 7, 9, 3, 6, 7)
MixedData <- construct(Factor, Outcome1, Outcome2, Outcome3)
```

## Analyses of the Simple Effects

Get an ANOVA separately for each simple effect.
```{r}
construct(Outcome1, Outcome2, Outcome3) |> describeEffectBy(by = Factor)
construct(Outcome1, Outcome2, Outcome3) |> estimateEffectBy(by = Factor)
construct(Outcome1, Outcome2, Outcome3) |> testEffectBy(by = Factor)
```

## Summary Statistics

Get the summary statistics separately within each simple effect.
```{r}
construct(Outcome1, Outcome2, Outcome3) |> describeSummaryBy(by = Factor)
```

Estimate, plot, test, and standardize the means separately within each simple effect.
```{r, Effects-Mixed-Means}
construct(Outcome1, Outcome2, Outcome3) |> estimateMeansBy(by = Factor)
construct(Outcome1, Outcome2, Outcome3) |> plotMeansBy(by = Factor)
construct(Outcome1, Outcome2, Outcome3) |> testMeansBy(by = Factor)
construct(Outcome1, Outcome2, Outcome3) |> standardizeMeansBy(by = Factor)
```

## Analyses of a Comparison

Analyze the specified comparison separately within each simple effect.
```{r, Effects-Mixed-Comparison}
construct(Outcome1, Outcome2) |> estimateDifferenceBy(by = Factor)
construct(Outcome1, Outcome2) |> plotDifferenceBy(by = Factor)
construct(Outcome1, Outcome2) |> testDifferenceBy(by = Factor)
construct(Outcome1, Outcome2) |> standardizeDifferenceBy(by = Factor)
```

## Analyses of a Contrast

Analyze the specified contrast separately within each simple effect.
```{r, Effects-Mixed-Contrast}
construct(Outcome1, Outcome2, Outcome3) |> estimateContrastBy(by = Factor, contrast = c(-1, .5, .5))
construct(Outcome1, Outcome2, Outcome3) |> plotContrastBy(by = Factor, contrast = c(-1, .5, .5))
construct(Outcome1, Outcome2, Outcome3) |> testContrastBy(by = Factor, contrast = c(-1, .5, .5))
construct(Outcome1, Outcome2, Outcome3) |> standardizeContrastBy(by = Factor, contrast = c(-1, .5, .5))
```
