---
title: "Effects Factorial Data Application"
description: >
  This page analyzes simple effects using factorial (between-subjects) data.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page analyzes simple effects using factorial (between-subjects) data.

## Data Management

This code inputs the variable names and creates a viewable data frame.
```{r}
FactorA <- c(rep(1, 20), rep(2, 20), rep(3, 20))
FactorA <- factor(FactorA, levels = c(1, 2, 3), labels = c("A1", "A2", "A3"))
FactorB <- c(rep(1, 10), rep(2, 10), rep(1, 10), rep(2, 10), rep(1, 10), rep(2, 10))
FactorB <- factor(FactorB, levels = c(1, 2), labels = c("B1", "B2"))
Outcome <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7, 5, 9, 10, 9, 11, 4, 11, 7, 6, 8, 7, 13, 11, 10, 13, 8, 11, 14, 12, 11, 7, 8, 7, 11, 10, 7, 8, 4, 8, 10, 9, 16, 11, 12, 15, 13, 9, 14, 11, 10, 8, 6, 8, 11, 5, 7, 9, 3, 6, 7)
FactorialData <- construct(FactorA, FactorB, Outcome)
```

## Analyses of Simple Effects

Get an ANOVA separately for each simple effect.
```{r}
(Outcome ~ FactorA) |> describeEffectBy(by = FactorB)
(Outcome ~ FactorA) |> estimateEffectBy(by = FactorB)
(Outcome ~ FactorA) |> testEffectBy(by = FactorB)
```

## Analyses of the Means

Get the summary statistics separately within each simple effect.
```{r}
(Outcome ~ FactorA) |> describeSummaryBy(by = FactorB)
```

Estimate, plot, test, and standardize the means separately within each simple effect.
```{r, Effects-Factorial-Means}
(Outcome ~ FactorA) |> estimateMeansBy(by = FactorB)
(Outcome ~ FactorA) |> plotMeansBy(by = FactorB)
(Outcome ~ FactorA) |> testMeansBy(by = FactorB)
(Outcome ~ FactorA) |> standardizeMeansBy(by = FactorB)
```

## Analyses of a Comparison

Analyze the specified comparison separately within each simple effect.
```{r, Effects-Factorial-Comparison}
(Outcome ~ FactorA) |> focus(A1, A2) |> estimateDifferenceBy(by = FactorB)
(Outcome ~ FactorA) |> focus(A1, A2) |> plotDifferenceBy(by = FactorB)
(Outcome ~ FactorA) |> focus(A1, A2) |> testDifferenceBy(by = FactorB)
(Outcome ~ FactorA) |> focus(A1, A2) |> standardizeDifferenceBy(by = FactorB)
```

## Analyses of a Contrast

Analyze the specified contrast separately within each simple effect.
```{r, Effects-Factorial-Contrast}
(Outcome ~ FactorA) |> estimateContrastBy(by = FactorB, contrast = c(-1, .5, .5))
(Outcome ~ FactorA) |> plotContrastBy(by = FactorB, contrast = c(-1, .5, .5))
(Outcome ~ FactorA) |> testContrastBy(by = FactorB, contrast = c(-1, .5, .5))
(Outcome ~ FactorA) |> standardizeContrastBy(by = FactorB, contrast = c(-1, .5, .5))
```
