---
title: "Exploratory OneWay Data Application"
description: >
  This page utilizes advanced methods to build plots that combine various elements using one-way (between-subjects) data.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page utilizes advanced methods to build plots that combine various elements using one-way (between-subjects) data.

## Data Management

This code inputs the variable names and creates a viewable data frame.
```{r}
Factor <- c(rep(1, 10), rep(2, 10), rep(3, 10))
Factor <- factor(Factor, levels = c(1, 2, 3), labels = c("Level1", "Level2", "Level3"))
Outcome <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7, 7, 13, 11, 10, 13, 8, 11, 14, 12, 11, 9, 16, 11, 12, 15, 13, 9, 14, 11, 10)
OneWayData <- construct(Factor, Outcome)
```

## Building Layers

The typical way to build a plot is to use separate calls for each plotting elements (e.g., data, boxplots) and using the "add" argument to put them on the same plot.
```{r, Exploratory-OneWay-Traditional}
(Outcome ~ Factor) |> plotData()
(Outcome ~ Factor) |> plotBoxes(add = TRUE)
```

This can be simplified by using an "add" version of the function call instead of using the longer "add" argument for the function call.
```{r, Exploratory-OneWay-Add}
(Outcome ~ Factor) |> plotData()
(Outcome ~ Factor) |> addBoxes()
```

Rather than separate lines for function calls, all plotting elements have passthrough capabilities that allow the them to be placed on the same line.
```{r, Exploratory-OneWay-Passthrough}
(Outcome ~ Factor) |> plotData() |> addBoxes()
```

## Common Layered Plots

Obtain violin plots using one call (and enhance the plot).
```{r, Exploratory-OneWay-Violins}
(Outcome ~ Factor) |> plotViolins(col = c("darkred", "darkblue", "darkgoldenrod"))
```

Obtain bean plots using one call (and enhance the plot).
```{r, Exploratory-OneWay-Beans}
(Outcome ~ Factor) |> plotBeans(col = c("darkred", "darkblue", "darkgoldenrod"))
```

Obtain raincloud plots using one call (and enhance the plot).
```{r, Exploratory-OneWay-Rainclouds}
(Outcome ~ Factor) |> plotRainclouds(col = c("darkred", "darkblue", "darkgoldenrod"))
```
