---
title: "Factorial Traditional Summary Example"
description: >
  This page examines a two-factor between-subjects (factorial) design using summary statistics input, focusing on omnibus and simple effects analyses.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page examines a two-factor between-subjects (factorial) design using summary statistics input, focusing on omnibus and simple effects analyses.

## Preliminary Tasks

### Data Entry

This code inputs the group summaries and creates a single summary table
```{r}
A1 <- c(N = 10, M = 8.000, SD = 1.414)
A2 <- c(N = 10, M = 11.000, SD = 2.211)
A3 <- c(N = 10, M = 12.000, SD = 2.449)
FactorialSummaryB1 <- construct(A1, A2, A3, class = "bss")
A1 <- c(N = 10, M = 8.000, SD = 2.449)
A2 <- c(N = 10, M = 8.000, SD = 2.000)
A3 <- c(N = 10, M = 7.000, SD = 2.211)
FactorialSummaryB2 <- construct(A1, A2, A3, class = "bss")
FactorialSummary <- combine(B1 = FactorialSummaryB1, B2 = FactorialSummaryB2, class = "bss")
```

### Summary Statistics

This code confirms the descriptive statistics from the summary tables.
```{r}
(FactorialSummary) |> describeSummary()
```

Plot the means and their confidence intervals for the design as a whole.
```{r, Factorial-Summary-Omnibus}
(FactorialSummary) |> plotFactorial(col = c("darkred", "darkblue"))
legend("topleft", inset = .01, box.lty = 0, pch = 16, legend = c("B1", "B2"), col = c("darkred", "darkblue"))
```

## Analyses of the Omnibus Effects

The omnibus analysis usually consists of an Analysis of Variance.

### Source Table

Get the source table associated with the main effects and the interaction.
```{r}
(FactorialSummary) |> describeFactorial()
```

### Proportion of Variance Accounted For

Get estimates of the proportion of variance accounted for by each effect (along with their confidence intervals).
```{r}
(FactorialSummary) |> estimateFactorial()
```

### Significance Tests

Finally, test the various effects for statistical significance.
```{r}
(FactorialSummary) |> testFactorial()
```

## Analyses of the Simple Effects

As a follow-up to an Analysis of Variance, it is cusotmary to examine the simple effects (essentially a single-factor ANOVA separately across the levels of another factor).

### Source Table

Get the source tables separately for the simple effects.
```{r}
(FactorialSummary) |> describeEffectBy()
```

### Proportion of Variance Accounted For

Get an estimate of the proportion of variance account for by the simple effect (and the confidence interval for that estimate).
```{r}
(FactorialSummary) |> estimateEffectBy()
```

### Significance Tests

Finally, test the simple effects for statistical significance.
```{r}
(FactorialSummary) |> testEffectBy()
```
