---
title: "Factorial Traditional Data Example"
description: >
  This page examines a two-factor between-subjects (factorial) design using raw data input, focusing on omnibus and simple effects analyses.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page examines a two-factor between-subjects (factorial) design using raw data input, focusing on omnibus and simple effects analyses.

## Data Management

This code inputs the variable names and creates a viewable data frame.
```{r}
FactorA <- c(rep(1, 20), rep(2, 20), rep(3, 20))
FactorA <- factor(FactorA, levels = c(1, 2, 3), labels = c("A1", "A2", "A3"))
FactorB <- c(rep(1, 10), rep(2, 10), rep(1, 10), rep(2, 10), rep(1, 10), rep(2, 10))
FactorB <- factor(FactorB, levels = c(1, 2), labels = c("B1", "B2"))
Outcome <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7, 5, 9, 10, 9, 11, 4, 11, 7, 6, 8, 7, 13, 11, 10, 13, 8, 11, 14, 12, 11, 7, 8, 7, 11, 10, 7, 8, 4, 8, 10, 9, 16, 11, 12, 15, 13, 9, 14, 11, 10, 8, 6, 8, 11, 5, 7, 9, 3, 6, 7)
FactorialData <- construct(FactorA, FactorB, Outcome)
```

This code provides a table of summary statistics.
```{r}
(Outcome ~ FactorA) |> describeSummaryBy(by = FactorB)
```

## Analyses of the Omnibus Effects

Get an ANOVA for the design as a whole, including a source table, an estimate of the proportion of variance accounted for, and an ANOVA test of the main effects and interaction.
```{r}
(Outcome ~ FactorA) |> describeFactorial(by = FactorB)
(Outcome ~ FactorA) |> estimateFactorial(by = FactorB)
(Outcome ~ FactorA) |> testFactorial(by = FactorB)
```

Plot the means and confidence intervals for the design as a whole.
```{r, Interaction-Factorial-Omnibus}
(Outcome ~ FactorA) |> plotFactorial(by = FactorB, col = c("darkred", "darkblue"))
legend("topleft", inset = .01, box.lty = 0, pch = 16, legend = c("B1", "B2"), col = c("darkred", "darkblue"))
```

## Analyses of the Simple Effects

Obtain a source table, estimate of proportion of variance accounted for, and an ANOVA test of statistical significance for the simple effect of FactorA (separately for the levels of FactorB).
```{r}
(Outcome ~ FactorA) |> describeEffectBy(by = FactorB)
(Outcome ~ FactorA) |> estimateEffectBy(by = FactorB)
(Outcome ~ FactorA) |> testEffectBy(by = FactorB)
```
