---
title: "Factorial Traditional Summary Example"
description: >
  This page examines a two-factor between-subjects (factorial) design using summary statistics input, focusing on omnibus and simple effects analyses.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page examines a two-factor between-subjects (factorial) design using summary statistics input, focusing on omnibus and simple effects analyses.

## Data Management

This code inputs the group summaries and creates a single summary table
```{r}
A1 <- c(N = 10, M = 8.000, SD = 1.414)
A2 <- c(N = 10, M = 11.000, SD = 2.211)
A3 <- c(N = 10, M = 12.000, SD = 2.449)
FactorialSummaryB1 <- construct(A1, A2, A3, class = "bss")
A1 <- c(N = 10, M = 8.000, SD = 2.449)
A2 <- c(N = 10, M = 8.000, SD = 2.000)
A3 <- c(N = 10, M = 7.000, SD = 2.211)
FactorialSummaryB2 <- construct(A1, A2, A3, class = "bss")
FactorialSummary <- combine(B1 = FactorialSummaryB1, B2 = FactorialSummaryB2, class = "bss")
```

This code confirms the descriptive statistics from the summary tables.
```{r}
(FactorialSummary) |> describeSummary()
```

## Analyses of the Omnibus Effects

Get an ANOVA for the design as a whole, including a source table, an estimate of the proportion of variance accounted for, and an ANOVA test of the main effects and interaction.
```{r}
(FactorialSummary) |> describeFactorial()
(FactorialSummary) |> estimateFactorial()
(FactorialSummary) |> testFactorial()
```

Plot the means and confidence intervals for the design as a whole.
```{r, Interaction-Factorial-Omnibus}
(FactorialSummary) |> plotFactorial(col = c("darkred", "darkblue"))
legend("topleft", inset = .01, box.lty = 0, pch = 16, legend = c("B1", "B2"), col = c("darkred", "darkblue"))
```

## Analyses of the Simple Effects

Obtain a source table, estimate of proportion of variance accounted for, and an ANOVA test of statistical significance for the simple effect of FactorA (separately for the levels of FactorB).
```{r}
(FactorialSummary) |> describeEffectBy()
(FactorialSummary) |> estimateEffectBy()
(FactorialSummary) |> testEffectBy()
```
