---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Factorial (Between-Subjects) Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Factorial (Between-Subjects) Tutorial with Summary Statistics

### Enter Summary Statistics

This code inputs the group summaries and creates a single summary table (for the first simple effect).
```{r}
A1 <- c(N=4,M=2.000,SD=2.449)
A2 <- c(N=4,M=6.000,SD=2.449)
A3 <- c(N=4,M=7.000,SD=2.449)
FactorialSummaryB1 <- rbind(A1,A2,A3)
class(FactorialSummaryB1) <- "bss"
```

And repeat the process to create the second subset.
```{r}
A1 <- c(N=4,M=4.000,SD=2.449)
A2 <- c(N=4,M=4.000,SD=2.449)
A3 <- c(N=4,M=5.000,SD=2.449)
FactorialSummaryB2 <- rbind(A1,A2,A3)
class(FactorialSummaryB2) <- "bss"
```

### Analyses of the Means

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

#### Confidence Intervals for the Means

This code will provide tables of confidence intervals for each level of the factor.
```{r}
estimateMeans(FactorialSummaryB1)
estimateMeans(FactorialSummaryB2)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateMeans(FactorialSummaryB1,conf.level=.99)
estimateMeans(FactorialSummaryB2,conf.level=.99)
```

#### Plot of the Confidence Intervals for the Means

This code will produce a graph of the confidence intervals for each level of the factor.
```{r,Factorial-MeansA}
plotMeans(FactorialSummaryB1)
plotMeans(FactorialSummaryB2)
```

Of course, it is possible to change from the default confidence level. Additionally, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence.
```{r,Factorial-MeansB}
plotMeans(FactorialSummaryB1,conf.level=.99,mu=5,rope=c(3,7))
plotMeans(FactorialSummaryB2,conf.level=.99,mu=5,rope=c(3,7))
```

#### Significance Tests for the Means

This code will produce a table of NHST separately for each level of the factor. In this case, all the means are tested against a value of zero.
```{r}
testMeans(FactorialSummaryB1)
testMeans(FactorialSummaryB2)
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
testMeans(FactorialSummaryB1,mu=5)
testMeans(FactorialSummaryB2,mu=5)
```

#### Effect Size for the Means

This code will produce a table of standardized mean differences separately for each level of the factor. In this case, the mean is compared to zero to form the effect size.
```{r}
standardizeMeans(FactorialSummaryB1)
standardizeMeans(FactorialSummaryB2)
```

Here too it is possible to alter the width of the confidence intervals and to establish a more plausible comparison value for the effect size.
```{r}
standardizeMeans(FactorialSummaryB1,mu=5,conf.level=.99)
standardizeMeans(FactorialSummaryB2,mu=5,conf.level=.99)
```

### Analyses of a Comparison

This section produces analyses that are equivalent to comparisons of two levels of a factor.

This code creates a new factor that identifies the two levels for comparison.
```{r}
CompSummaryB1 <- FactorialSummaryB1[c("A1","A2"),]
class(CompSummaryB1) <- "bss"
CompSummaryB2 <- FactorialSummaryB2[c("A1","A2"),]
class(CompSummaryB2) <- "bss"
```

#### Confidence Interval for a Mean Difference

This code estimates the confidence interval of the difference.
```{r}
estimateDifference(CompSummaryB1)
estimateDifference(CompSummaryB2)
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
estimateDifference(CompSummaryB1,conf.level=.99)
estimateDifference(CompSummaryB2,conf.level=.99)
```

#### Plot of the Confidence Interval for the Mean Difference

This code obtains and plots the confidence intervals for the groups and the mean difference in the identified comparison.
```{r,Factorial-DifferenceA}
plotDifference(CompSummaryB1)
plotDifference(CompSummaryB2)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added.
```{r,Factorial-DifferenceB}
plotDifference(CompSummaryB1,conf.level=.99,rope=c(-2,2))
plotDifference(CompSummaryB2,conf.level=.99,rope=c(-2,2))
```

#### Significance Test of the Mean Difference

This code produces NHST for the identified comparison (using a default test value of zero).
```{r}
testDifference(CompSummaryB1)
testDifference(CompSummaryB2)
```

If the default value of zero is not plausible, it too can be changed.
```{r}
testDifference(CompSummaryB1,mu=-2)
testDifference(CompSummaryB2,mu=-2)
```

#### Effect Size for the Mean Difference

This code calculates a standardized mean difference for the comparison and its confidence interval.
```{r}
standardizeDifference(CompSummaryB1)
standardizeDifference(CompSummaryB2)
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
standardizeDifference(CompSummaryB1,conf.level=.99)
standardizeDifference(CompSummaryB2,conf.level=.99)
```

### Analyses of a Contrast

This section produces analyses that are equivalent to analyses involving multiple levels of a factor.

This code identifies a contrast among the groups.
```{r}
A1vsOthers <- c(-1,.5,.5)
```

#### Confidence Interval for a Contrast

This code produces a confidence interval for that contrast.
```{r}
estimateContrast(FactorialSummaryB1,contrast=A1vsOthers)
estimateContrast(FactorialSummaryB2,contrast=A1vsOthers)
```

As in all other cases, the default value of the confidence interval can be changed.
```{r}
estimateContrast(FactorialSummaryB1,contrast=A1vsOthers,conf.level=.99)
estimateContrast(FactorialSummaryB2,contrast=A1vsOthers,conf.level=.99)
```

#### Plots of Confidence Intervals for a Contrast

This code obtains and plots the confidence intervals for the groups and the mean difference in the identified contrast.
```{r,Factorial-ContrastA}
plotContrast(FactorialSummaryB1,contrast=A1vsOthers)
plotContrast(FactorialSummaryB2,contrast=A1vsOthers)
```

The width of the confidence interval for the contrast can be altered and a region of practical equivalence can be added.
```{r,Factorial-ContrastB}
plotContrast(FactorialSummaryB1,contrast=A1vsOthers,labels=c("A1","Others"),conf.level=.99,rope=c(-2,2))
plotContrast(FactorialSummaryB2,contrast=A1vsOthers,labels=c("A1","Others"),conf.level=.99,rope=c(-2,2))
```

#### Significance Test for a Contrast

This code produces a NHST for the identified contrast. It tests the contrast against a value of zero by default.
```{r}
testContrast(FactorialSummaryB1,contrast=A1vsOthers)
testContrast(FactorialSummaryB2,contrast=A1vsOthers)
```

If desired, the contrast can be tested against other values.
```{r}
testContrast(FactorialSummaryB1,contrast=A1vsOthers,mu=4)
testContrast(FactorialSummaryB2,contrast=A1vsOthers,mu=4)
```

#### Effect Size for a Contrast

This code calculates a standardized contrast and its confidence interval.
```{r}
standardizeContrast(FactorialSummaryB1,contrast=A1vsOthers)
standardizeContrast(FactorialSummaryB2,contrast=A1vsOthers)
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
standardizeContrast(FactorialSummaryB1,contrast=A1vsOthers,conf.level=.99)
standardizeContrast(FactorialSummaryB2,contrast=A1vsOthers,conf.level=.99)
```

### Analyses of the Pairwise Comparisons

This section provides analyses of all possible pairwise comparisons among the levels of the factor.

#### Confidence Intervals for the Pairwise Comparisons

This code will provide a table of descriptive statistics and confidence intervals for each pairwise comparison.

```{r}
estimatePairwise(FactorialSummaryB1)
estimatePairwise(FactorialSummaryB2)
```

The code defaults to 95% confidence intervals. This can be changed if desired.

```{r}
estimatePairwise(FactorialSummaryB1,conf.level=.99)
estimatePairwise(FactorialSummaryB2,conf.level=.99)
```

#### Plots of the Confidence Intervals for the Pairwise Comparisons

This code will produce a graph of the confidence intervals for each of the pairwise comparisons.

```{r,Factorial-PairwiseA}
plotPairwise(FactorialSummaryB1)
plotPairwise(FactorialSummaryB2)
```

Of course, it is possible to change from the default confidence level. Additionally, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence.

```{r,Factorial-PairwiseB}
plotPairwise(FactorialSummaryB1,mu=-2,conf.level=.99,rope=c(-4,0))
plotPairwise(FactorialSummaryB2,mu=-2,conf.level=.99,rope=c(-4,0))
```

#### Significance Tests of the Pairwise Comparisons

This code will produce a table of NHST for each of the pairwise comparisons. In this case, all the comparisons are tested against a value of zero.

```{r}
testPairwise(FactorialSummaryB1)
testPairwise(FactorialSummaryB2)
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).

```{r}
testPairwise(FactorialSummaryB1,mu=-2)
testPairwise(FactorialSummaryB2,mu=-2)
```

#### Effect Sizes for the Pairwise Comparisons

This code will produce a table of standardized mean differences for each pairwise comparison. 

```{r}
standardizePairwise(FactorialSummaryB1)
standardizePairwise(FactorialSummaryB2)
```

Here too it is possible to alter the width of the confidence intervals.

```{r}
standardizePairwise(FactorialSummaryB1,conf.level=.99)
standardizePairwise(FactorialSummaryB2,conf.level=.99)
```
