---
title: "Independent Groups Data Example"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Independent Groups Data Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Data Management

### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Factor <- c(rep(1, 10), rep(2, 10))
Factor <- factor(Factor, levels = c(1, 2), labels = c("Level1", "Level2"))
Outcome <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7, 7, 13, 11, 10, 13, 8, 11, 14, 12, 11)
IndependentData <- construct(Factor, Outcome)
```

### Summary Statistics

This code obtains the descriptive statistics for the data frame.
```{r}
(Outcome ~ Factor) |> describeSummary()
```

## Analyses of the Means

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

### Confidence Intervals

This code will provide a table of confidence intervals for each level of the factor.
```{r}
(Outcome ~ Factor) |> estimateMeans()
```

This code will produce a graph of the confidence intervals for each level of the factor.
```{r, Independent-Data-MeansA}
(Outcome ~ Factor) |> plotMeans()
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(Outcome ~ Factor) |> estimateMeans(conf.level = .99)
```

For the graph, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence in addition to changing the confidence level.
```{r, Independent-Data-MeansB}
(Outcome ~ Factor) |> plotMeans(conf.level = .99, line = 9, rope = c(8, 10))
```

### Significance Tests

This code will produce a table of NHST separately for each level of the factor. In this case, all the means are tested against a value of zero.
```{r}
(Outcome ~ Factor) |> testMeans()
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
(Outcome ~ Factor) |> testMeans(mu = 9)
```

### Standardized Effect Sizes

This code will produce a table of standardized mean differences separately for each level of the factor. In this case, the mean is compared to zero to form the effect size.
```{r}
(Outcome ~ Factor) |> standardizeMeans()
```

Here too it is possible to alter the width of the confidence intervals and to establish a more plausible comparison value for the mean.
```{r}
(Outcome ~ Factor) |> standardizeMeans(mu = 9, conf.level = .99)
```

## Analyses of the Comparison

This section produces analyses that examine the difference among the two levels of the factor.

### Confidence Interval

This code estimates the confidence interval of the difference.
```{r}
(Outcome ~ Factor) |> estimateDifference()
```

This code obtains and plots the confidence interval of mean difference.
```{r, Independent-Data-DifferenceA}
(Outcome ~ Factor) |> plotDifference()
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
(Outcome ~ Factor) |> estimateDifference(conf.level = .99)
```

Once again, the confidence levels can be changed away from the default and a comparison line to represent a population (or test) value and a region of practical equivalence can be added to the graph.
```{r, Independent-Data-DifferenceB}
(Outcome ~ Factor) |> plotDifference(conf.level = .99, line = 0, rope = c(-2, 2))
```

If you wish, you can get the confidence intervals for the means and the mean difference in one command.

```{r}
(Outcome ~ Factor) |> estimateComparison()
```

This code produces a difference plot using the confidence intervals for the means and the mean difference.

```{r, Independent-Data-ComparisonA}
(Outcome ~ Factor) |> plotComparison()
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
(Outcome ~ Factor) |> estimateComparison(conf.level = .99)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r, Independent-Data-ComparisonB}
(Outcome ~ Factor) |> plotComparison(conf.level = .99, rope = c(-2, 2))
```

### Significance Test

This code produces NHST for the mean difference (using a default test value of zero).
```{r}
(Outcome ~ Factor) |> testDifference()
```

If the default value of zero is not plausible, it too can be changed.
```{r}
(Outcome ~ Factor) |> testDifference(mu = 2)
```

### Standardized Effect Size

This code calculates a standardized mean difference and its confidence interval.
```{r}
(Outcome ~ Factor) |> standardizeDifference()
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
(Outcome ~ Factor) |> standardizeDifference(conf.level = .99)
```
