---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Independent Groups Data Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Independent Groups Data Tutorial

This page analyzes a two-group between-subjects (independent groups) design using raw data input.

### Data Management

#### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Factor <- c(rep(1,4),rep(2,4))
Outcome <- c(0,0,3,5,4,7,4,9)
Factor <- factor(Factor,levels=c(1,2),labels=c("Level1","Level2"))
IndependentData <- data.frame(Factor,Outcome)
```

#### Descriptive Statistics

This code obtains the descriptive statistics for the data frame.
```{r}
describeMeans(Outcome~Factor)
```

### Analyses of the Means

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

#### Confidence Intervals

This code will provide a table of confidence intervals for each level of the factor.
```{r}
estimateMeans(Outcome~Factor)
```

This code will produce a graph of the confidence intervals for each level of the factor.
```{r,Independent-Data-MeansA}
plotMeans(Outcome~Factor)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateMeans(Outcome~Factor,conf.level=.99)
```

For the graph, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence in addition to changing the confidence level.
```{r,Independent-Data-MeansB}
plotMeans(Outcome~Factor,conf.level=.99,line=5,rope=c(3,7))
```

#### Significance Tests

This code will produce a table of NHST separately for each level of the factor. In this case, all the means are tested against a value of zero.
```{r}
testMeans(Outcome~Factor)
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
testMeans(Outcome~Factor,mu=5)
```

#### Standardized Effect Sizes

This code will produce a table of standardized mean differences separately for each level of the factor. In this case, the mean is compared to zero to form the effect size.
```{r}
estimateStandardizedMeans(Outcome~Factor)
```

Here too it is possible to alter the width of the confidence intervals and to establish a more plausible comparison value for the mean.
```{r}
estimateStandardizedMeans(Outcome~Factor,mu=5,conf.level=.99)
```

### Analyses of the Comparison

This section produces analyses that examine the difference among the two levels of the factor.

#### Confidence Interval

This code estimates the confidence interval of the difference.
```{r}
estimateMeanDifference(Outcome~Factor)
```

This code obtains and plots the confidence interval of mean difference.
```{r,Independent-Data-DifferenceA}
plotMeanDifference(Outcome~Factor)
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
estimateMeanDifference(Outcome~Factor,conf.level=.99)
```

Once again, the confidence levels can be changed away from the default and a comparison line to represent a population (or test) value and a region of practical equivalence can be added to the graph.
```{r,Independent-Data-DifferenceB}
plotMeanDifference(Outcome~Factor,conf.level=.99,line=0,rope=c(-2,2))
```

If you wish, you can get the confidence intervals for the means and the mean difference in one command.

```{r}
estimateMeanComparison(Outcome~Factor)
```

This code produces a difference plot using the confidence intervals for the means and the mean difference.

```{r,Independent-Data-ComparisonA}
plotMeanComparison(Outcome~Factor)
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
estimateMeanComparison(Outcome~Factor,conf.level=.99)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r,Independent-Data-ComparisonB}
plotMeanComparison(Outcome~Factor,conf.level=.99,rope=c(-2,2))
```

#### Significance Test

This code produces NHST for the mean difference (using a default test value of zero).
```{r}
testMeanDifference(Outcome~Factor)
```

If the default value of zero is not plausible, it too can be changed.
```{r}
testMeanDifference(Outcome~Factor,mu=2)
```

#### Standardized Effect Size

This code calculates a standardized mean difference and its confidence interval.
```{r}
estimateStandardizedMeanDifference(Outcome~Factor)
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
estimateStandardizedMeanDifference(Outcome~Factor,conf.level=.99)
```
