---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Mixed Design Data Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## Mixed Design Data Tutorial

### Data Management

#### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Factor <- c(1,1,1,1,2,2,2,2)
Outcome1 <- c(0,0,3,5,9,4,6,9)
Outcome2 <- c(4,7,4,9,6,3,3,8)
Outcome3 <- c(4,9,6,9,5,3,8,8)
Factor <- factor(Factor,levels=c(1,2),labels=c("Level1","Level2"))
MixedData <- data.frame(Factor,Outcome1,Outcome2,Outcome3)
```

This code subsets the data into two different data frames (for simple effects analysis).
```{r}
MixedDataL1 <- subset(MixedData,Factor=="Level1")
MixedDataL2 <- subset(MixedData,Factor=="Level2")
```

#### Descriptive Statistics

This code will produce raincloud plots for better understanding of the distributions.
```{r,Mixed-Rainclouds}
with(MixedDataL1,plotRainclouds(cbind(Outcome1,Outcome2,Outcome3)))
with(MixedDataL2,plotRainclouds(cbind(Outcome1,Outcome2,Outcome3)))
```

This code obtains the descriptive statistics for the two data frames.
```{r}
with(MixedDataL1,describeMeans(cbind(Outcome1,Outcome2,Outcome3)))
with(MixedDataL2,describeMeans(cbind(Outcome1,Outcome2,Outcome3)))
```

### Analyses of the Means

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

#### Confidence Intervals

This code will provide tables of confidence intervals for each level of the factor.
```{r}
with(MixedDataL1,estimateMeans(cbind(Outcome1,Outcome2,Outcome3)))
with(MixedDataL2,estimateMeans(cbind(Outcome1,Outcome2,Outcome3)))
```

This code will produce a graph of the confidence intervals for each level of the factor.
```{r,Mixed-MeansA}
with(MixedDataL1,plotMeans(cbind(Outcome1,Outcome2,Outcome3)))
with(MixedDataL2,plotMeans(cbind(Outcome1,Outcome2,Outcome3)))
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
with(MixedDataL1,estimateMeans(cbind(Outcome1,Outcome2,Outcome3),conf.level=.99))
with(MixedDataL2,estimateMeans(cbind(Outcome1,Outcome2,Outcome3),conf.level=.99))
```

For the graph, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence in addition to changing the confidence level.
```{r,Mixed-MeansB}
with(MixedDataL1,plotMeans(cbind(Outcome1,Outcome2,Outcome3),conf.level=.99,line=5,rope=c(3,7)))
with(MixedDataL2,plotMeans(cbind(Outcome1,Outcome2,Outcome3),conf.level=.99,line=5,rope=c(3,7)))
```

#### Significance Tests

This code will produce a table of NHST separately for each level of the factor. In this case, all the means are tested against a value of zero.
```{r}
with(MixedDataL1,testMeans(cbind(Outcome1,Outcome2,Outcome3)))
with(MixedDataL2,testMeans(cbind(Outcome1,Outcome2,Outcome3)))
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
with(MixedDataL1,testMeans(cbind(Outcome1,Outcome2,Outcome3),mu=5))
with(MixedDataL2,testMeans(cbind(Outcome1,Outcome2,Outcome3),mu=5))
```

#### Standardized Effect Sizes

This code will produce a table of standardized mean differences separately for each level of the factor. In this case, the mean is compared to zero to form the effect size.
```{r}
with(MixedDataL1,estimateStandardizedMeans(cbind(Outcome1,Outcome2,Outcome3)))
with(MixedDataL2,estimateStandardizedMeans(cbind(Outcome1,Outcome2,Outcome3)))
```

Here too it is possible to alter the width of the confidence intervals and to establish a more plausible comparison value for the mean.
```{r}
with(MixedDataL1,estimateStandardizedMeans(cbind(Outcome1,Outcome2,Outcome3),mu=5,conf.level=.99))
with(MixedDataL2,estimateStandardizedMeans(cbind(Outcome1,Outcome2,Outcome3),mu=5,conf.level=.99))
```

### Analyses of a Comparison

This section produces analyses that are equivalent to comparisons of two levels of a factor.

#### Confidence Intervals

This code identifies the two levels for comparison and estimates the confidence interval of the difference.
```{r}
with(MixedDataL1,estimateMeanDifference(cbind(Outcome1,Outcome2)))
with(MixedDataL2,estimateMeanDifference(cbind(Outcome1,Outcome2)))
```

This code obtains and plots the confidence intervals for the mean difference in the identified comparison.
```{r,Mixed-DifferenceA}
with(MixedDataL1,plotMeanDifference(cbind(Outcome1,Outcome2)))
with(MixedDataL2,plotMeanDifference(cbind(Outcome1,Outcome2)))
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
with(MixedDataL1,estimateMeanDifference(cbind(Outcome1,Outcome2),conf.level=.99))
with(MixedDataL2,estimateMeanDifference(cbind(Outcome1,Outcome2),conf.level=.99))
```

Once again, the confidence levels can be changed away from the default and a comparison line to represent a population (or test) value and a region of practical equivalence can be added to the graph.
```{r,Mixed-DifferenceB}
with(MixedDataL1,plotMeanDifference(cbind(Outcome1,Outcome2),conf.level=.99,line=0,rope=c(-2,2)))
with(MixedDataL2,plotMeanDifference(cbind(Outcome1,Outcome2),conf.level=.99,line=0,rope=c(-2,2)))
```

If you wish, you can get the confidence intervals for the means and the mean difference in one command.
```{r}
with(MixedDataL1,estimateMeanComparison(cbind(Outcome1,Outcome2)))
with(MixedDataL2,estimateMeanComparison(cbind(Outcome1,Outcome2)))
```

This code produces a difference plot using the confidence intervals for the means and the mean difference.
```{r,Mixed-ComparisonA}
with(MixedDataL1,plotMeanComparison(cbind(Outcome1,Outcome2)))
with(MixedDataL2,plotMeanComparison(cbind(Outcome1,Outcome2)))
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
with(MixedDataL1,estimateMeanComparison(cbind(Outcome1,Outcome2),conf.level=.99))
with(MixedDataL2,estimateMeanComparison(cbind(Outcome1,Outcome2),conf.level=.99))
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r,Mixed-ComparisonB}
with(MixedDataL1,plotMeanComparison(cbind(Outcome1,Outcome2),conf.level=.99,rope=c(-2,2)))
with(MixedDataL2,plotMeanComparison(cbind(Outcome1,Outcome2),conf.level=.99,rope=c(-2,2)))
```

#### Significance Tests

This code produces NHST for the identified comparison (using a default test value of zero).
```{r}
with(MixedDataL1,testMeanDifference(cbind(Outcome1,Outcome2)))
with(MixedDataL2,testMeanDifference(cbind(Outcome1,Outcome2)))
```

If the default value of zero is not plausible, it too can be changed.
```{r}
with(MixedDataL1,testMeanDifference(cbind(Outcome1,Outcome2),mu=-2))
with(MixedDataL2,testMeanDifference(cbind(Outcome1,Outcome2),mu=-2))
```

#### Standardized Effect Sizes

This code calculates a standardized mean difference for the comparison and its confidence interval.
```{r}
with(MixedDataL1,estimateStandardizedMeanDifference(cbind(Outcome1,Outcome2)))
with(MixedDataL2,estimateStandardizedMeanDifference(cbind(Outcome1,Outcome2)))
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
with(MixedDataL1,estimateStandardizedMeanDifference(cbind(Outcome1,Outcome2),conf.level=.99))
with(MixedDataL2,estimateStandardizedMeanDifference(cbind(Outcome1,Outcome2),conf.level=.99))
```

### Analyses of a Contrast

This section produces analyses that are equivalent to analyses involving multiple levels of a factor.

This code identifies a contrast among the levels.
```{r}
O1vsOthers <- c(-1,.5,.5)
```

#### Confidence Intervals

This code produces a confidence interval for that contrast.
```{r}
with(MixedDataL1,estimateMeanContrast(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers))
with(MixedDataL2,estimateMeanContrast(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers))
```

This code obtains and plots the confidence intervals for the mean difference in the identified contrast.
```{r,Mixed-ContrastA}
with(MixedDataL1,plotMeanContrast(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers))
with(MixedDataL2,plotMeanContrast(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers))
```

As in all other cases, the default value of the confidence interval can be changed.
```{r}
with(MixedDataL1,estimateMeanContrast(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers,conf.level=.99))
with(MixedDataL2,estimateMeanContrast(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers,conf.level=.99))
```

The width of the confidence interval for the contrast can be altered and a comparison line to represent a population (or test) value and a region of practical equivalence can be added to the graph.
```{r,Mixed-ContrastB}
with(MixedDataL1,plotMeanContrast(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers,conf.level=.99,line=0,rope=c(-2,2)))
with(MixedDataL2,plotMeanContrast(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers,conf.level=.99,line=0,rope=c(-2,2)))
```

If you wish, you can get the confidence intervals for the mean subsets and the mean contrast in one command.
```{r}
with(MixedDataL1,estimateMeanSubsets(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers))
with(MixedDataL2,estimateMeanSubsets(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers))
```

This code produces a difference plot using the confidence intervals for the mean subsets and the mean contrast.
```{r,Mixed-SubsetsA}
with(MixedDataL1,plotMeanSubsets(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers))
with(MixedDataL2,plotMeanSubsets(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers))
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
with(MixedDataL1,estimateMeanSubsets(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers,conf.level=.99))
with(MixedDataL2,estimateMeanSubsets(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers,conf.level=.99))
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r,Mixed-SubsetsB}
with(MixedDataL1,plotMeanSubsets(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers,labels=c("Outcome1","Others"),conf.level=.99,rope=c(-2,2)))
with(MixedDataL2,plotMeanSubsets(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers,labels=c("Outcome1","Others"),conf.level=.99,rope=c(-2,2)))
```

#### Significance Tests

This code produces a NHST for the identified contrast. It tests the contrast against a value of zero by default.
```{r}
with(MixedDataL1,testMeanContrast(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers))
with(MixedDataL2,testMeanContrast(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers))
```

If desired, the contrast can be tested against other values.
```{r}
with(MixedDataL1,testMeanContrast(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers,mu=4))
with(MixedDataL2,testMeanContrast(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers,mu=4))
```

#### Standardized Effect Sizes

This code calculates a standardized contrast and its confidence interval.
```{r}
with(MixedDataL1,estimateStandardizedMeanContrast(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers))
with(MixedDataL2,estimateStandardizedMeanContrast(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers))
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
with(MixedDataL1,estimateStandardizedMeanContrast(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers,conf.level=.99))
with(MixedDataL2,estimateStandardizedMeanContrast(cbind(Outcome1,Outcome2,Outcome3),contrast=O1vsOthers,conf.level=.99))
```
