---
title: "Mixed Traditional Summary Example"
description: >
  This page examines a two-factor mixed design (one between-subjects and one within-subjects factor) using summary statistics input, focusing on omnibus and simple effects analyses.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page examines a two-factor mixed design (one between-subjects and one within-subjects factor) using summary statistics input, focusing on omnibus and simple effects analyses.

## Data Management

This code inputs the variable summaries and creates a summary table.
```{r}
Outcome1 <- c(N = 10, M = 8.000, SD = 1.414)
Outcome2 <- c(N = 10, M = 11.000, SD = 2.211)
Outcome3 <- c(N = 10, M = 12.000, SD = 2.449)
MixedSummaryL1 <- construct(Outcome1, Outcome2, Outcome3, class = "wss")
Outcome1 <- c(N = 10, M = 8.000, SD = 2.449)
Outcome2 <- c(N = 10, M = 8.000, SD = 2.000)
Outcome3 <- c(N = 10, M = 7.000, SD = 2.211)
MixedSummaryL2 <- construct(Outcome1, Outcome2, Outcome3, class = "wss")
MixedSummary <- combine(L1 = MixedSummaryL1, L2 = MixedSummaryL2, class = "wss")
```

This code creates correlation matrices.
```{r}
Outcome1 <- c(1.000, .533, .385)
Outcome2 <- c(.533, 1.000, .574)
Outcome3 <- c(.385, .574, 1.000)
MixedCorrL1 <- construct(Outcome1, Outcome2, Outcome3, class = "corr")
Outcome1 <- c(1.000, .408, .164)
Outcome2 <- c(.408, 1.000, .553)
Outcome3 <- c(.164, .553, 1.000)
MixedCorrL2 <- construct(Outcome1, Outcome2, Outcome3, class = "corr")
MixedCorr <- combine(L1 = MixedCorrL1, L2 = MixedCorrL2, class = "corr")
```

This code confirms the descriptive statistics from the summary tables.
```{r}
(MixedSummary) |> describeSummary()
(MixedCorr) |> describeCorrelations()
```

## Analyses of the Omnibus Effects

Get an ANOVA for the design as a whole, including a source table, an estimate of the proportion of variance accounted for, and an ANOVA test of the main effects and interaction.
```{r}
(MixedSummary) |> describeFactorial(MixedCorr)
(MixedSummary) |> estimateFactorial(MixedCorr)
(MixedSummary) |> testFactorial(MixedCorr)
```

Plot the means and confidence intervals for the design as a whole.
```{r, Interaction-Mixed-Omnibus}
(MixedSummary) |> plotFactorial(MixedCorr, col = c("darkred", "darkblue"))
legend("topleft", inset = .01, box.lty = 0, pch = 16, legend = c("Level1", "Level2"), col = c("darkred", "darkblue"))
```

## Analyses of the Simple Effects

Obtain a source table, estimate of proportion of variance accounted for, and an ANOVA test of statistical significance for the simple effect of Outcome (separately for the levels of Factor).
```{r}
(MixedSummary) |> describeEffectBy(MixedCorr)
(MixedSummary) |> estimateEffectBy(MixedCorr)
(MixedSummary) |> testEffectBy(MixedCorr)
```
