---
title: "Mixed Summary Traditional"
description: >
  This page examines a two-factor mixed design (one between-subjects and one within-subjects factor) using summary statistics input, focusing on omnibus and simple effects analyses.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page examines a two-factor mixed design (one between-subjects and one within-subjects factor) using summary statistics input, focusing on omnibus and simple effects analyses.

## Preliminary Tasks

### Data Entry

This code inputs the variable summaries and creates a summary table.
```{r}
Outcome1 <- c(N = 10, M = 8.000, SD = 1.414)
Outcome2 <- c(N = 10, M = 11.000, SD = 2.211)
Outcome3 <- c(N = 10, M = 12.000, SD = 2.449)
MixedMomentsL1 <- construct(Outcome1, Outcome2, Outcome3, class = "wsm")
Outcome1 <- c(N = 10, M = 8.000, SD = 2.449)
Outcome2 <- c(N = 10, M = 8.000, SD = 2.000)
Outcome3 <- c(N = 10, M = 7.000, SD = 2.211)
MixedMomentsL2 <- construct(Outcome1, Outcome2, Outcome3, class = "wsm")
MixedMoments <- combine(L1 = MixedMomentsL1, L2 = MixedMomentsL2)
```

This code creates correlation matrices.
```{r}
Outcome1 <- c(1.000, .533, .385)
Outcome2 <- c(.533, 1.000, .574)
Outcome3 <- c(.385, .574, 1.000)
MixedCorrL1 <- construct(Outcome1, Outcome2, Outcome3, class = "cor")
Outcome1 <- c(1.000, .408, .164)
Outcome2 <- c(.408, 1.000, .553)
Outcome3 <- c(.164, .553, 1.000)
MixedCorrL2 <- construct(Outcome1, Outcome2, Outcome3, class = "cor")
MixedCorr <- combine(L1 = MixedCorrL1, L2 = MixedCorrL2)
```

### Summary Statistics

This code confirms the descriptive statistics from the summary tables.
```{r}
(MixedMoments) |> describeMoments()
(MixedCorr) |> describeCorrelations()
```

Plot the means and confidence intervals for the design as a whole.
```{r, Mixed-Summary-Omnibus}
(MixedMoments) |> plotFactorial(col = c("darkred", "darkblue"))
legend("topleft", inset = .01, box.lty = 0, pch = 16, legend = c("Level1", "Level2"), col = c("darkred", "darkblue"))
```

## Analyses of the Omnibus Effects

The omnibus analysis usually consists of an Analysis of Variance.

### Source Table

Get the source table associated with the main effects and the interaction.

```{r}
(MixedMoments) |> describeFactorial(MixedCorr)
```

### Proportion of Variance Accounted For

Get estimates of the proportion of variance accounted for by each effect (along with their confidence intervals).
```{r}
(MixedMoments) |> estimateFactorial(MixedCorr)
```

### Significance Tests

Finally, test the various effects for statistical significance.
```{r}
(MixedMoments) |> testFactorial(MixedCorr)
```

## Analyses of the Simple Effects

As a follow-up to an Analysis of Variance, it is cusotmary to examine the simple effects (essentially a single-factor ANOVA separately across the levels of another factor).

### Source Table

Get the source tables separately for the simple effects.
```{r}
(MixedMoments) |> describeEffect(MixedCorr)
```

### Proportion of Variance Accounted For

Get an estimate of the proportion of variance account for by the simple effect (and the confidence interval for that estimate).
```{r}
(MixedMoments) |> estimateEffect(MixedCorr)
```

### Significance Tests

Finally, test the simple effects for statistical significance.
```{r}
(MixedMoments) |> testEffect(MixedCorr)
```
