---
title: "Mixed Traditional Data Example"
description: >
  This page examines a two-factor mixed design (one between-subjects and one within-subjects factor) using raw data input, focusing on omnibus and simple effects analyses.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page examines a two-factor mixed design (one between-subjects and one within-subjects factor) using raw data input, focusing on omnibus and simple effects analyses.

## Preliminary Tasks

### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Factor <- c(rep(1, 10), rep(2, 10))
Factor <- factor(Factor, levels = c(1, 2), labels = c("Level1", "Level2"))
Outcome1 <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7, 5, 9, 10, 9, 11, 4, 11, 7, 6, 8)
Outcome2 <- c(7, 13, 11, 10, 13, 8, 11, 14, 12, 11, 7, 8, 7, 11, 10, 7, 8, 4, 8, 10)
Outcome3 <- c(9, 16, 11, 12, 15, 13, 9, 14, 11, 10, 8, 6, 8, 11, 5, 7, 9, 3, 6, 7)
MixedData <- construct(Factor, Outcome1, Outcome2, Outcome3)
```

### Summary Statistics

This code provides a table of summary statistics and a table of correlations.
```{r}
(MixedData) |> focus(Outcome1, Outcome2, Outcome3) |> describeSummaryBy(by = Factor)
(MixedData) |> focus(Outcome1, Outcome2, Outcome3) |> describeCorrelationsBy(by = Factor)
```

Plot the means and confidence intervals for the design as a whole.
```{r, Interaction-Mixed-Omnibus}
(MixedData) |> focus(Outcome1, Outcome2, Outcome3) |> plotFactorial(by = Factor, col = c("darkred", "darkblue"))
legend("topleft", inset = .01, box.lty = 0, pch = 16, legend = c("Level1", "Level2"), col = c("darkred", "darkblue"))
```

## Analyses of the Omnibus Effects

The omnibus analysis usually consists of an Analysis of Variance.

### Source Table

Get the source table associated with the main effects and the interaction.
```{r}
(MixedData) |> focus(Outcome1, Outcome2, Outcome3) |> describeFactorial(by = Factor)
```

### Proportion of Variance Accounted For

Get estimates of the proportion of variance accounted for by each effect (along with their confidence intervals).
```{r}
(MixedData) |> focus(Outcome1, Outcome2, Outcome3) |> estimateFactorial(by = Factor)
```

### Significance Tests

Finally, test the various effects for statistical significance.
```{r}
(MixedData) |> focus(Outcome1, Outcome2, Outcome3) |> testFactorial(by = Factor)
```

## Analyses of the Simple Effects

As a follow-up to an Analysis of Variance, it is cusotmary to examine the simple effects (essentially a single-factor ANOVA separately across the levels of another factor).

### Source Table

Get the source tables separately for the simple effects.
```{r}
(MixedData) |> focus(Outcome1, Outcome2, Outcome3) |> describeEffectBy(by = Factor)
```

### Proportion of Variance Accounted For

Get an estimate of the proportion of variance account for by the simple effect (and the confidence interval for that estimate).
```{r}
(MixedData) |> focus(Outcome1, Outcome2, Outcome3) |> estimateEffectBy(by = Factor)
```

### Significance Tests

Finally, test the simple effects for statistical significance.
```{r}
(MixedData) |> focus(Outcome1, Outcome2, Outcome3) |> testEffectBy(by = Factor)
```
