---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Mixed Design Tutorial with Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Mixed Design Tutorial with Data

### Enter Data

This code inputs the variable names and creates a viewable data frame.
```{r}
Factor <- c(1,1,1,1,2,2,2,2)
Time1 <- c(0,0,3,5,3,1,6,6)
Time2 <- c(4,7,4,9,2,2,5,7)
Time3 <- c(4,9,6,9,2,4,7,7)
Factor <- factor(Factor,levels=c(1,2),labels=c("Group1","Group2"))
MixedData <- data.frame(Factor,Time1,Time2,Time3)
```

This code subsets the data into two different data frames (for simple effects analysis).
```{r}
DataSubsetG1 <- subset(MixedData,Factor=="Group1")
DataSubsetG2 <- subset(MixedData,Factor=="Group2")
```

### Analyses of Multiple Variables

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

#### Confidence Intervals for the Means

This code will provide a table of descriptive statistics and confidence intervals for each level of the factor.
```{r}
with(DataSubsetG1,estimateMeans(Time1,Time2,Time3))
with(DataSubsetG2,estimateMeans(Time1,Time2,Time3))
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
with(DataSubsetG1,estimateMeans(Time1,Time2,Time3,conf.level=.99))
with(DataSubsetG2,estimateMeans(Time1,Time2,Time3,conf.level=.99))
```

#### Confidence Intervals for the Means

This code will provide a table of descriptive statistics and confidence intervals for each level of the factor.
```{r}
with(DataSubsetG1,estimateMeans(Time1,Time2,Time3))
with(DataSubsetG2,estimateMeans(Time1,Time2,Time3))
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
with(DataSubsetG1,estimateMeans(Time1,Time2,Time3,conf.level=.99))
with(DataSubsetG2,estimateMeans(Time1,Time2,Time3,conf.level=.99))
```

#### Plots of Confidence Intervals for the Means

This code will produce a graph of the confidence intervals for each level of the factor.
```{r,Mixed-MeansA}
with(DataSubsetG1,plotMeans(Time1,Time2,Time3))
with(DataSubsetG2,plotMeans(Time1,Time2,Time3))
```

Of course, it is possible to change from the default confidence level. Additionally, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence.
```{r,Mixed-MeansB}
with(DataSubsetG1,plotMeans(Time1,Time2,Time3,conf.level=.99,mu=5,rope=c(3,7)))
with(DataSubsetG2,plotMeans(Time1,Time2,Time3,conf.level=.99,mu=5,rope=c(3,7)))
```

#### Significance Tests for the Means

This code will produce a table of NHST separately for each level of the factor. In this case, all the means are tested against a value of zero.
```{r}
with(DataSubsetG1,testMeans(Time1,Time2,Time3))
with(DataSubsetG2,testMeans(Time1,Time2,Time3))
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
with(DataSubsetG1,testMeans(Time1,Time2,Time3,mu=5))
with(DataSubsetG2,testMeans(Time1,Time2,Time3,mu=5))
```

#### Effect Size for the Means

This code will produce a table of standardized mean differences separately for each level of the factor. In this case, the mean is compared to zero to form the effect size.
```{r}
with(DataSubsetG1,standardizeMeans(Time1,Time2,Time3))
with(DataSubsetG2,standardizeMeans(Time1,Time2,Time3))
```

Here too it is possible to alter the width of the confidence intervals and to establish a more plausible comparison value for the effect size.
```{r}
with(DataSubsetG1,standardizeMeans(Time1,Time2,Time3,mu=5,conf.level=.99))
with(DataSubsetG2,standardizeMeans(Time1,Time2,Time3,mu=5,conf.level=.99))
```

### Analyses of a Variable Comparison

This section produces analyses that are equivalent to comparisons of two levels of a factor.

#### Confidence Interval for the Mean Difference

This code identifies the two levels for comparison and estimates the confidence interval of the difference.
```{r}
with(DataSubsetG1,estimateDifference(Time1,Time2))
with(DataSubsetG2,estimateDifference(Time1,Time2))
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
with(DataSubsetG1,estimateDifference(Time1,Time2,conf.level=.99))
with(DataSubsetG2,estimateDifference(Time1,Time2,conf.level=.99))
```

#### Plots of Confidence Intervals for the Mean Difference

This code obtains and plots the confidence intervals for the levels and the mean difference in the identified comparison.
```{r,Mixed-DifferenceA}
with(DataSubsetG1,plotDifference(Time1,Time2))
with(DataSubsetG2,plotDifference(Time1,Time2))
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added.
```{r,Mixed-DifferenceB}
with(DataSubsetG1,plotDifference(Time1,Time2,conf.level=.99,rope=c(-2,2)))
with(DataSubsetG2,plotDifference(Time1,Time2,conf.level=.99,rope=c(-2,2)))
```

#### Significance Test for the Mean Difference

This code produces NHST for the identified comparison (using a default test value of zero).
```{r}
with(DataSubsetG1,testDifference(Time1,Time2))
with(DataSubsetG2,testDifference(Time1,Time2))
```

If the default value of zero is not plausible, it too can be changed.
```{r}
with(DataSubsetG1,testDifference(Time1,Time2,mu=-2))
with(DataSubsetG2,testDifference(Time1,Time2,mu=-2))
```

#### Effect Size for the Mean Difference

This code calculates a standardized mean difference for the comparison and its confidence interval.
```{r}
with(DataSubsetG1,standardizeDifference(Time1,Time2))
with(DataSubsetG2,standardizeDifference(Time1,Time2))
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
with(DataSubsetG1,standardizeDifference(Time1,Time2,conf.level=.99))
with(DataSubsetG2,standardizeDifference(Time1,Time2,conf.level=.99))
```

### Analyses of a Variable Contrast

This section produces analyses that are equivalent to analyses involving multiple levels of a factor.

This code identifies a contrast among the levels.
```{r}
T1vsOthers <- c(-1,.5,.5)
```

#### Confidence Interval for the Contrast

This code produces a confidence interval for that contrast.
```{r}
with(DataSubsetG1,estimateContrast(Time1,Time2,Time3,contrast=T1vsOthers))
with(DataSubsetG2,estimateContrast(Time1,Time2,Time3,contrast=T1vsOthers))
```

As in all other cases, the default value of the confidence interval can be changed.
```{r}
with(DataSubsetG1,estimateContrast(Time1,Time2,Time3,contrast=T1vsOthers,conf.level=.99))
with(DataSubsetG2,estimateContrast(Time1,Time2,Time3,contrast=T1vsOthers,conf.level=.99))
```

#### Plots of Confidence Intervals for a Contrast

This code obtains and plots the confidence intervals for the groups and the mean difference in the identified contrast.
```{r,Mixed-ContrastA}
with(DataSubsetG1,plotContrast(Time1,Time2,Time3,contrast=T1vsOthers))
with(DataSubsetG2,plotContrast(Time1,Time2,Time3,contrast=T1vsOthers))
```

The width of the confidence interval for the contrast can be altered and a region of practical equivalence can be added.
```{r,Mixed-ContrastB}
with(DataSubsetG1,plotContrast(Time1,Time2,Time3,contrast=T1vsOthers,labels=c("Time1","Others"),conf.level=.99,rope=c(-2,2)))
with(DataSubsetG2,plotContrast(Time1,Time2,Time3,contrast=T1vsOthers,labels=c("Time1","Others"),conf.level=.99,rope=c(-2,2)))
```

#### Significance Test for the Contrast

This code produces a NHST for the identified contrast. It tests the contrast against a value of zero by default.
```{r}
with(DataSubsetG1,testContrast(Time1,Time2,Time3,contrast=T1vsOthers))
with(DataSubsetG2,testContrast(Time1,Time2,Time3,contrast=T1vsOthers))
```

If desired, the contrast can be tested against other values.
```{r}
with(DataSubsetG1,testContrast(Time1,Time2,Time3,contrast=T1vsOthers,mu=4))
with(DataSubsetG2,testContrast(Time1,Time2,Time3,contrast=T1vsOthers,mu=4))
```

#### Effect Size for the Contrast

This code calculates a standardized contrast and its confidence interval.
```{r}
with(DataSubsetG1,standardizeContrast(Time1,Time2,Time3,contrast=T1vsOthers))
with(DataSubsetG2,standardizeContrast(Time1,Time2,Time3,contrast=T1vsOthers))
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
with(DataSubsetG1,standardizeContrast(Time1,Time2,Time3,contrast=T1vsOthers,conf.level=.99))
with(DataSubsetG2,standardizeContrast(Time1,Time2,Time3,contrast=T1vsOthers,conf.level=.99))
```
