---
title: "Multiple Regression Data Example"
output:
  github_document:
    preserve_yaml: FALSE
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page analyzes multiple regression models using raw data input.

## Data Management

### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Predictor1 <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7)
Predictor2 <- c(7, 13, 11, 10, 13, 8, 11, 14, 12, 11)
Criterion <- c(9, 16, 11, 12, 15, 13, 9, 14, 11, 10)
RegressionData <- construct(Predictor1, Predictor2, Criterion)
```

### Summary Statistics

This code obtains the descriptive statistics for the data frame.
```{r}
(RegressionData) |> describeSummary()
(RegressionData) |> describeCorrelations()
```

## Analyses of the Overall Model

This section produces analyses of the overall regression model.

This code will produce a source table associated with the regression model.
```{r}
(RegressionData) |> describeModel()
```

### Confidence Interval

This code will produce the confidence interval for R Squared.
```{r}
(RegressionData) |> estimateModel()
```

The code defaults to 90% confidence intervals. This can be changed if desired.
```{r}
(RegressionData) |> estimateModel(conf.level = .95)
```

### Significance Test

This code will calculate NHST for the regression model.
```{r}
(RegressionData) |> testModel()
```

## Analyses of the Regression Coefficients

This section analyses the regression coefficients obtained from the overall model.

### Confidence Intervals 

This code will provide a table of confidence intervals for each of the regression coefficients.
```{r}
(RegressionData) |> estimateCoefficients()
```

This code will produce a graph of the confidence intervals for each of the regression coefficients.
```{r, Multiple-Data-CoefficientsA}
(RegressionData) |> plotCoefficients()
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(RegressionData) |> estimateCoefficients(conf.level = .99)
```

For the graph, it is possible to plot just coefficients for the predictors (minus the intercept) in addition to changing the confidence level.
```{r, Multiple-Data-CoefficientsB}
(RegressionData) |> plotCoefficients(conf.level = .99, line = 0, intercept = FALSE)
```

### Significance Tests

This code will produce a table of NHST separately for each of the regression coefficients. In this case, all the coefficients are tested against a value of zero.
```{r}
(RegressionData) |> testCoefficients()
```

### Standardized Coefficients

This code will provide a table of confidence intervals for each of the standardized coefficients.
```{r}
(RegressionData) |> standardizeCoefficients()
```

As in other places, the code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(RegressionData) |> standardizeCoefficients(conf.level = .99)
```
