---
title: "Multiple Correlations Summary Example"
description: >
  This page analyzes a set of correlations among variables using summary statistics input.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page analyzes a set of correlations among variables using summary statistics input.

## Preliminary Tasks

### Data Entry

This code inputs the variable summaries and creates a summary table.
```{r}
Outcome1 <- c(N = 10, M = 8.000, SD = 1.414)
Outcome2 <- c(N = 10, M = 11.000, SD = 2.211)
Outcome3 <- c(N = 10, M = 12.000, SD = 2.449)
RepeatedSummary <- construct(Outcome1, Outcome2, Outcome3, class = "wss")
```

This code creates a correlation matrix.
```{r}
Outcome1 <- c(1.000, .533, .385)
Outcome2 <- c(.533, 1.000, .574)
Outcome3 <- c(.385, .574, 1.000)
RepeatedCorr <- construct(Outcome1, Outcome2, Outcome3, class = "corr")
```

### Summary Statistics

This code confirms the descriptive statistics from the summary tables.
```{r}
(RepeatedSummary) |> describeSummary()
(RepeatedCorr) |> describeCorrelations()
```

## Analyses of a Correlation

This section produces analyses of a single correlation.

### Scatterlot and Confidence Ellipse

This code provides a confidence ellipse for the bivariate relationship. Because there is no raw data, no data points are visible and the code defaults instead to an ellipse.
```{r, Correlations-Summary-ScatterD}
(RepeatedSummary) |> focus(Outcome1, Outcome2) |> plotScatter(RepeatedCorr)
```

The ellipse can be altered for different confidence levels.
```{r, Correlations-Summary-ScatterE}
(RepeatedSummary) |> focus(Outcome1, Outcome2) |> plotScatter(RepeatedCorr, conf.level = .99)
```

### Confidence Interval

This code will provide the confidence interval for the correlation.
```{r}
(RepeatedSummary) |> focus(Outcome1, Outcome2) |> estimateCorrelations(RepeatedCorr)
```

This code will produce a graph of the confidence interval for the correlation.
```{r, Correlations-Summary-IntervalsA}
(RepeatedSummary) |> focus(Outcome1, Outcome2) |> plotCorrelations(RepeatedCorr)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(RepeatedSummary) |> focus(Outcome1, Outcome2) |> estimateCorrelations(RepeatedCorr, conf.level = .99)
```

Of course, it is possible to change from the default confidence level in the graph. It is also possible to add a comparison value and a region of practical equivalence.
```{r, Correlations-Summary-IntervalsB}
(RepeatedSummary) |> focus(Outcome1, Outcome2) |> plotCorrelations(RepeatedCorr, conf.level = .99, line = 0, rope = c(-.2, .2))
```

### Significance Test

This code will produce a table of NHST for the correlation (against a value of zero).
```{r}
(RepeatedSummary) |> focus(Outcome1, Outcome2) |> testCorrelations(RepeatedCorr)
```

## Analyses of Several Correlations

This section analyzes the correlations among multiple variables.

### Confidence Intervals

This code will provide the confidence intervals for the correlations.
```{r}
(RepeatedSummary) |> estimateCorrelations(RepeatedCorr)
```

This code will produce a graph of the confidence intervals for the correlations.
```{r, Correlations-Summary-IntervalsC}
(RepeatedSummary) |> plotCorrelations(RepeatedCorr)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(RepeatedSummary) |> estimateCorrelations(RepeatedCorr, conf.level = .99)
```

Of course, it is possible to change from the default confidence level in the graph. It is also possible to add a comparison value and a region of practical equivalence.
```{r, Correlations-Summary-IntervalsD}
(RepeatedSummary) |> plotCorrelations(RepeatedCorr, conf.level = .99, line = 0, rope = c(-.2, .2))
```

### Significance Tests

This code will produce a table of NHST for the correlations (against a value of zero).
```{r}
(RepeatedSummary) |> testCorrelations(RepeatedCorr)
```
