---
title: "Multiple Correlations Data Example"
description: >
  This page analyzes a set of correlations among variables using raw data input.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page analyzes a set of correlations among variables using raw data input.

## Data Management

### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Outcome1 <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7)
Outcome2 <- c(7, 13, 11, 10, 13, 8, 11, 14, 12, 11)
Outcome3 <- c(9, 16, 11, 12, 15, 13, 9, 14, 11, 10)
RepeatedData <- construct(Outcome1, Outcome2, Outcome3)
```

### Summary Statistics

This code obtains the descriptive statistics for the data frame.
```{r}
(RepeatedData) |> describeSummary()
(RepeatedData) |> describeCorrelations()
```

## Analyses of a Correlation

This section produces analyses of a single correlation.

### Confidence Interval

This code will provide the confidence interval for the correlation.
```{r}
(RepeatedData) |> focus(Outcome1, Outcome2) |> estimateCorrelations()
```

This code will produce a graph of the confidence interval for the correlation.
```{r, Correlations-Data-IntervalsA}
(RepeatedData) |> focus(Outcome1, Outcome2) |> plotCorrelations()
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(RepeatedData) |> focus(Outcome1, Outcome2) |> estimateCorrelations(conf.level = .99)
```

Of course, it is possible to change from the default confidence level in the graph. It is also possible to add a comparison value and a region of practical equivalence.
```{r, Correlations-Data-IntervalsB}
(RepeatedData) |> focus(Outcome1, Outcome2) |> plotCorrelations(conf.level = .99, line = 0, rope = c(-.2, .2))
```

#### Scatterlot and Confidence Ellipse

This code provides a scatterplot for the bivariate relationship.
```{r, Correlation-Data-ScatterA}
(RepeatedData) |> focus(Outcome1, Outcome2) |> plotScatter()
```

This code provides a scatterplot along with a 95% confidence ellipse for the data.
```{r, Correlations-Data-ScatterB}
(RepeatedData) |> focus(Outcome1, Outcome2) |> plotScatter(ellipse = TRUE)
```

The ellipse can be altered for different confidence levels.
```{r, Correlations-Data-ScatterC}
(RepeatedData) |> focus(Outcome1, Outcome2) |> plotScatter(ellipse = TRUE, conf.level = .99)
```

### Significance Test

This code will produce a table of NHST for the correlation (against a value of zero).
```{r}
(RepeatedData) |> focus(Outcome1, Outcome2) |> testCorrelations()
```

## Analyses of Several Correlations

This section analyzes the correlations among multiple variables.

### Confidence Intervals

This code will provide the confidence intervals for the correlations.
```{r}
(RepeatedData) |> estimateCorrelations()
```

This code will produce a graph of the confidence intervals for the correlations.
```{r, Correlations-Data-IntervalsC}
(RepeatedData) |> plotCorrelations()
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(RepeatedData) |> estimateCorrelations(conf.level = .99)
```

Of course, it is possible to change from the default confidence level in the graph. It is also possible to add a comparison value and a region of practical equivalence.
```{r, Correlations-Data-IntervalsD}
(RepeatedData) |> plotCorrelations(conf.level = .99, line = 0, rope = c(-.2, .2))
```

### Significance Tests

This code will produce a table of NHST for the correlations (against a value of zero).
```{r}
(RepeatedData) |> testCorrelations()
```
