---
title: "Multiple Regression Summary Example"
description: >
  This page analyzes multiple regression models using summary statistics input.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page analyzes multiple regression models using summary statistics input.

## Preliminary Tasks

### Data Entry

This code inputs the variable summaries and creates a summary table. Note that analyses assume that the last variable is the criterion and the previous variables are the predictors.
```{r}
Predictor1 <- c(N = 10, M = 8.000, SD = 1.414)
Predictor2 <- c(N = 10, M = 11.000, SD = 2.211)
Criterion <- c(N = 10, M = 12.000, SD = 2.449)
RegressionSummary <- construct(Predictor1, Predictor2, Criterion, class = "wss")
```

This code creates a correlation matrix.
```{r}
Predictor1 <- c(1.000, .533, .385)
Predictor2 <- c(.533, 1.000, .574)
Criterion <- c(.385, .574, 1.000)
RegressionCorr <- construct(Predictor1, Predictor2, Criterion, class = "corr")
```

### Summary Statistics

This code confirms the descriptive statistics from the summary tables.
```{r}
(RegressionSummary) |> describeSummary()
(RegressionCorr) |> describeCorrelations()
```

## Analyses of the Overall Model

This section produces analyses of the overall regression model.

This code will produce a source table associated with the regression model.
```{r}
(RegressionSummary) |> describeModel(RegressionCorr)
```

### Confidence Interval

This code will produce the confidence interval for R Squared.
```{r}
(RegressionSummary) |> estimateModel(RegressionCorr)
```

The code defaults to 90% confidence intervals. This can be changed if desired.
```{r}
(RegressionSummary) |> estimateModel(RegressionCorr, conf.level = .95)
```

### Significance Test

This code will calculate NHST for the regression model.
```{r}
(RegressionSummary) |> testModel(RegressionCorr)
```

## Analyses of the Regression Coefficients

This section analyses the regression coefficients obtained from the overall model.

### Confidence Intervals

This code will provide a table of confidence intervals for each of the regression coefficients.
```{r}
(RegressionSummary) |> estimateCoefficients(RegressionCorr)
```

This code will produce a graph of the confidence intervals for each of the regression coefficients.
```{r, Multiple-Summary-CoefficientsA}
(RegressionSummary) |> plotCoefficients(RegressionCorr)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(RegressionSummary) |> estimateCoefficients(RegressionCorr, conf.level = .99)
```

For the graph, it is possible to plot just coefficients for the predictors (minus the intercept) in addition to changing the confidence level.
```{r, Multiple-Summary-CoefficientsB}
(RegressionSummary) |> plotCoefficients(RegressionCorr, conf.level = .99, line = 0, intercept = FALSE)
```

### Significance Tests

This code will produce a table of NHST separately for each of the regression coefficients. In this case, all the coefficients are tested against a value of zero.
```{r}
(RegressionSummary) |> testCoefficients(RegressionCorr)
```

### Standardized Coefficients

This code will provide a table of confidence intervals for each of the standardized coefficients.
```{r}
(RegressionSummary) |> standardizeCoefficients(RegressionCorr)
```

As in other places, the code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(RegressionSummary) |> standardizeCoefficients(RegressionCorr, conf.level = .99)
```
