---
subtitle: "Multiple Regression Data Example"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Multiple Regression Data Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Multiple Regression Data Example

This page analyzes multiple regression models using raw data input.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

#### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Predictor1 <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7)
Predictor2 <- c(7, 13, 11, 10, 13, 8, 11, 14, 12, 11)
Criterion <- c(9, 16, 11, 12, 15, 13, 9, 14, 11, 10)
RegressionData <- construct(Predictor1, Predictor2, Criterion)
```

#### Summary Statistics

This code obtains the descriptive statistics for the data frame.
```{r}
(RegressionData) |> describeSummary()
(RegressionData) |> describeCorrelations()
```

### Analyses of the Overall Model

This section produces analyses of the overall regression model.

#### Confidence Interval

This code will produce the confidence interval for R Squared.
```{r}
(RegressionData) |> estimateRegressionOmnibus()
```

The code defaults to 90% confidence intervals. This can be changed if desired.
```{r}
(RegressionData) |> estimateRegressionOmnibus(conf.level = .95)
```

#### Significance Test

This code will produce a source table associated with the regression model.
```{r}
(RegressionData) |> describeRegressionOmnibus()
```

This code will calculate NHST for the regression model.
```{r}
(RegressionData) |> testRegressionOmnibus()
```

### Analyses of the Regression Coefficients

This section analyses the regression coefficients obtained from the overall model.

#### Confidence Intervals 

This code will provide a table of confidence intervals for each of the regression coefficients.
```{r}
(RegressionData) |> estimateRegressionCoefficients()
```

This code will produce a graph of the confidence intervals for each of the regression coefficients.
```{r, Multiple-Data-CoefficientsA}
(RegressionData) |> plotRegressionCoefficients()
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(RegressionData) |> estimateRegressionCoefficients(conf.level = .99)
```

For the graph, it is possible to plot just coefficients for the predictors (minus the intercept) in addition to changing the confidence level.
```{r, Multiple-Data-CoefficientsB}
(RegressionData) |> plotRegressionCoefficients(conf.level = .99, line = 0, intercept = FALSE)
```

#### Significance Tests

This code will produce a table of NHST separately for each of the regression coefficients. In this case, all the coefficients are tested against a value of zero.
```{r}
(RegressionData) |> testRegressionCoefficients()
```

#### Standardized Coefficients

This code will provide a table of confidence intervals for each of the standardized coefficients.
```{r}
(RegressionData) |> estimateStandardizedRegressionCoefficients()
```

This code will produce a graph of the confidence intervals for each of the standardized coefficients.
```{r, Multiple-Data-StandardizedA}
(RegressionData) |> plotStandardizedRegressionCoefficients()
```

As in other places, the code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(RegressionData) |> estimateStandardizedRegressionCoefficients(conf.level = .99)
```

For the graph, it is possible to change the confidence level.
```{r, Multiple-Data-StandardizedB}
(RegressionData) |> plotStandardizedRegressionCoefficients(conf.level = .99)
```
