---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{One Sample Tutorial with Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r globalOptions,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,loadEASI,include=FALSE}
library(EASI)
```

## One Sample Tutorial with Data

### Enter Data

This code inputs the variable name and creates a viewable data frame.
```{r}
Outcome <- c(0,0,3,5,4,7,4,9)
OneSampleData <- data.frame(Outcome)
```

### Analyses of the Group

This section produces analyses that are equivalent to one-sample analyses for the variable.

#### Confidence Interval for the Mean

This code will provide a table of descriptive statistics and confidence intervals for the variable.
```{r}
estimateMeans(Outcome)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateMeans(Outcome,conf.level=.99)
```

#### Plots of the Confidence Intervals for the Mean

This code will produce a graph of the confidence interval for the variable.
```{r,OneSample-MeansA}
plotMeans(Outcome)
```

Of course, it is possible to change from the default confidence level. Additionally, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence.
```{r,OneSample-MeansB}
plotMeans(Outcome,conf.level=.99,mu=5,rope=c(3,7))
```

#### Significance Tests for the Mean

This code will produce a table of NHST sfor the variable. In this case, the mean is tested against a value of zero.
```{r}
testMeans(Outcome)
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
testMeans(Outcome,mu=5)
```

#### Effect Sizes for the Mean

This code will produce a table of standardized mean difference for the variable. In this case, the mean is compared to zero to form the effect size.
```{r}
standardizeMeans(Outcome)
```

Here too it is possible to alter the width of the confidence intervals and to establish a more plausible comparison value for the effect size.
```{r}
standardizeMeans(Outcome,mu=5,conf.level=.99)
```
