---
title: "One Sample Data Example"
output:
  github_document:
    preserve_yaml: FALSE
---

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page analyzes a single-group (one sample) design using raw data input.

## Data Management

### Data Entry

This code inputs the variable name and creates a viewable data frame.
```{r}
Outcome <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7)
OneSampleData <- construct(Outcome)
```

### Summary Statistics

This code obtains the descriptive statistics for the data frame.
```{r}
(Outcome) |> describeSummary()
```

## Analyses of the Mean

This section produces analyses that are equivalent to one-sample analyses for the variable.

### Confidence Interval

This code will provide a confidence interval for the variable.
```{r}
(Outcome) |> estimateMeans()
```

This code will produce a graph of the confidence interval for the variable.
```{r, OneSample-Data-MeansA}
(Outcome) |> plotMeans()
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(Outcome) |> estimateMeans(conf.level = .99)
```

For the graph, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence in addition to changing the confidence level.
```{r, OneSample-Data-MeansB}
(Outcome) |> plotMeans(conf.level = .99, line = 9, rope = c(8, 10))
```

### Significance Test

This code will produce a table of NHST for the variable. In this case, the mean is tested against a value of zero.
```{r}
(Outcome) |> testMeans()
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
(Outcome) |> testMeans(mu = 9)
```

### Standardized Effect Size

This code will provide the standardized mean difference for the variable. In this case, the mean is compared to zero to form the effect size.
```{r}
(Outcome) |> standardizeMeans()
```

Here too it is possible to alter the width of the confidence interval and to establish a more plausible comparison value for the mean.
```{r}
(Outcome) |> standardizeMeans(mu = 9, conf.level = .99)
```
