---
title: "One Sample Tutorial with Summary Statistics"
author: "Craig A. Wendorf"
date: "2020-10-20"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{One Sample Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8",filename="render_toc.R")
```

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## One Sample Tutorial with Summary Statistics

### Table of Contents

```{r toc, echo=FALSE}
sourceDir <- getSrcDirectory(function(dummy) {dummy})
setwd(sourceDir)
render_toc("OneSampleSummaryTutorial.Rmd")
```

### Data Management

This code inputs the variable and creates a single summary table.
```{r}
Outcome <- c(N=8,M=4.000,SD=3.117)
OneSampleSummary <- rbind(Outcome)
class(OneSampleSummary) <- "wss"
```

### Analyses of the Mean

This section produces analyses that are equivalent to one-sample analyses for the variable.

#### Confidence Interval for the Mean

This code will provide a confidence interval for the variable.
```{r}
estimateMeans(OneSampleSummary)
```

This code will produce a graph of the confidence interval for the variable.
```{r,OneSample-MeansA}
plotMeans(OneSampleSummary)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateMeans(OneSampleSummary,conf.level=.99)
```

For the graph, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence in addition to changing the confidence level.
```{r,OneSample-MeansB}
plotMeans(OneSampleSummary,conf.level=.99,mu=5,rope=c(3,7))
```

#### Significance Test for the Mean

This code will produce a table of NHST for the variable. In this case, the mean is tested against a value of zero.
```{r}
testMeans(OneSampleSummary)
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
testMeans(OneSampleSummary,mu=5)
```

#### Standardized Effect Size for the Mean

This code will provide the standardized mean difference for the variable. In this case, the mean is compared to zero to form the effect size.
```{r}
estimateStandardizedMeans(OneSampleSummary)
```

Here too it is possible to alter the width of the confidence interval and to establish a more plausible comparison value in calculating the effect size.
```{r}
estimateStandardizedMeans(OneSampleSummary,mu=5,conf.level=.99)
```
