---
title: "OneWay (Between-Subjects) Tutorial with Summary Statistics"
author: "Craig A. Wendorf"
date: "2020-10-20"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{OneWay (Between-Subjects) Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8",filename="render_toc.R")
```

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## OneWay (Between-Subjects) Tutorial with Summary Statistics

### Table of Contents

```{r toc, echo=FALSE}
sourceDir <- getSrcDirectory(function(dummy) {dummy})
setwd(sourceDir)
render_toc("OneWaySummaryTutorial.Rmd")
```

### Data Management

This code inputs the group summaries and creates a single summary table.
```{r}
Level1 <- c(N=4,M=2.000,SD=2.449)
Level2 <- c(N=4,M=6.000,SD=2.449)
Level3 <- c(N=4,M=7.000,SD=2.449)
OneWaySummary <- rbind(Level1,Level2,Level3)
class(OneWaySummary) <- "bss"
```

### Analyses of the Means

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

#### Confidence Intervals for the Means

This code will provide a table of confidence intervals for each level of the factor.
```{r}
estimateMeans(OneWaySummary)
```

This code will produce a graph of the confidence intervals for each level of the factor.
```{r,OneWay-MeansA}
plotMeans(OneWaySummary)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateMeans(OneWaySummary,conf.level=.99)
```

For the graph, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence in addition to changing the confidence level.
```{r,OneWay-MeansB}
plotMeans(OneWaySummary,conf.level=.99,mu=5,rope=c(3,7))
```

#### Significance Tests for the Means

This code will produce a table of NHST separately for each level of the factor. In this case, all the means are tested against a value of zero.
```{r}
testMeans(OneWaySummary)
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
testMeans(OneWaySummary,mu=5)
```

#### Standardized Effect Sizes for the Means

This code will produce a table of standardized mean differences separately for each level of the factor. In this case, the mean is compared to zero to form the effect size.
```{r}
estimateStandardizedMeans(OneWaySummary)
```

Here too it is possible to alter the width of the confidence intervals and to establish a more plausible comparison value for the effect size.
```{r}
estimateStandardizedMeans(OneWaySummary,mu=5,conf.level=.99)
```
 
### Analyses of a Comparison

This section produces analyses that are equivalent to comparisons of two levels of a factor.

This code creates a new table that identifies the two levels for comparison.
```{r}
CompSummary <- OneWaySummary[c("Level1","Level2"),]
class(CompSummary) <- "bss"
```

#### Confidence Interval for a Mean Difference

This code estimates the confidence interval of the difference.
```{r}
estimateMeanDifference(CompSummary)
```

This code obtains and plots the confidence intervals for the mean difference in the identified comparison.
```{r,OneWay-DifferenceA}
plotMeanDifference(CompSummary)
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
estimateMeanDifference(CompSummary,conf.level=.99)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r,OneWay-DifferenceB}
plotMeanDifference(CompSummary,conf.level=.99,rope=c(-2,2))
```

#### Confidence Intervals for the Comparison

If you wish, you can get the confidence intervals for the means and the mean difference in one command.
```{r}
estimateMeanComparison(CompSummary)
```

This code produces a difference plot using the confidence intervals for the means and the mean difference.
```{r,OneWay-ComparisonA}
plotMeanComparison(CompSummary)
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
estimateMeanComparison(CompSummary,conf.level=.99)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r,OneWay-ComparisonB}
plotMeanComparison(CompSummary,conf.level=.99,rope=c(-2,2))
```

#### Significance Test for a Mean Difference

This code produces NHST for the identified comparison (using a default test value of zero).
```{r}
testMeanDifference(CompSummary)
```

If the default value of zero is not plausible, it too can be changed.
```{r}
testMeanDifference(CompSummary,mu=-2)
```

#### Standardized Effect Size for the Mean Difference

This code calculates a standardized mean difference for the comparison and its confidence interval.
```{r}
estimateStandardizedMeanDifference(CompSummary)
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
estimateStandardizedMeanDifference(CompSummary,conf.level=.99)
```

### Analyses of a Contrast

This section produces analyses that are equivalent to analyses involving multiple levels of a factor.

This code identifies a contrast among the groups
```{r}
L1vsOthers <- c(-1,.5,.5)
```

#### Confidence Interval for a Contrast

This code produces a confidence interval for that contrast.
```{r}
estimateMeanContrast(OneWaySummary,contrast=L1vsOthers)
```

This code obtains and plots the confidence intervals for the groups and the mean difference in the identified contrast.
```{r,OneWay-ContrastA}
plotMeanContrast(OneWaySummary,contrast=L1vsOthers)
````

As in all other cases, the default value of the confidence interval can be changed.
```{r}
estimateMeanContrast(OneWaySummary,contrast=L1vsOthers,conf.level=.99)
```

The width of the confidence interval for the contrast can be altered and a region of practical equivalence can be added to the graph.
```{r,OneWay-ContrastB}
plotMeanContrast(OneWaySummary,contrast=L1vsOthers,conf.level=.99,rope=c(-2,2))
```

#### Confidence Intervals for the Subsets

If you wish, you can get the confidence intervals for the mean subsets and the mean contrast in one command.
```{r}
estimateMeanSubsets(OneWaySummary,contrast=L1vsOthers)
```

This code produces a difference plot using the confidence intervals for the mean subsets and the mean contrast.
```{r,OneWay-SubsetsA}
plotMeanSubsets(OneWaySummary,contrast=L1vsOthers)
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
estimateMeanSubsets(OneWaySummary,contrast=L1vsOthers,conf.level=.99)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r,OneWay-SubsetsB}
plotMeanSubsets(OneWaySummary,contrast=L1vsOthers,labels=c("Level1","Others"),conf.level=.99,rope=c(-2,2))
```

#### Significance Test for a Contrast

This code produces a NHST for the identified contrast. It tests the contrast against a value of zero by default.
```{r}
testMeanContrast(OneWaySummary,contrast=L1vsOthers)
```

If desired, the contrast can be tested against other values.
```{r}
testMeanContrast(OneWaySummary,contrast=L1vsOthers,mu=4)
```

#### Standardized Effect Size for a Contrast

This code calculates a standardized contrast and its confidence interval.
```{r}
estimateStandardizedMeanContrast(OneWaySummary,contrast=L1vsOthers)
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
estimateStandardizedMeanContrast(OneWaySummary,contrast=L1vsOthers,conf.level=.99)
```

### Analyses of the Pairwise Comparisons

This section provides analyses of all possible pairwise comparisons among the levels of the factor.

#### Confidence Intervals for the Pairwise Comparisons

This code will provide a table of descriptive statistics and confidence intervals for each pairwise comparison.
```{r}
estimateMeansPairwise(OneWaySummary)
```

This code will produce a graph of the confidence intervals for each of the pairwise comparisons.
```{r,OneWay-PairwiseA}
plotMeansPairwise(OneWaySummary)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateMeansPairwise(OneWaySummary,conf.level=.99)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r,OneWay-PairwiseB}
plotMeansPairwise(OneWaySummary,mu=-2,conf.level=.99,rope=c(-4,0))
```

#### Significance Tests of the Pairwise Comparisons

This code will produce a table of NHST for each of the pairwise comparisons. In this case, all the comparisons are tested against a value of zero.
```{r}
testMeansPairwise(OneWaySummary)
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
testMeansPairwise(OneWaySummary,mu=-2)
```

#### Standardized Effect Sizes for the Pairwise Comparisons

This code will produce a table of standardized mean differences for each pairwise comparison. 
```{r}
estimateStandardizedMeansPairwise(OneWaySummary)
```

Here too it is possible to alter the width of the confidence intervals.
```{r}
estimateStandardizedMeansPairwise(OneWaySummary,conf.level=.99)
```
