---
title: "OneWay Summary Advanced"
description: >
  This page examines a single-factor between-subjects (one-way) design using summary statistics input, adding color and plausibility curves to plots of comparisons and contrasts.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page examines a single-factor between-subjects (one-way) design using raw data input, adding color and plausibility curves to plots of comparisons and contrasts.

## Data Management

This code inputs the variable names and creates a viewable data frame.
```{r}
Level1 <- c(N = 10, M = 8.000, SD = 1.414)
Level2 <- c(N = 10, M = 11.000, SD = 2.211)
Level3 <- c(N = 10, M = 12.000, SD = 2.449)
OneWayMoments <- construct(Level1, Level2, Level3, class = "bsm")
```

## Analyses of the Means

As shown elsewhere, the standard EASI plot includes just the confidence intervals for means plus their values. 
```{r, OneWay-Summary-MeansC}
(OneWayMoments) |> plotMeans()
```

To enhance the plot to match other implementations of estimation statistics, it can be have plausibility curves added, have colors modified, and have the values suppresed.
```{r, OneWay-Summary-MeansD}
(OneWayMoments) |> plotMeans(main = "Confidence Intervals and Plausibility Curves", values = FALSE, line = 9, col = c("darkred", "darkblue", "darkgoldenrod"))
(OneWayMoments) |> addPlausible(col = c("darkred", "darkblue", "darkgoldenrod"))
```

## Analyses of a Comparison

Select levels for a comparison and get a simple plot of the confidence intervals and values.
```{r, OneWay-Summary-ComparisonC}
(OneWayMoments) |> focus(Level1, Level2) |> plotComparison()
```

Get an enhanced plot that includes a plausibility curve just for the comparison.
```{r, OneWay-Summary-ComparisonD}
(OneWayMoments) |> focus(Level1, Level2) |> plotComparison(main = "Confidence Intervals and a Plausibility Curve", values = FALSE, ylim = c(0, 20))
(OneWayMoments) |> focus(Level1, Level2) |> addPlausible(col = c("white", "white", "darkgoldenrod"))
```

## Analyses of a Mean Contrast

Create a contrast and get a plot of the mean subsets and the contrast (along with their values).
```{r, OneWay-Summary-SubsetsC}
(OneWayMoments) |> plotSubsets(contrast = c(-1, .5, .5), labels = c("Level1", "Others"))
```

Create an enhanced plot of the mean subsets, adding a plausibility curve to the subsets and the contrast.
```{r, OneWay-Summary-SubsetsD}
(OneWayMoments) |> plotSubsets(contrast = c(-1, .5, .5), main = "Confidence Intervals with Plausibility Curves", labels = c("Level1", "Others"), ylim = c(0, 20), values = FALSE, col = c("blue", "forestgreen", "black"))
(OneWayMoments) |> addPlausible(contrast = c(-1, .5, .5), type = c("right", "right", "right"), col = c("black", "black", "black"))
```
