---
title: "OneWay Summary Contrasts"
description: >
  This page examines a single-factor between-subjects (one-way) design using summary statistics input, focusing on comparisons and contrasts.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page examines a single-factor between-subjects (one-way) design using summary statistics input, focusing on comparisons and contrasts.

## Preliminary Tasks

### Data Entry

This code inputs the group summaries and creates a single summary table.
```{r}
Level1 <- c(N = 10, M = 8.000, SD = 1.414)
Level2 <- c(N = 10, M = 11.000, SD = 2.211)
Level3 <- c(N = 10, M = 12.000, SD = 2.449)
OneWayMoments <- construct(Level1, Level2, Level3, class = "bsm")
```

### Summary Statistics

This code confirms the descriptive statistics from the summary table.
```{r}
(OneWayMoments) |> describeMoments()
```

Plot the summary statistics. The bars represent standard deviations.
```{r, OneWay-Summary-Moments}
(OneWayMoments) |> plotMoments()
```

## Analyses of the Means

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

### Confidence Intervals

This code will provide a table of confidence intervals for each level of the factor.
```{r}
(OneWayMoments) |> estimateMeans()
```

This code will produce a graph of the confidence intervals for each level of the factor.
```{r, OneWay-Summary-MeansA}
(OneWayMoments) |> plotMeans()
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(OneWayMoments) |> estimateMeans(conf.level = .99)
```

For the graph, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence in addition to changing the confidence level.
```{r, OneWay-Summary-MeansB}
(OneWayMoments) |> plotMeans(conf.level = .99, line = 9, rope = c(8, 10))
```

### Significance Tests

This code will produce a table of NHST separately for each level of the factor. In this case, all the means are tested against a value of zero.
```{r}
(OneWayMoments) |> testMeans()
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
(OneWayMoments) |> testMeans(mu = 9)
```

### Standardized Effect Sizes

This code will produce a table of standardized mean differences separately for each level of the factor. In this case, the mean is compared to zero to form the effect size.
```{r}
(OneWayMoments) |> standardizeMeans()
```

Here too it is possible to alter the width of the confidence intervals and to establish a more plausible comparison value for the mean.
```{r}
(OneWayMoments) |> standardizeMeans(mu = 9, conf.level = .99)
```
 
## Analyses of a Comparison

This section produces analyses involving comparisons of two levels of a factor.

### Confidence Intervals

This code estimates the confidence interval of the difference.
```{r}
(OneWayMoments) |> focus("Level1", "Level2") |> estimateDifference()
```

This code obtains and plots the confidence intervals for the mean difference in the identified comparison.
```{r, OneWay-Summary-DifferenceA}
(OneWayMoments) |> focus("Level1", "Level2") |> plotDifference()
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
(OneWayMoments) |> focus("Level1", "Level2") |> estimateDifference(conf.level = .99)
```

Once again, the confidence levels can be changed away from the default and a comparison line to represent a population (or test) value and a region of practical equivalence can be added to the graph.
```{r, OneWay-Summary-DifferenceB}
(OneWayMoments) |> focus("Level1", "Level2") |> plotDifference(conf.level = .99, line = 0, rope = c(-2, 2))
```

If you wish, you can get the confidence intervals for the means and the mean difference in one command.
```{r}
(OneWayMoments) |> focus("Level1", "Level2") |> estimateComparison()
```

This code produces a difference plot using the confidence intervals for the means and the mean difference.
```{r, OneWay-Summary-ComparisonA}
(OneWayMoments) |> focus("Level1", "Level2") |> plotComparison()
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
(OneWayMoments) |> focus("Level1", "Level2") |> estimateComparison(conf.level = .99)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r, OneWay-Summary-ComparisonB}
(OneWayMoments) |> focus("Level1", "Level2") |> plotComparison(conf.level = .99, rope = c(-2, 2))
```

### Significance Test

This code produces NHST for the identified comparison (using a default test value of zero).
```{r}
(OneWayMoments) |> focus("Level1", "Level2") |> testDifference()
```

If the default value of zero is not plausible, it too can be changed.
```{r}
(OneWayMoments) |> focus("Level1", "Level2") |> testDifference(mu = -2)
```

### Standardized Effect Size

This code calculates a standardized mean difference for the comparison and its confidence interval.
```{r}
(OneWayMoments) |> focus("Level1", "Level2") |> standardizeDifference()
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
(OneWayMoments) |> focus("Level1", "Level2") |> standardizeDifference(conf.level = .99)
```

## Analyses of a Contrast

This section produces analyses involving multiple levels of a factor.

### Confidence Intervals

This code produces a confidence interval for a specified contrast.
```{r}
(OneWayMoments) |> estimateContrast(contrast = c(-1, .5, .5))
```

This code obtains and plots the confidence intervals for the groups and the mean difference in the identified contrast.
```{r, OneWay-Summary-ContrastA}
(OneWayMoments) |> plotContrast(contrast = c(-1, .5, .5))
```

As in all other cases, the default value of the confidence interval can be changed.
```{r}
(OneWayMoments) |> estimateContrast(contrast = c(-1, .5, .5), conf.level = .99)
```

The width of the confidence interval for the contrast can be altered and a comparison line to represent a population (or test) value and a region of practical equivalence can be added to the graph.
```{r, OneWay-Summary-ContrastB}
(OneWayMoments) |> plotContrast(contrast = c(-1, .5, .5), conf.level = .99, line = 0, rope = c(-2, 2))
```

If you wish, you can get the confidence intervals for the mean subsets and the mean contrast in one command.
```{r}
(OneWayMoments) |> estimateSubsets(contrast = c(-1, .5, .5))
```

This code produces a difference plot using the confidence intervals for the mean subsets and the mean contrast.
```{r, OneWay-Summary-SubsetsA}
(OneWayMoments) |> plotSubsets(contrast = c(-1, .5, .5))
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
(OneWayMoments) |> estimateSubsets(contrast = c(-1, .5, .5), conf.level = .99)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r, OneWay-Summary-SubsetsB}
(OneWayMoments) |> plotSubsets(contrast = c(-1, .5, .5), labels = c("Level1", "Others"), conf.level = .99, rope = c(-2, 2))
```

### Significance Test

This code produces a NHST for the identified contrast. It tests the contrast against a value of zero by default.
```{r}
(OneWayMoments) |> testContrast(contrast = c(-1, .5, .5))
```

If desired, the contrast can be tested against other values.
```{r}
(OneWayMoments) |> testContrast(contrast = c(-1, .5, .5), mu = 4)
```

### Standardized Effect Size

This code calculates a standardized contrast and its confidence interval.
```{r}
(OneWayMoments) |> standardizeContrast(contrast = c(-1, .5, .5))
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
(OneWayMoments) |> standardizeContrast(contrast = c(-1, .5, .5), conf.level = .99)
```

## Analyses of a Complex Contrast

This section examines a complex contrast among multiple means.

### Confidence Intervals

Create a single contrast to compare the first group to the grand mean (which requires some arithmetic). Then estimate and plot the contrast.
```{r, OneWay-Summary-ComplexA}
(OneWayMoments) |> estimateContrast(contrast = c(2/3, -1/3, -1/3))
(OneWayMoments) |> plotContrast(contrast = c(2/3, -1/3, -1/3))
```

Rather than setting just one contrast, set two contrasts: one for the Grand Mean and one for Level 1. Estimate and plot the confidence intervals for each contrast and the difference between contrasts.
```{r, OneWay-Summary-ComplexB}
(OneWayMoments) |> estimateComplex(contrast1 = c(1/3, 1/3, 1/3), contrast2 = c(1, 0, 0), labels = c("GrandMean", "L1Only"))
(OneWayMoments) |> plotComplex(contrast1 = c(1/3, 1/3, 1/3), contrast2 = c(1, 0, 0), labels = c("GrandMean", "L1Only"))
```

### Significance Tests

The two versions of the contrast can be tested for statistical significance.
```{r}
(OneWayMoments) |> testContrast(contrast = c(2/3, -1/3, -1/3))
(OneWayMoments) |> testComplex(contrast1 = c(1/3, 1/3, 1/3), contrast2 = c(1, 0, 0), labels = c("GrandMean", "L1Only"))
```
