---
title: "Paired Samples Summary Statistics Example"
output:
  github_document:
    preserve_yaml: FALSE
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page analyzes a within-subjects (paired samples) design for two time points using summary statistics input.

## Data Management

### Data Entry

This code inputs the variable summaries and creates a summary table.
```{r}
Outcome1 <- c(N = 10, M = 8.000, SD = 1.414)
Outcome2 <- c(N = 10, M = 11.000, SD = 2.211)
PairedSummary <- construct(Outcome1, Outcome2, class = "wss")
```

This code creates a correlation matrix.
```{r}
Outcome1 <- c(1.000, .533)
Outcome2 <- c(.533, 1.000)
PairedCorr <- construct(Outcome1, Outcome2, class = "corr")
```

### Summary Statistics

This code confirms the descriptive statistics from the summary tables.
```{r}
(PairedSummary) |> describeSummary()
(PairedCorr) |> describeCorrelations()
```

## Analyses of the Means

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

### Confidence Intervals

This code will provide a table of confidence intervals for each level of the factor.
```{r}
(PairedSummary) |> estimateMeans()
```

This code will produce a graph of the confidence intervals for each level of the factor.
```{r, Paired-Summary-MeansA}
(PairedSummary) |> plotMeans()
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(PairedSummary) |> estimateMeans(conf.level = .99)
```

For the graph, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence in addition to changing the confidence level.
```{r, Paired-Summary-MeansB}
(PairedSummary) |> plotMeans(conf.level = .99, line = 9, rope = c(8, 10))
```

### Significance Tests

This code will produce a table of NHST separately for each level of the factor. In this case, all the means are tested against a value of zero.
```{r}
(PairedSummary) |> testMeans()
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
(PairedSummary) |> testMeans(mu = 9)
```

### Standardized Effect Sizes

This code will produce a table of standardized mean differences separately for each level of the factor. In this case, the mean is compared to zero to form the effect size.
```{r}
(PairedSummary) |> standardizeMeans()
```

Here too it is possible to alter the width of the confidence intervals and to establish a more plausible comparison value for the mean.
```{r}
(PairedSummary) |> standardizeMeans(mu = 9, conf.level = .99)
```

## Analyses of the Comparison

This section produces analyses that examine the difference among the two levels of the factor.

### Confidence Intervals

This code estimates the confidence interval of the difference.
```{r}
(PairedSummary) |> estimateDifference(PairedCorr)
```

This code obtains and plots the confidence intervals for the mean difference.
```{r, Paired-Summary-DifferenceA}
(PairedSummary) |> plotDifference(PairedCorr)
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
(PairedSummary) |> estimateDifference(PairedCorr, conf.level = .99)
```

Once again, the confidence levels can be changed away from the default and a comparison line to represent a population (or test) value and a region of practical equivalence can be added to the graph.
```{r, Paired-Summary-DifferenceB}
(PairedSummary) |> plotDifference(PairedCorr, conf.level = .99, line = 0, rope = c(-2, 2))
```

If you wish, you can get the confidence intervals for the means and the mean difference in one command.
```{r}
(PairedSummary) |> estimateComparison(PairedCorr)
```

This code produces a difference plot using the confidence intervals for the means and the mean difference.
```{r, Paired-Summary-ComparisonA}
(PairedSummary) |> plotComparison(PairedCorr)
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
(PairedSummary) |> estimateComparison(PairedCorr, conf.level = .99)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r, Paired-Summary-ComparisonB}
(PairedSummary) |> plotComparison(PairedCorr, conf.level = .99, rope = c(-2, 2))
```

### Significance Test

This code produces NHST for the mean difference (using a default test value of zero).
```{r}
(PairedSummary) |> testDifference(PairedCorr)
```

If the default value of zero is not plausible, it too can be changed.
```{r}
(PairedSummary) |> testDifference(PairedCorr, mu = -2)
```

### Standardized Effect Size

This code calculates a standardized mean difference and its confidence interval.
```{r}
(PairedSummary) |> standardizeDifference(PairedCorr)
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
(PairedSummary) |> standardizeDifference(PairedCorr, conf.level = .99)
```
