---
title: "Plausible OneWay Data Application"
description: >
  This page adds data and plausibility curves to confidence interval plots of comparisons and contrasts using one-way (between-subjects) data.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page adds data and plausibility curves to confidence interval plots of comparisons and contrasts using one-way (between-subjects) data.

## Data Management

This code inputs the variable names and creates a viewable data frame.
```{r}
Factor <- c(rep(1, 10), rep(2, 10), rep(3, 10))
Factor <- factor(Factor, levels = c(1, 2, 3), labels = c("Level1", "Level2", "Level3"))
Outcome <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7, 7, 13, 11, 10, 13, 8, 11, 14, 12, 11, 9, 16, 11, 12, 15, 13, 9, 14, 11, 10)
OneWayData <- construct(Factor, Outcome)
```

## Analyses of the Means

Estimate and get a simple plot of the confidence intervals.
```{r, Plausible-OneWay-ConfidenceA}
(Outcome ~ Factor) |> estimateMeans()
(Outcome ~ Factor) |> plotMeans()
```

Get an enhanced plot of data and confidence intervals.
```{r, Plausible-OneWay-ConfidenceB}
(Outcome ~ Factor) |> plotData(main = "Data and Confidence Intervals", method = "stack", col = c("darkred", "darkblue", "darkgoldenrod"))
(Outcome ~ Factor) |> addMeans(values = FALSE, line = 9, col = c("darkred", "darkblue", "darkgoldenrod"))
```

## Analyses of a Comparison

Create a comparison and get a simple plot of the confidence intervals.
```{r, Plausible-OneWay-ComparisonA}
(Outcome ~ Factor) |> focus(Level1, Level2) |> estimateComparison()
(Outcome ~ Factor) |> focus(Level1, Level2) |> plotComparison()
```

Get an enhanced plot of data and confidence intervals with a plausibility curve.
```{r, Plausible-OneWay-ComparisonB}
(Outcome ~ Factor) |> focus(Level1, Level2) |> plotComparison(main = "Data, Confidence Intervals, and a Plausibility Curve", ylim = c(0, 20), values = FALSE, col = c("darkred", "darkblue", "black"))
(Outcome ~ Factor) |> focus(Level1, Level2) |> addPlausible(type = c("none", "none", "right"), col = c("darkred", "darkblue", "black"))
(Outcome ~ Factor) |> focus(Level1, Level2) |> addData(method = "stack", col = c("darkred", "darkblue", "black"))
```

## Analyses of a Mean Contrast

Create a contrast and get a plot of the mean subsets and the contrast.
```{r, Plausible-OneWay-ContrastA}
(Outcome ~ Factor) |> estimateSubsets(contrast = c(-1, .5, .5), labels = c("Level1", "Others"))
(Outcome ~ Factor) |> plotSubsets(contrast = c(-1, .5, .5), labels = c("Level1", "Others"))
```

Create an enhanced plot of the means and the mean subsets with a plausibility curve.
```{r, Plausible-OneWay-ContrastB}
(Outcome ~ Factor) |> plotSubsets(contrast = c(-1, .5, .5), main = "Confidence Intervals and a Plausibility Curve", labels = c("Level1", "Others"), ylim = c(0, 20), values = FALSE, col = c("darkred", "darkblue", "black"))
(Outcome ~ Factor) |> addPlausible(contrast = c(-1, .5, .5), type = c("none", "none", "right"), col = c("darkred", "darkblue", "black"))
```
