---
title: "Relational Repeated Measures (Within-Subjects) Tutorial with Summary Statistics"
author: "Craig A. Wendorf"
date: "2020-10-20"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Relational Repeated Measures (Within-Subjects) Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8",filename="render_toc.R")
```

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Relational Repeated Measures (Within-Subjects) Tutorial with Summary Statistics

### Table of Contents

```{r toc, echo=FALSE}
sourceDir <- getSrcDirectory(function(dummy) {dummy})
setwd(sourceDir)
render_toc("RelationalRepeatedSummaryTutorial.Rmd")
```

### Data Management

This code inputs the variable summaries and creates a summary table.
```{r}
Outcome1 <- c(N=4,M=2.000,SD=2.449)
Outcome2 <- c(N=4,M=6.000,SD=2.449)
Outcome3 <- c(N=4,M=7.000,SD=2.449)
RepeatedSummary <- rbind(Outcome1,Outcome2,Outcome3)
class(RepeatedSummary) <- "wss"
```

This code creates a correlation matrix, enters just the top triangle, and then uses a function to fill in the whole matrix.
```{r}
RepeatedCorr <- declareCorrelations("Outcome1","Outcome2","Outcome3")
RepeatedCorr["Outcome1","Outcome2"] <- .500
RepeatedCorr["Outcome1","Outcome3"] <- .056
RepeatedCorr["Outcome2","Outcome3"] <- .389
RepeatedCorr <- fillCorrelations(RepeatedCorr)
```

### Analyses of the Omnibus Effect

This section produces analyses that are the traditional way to represent and test overall variable differences.

#### Confidence Intervals for the Means

This code will provide a table of confidence intervals for each of the variables.
```{r}
estimateMeans(RepeatedSummary)
```

This code will produce a graph of the confidence intervals for each of the variables.
```{r,RelationalRepeated-Means}
plotMeans(RepeatedSummary)
```

#### Significance Tests for the Omnibus Effect

This code provides an ANOVA source table for the omnibus effect.
```{r}
describeMeansOmnibus(RepeatedSummary,RepeatedCorr)
testMeansOmnibus(RepeatedSummary,RepeatedCorr)
```

### Analyses of the Pairwise Comparisons

This section provides analyses of all possible pairwise comparisons among the variables.

#### Confidence Intervals for the Pairwise Comparisons

This code will provide a table of descriptive statistics and confidence intervals for each pairwise comparison.

```{r}
estimateMeansPairwise(RepeatedSummary,RepeatedCorr)
```

This code will produce a graph of the confidence intervals for each of the pairwise comparisons.
```{r,RelationalRepeated-Pairwise}
plotMeansPairwise(RepeatedSummary,RepeatedCorr,mu=0)
```

#### Significance Tests of the Pairwise Comparisons

This code will produce a table of NHST for each of the pairwise comparisons. In this case, all the comparisons are tested against a value of zero.
```{r}
testMeansPairwise(RepeatedSummary,RepeatedCorr)
```

### Analyses of the Pairwise Comparisons Using Relational Intervals

This section provides analyses of all possible pairwise comparisons among the variables using relational intervals.

#### Confidence and Relational Intervals for the Pairwise Comparisons

This code will provide a table of confidence and relational intervals for each pairwise comparison.
```{r}
estimateMeansRelational(RepeatedSummary,RepeatedCorr)
```

This code will produce a graph of the confidence and relational intervals for each of the pairwise comparisons.
```{r,RelationalRepeated-RelationalA}
plotMeansRelational(RepeatedSummary,RepeatedCorr)
```

The code defaults to 95% confidence and relational intervals. This can be changed if desired.
```{r}
estimateMeansRelational(RepeatedSummary,RepeatedCorr,conf.level=.99)
```

For the graph, it is possible to change the confidence level.
```{r,RelationalRepeated-RelationalB}
plotMeansRelational(RepeatedSummary,RepeatedCorr,conf.level=.99)
```
