---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "2021-03-16"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Relational OneWay (Between-Subjects) Tutorial with Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Relational OneWay (Between-Subjects) Tutorial with Data

### Data Management

#### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Factor <- c(rep(1,4),rep(2,4),rep(3,4))
Outcome <- c(0,0,3,5,4,7,4,9,9,6,4,9)
Factor <- factor(Factor,levels=c(1,2,3),labels=c("Level1","Level2","Level3"))
OneWayData <- data.frame(Factor,Outcome)
```

#### Plot of the Data

```{r,OneWay-Boxes}
plotBoxes(Outcome~Factor)
plotDensity(Outcome~Factor,add=TRUE)
plotData(Outcome~Factor,add=TRUE)
```

#### Descriptive Statistics

This code obtains the descriptive statistics for the data frame.
```{r}
describeMeans(Outcome~Factor)
```

### Analyses of the Omnibus Effect

This section produces analyses that are the traditional way to represent and test overall group differences.

#### Confidence Intervals

This code will provide a table of confidence intervals for each level of the factor.
```{r}
estimateMeans(Outcome~Factor)
```

This code will produce a graph of the confidence intervals for each level of the factor.
```{r,RelationalOneWay-Means}
plotMeans(Outcome~Factor)
```

#### Significance Test

This code provides an ANOVA source table for the omnibus effect.
```{r}
describeMeansOmnibus(Outcome~Factor)
testMeansOmnibus(Outcome~Factor)
```

### Analyses of the Pairwise Comparisons

This section provides analyses of all possible pairwise comparisons among the levels of the factor.

#### Confidence Intervals

This code will provide a table of descriptive statistics and confidence intervals for each pairwise comparison.

```{r}
estimateMeansPairwise(Outcome~Factor)
```

This code will produce a graph of the confidence intervals for each of the pairwise comparisons.
```{r,RelationalOneWay-Pairwise}
plotMeansPairwise(Outcome~Factor,mu=0)
```

#### Significance Tests

This code will produce a table of NHST for each of the pairwise comparisons. In this case, all the comparisons are tested against a value of zero.
```{r}
testMeansPairwise(Outcome~Factor)
```

### Analyses of the Pairwise Comparisons Using Relational Intervals

This section provides analyses of all possible pairwise comparisons among the levels of the factor using relational intervals.

#### Confidence and Relational Intervals

This code will provide a table of confidence and relational intervals for each pairwise comparison.
```{r}
estimateMeansRelational(Outcome~Factor)
```

This code will produce a graph of the confidence and relational intervals for each of the pairwise comparisons.
```{r,RelationalOneWay-RelationalA}
plotMeansRelational(Outcome~Factor)
```

The code defaults to 95% confidence and relational intervals. This can be changed if desired.
```{r}
estimateMeansRelational(Outcome~Factor,conf.level=.99)
```

For the graph, it is possible to change the confidence level.
```{r,RelationalOneWay-RelationalB}
plotMeansRelational(Outcome~Factor,conf.level=.99)
```
