---
title: "Repeated Alternative Data Example"
description: >
  This page examines a single-factor within-subjects (repeated measures) design using raw data input, focusing on comparisons and contrasts.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, comment = NA)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page examines a single-factor within-subjects (repeated measures) design using raw data input, focusing on comparisons and contrasts.

## Preliminary Tasks

### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Outcome1 <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7)
Outcome2 <- c(7, 13, 11, 10, 13, 8, 11, 14, 12, 11)
Outcome3 <- c(9, 16, 11, 12, 15, 13, 9, 14, 11, 10)
RepeatedData <- construct(Outcome1, Outcome2, Outcome3)
```

### Summary Statistics

This code obtains the descriptive statistics for the data frame.
```{r}
(RepeatedData) |> describeSummary()
```

Plot the summary statistics. The bars represent standard deviations, with dotted lines as the default but solid lines representing the sides with more skew.
```{r, Repeated-Data-Summary}
(RepeatedData) |> plotSummary()
```

## Analyses of the Means

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

### Confidence Intervals

This code will provide a table of confidence intervals for each level of the factor.
```{r}
(RepeatedData) |> estimateMeans()
```

This code will produce a graph of the confidence intervals for each level of the factor.
```{r, Repeated-Data-MeansA}
(RepeatedData) |> plotMeans()
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(RepeatedData) |> estimateMeans(conf.level = .99)
```

For the graph, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence in addition to changing the confidence level.
```{r, Repeated-Data-MeansB}
(RepeatedData) |> plotMeans(conf.level = .99, line = 9, rope = c(8, 10))
```

### Significance Tests

This code will produce a table of NHST separately for each level of the factor. In this case, all the means are tested against a value of zero.
```{r}
(RepeatedData) |> testMeans()
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
(RepeatedData) |> testMeans(mu = 9)
```

### Standardized Effect Sizes

This code will produce a table of standardized mean differences separately for each level of the factor. In this case, the mean is compared to zero to form the effect size.
```{r}
(RepeatedData) |> standardizeMeans()
```

Here too it is possible to alter the width of the confidence intervals and to establish a more plausible comparison value for the mean.
```{r}
(RepeatedData) |> standardizeMeans(mu = 9, conf.level = .99)
```

## Analyses of a Comparison

This section produces analyses involving comparisons of two levels of a factor.

### Confidence Intervals

This code identifies the two levels for comparison and estimates the confidence interval of the difference.
```{r}
(RepeatedData) |> focus(Outcome1, Outcome2) |> estimateDifference()
```

This code obtains and plots the confidence intervals for the mean difference in the identified comparison.
```{r, Repeated-Data-DifferenceA}
(RepeatedData) |> focus(Outcome1, Outcome2) |> plotDifference()
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
(RepeatedData) |> focus(Outcome1, Outcome2) |> estimateDifference(conf.level = .99)
```

Once again, the confidence levels can be changed away from the default and a comparison line to represent a population (or test) value and a region of practical equivalence can be added to the graph..
```{r, Repeated-Data-DifferenceB}
(RepeatedData) |> focus(Outcome1, Outcome2) |> plotDifference(conf.level = .99, line = 0, rope = c(-2, 2))
```

If you wish, you can get the confidence intervals for the means and the mean difference in one command.
```{r}
(RepeatedData) |> focus(Outcome1, Outcome2) |> estimateComparison()
```

This code produces a difference plot using the confidence intervals for the means and the mean difference.
```{r, Repeated-Data-ComparisonA}
(RepeatedData) |> focus(Outcome1, Outcome2) |> plotComparison()
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
(RepeatedData) |> focus(Outcome1, Outcome2) |> estimateComparison(conf.level = .99)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r, Repeated-Data-ComparisonB}
(RepeatedData) |> focus(Outcome1, Outcome2) |> plotComparison(conf.level = .99, rope = c(-2, 2))
```

### Significance Test

This code produces NHST for the identified comparison (using a default test value of zero).
```{r}
(RepeatedData) |> focus(Outcome1, Outcome2) |> testDifference()
```

If the default value of zero is not plausible, it too can be changed.
```{r}
(RepeatedData) |> focus(Outcome1, Outcome2) |> testDifference(mu = -2)
```

### Standardized Effect Size

This code calculates a standardized mean difference for the comparison and its confidence interval.
```{r}
(RepeatedData) |> focus(Outcome1, Outcome2) |> standardizeDifference()
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
(RepeatedData) |> focus(Outcome1, Outcome2) |> standardizeDifference(conf.level = .99)
```

## Analyses of a Contrast

This section produces analyses involving multiple levels of a factor.

### Confidence Intervals

This code produces a confidence interval for a specified contrast.
```{r}
(RepeatedData) |> estimateContrast(contrast = c(-1, .5, .5))
```

This code obtains and plots the confidence intervals for the mean difference in the identified contrast.
```{r, Repeated-Data-ContrastA}
(RepeatedData) |> plotContrast(contrast = c(-1, .5, .5))
```

As in all other cases, the default value of the confidence interval can be changed.
```{r}
(RepeatedData) |> estimateContrast(contrast = c(-1, .5, .5), conf.level = .99)
```

The width of the confidence interval for the contrast can be altered and a comparison line to represent a population (or test) value and a region of practical equivalence can be added to the graph.
```{r, Repeated-Data-ContrastB}
(RepeatedData) |> plotContrast(contrast = c(-1, .5, .5), conf.level = .99, line = 0, rope = c(-2, 2))
```

If you wish, you can get the confidence intervals for the mean subsets and the mean contrast in one command.
```{r}
(RepeatedData) |> estimateSubsets(contrast = c(-1, .5, .5))
```

This code produces a difference plot using the confidence intervals for the mean subsets and the mean contrast.
```{r, Repeated-Data-SubsetsA}
(RepeatedData) |> plotSubsets(contrast = c(-1, .5, .5))
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
(RepeatedData) |> estimateSubsets(contrast = c(-1, .5, .5), conf.level = .99)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r, Repeated-Data-SubsetsB}
(RepeatedData) |> plotSubsets(contrast = c(-1, .5, .5), labels = c("Outcome1", "Others"), conf.level = .99, rope = c(-2, 2))
```

### Significance Test

This code produces a NHST for the identified contrast. It tests the contrast against a value of zero by default.
```{r}
(RepeatedData) |> testContrast(contrast = c(-1, .5, .5))
```

If desired, the contrast can be tested against other values.
```{r}
(RepeatedData) |> testContrast(contrast = c(-1, .5, .5), mu = 4)
```

### Standardized Effect Size

This code calculates a standardized contrast and its confidence interval.
```{r}
(RepeatedData) |> standardizeContrast(contrast = c(-1, .5, .5))
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
(RepeatedData) |> standardizeContrast(contrast = c(-1, .5, .5), conf.level = .99)
```

## Analyses of a Complex Contrast

This section examines a complex contrast among multiple means.

### Confidence Intervals

Create a single contrast to compare the first variable to the grand mean (which requires some arithmetic). Then esimate and plot the contrast.
```{r, Repeated-Data-ComplexA}
(RepeatedData) |> estimateContrast(contrast = c(2/3, -1/3, -1/3))
(RepeatedData) |> plotContrast(contrast = c(2/3, -1/3, -1/3))
```

Rather than setting just one contrast, set two contrasts: one for the Grand Mean and one for Level 1. Estimate and plot the confidence intervals for each contrast and the difference between contrasts.
```{r, Repeated-Data-ComplexB}
(RepeatedData) |> estimateComplex(contrast1 = c(1/3, 1/3, 1/3), contrast2 = c(1, 0, 0), labels = c("GrandMean", "O1Only"))
(RepeatedData) |> plotComplex(contrast1 = c(1/3, 1/3, 1/3), contrast2 = c(1, 0, 0), labels = c("GrandMean", "O1Only"))
```

### Significance Tests

The two versions of the contrast can be tested for statistical significance.
```{r}
(RepeatedData) |> testContrast(contrast = c(2/3, -1/3, -1/3))
(RepeatedData) |> testComplex(contrast1 = c(1/3, 1/3, 1/3), contrast2 = c(1, 0, 0), labels = c("GrandMean", "L1Only"))
```
