---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "2020-11-20"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Repeated Measures (Within-Subjects) Correlations Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Repeated Measures (Within-Subjects) Correlations Tutorial with Summary Statistics

### Data Management

This code inputs the variable summaries and creates a summary table.
```{r}
Outcome1 <- c(N=4,M=2.000,SD=2.449)
Outcome2 <- c(N=4,M=6.000,SD=2.449)
Outcome3 <- c(N=4,M=7.000,SD=2.449)
RepeatedSummary <- rbind(Outcome1,Outcome2,Outcome3)
class(RepeatedSummary) <- "wss"
```

This code creates a correlation matrix, enters just the top triangle, and then uses a function to fill in the whole matrix.
```{r}
RepeatedCorr <- declareCorrelations("Outcome1","Outcome2","Outcome3")
RepeatedCorr["Outcome1","Outcome2"] <- .500
RepeatedCorr["Outcome1","Outcome3"] <- .056
RepeatedCorr["Outcome2","Outcome3"] <- .389
RepeatedCorr <- fillCorrelations(RepeatedCorr)
```

### Analyses of a Correlation

This section produces analyses of a single correlation.

This code creates a tables that identify the two variables for correlating.
```{r}
CompSummary <- RepeatedSummary[c("Outcome1","Outcome2"),]
class(CompSummary) <- "wss"
CompCorr <- RepeatedCorr[c("Outcome1","Outcome2"),c("Outcome1","Outcome2")]
```

#### Confidence Interval

This code will provide the confidence interval for the correlation.
```{r}
estimateCorrelations(CompSummary,CompCorr)
```

This code will produce a graph of the confidence interval for the correlation.
```{r,RepeatedCorrelation-A}
plotCorrelations(CompSummary,CompCorr)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateCorrelations(CompSummary,CompCorr,conf.level=.99)
```

Of course, it is possible to change from the default confidence level in the graph.
```{r,RepeatedCorrelation-B}
plotCorrelations(CompSummary,CompCorr,conf.level=.99)
```

#### Significance Test

This code will produce a table of NHST for the correlation (against a value of zero).
```{r}
testCorrelations(CompSummary,CompCorr)
```

### Analyses of Several Correlations

This section analyzes the correlations among multiple variables.

#### Confidence Intervals

This code will provide the confidence intervals for the correlations.
```{r}
estimateCorrelations(RepeatedSummary,RepeatedCorr)
```

This code will produce a graph of the confidence intervals for the correlations.
```{r,RepeatedCorrelations-A}
plotCorrelations(RepeatedSummary,RepeatedCorr)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateCorrelations(RepeatedSummary,RepeatedCorr,conf.level=.99)
```

Of course, it is possible to change from the default confidence level in the graph.
```{r,RepeatedCorrelations-B}
plotCorrelations(RepeatedSummary,RepeatedCorr,conf.level=.99)
```

#### Significance Tests

This code will produce a table of NHST for the correlations (against a value of zero).
```{r}
testCorrelations(RepeatedSummary,RepeatedCorr)
```
