---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Repeated Measures (Within-Subjects) Tutorial with Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Repeated Measures (Within-Subjects) Tutorial with Data

### Data Management

#### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Outcome1 <- c(0,0,3,5)
Outcome2 <- c(4,7,4,9)
Outcome3 <- c(9,6,4,9)
RepeatedData <- data.frame(Outcome1,Outcome2,Outcome3)
```

#### Plot of the Data

This code provides a boxplot, stacked data, and a density plot for each level.
```{r,Repeated-Boxes}
plotBoxes(Outcome1,Outcome2,Outcome3)
plotDensity(Outcome1,Outcome2,Outcome3,add=TRUE)
plotData(Outcome1,Outcome2,Outcome3,add=TRUE)
```

#### Descriptive Statistics

This code obtains the descriptive statistics for the data frame.
```{r}
describeMeans(Outcome1,Outcome2,Outcome3)
```

### Analyses of the Means

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

#### Confidence Intervals

This code will provide a table of confidence intervals for each level of the factor.
```{r}
estimateMeans(Outcome1,Outcome2,Outcome3)
```

This code will produce a graph of the confidence intervals for each level of the factor.
```{r,Repeated-MeansA}
plotMeans(Outcome1,Outcome2,Outcome3)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateMeans(Outcome1,Outcome2,Outcome3,conf.level=.99)
```

For the graph, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence in addition to changing the confidence level.
```{r,Repeated-MeansB}
plotMeans(Outcome1,Outcome2,Outcome3,conf.level=.99,line=5,rope=c(3,7))
```

#### Significance Tests

This code will produce a table of NHST separately for each level of the factor. In this case, all the means are tested against a value of zero.
```{r}
testMeans(Outcome1,Outcome2,Outcome3)
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
testMeans(Outcome1,Outcome2,Outcome3,mu=5)
```

#### Standardized Effect Sizes

This code will produce a table of standardized mean differences separately for each level of the factor. In this case, the mean is compared to zero to form the effect size.
```{r}
estimateStandardizedMeans(Outcome1,Outcome2,Outcome3)
```

Here too it is possible to alter the width of the confidence intervals and to establish a more plausible comparison value for the mean.
```{r}
estimateStandardizedMeans(Outcome1,Outcome2,Outcome3,mu=5,conf.level=.99)
```

### Analyses of a Comparison

This section produces analyses that are equivalent to comparisons of two levels of a factor.

#### Confidence Intervals

This code identifies the two levels for comparison and estimates the confidence interval of the difference.
```{r}
estimateMeanDifference(Outcome1,Outcome2)
```

This code obtains and plots the confidence intervals for the mean difference in the identified comparison.
```{r,Repeated-DifferenceA}
plotMeanDifference(Outcome1,Outcome2)
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
estimateMeanDifference(Outcome1,Outcome2,conf.level=.99)
```

Once again, the confidence levels can be changed away from the default and a comparison line to represent a population (or test) value and a region of practical equivalence can be added to the graph..
```{r,Repeated-DifferenceB}
plotMeanDifference(Outcome1,Outcome2,conf.level=.99,line=0,rope=c(-2,2))
```

If you wish, you can get the confidence intervals for the means and the mean difference in one command.
```{r}
estimateMeanComparison(Outcome1,Outcome2)
```

This code produces a difference plot using the confidence intervals for the means and the mean difference.
```{r,Repeated-ComparisonA}
plotMeanComparison(Outcome1,Outcome2)
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
estimateMeanComparison(Outcome1,Outcome2,conf.level=.99)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r,Repeated-ComparisonB}
plotMeanComparison(Outcome1,Outcome2,conf.level=.99,rope=c(-2,2))
```

#### Significance Test

This code produces NHST for the identified comparison (using a default test value of zero).
```{r}
testMeanDifference(Outcome1,Outcome2)
```

If the default value of zero is not plausible, it too can be changed.
```{r}
testMeanDifference(Outcome1,Outcome2,mu=-2)
```

#### Standardized Effect Size

This code calculates a standardized mean difference for the comparison and its confidence interval.
```{r}
estimateStandardizedMeanDifference(Outcome1,Outcome2)
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
estimateStandardizedMeanDifference(Outcome1,Outcome2,conf.level=.99)
```

### Analyses of a Contrast

This section produces analyses that are equivalent to analyses involving multiple levels of a factor.

This code identifies a contrast among the levels.
```{r}
O1vsOthers <- c(-1,.5,.5)
```

#### Confidence Intervals

This code produces a confidence interval for that contrast.
```{r}
estimateMeanContrast(Outcome1,Outcome2,Outcome3,contrast=O1vsOthers)
```

This code obtains and plots the confidence intervals for the mean difference in the identified contrast.
```{r,Repeated-ContrastA}
plotMeanContrast(Outcome1,Outcome2,Outcome3,contrast=O1vsOthers)
```

As in all other cases, the default value of the confidence interval can be changed.
```{r}
estimateMeanContrast(Outcome1,Outcome2,Outcome3,contrast=O1vsOthers,conf.level=.99)
```

The width of the confidence interval for the contrast can be altered and a comparison line to represent a population (or test) value and a region of practical equivalence can be added to the graph.
```{r,Repeated-ContrastB}
plotMeanContrast(Outcome1,Outcome2,Outcome3,contrast=O1vsOthers,conf.level=.99,line=0,rope=c(-2,2))
```

If you wish, you can get the confidence intervals for the mean subsets and the mean contrast in one command.
```{r}
estimateMeanSubsets(Outcome1,Outcome2,Outcome3,contrast=O1vsOthers)
```

This code produces a difference plot using the confidence intervals for the mean subsets and the mean contrast.
```{r,Repeated-SubsetsA}
plotMeanSubsets(Outcome1,Outcome2,Outcome3,contrast=O1vsOthers)
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
estimateMeanSubsets(Outcome1,Outcome2,Outcome3,contrast=O1vsOthers,conf.level=.99)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r,Repeated-SubsetsB}
plotMeanSubsets(Outcome1,Outcome2,Outcome3,contrast=O1vsOthers,labels=c("Outcome1","Others"),conf.level=.99,rope=c(-2,2))
```

#### Significance Test

This code produces a NHST for the identified contrast. It tests the contrast against a value of zero by default.
```{r}
testMeanContrast(Outcome1,Outcome2,Outcome3,contrast=O1vsOthers)
```

If desired, the contrast can be tested against other values.
```{r}
testMeanContrast(Outcome1,Outcome2,Outcome3,contrast=O1vsOthers,mu=4)
```

#### Standardized Effect Size

This code calculates a standardized contrast and its confidence interval.
```{r}
estimateStandardizedMeanContrast(Outcome1,Outcome2,Outcome3,contrast=O1vsOthers)
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
estimateStandardizedMeanContrast(Outcome1,Outcome2,Outcome3,contrast=O1vsOthers,conf.level=.99)
```

### Analyses of the Pairwise Comparisons

This section provides analyses of all possible pairwise comparisons among the levels of the factor.

#### Confidence Intervals

This code will provide a table of descriptive statistics and confidence intervals for each pairwise comparison.
```{r}
estimateMeansPairwise(Outcome1,Outcome2,Outcome3)
```

This code will produce a graph of the confidence intervals for each of the pairwise comparisons.
```{r,Repeated-PairwiseA}
plotMeansPairwise(Outcome1,Outcome2,Outcome3)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateMeansPairwise(Outcome1,Outcome2,Outcome3,conf.level=.99)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r,Repeated-PairwiseB}
plotMeansPairwise(Outcome1,Outcome2,Outcome3,line=-2,conf.level=.99,rope=c(-4,0))
```

#### Significance Tests

This code will produce a table of NHST for each of the pairwise comparisons. In this case, all the comparisons are tested against a value of zero.
```{r}
testMeansPairwise(Outcome1,Outcome2,Outcome3)
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
testMeansPairwise(Outcome1,Outcome2,Outcome3,mu=-2)
```

#### Standardized Effect Sizes

This code will produce a table of standardized mean differences for each pairwise comparison. 
```{r}
estimateStandardizedMeansPairwise(Outcome1,Outcome2,Outcome3)
```

Here too it is possible to alter the width of the confidence intervals.
```{r}
estimateStandardizedMeansPairwise(Outcome1,Outcome2,Outcome3,conf.level=.99)
```
