---
subtitle: "Set of Correlations Summary Statistics Tutorial"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Set of Correlations Summary Statistics Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
# suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Set of Correlations Summary Statistics Tutorial

This page analyzes ba set of correlations among variables using summary statistics input.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

This code inputs the variable summaries and creates a summary table.
```{r}
Outcome1 <- c(N = 4, M = 2.000, SD = 2.449)
Outcome2 <- c(N = 4, M = 6.000, SD = 2.449)
Outcome3 <- c(N = 4, M = 7.000, SD = 2.449)
RepeatedSummary <- rbind(Outcome1, Outcome2, Outcome3)
class(RepeatedSummary) <- "wss"
```

This code creates a correlation matrix, enters just the top triangle, and then uses a function to fill in the whole matrix.
```{r}
RepeatedCorr <- declareCorrelations("Outcome1", "Outcome2", "Outcome3")
RepeatedCorr["Outcome1", "Outcome2"] <- .500
RepeatedCorr["Outcome1", "Outcome3"] <- .056
RepeatedCorr["Outcome2", "Outcome3"] <- .389
RepeatedCorr <- fillCorrelations(RepeatedCorr)
```

### Analyses of a Correlation

This section produces analyses of a single correlation.

This code creates a tables that identify the two variables for correlating.
```{r}
CompSummary <- RepeatedSummary[c("Outcome1", "Outcome2"), ]
class(CompSummary) <- "wss"
CompCorr <- RepeatedCorr[c("Outcome1", "Outcome2"), c("Outcome1", "Outcome2")]
```

#### Confidence Interval

This code will provide the confidence interval for the correlation.
```{r}
estimateCorrelations(CompSummary, CompCorr)
```

This code will produce a graph of the confidence interval for the correlation.
```{r,SetCorrelations-Summary-IntervalsA}
plotCorrelations(CompSummary, CompCorr)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateCorrelations(CompSummary, CompCorr, conf.level = .99)
```

Of course, it is possible to change from the default confidence level in the graph. It is also possible to add a comparison value and a region of practical equivalence.
```{r,SetCorrelations-Summary-IntervalsB}
plotCorrelations(CompSummary, CompCorr, conf.level = .99, line = 0, rope = c(-.2, .2))
```

#### Significance Test

This code will produce a table of NHST for the correlation (against a value of zero).
```{r}
testCorrelations(CompSummary, CompCorr)
```

### Analyses of Several Correlations

This section analyzes the correlations among multiple variables.

#### Confidence Intervals

This code will provide the confidence intervals for the correlations.
```{r}
estimateCorrelations(RepeatedSummary, RepeatedCorr)
```

This code will produce a graph of the confidence intervals for the correlations.
```{r,SetCorrelations-Summary-IntervalsC}
plotCorrelations(RepeatedSummary, RepeatedCorr)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateCorrelations(RepeatedSummary, RepeatedCorr, conf.level = .99)
```

Of course, it is possible to change from the default confidence level in the graph. It is also possible to add a comparison value and a region of practical equivalence.
```{r,SetCorrelations-Summary-IntervalsD}
plotCorrelations(RepeatedSummary, RepeatedCorr, conf.level = .99, line = 0, rope = c(-.2, .2))
```

#### Significance Tests

This code will produce a table of NHST for the correlations (against a value of zero).
```{r}
testCorrelations(RepeatedSummary, RepeatedCorr)
```
