---
title: "Single Correlation Summary Statistics Example"
description: >
  This page analyzes a single correlation between two variables using summary statistics input.
output: rmarkdown::html_vignette
---

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page analyzes a single correlation between two variables using summary statistics input.

## Data Management

### Data Entry

This code inputs the variable summaries and creates a summary table.
```{r}
Outcome1 <- c(N = 10, M = 8.000, SD = 1.414)
Outcome2 <- c(N = 10, M = 11.000, SD = 2.211)
PairedSummary <- construct(Outcome1, Outcome2, class = "wss")
```

This code creates a correlation matrix.
```{r}
Outcome1 <- c(1.000, .533)
Outcome2 <- c(.533, 1.000)
PairedCorr <- construct(Outcome1, Outcome2, class = "corr")
```

### Summary Statistics

This code confirms the descriptive statistics from the summary tables.
```{r}
(PairedSummary) |> describeSummary()
(PairedCorr) |> describeCorrelations()
```

### Plot of the Data

This code provides a confidence ellipse for the bivariate relationship. Because there is no raw data, no data points are visible and the code defaults instead to an ellipse.
```{r, SingleCorrelation-Summary-ScatterD}
(PairedSummary) |> plotScatter(PairedCorr)
```

The ellipse can be altered for different confidence levels.
```{r, SingleCorrelation-Summary-ScatterE}
(PairedSummary) |> plotScatter(PairedCorr, conf.level = .99)
```

## Analyses of a Correlation

This section produces analyses of the correlation.

### Confidence Interval

This code will provide the confidence interval for the correlation.
```{r}
(PairedSummary) |> estimateCorrelations(PairedCorr)
```

This code will produce a graph of the confidence interval for the correlation.
```{r, SingleCorrelation-Summary-IntervalsA}
(PairedSummary) |> plotCorrelations(PairedCorr)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(PairedSummary) |> estimateCorrelations(PairedCorr, conf.level = .99)
```

Of course, it is possible to change from the default confidence level and to add a comparison line and a region of practical equivalence to the graph.
```{r, SingleCorrelation-Summary-IntervalsB}
(PairedSummary) |> plotCorrelations(PairedCorr, conf.level = .99, line = 0, rope = c(-.2, .2))
```

### Significance Test

This code will produce a table of NHST for the correlation (against a value of zero).
```{r}
(PairedSummary) |> testCorrelations(PairedCorr)
```
