---
title: "Single Correlation Data Example"
output:
  github_document:
    preserve_yaml: FALSE
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

This page analyzes a single correlation between two variables using raw data input.

## Data Management

### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
Outcome1 <- c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7)
Outcome2 <- c(7, 13, 11, 10, 13, 8, 11, 14, 12, 11)
PairedData <- construct(Outcome1, Outcome2)
```

### Summary Statistics

This code obtains the descriptive statistics for the data frame.
```{r}
(PairedData) |> describeSummary()
(PairedData) |> describeCorrelations()
```

### Plot of the Data

This code provides a scatterplot for the bivariate relationship.
```{r, SingleCorrelation-Data-ScatterA}
(PairedData) |> plotScatter()
```

This code provides a scatterplot along with a 95% confidence ellipse for the data.
```{r, SingleCorrelation-Data-ScatterB}
(PairedData) |> plotScatter(ellipse = TRUE)
```

The ellipse can be altered for different confidence levels.
```{r, SingleCorrelation-Data-ScatterC}
(PairedData) |> plotScatter(ellipse = TRUE, conf.level = .99)
```

## Analyses of a Correlation

This section produces analyses of the correlation.

### Confidence Interval

This code will provide the confidence interval for the correlation.
```{r}
(PairedData) |> estimateCorrelations()
```

This code will produce a graph of the confidence interval for the correlation.
```{r, SingleCorrelation-Data-IntervalsA}
(PairedData) |> plotCorrelations()
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(PairedData) |> estimateCorrelations(conf.level = .99)
```

Of course, it is possible to change from the default confidence level and to add a comparison line and a region of practical equivalence to the graph.
```{r, SingleCorrelation-Data-IntervalsB}
(PairedData) |> plotCorrelations(conf.level = .99, line = 0, rope = c(-.2, .2))
```

### Significance Test

This code will produce a table of NHST for the correlation (against a value of zero).
```{r}
(PairedData) |> testCorrelations()
```
