---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Analyze - OneWay (Between-Subjects) Tutorial with Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Analyze - OneWay (Between-Subjects) Tutorial with Data

### Enter Data

This code inputs the variable names and creates a viewable data frame.

```{r}
Factor <- c(rep(1,4),rep(2,4),rep(3,4))
Outcome <- c(0,0,3,5,4,7,4,9,9,6,4,9)
Factor <- factor(Factor,levels=c(1,2,3),labels=c("Level1","Level2","Level3"))
OneWayData <- data.frame(Factor,Outcome)
```

### Analyses of Multiple Groups

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

This code will provide a table of descriptive statistics and confidence intervals, a table of NHST, and a table of standardized mean differences for each level of the factor.

```{r,AnalyzeOneWay-MeansA}
analyzeMeans(Outcome~Factor)
```

It is also possible to alter the width of the confidence intervals, add a comparison value for the means, and to add a region of practical equivalence.

```{r,AnalyzeOneWay-MeansB}
analyzeMeans(Outcome~Factor,mu=5,conf.level=.99,rope=c(3,7))
```

### Analyses of a Group Comparison

This section produces analyses that are equivalent to comparisons of two levels of a factor.

This code creates a new factor that identifies the two levels for comparison. It also provides table for the confidence interval of the difference, a table of NHST for the difference, and a table of the standardized mean difference.

```{r,AnalyzeOneWay-DifferenceA}
Comparison=factor(Factor,c("Level1","Level2"))
analyzeDifference(Outcome~Comparison)
```

As always, a interval width can be altered, and comparison values and a region of practical equivalence can be added.

```{r,AnalyzeOneWay-DifferenceB}
analyzeDifference(Outcome~Comparison,mu=-2,conf.level=.99,rope=c(-2,2))
```

### Analyses of a Group Contrast

This section produces analyses that are equivalent to analyses involving multiple levels of a factor.

This code identifies a contrast among the groups. It also provides table for the confidence interval for the contrast, a table of NHST for the contrast, and a table of the standardized contrast.

```{r,AnalyzeOneWay-ContrastA}
L1vsOthers <- c(-1,.5,.5)
analyzeContrast(Outcome~Factor,contrast=L1vsOthers)
```

Finally, a comparison value, a region of practical equivalence, and a custom interval width can be specified.

```{r,AnalyzeOneWay-ContrastB}
analyzeContrast(Outcome~Factor,contrast=L1vsOthers,mu=4,conf.level=.99,rope=c(-2,2))
```
