---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Analyze - Repeated Measures (Within-Subjects) Tutorial with Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Analyze - Repeated Measures (Within-Subjects) Tutorial with Data

### Enter Data

This code inputs the variable names and creates a viewable data frame.

```{r}
Time1 <- c(0,0,3,5)
Time2 <- c(4,7,4,9)
Time3 <- c(9,6,4,9)
RepeatedData <- data.frame(Time1,Time2,Time3)
```

### Analyses of Multiple Variables

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

This code will provide a table of descriptive statistics and confidence intervals, a table of NHST, and a table of standardized mean differences for each level of the factor.

```{r,AnalyzeRepeated-MeansA}
analyzeMeans(Time1,Time2,Time3)
```

It is also possible to alter the width of the confidence intervals, add a comparison value for the means, and to add a region of practical equivalence.

```{r,AnalyzeRepeated-MeansB}
analyzeMeans(Time1,Time2,Time3,mu=5,conf.level=.99,rope=c(3,7))
```

### Analyses of a Variable Comparison

This section produces analyses that are equivalent to comparisons of two levels of a factor.

This code creates a new factor that identifies the two levels for comparison. It also provides table for the confidence interval of the difference, a table of NHST for the difference, and a table of the standardized mean difference.

```{r,AnalyzeRepeated-DifferenceA}
analyzeDifference(Time1,Time2)
```

As always, a interval width can be altered, and comparison values and a region of practical equivalence can be added.

```{r,AnalyzeRepeated-DifferenceB}
analyzeDifference(Time1,Time2,mu=-2,conf.level=.99,rope=c(-2,2))
```

### Analyses of a Variable Contrast

This section produces analyses that are equivalent to analyses involving multiple levels of a factor.

This code identifies a contrast among the levels. It also provides table for the confidence interval for the contrast, a table of NHST for the contrast, and a table of the standardized contrast.

```{r,AnalyzeRepeated-ContrastA}
T1vsOthers <- c(-1,.5,.5)
analyzeContrast(Time1,Time2,Time3,contrast=T1vsOthers)
```

Finally, a comparison value, a region of practical equivalence, and a custom interval width can be specified.

```{r,AnalyzeRepeated-ContrastB}
analyzeContrast(Time1,Time2,Time3,contrast=T1vsOthers,mu=4,conf.level=.99,rope=c(-2,2))
```
