---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Analyze - OneWay (Between-Subjects) Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Analyze - OneWay (Between-Subjects) Tutorial with Summary Statistics

### Enter Summary Statistics

This code inputs the group summaries and creates a single summary table.

```{r}
Group1 <- c(N=4,M=2.000,SD=2.449)
Group2 <- c(N=4,M=6.000,SD=2.449)
Group3 <- c(N=4,M=7.000,SD=2.449)
OneWaySummary <- rbind(Group1,Group2,Group3)
class(OneWaySummary) <- "bss"
```

### Analyses of Multiple Groups

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

This code will provide a table of descriptive statistics and confidence intervals, a table of NHST, and a table of standardized mean differences for each level of the factor.

```{r,AnalyzeOneWay-MeansA}
analyzeMeans(OneWaySummary)
```

It is also possible to alter the width of the confidence intervals, add a comparison value for the means, and to add a region of practical equivalence.

```{r,AnalyzeOneWay-MeansB}
analyzeMeans(OneWaySummary,mu=5,conf.level=.99,rope=c(3,7))
```

### Analyses of a Group Comparison

This section produces analyses that are equivalent to comparisons of two levels of a factor.

This code creates a new table that identifies the two levels for comparison. It also provides table for the confidence interval of the difference, a table of NHST for the difference, and a table of the standardized mean difference.

```{r,AnalyzeOneWay-DifferenceA}
CompSummary <- OneWaySummary[c("Group1","Group2"),]
class(CompSummary) <- "bss"
analyzeDifference(CompSummary)
```

As always, a interval width can be altered, and comparison values and a region of practical equivalence can be added.

```{r,AnalyzeOneWay-DifferenceB}
analyzeDifference(CompSummary,mu=-2,conf.level=.99,rope=c(-2,2))
```

### Analyses of a Group Contrast

This section produces analyses that are equivalent to analyses involving multiple levels of a factor.

This code identifies a contrast among the groups. It also provides table for the confidence interval for the contrast, a table of NHST for the contrast, and a table of the standardized contrast.

```{r,AnalyzeOneWay-ContrastA}
G1vsOthers <- c(-1,.5,.5)
analyzeContrast(OneWaySummary,contrast=G1vsOthers)
```

Finally, a comparison value, a region of practical equivalence, and a custom interval width can be specified.

```{r,AnalyzeOneWay-ContrastB}
analyzeContrast(OneWaySummary,contrast=G1vsOthers,mu=4,conf.level=.99,rope=c(-2,2))
```
