---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{FactorialBy - Factorial (Between-Subjects) Tutorial with Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## FactorialBy - Factorial (Between-Subjects) Tutorial with Data

### Enter Data

```{r}
FactorA <- c(1,1,1,1,2,2,2,2,3,3,3,3,1,1,1,1,2,2,2,2,3,3,3,3)
FactorB <- c(1,1,1,1,1,1,1,1,1,1,1,1,2,2,2,2,2,2,2,2,2,2,2,2)
Outcome <- c(0,0,3,5,4,7,4,9,4,9,6,9,3,1,6,6,2,2,5,7,2,4,7,7)
FactorA <- factor(FactorA,levels=c(1,2,3),labels=c("A1","A2","A3"))
FactorB <- factor(FactorB,levels=c(1,2),labels=c("B1","B2"))
FactorialData <- data.frame(FactorA,FactorB,Outcome)
```

### Analyses of Multiple Groups

#### Confidence Intervals for the Means

```{r}
estimateMeansBy(Outcome~FactorA,by=FactorB)
```

```{r}
estimateMeansBy(Outcome~FactorA,by=FactorB,conf.level=.99)
```

#### Plot of the Confidence Intervals for the Means

```{r,FactorialBy-MeansA}
plotMeansBy(Outcome~FactorA,by=FactorB)
```

```{r,FactorialBy-MeansB}
plotMeansBy(Outcome~FactorA,by=FactorB,conf.level=.99,mu=5,rope=c(3,7))
```

#### Significance Tests for the Means

```{r}
testMeansBy(Outcome~FactorA,by=FactorB)
```

```{r}
testMeansBy(Outcome~FactorA,by=FactorB,mu=5)
```

#### Effect Size for the Means

```{r}
standardizeMeansBy(Outcome~FactorA,by=FactorB)
```

```{r}
standardizeMeansBy(Outcome~FactorA,by=FactorB,conf.level=.99,mu=5)
```

### Analyses of a Group Comparison

```{r}
Comparison=factor(FactorA,c("A1","A2"))
CompData=na.omit(data.frame(Outcome,Comparison,FactorB))
```

#### Confidence Interval for a Mean Difference

```{r}
with(CompData,estimateDifferenceBy(Outcome~Comparison,by=FactorB))
```

```{r}
with(CompData,estimateDifferenceBy(Outcome~Comparison,by=FactorB,conf.level=.99))
```

#### Plot of the Confidence Interval for the Mean Difference

```{r,FactorialBy-DifferenceA}
with(CompData,plotDifferenceBy(Outcome~Comparison,by=FactorB))
```

```{r,FactorialBy-DifferenceB}
with(CompData,plotDifferenceBy(Outcome~Comparison,by=FactorB,conf.level=.99,rope=c(-2,2)))
```

#### Significance Test for the Mean Difference

```{r}
with(CompData,testDifferenceBy(Outcome~Comparison,by=FactorB))
```

```{r}
with(CompData,testDifferenceBy(Outcome~Comparison,by=FactorB,mu=2))
```

#### Effect Size for the Mean Difference

```{r}
with(CompData,standardizeDifferenceBy(Outcome~Comparison,by=FactorB))
```

```{r}
with(CompData,standardizeDifferenceBy(Outcome~Comparison,by=FactorB,conf.level=.99,mu=2))
```

### Analyses of a Factor Contrast

```{r}
A1vsOthers <- c(-1,.5,.5)
```

#### Confidence Interval for a Contrast

```{r}
estimateContrastBy(Outcome~FactorA,by=FactorB,contrast=A1vsOthers)
```

```{r}
estimateContrastBy(Outcome~FactorA,by=FactorB,contrast=A1vsOthers,conf.level=.99)
```

#### Plots of Confidence Intervals for a Contrast

```{r,FactorialBy-ContrastA}
plotContrastBy(Outcome~FactorA,by=FactorB,contrast=A1vsOthers)
```

```{r,FactorialBy-ContrastB}
plotContrastBy(Outcome~FactorA,by=FactorB,contrast=A1vsOthers,labels=c("A1","Others"),conf.level=.99,rope=c(-2,2))
```

#### Significance Test for a Contrast

```{r}
testContrastBy(Outcome~FactorA,by=FactorB,contrast=A1vsOthers)
```

```{r}
testContrastBy(Outcome~FactorA,by=FactorB,contrast=A1vsOthers,mu=4)
```

#### Effect Size for a Contrast

```{r}
standardizeContrastBy(Outcome~FactorA,by=FactorB,contrast=A1vsOthers)
```

```{r}
standardizeContrastBy(Outcome~FactorA,by=FactorB,contrast=A1vsOthers,conf.level=.99)
```
