---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{FactorialBy - Factorial (Between-Subjects) Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## FactorialBy - Factorial (Between-Subjects) Tutorial with Summary Statistics

### Enter Summary Statistics

```{r}
A1 <- c(N=4,M=2.000,SD=2.449)
A2 <- c(N=4,M=6.000,SD=2.449)
A3 <- c(N=4,M=7.000,SD=2.449)
BetweenSummaryB1 <- rbind(A1,A2,A3)

A1 <- c(N=4,M=4.000,SD=2.449)
A2 <- c(N=4,M=4.000,SD=2.449)
A3 <- c(N=4,M=5.000,SD=2.449)
BetweenSummaryB2 <- rbind(A1,A2,A3)

FactorialSummary <- list("B1"=BetweenSummaryB1,"B2"=BetweenSummaryB2)
class(FactorialSummary) <- "bss"
```

### Analyses of Multiple Groups

#### Confidence Intervals for the Means

```{r}
estimateMeansBy(FactorialSummary)
```

```{r}
estimateMeansBy(FactorialSummary,conf.level=.99)
```

#### Plot of the Confidence Intervals for the Means

```{r,FactorialBy-MeansA}
plotMeansBy(FactorialSummary)
```

```{r,FactorialBy-MeansB}
plotMeansBy(FactorialSummary,conf.level=.99,mu=5,rope=c(3,7))
```

#### Significance Tests for the Means

```{r}
testMeansBy(FactorialSummary)
```

```{r}
testMeansBy(FactorialSummary,mu=5)
```

#### Effect Size for the Means

```{r}
standardizeMeansBy(FactorialSummary)
```

```{r}
standardizeMeansBy(FactorialSummary,conf.level=.99,mu=5)
```

### Analyses of a Group Comparison

```{r}
CompSummaryB1 <- BetweenSummaryB1[c("A1","A2"),]
CompSummaryB2 <- BetweenSummaryB2[c("A1","A2"),]
CompSummary <- list("B1"=CompSummaryB1,"B2"=CompSummaryB2)
class(CompSummary) <- "bss"
```

#### Confidence Interval for a Mean Difference

```{r}
estimateDifferenceBy(CompSummary)
```

```{r}
estimateDifferenceBy(CompSummary,conf.level=.99)
```

#### Plot of the Confidence Interval for the Mean Difference

```{r,FactorialBy-DifferenceA}
plotDifferenceBy(CompSummary)
```

```{r,FactorialBy-DifferenceB}
plotDifferenceBy(CompSummary,conf.level=.99,rope=c(-2,2)) 
```

#### Significance Test for the Mean Difference

```{r}
testDifferenceBy(CompSummary)
```

```{r}
testDifferenceBy(CompSummary,mu=-2)
```

#### Effect Size for the Mean Difference

```{r}
standardizeDifferenceBy(CompSummary)
```

```{r}
standardizeDifferenceBy(CompSummary,conf.level=.99,mu=-2)
```

### Analyses of a Factor Contrast

```{r}
A1vsOthers <- c(-1,.5,.5)
```

#### Confidence Interval for a Contrast

```{r}
estimateContrastBy(FactorialSummary,contrast=A1vsOthers)
```

```{r}
estimateContrastBy(FactorialSummary,contrast=A1vsOthers,conf.level=.99)
```

#### Plots of Confidence Intervals for a Contrast

```{r,FactorialBy-ContrastA}
plotContrastBy(FactorialSummary,contrast=A1vsOthers)
```

```{r,FactorialBy-ContrastB}
plotContrastBy(FactorialSummary,contrast=A1vsOthers,labels=c("A1","Others"),conf.level=.99,rope=c(-2,2))
```

#### Significance Test for a Contrast

```{r}
testContrastBy(FactorialSummary,contrast=A1vsOthers)
```

```{r}
testContrastBy(FactorialSummary,contrast=A1vsOthers,mu=4)
```

#### Effect Size for a Contrast

```{r}
standardizeContrastBy(FactorialSummary,contrast=A1vsOthers)
```

```{r}
standardizeContrastBy(FactorialSummary,contrast=A1vsOthers,conf.level=.99)
```
