---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{MixedBy - Mixed Design (Between-Subjects and Within-Subjects) Tutorial with Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## MixedBy - Mixed Design (Between-Subjects and Within-Subjects) Tutorial with Data

### Enter Data

```{r}
Factor <- c(1,1,1,1,2,2,2,2)
Outcome1 <- c(0,0,3,5,1,3,6,6)
Outcome2 <- c(4,7,4,9,3,1,6,6)
Outcome3 <- c(4,9,6,9,3,3,6,8)
Factor <- factor(Factor,levels=c(1,2),labels=c("Level1","Level2"))
MixedData <- data.frame(Factor,Outcome1,Outcome2,Outcome3)
```

### Analyses of Multiple Variables

#### Confidence Intervals for the Means

```{r}
estimateMeansBy(Outcome1,Outcome2,Outcome3,by=Factor)
```

```{r}
estimateMeansBy(Outcome1,Outcome2,Outcome3,by=Factor,conf.level=.99)
```

#### Plots of Confidence Intervals for the Means

```{r,MixedBy-MeansA}
plotMeansBy(Outcome1,Outcome2,Outcome3,by=Factor)
```

```{r,MixedBy-MeansB}
plotMeansBy(Outcome1,Outcome2,Outcome3,by=Factor,conf.level=.99,mu=5,rope=c(3,7)) 
```

#### Significance Tests for the Means

```{r}
testMeansBy(Outcome1,Outcome2,Outcome3,by=Factor)
```

```{r}
testMeansBy(Outcome1,Outcome2,Outcome3,by=Factor,mu=5)
```

#### Effect Size for the Means

```{r}
standardizeMeansBy(Outcome1,Outcome2,Outcome3,by=Factor)
```

```{r}
standardizeMeansBy(Outcome1,Outcome2,Outcome3,by=Factor,mu=5,conf.level=.99)
```

### Analyses of a Variable Comparison

#### Confidence Interval for the Mean Difference

```{r}
estimateDifferenceBy(Outcome1,Outcome2,by=Factor)
```

```{r}
estimateDifferenceBy(Outcome1,Outcome2,by=Factor,conf.level=.99)
```

#### Plots of Confidence Intervals for the Mean Difference

```{r,MixedBy-DifferenceA}
plotDifferenceBy(Outcome1,Outcome2,by=Factor)
```

```{r,MixedBy-DifferenceB}
plotDifferenceBy(Outcome1,Outcome2,by=Factor,conf.level=.99,rope=c(-2,2))
```

#### Significance Test for the Mean Difference

```{r}
testDifferenceBy(Outcome1,Outcome2,by=Factor)
```

```{r}
testDifferenceBy(Outcome1,Outcome2,by=Factor,mu=-2)
```

#### Effect Size for the Mean Difference

```{r}
standardizeDifferenceBy(Outcome1,Outcome2,by=Factor)
```

```{r}
standardizeDifferenceBy(Outcome1,Outcome2,by=Factor,conf.level=.99)
```

### Analyses of a Variable Contrast

```{r}
O1vsOthers <- c(-1,.5,.5)
```

#### Confidence Interval for the Contrast

```{r}
estimateContrastBy(Outcome1,Outcome2,Outcome3,by=Factor,contrast=O1vsOthers)
```

```{r}
estimateContrastBy(Outcome1,Outcome2,Outcome3,by=Factor,contrast=O1vsOthers,conf.level=.99)
```

#### Plots of Confidence Intervals for a Contrast

```{r,MixedBy-ContrastA}
plotContrastBy(Outcome1,Outcome2,Outcome3,by=Factor,contrast=O1vsOthers)
```

```{r,MixedBy-ContrastB}
plotContrastBy(Outcome1,Outcome2,Outcome3,by=Factor,contrast=O1vsOthers,labels=c("Outcome1","Others"),conf.level=.99,rope=c(-2,2))
```

#### Significance Test for the Contrast

```{r}
testContrastBy(Outcome1,Outcome2,Outcome3,by=Factor,contrast=O1vsOthers)
```

```{r}
testContrastBy(Outcome1,Outcome2,Outcome3,by=Factor,contrast=O1vsOthers,mu=4)
```

#### Effect Size for the Contrast

```{r}
standardizeContrastBy(Outcome1,Outcome2,Outcome3,by=Factor,contrast=O1vsOthers)
```

```{r}
standardizeContrastBy(Outcome1,Outcome2,Outcome3,by=Factor,contrast=O1vsOthers,conf.level=.99)
```
