---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{MixedBy - Mixed Design (Between-Subjects and Within-Subjects) Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## MixedBy - Mixed Design (Between-Subjects and Within-Subjects) Tutorial with Summary Statistics

### Enter Summary Statistics

```{r}
Time1 <- c(N=4,M=2.000,SD=2.449)
Time2 <- c(N=4,M=6.000,SD=2.449)
Time3 <- c(N=4,M=7.000,SD=2.449)
WithinSummaryG1 <- rbind(Time1,Time2,Time3)

Time1 <- c(N=4,M=4.000,SD=2.449)
Time2 <- c(N=4,M=4.000,SD=2.449)
Time3 <- c(N=4,M=5.000,SD=2.449)
WithinSummaryG2 <- rbind(Time1,Time2,Time3)

MixedSummary <- list("LeveG1"=WithinSummaryG1,"LeveG2"=WithinSummaryG2)
class(MixedSummary) <- "wss"

WithinCorrG1 <- declareCorrMatrix("Time1","Time2","Time3")
WithinCorrG1["Time1",] <- c(1.000,.500,.389)
WithinCorrG1["Time2",] <- c(.500,1.000,.889)
WithinCorrG1["Time3",] <- c(.389,.889,1.000)

WithinCorrG2 <- declareCorrMatrix("Time1","Time2","Time3")
WithinCorrG2["Time1",] <- c(1.000,.889,.778)
WithinCorrG2["Time2",] <- c(.889,1.000,.889)
WithinCorrG2["Time3",] <- c(.778,.889,1.000)

MixedCorr <- list("LeveG1"=WithinCorrG1,"LeveG2"=WithinCorrG2)
class(MixedCorr) <- "wss"
```

### Analyses of Multiple Variables

#### Confidence Intervals for the Means

```{r}
estimateMeansBy(MixedSummary)
```

```{r}
estimateMeansBy(MixedSummary,conf.level=.99)
```

#### Plots of Confidence Intervals for the Means

```{r,MixedBy-MeansA}
plotMeansBy(MixedSummary)
```

```{r,MixedBy-MeansB}
plotMeansBy(MixedSummary,conf.level=.99,mu=5,rope=c(3,7))
```

#### Significance Tests for the Means

```{r}
testMeansBy(MixedSummary)
```

```{r}
testMeansBy(MixedSummary,mu=5)
```

#### Effect Size for the Means

```{r}
standardizeMeansBy(MixedSummary)
```

```{r}
standardizeMeansBy(MixedSummary,mu=5,conf.level=.99)
```

### Analyses of a Variable Comparison

```{r}
CompSummaryG1 <- WithinSummaryG1[c("Time1","Time2"),]
CompSummaryG2 <- WithinSummaryG2[c("Time1","Time2"),]
CompSummary <- list("Group1"=WithinSummaryG1,"Group2"=WithinSummaryG2)
class(CompSummary) <- "wss"
```

#### Confidence Interval for the Mean Difference

```{r}
estimateDifferenceBy(CompSummary,MixedCorr)
```

```{r}
estimateDifferenceBy(CompSummary,MixedCorr,conf.level=.99)
```

#### Plots of Confidence Intervals for the Mean Difference

```{r,MixedBy-DifferenceA}
plotDifferenceBy(CompSummary,MixedCorr)
```

```{r,MixedBy-DifferenceB}
plotDifferenceBy(CompSummary,MixedCorr,conf.level=.99,rope=c(-2,2))
```

#### Significance Test for the Mean Difference

```{r}
testDifferenceBy(CompSummary,MixedCorr)
```

```{r}
testDifferenceBy(CompSummary,MixedCorr,mu=-2)
```

#### Effect Size for the Mean Difference

```{r}
standardizeDifferenceBy(CompSummary,MixedCorr)
```

```{r}
standardizeDifferenceBy(CompSummary,MixedCorr,conf.level=.99)
```

### Analyses of a Variable Contrast

```{r}
T1vsOthers <- c(-1,.5,.5)
```

#### Confidence Interval for the Contrast

```{r}
estimateContrastBy(MixedSummary,MixedCorr,contrast=T1vsOthers)
```

```{r}
estimateContrastBy(MixedSummary,MixedCorr,contrast=T1vsOthers,conf.level=.99)
```

#### Plots of Confidence Intervals for a Contrast

```{r,MixedBy-ContrastA}
plotContrastBy(MixedSummary,MixedCorr,contrast=T1vsOthers)
```

```{r,MixedBy-ContrastB}
plotContrastBy(MixedSummary,MixedCorr,contrast=T1vsOthers,labels=c("Time1","Others"),conf.level=.99,rope=c(-2,2))
```

#### Significance Test for the Contrast

```{r}
testContrastBy(MixedSummary,MixedCorr,contrast=T1vsOthers)
```

```{r}
testContrastBy(MixedSummary,MixedCorr,contrast=T1vsOthers,mu=4)
```

#### Effect Size for the Contrast

```{r}
standardizeContrastBy(MixedSummary,MixedCorr,contrast=T1vsOthers)
```

```{r}
standardizeContrastBy(MixedSummary,MixedCorr,contrast=T1vsOthers,conf.level=.99)
```
