---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{MixedBy - Mixed Design (Between-Subjects and Within-Subjects) Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## MixedBy - Mixed Design (Between-Subjects and Within-Subjects) Tutorial with Summary Statistics

### Enter Summary Statistics

This code inputs the variable summaries and creates a summary table.

```{r}
Outcome1 <- c(N=4,M=2.000,SD=2.449)
Outcome2 <- c(N=4,M=6.000,SD=2.449)
Outcome3 <- c(N=4,M=7.000,SD=2.449)
WithinSummaryL1 <- rbind(Outcome1,Outcome2,Outcome3)

Outcome1 <- c(N=4,M=4.000,SD=2.449)
Outcome2 <- c(N=4,M=4.000,SD=2.449)
Outcome3 <- c(N=4,M=5.000,SD=2.449)
WithinSummaryL2 <- rbind(Outcome1,Outcome2,Outcome3)

MixedSummary <- list("Level1"=WithinSummaryL1,"Level2"=WithinSummaryL2)
class(MixedSummary) <- "wss"
```

This code creates a correlation matrix, enters just the top triangle, and then uses a function to fill in the whole matrix.

```{r}
WithinCorrL1 <- declareCorrMatrix("Outcome1","Outcome2","Outcome3")
WithinCorrL1["Outcome1",] <- c(1.000,.500,.389)
WithinCorrL1["Outcome2",] <- c(.500,1.000,.889)
WithinCorrL1["Outcome3",] <- c(.389,.889,1.000)

WithinCorrL2 <- declareCorrMatrix("Outcome1","Outcome2","Outcome3")
WithinCorrL2["Outcome1",] <- c(1.000,.889,.778)
WithinCorrL2["Outcome2",] <- c(.889,1.000,.889)
WithinCorrL2["Outcome3",] <- c(.778,.889,1.000)

MixedCorr <- list("Level1"=WithinCorrL1,"Level2"=WithinCorrL2)
class(MixedCorr) <- "wss"
```

### Analyses of Multiple Variables

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

#### Confidence Intervals for the Means

This code will provide a table of descriptive statistics and confidence intervals for each level of the factor.

```{r}
estimateMeansBy(MixedSummary)
```

The code defaults to 95% confidence intervals. This can be changed if desired.

```{r}
estimateMeansBy(MixedSummary,conf.level=.99)
```

#### Plots of Confidence Intervals for the Means

This code will produce a graph of the confidence intervals for each level of the factor.

```{r,MixedBy-MeansA}
plotMeansBy(MixedSummary)
```

Of course, it is possible to change from the default confidence level. Additionally, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence.

```{r,MixedBy-MeansB}
plotMeansBy(MixedSummary,conf.level=.99,mu=5,rope=c(3,7))
```

#### Significance Tests for the Means

This code will produce a table of NHST separately for each level of the factor. In this case, all the means are tested against a value of zero.

```{r}
testMeansBy(MixedSummary)
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).

```{r}
testMeansBy(MixedSummary,mu=5)
```

#### Effect Size for the Means

This code will produce a table of standardized mean differences separately for each level of the factor. In this case, the mean is compared to zero to form the effect size.

```{r}
standardizeMeansBy(MixedSummary)
```

Here too it is possible to alter the width of the confidence intervals and to establish a more plausible comparison value for the effect size.

```{r}
standardizeMeansBy(MixedSummary,mu=5,conf.level=.99)
```

### Analyses of a Variable Comparison

This section produces analyses that are equivalent to comparisons of two levels of a factor.

This code creates a new table that identifies the two levels for comparison and repeats for the second subset.

```{r}
CompSummaryL1 <- WithinSummaryL1[c("Outcome1","Outcome2"),]
CompSummaryL2 <- WithinSummaryL2[c("Outcome1","Outcome2"),]
CompSummary <- list("Level1"=WithinSummaryL1,"Level2"=WithinSummaryL2)
class(CompSummary) <- "wss"
```

#### Confidence Interval for the Mean Difference

This code identifies the two levels for comparison and estimates the confidence interval of the difference.

```{r}
estimateDifferenceBy(CompSummary,MixedCorr)
```

Of course, you can change the confidence level from the default 95% if desired.

```{r}
estimateDifferenceBy(CompSummary,MixedCorr,conf.level=.99)
```

#### Plots of Confidence Intervals for the Mean Difference

This code obtains and plots the confidence intervals for the levels and the mean difference in the identified comparison.

```{r,MixedBy-DifferenceA}
plotDifferenceBy(CompSummary,MixedCorr)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added.

```{r,MixedBy-DifferenceB}
plotDifferenceBy(CompSummary,MixedCorr,conf.level=.99,rope=c(-2,2))
```

#### Significance Test for the Mean Difference

This code produces NHST for the identified comparison (using a default test value of zero).

```{r}
testDifferenceBy(CompSummary,MixedCorr)
```

If the default value of zero is not plausible, it too can be changed.

```{r}
testDifferenceBy(CompSummary,MixedCorr,mu=-2)
```

#### Effect Size for the Mean Difference

This code calculates a standardized mean difference for the comparison and its confidence interval.

```{r}
standardizeDifferenceBy(CompSummary,MixedCorr)
```

The width of the confidence interval for the effect size can be altered if desired.

```{r}
standardizeDifferenceBy(CompSummary,MixedCorr,conf.level=.99)
```

### Analyses of a Variable Contrast

This section produces analyses that are equivalent to analyses involving multiple levels of a factor.

This code identifies a contrast among the levels.

```{r}
O1vsOthers <- c(-1,.5,.5)
```

#### Confidence Interval for the Contrast

This code produces a confidence interval for that contrast.

```{r}
estimateContrastBy(MixedSummary,MixedCorr,contrast=O1vsOthers)
```

As in all other cases, the default value of the confidence interval can be changed.

```{r}
estimateContrastBy(MixedSummary,MixedCorr,contrast=O1vsOthers,conf.level=.99)
```

#### Plots of Confidence Intervals for a Contrast

This code obtains and plots the confidence intervals for the groups and the mean difference in the identified contrast.

```{r,MixedBy-ContrastA}
plotContrastBy(MixedSummary,MixedCorr,contrast=O1vsOthers)
```

The width of the confidence interval for the contrast can be altered and a region of practical equivalence can be added.

```{r,MixedBy-ContrastB}
plotContrastBy(MixedSummary,MixedCorr,contrast=O1vsOthers,labels=c("Outcome1","Others"),conf.level=.99,rope=c(-2,2))
```

#### Significance Test for the Contrast

This code produces a NHST for the identified contrast. It tests the contrast against a value of zero by default.

```{r}
testContrastBy(MixedSummary,MixedCorr,contrast=O1vsOthers)
```

If desired, the contrast can be tested against other values.

```{r}
testContrastBy(MixedSummary,MixedCorr,contrast=O1vsOthers,mu=4)
```

#### Effect Size for the Contrast

This code calculates a standardized contrast and its confidence interval.

```{r}
standardizeContrastBy(MixedSummary,MixedCorr,contrast=O1vsOthers)
```

The width of the confidence interval for the effect size can be altered if desired.

```{r}
standardizeContrastBy(MixedSummary,MixedCorr,contrast=O1vsOthers,conf.level=.99)
```
