---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{MixedBy - Mixed Design (Between-Subjects and Within-Subjects) Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## MixedBy - Mixed Design (Between-Subjects and Within-Subjects) Tutorial with Summary Statistics

### Enter Summary Statistics

```{r}
Outcome1 <- c(N=4,M=2.000,SD=2.449)
Outcome2 <- c(N=4,M=6.000,SD=2.449)
Outcome3 <- c(N=4,M=7.000,SD=2.449)
WithinSummaryL1 <- rbind(Outcome1,Outcome2,Outcome3)

Outcome1 <- c(N=4,M=4.000,SD=2.449)
Outcome2 <- c(N=4,M=4.000,SD=2.449)
Outcome3 <- c(N=4,M=5.000,SD=2.449)
WithinSummaryL2 <- rbind(Outcome1,Outcome2,Outcome3)

MixedSummary <- list("Level1"=WithinSummaryL1,"Level2"=WithinSummaryL2)
class(MixedSummary) <- "wss"

WithinCorrL1 <- declareCorrMatrix("Outcome1","Outcome2","Outcome3")
WithinCorrL1["Outcome1",] <- c(1.000,.500,.389)
WithinCorrL1["Outcome2",] <- c(.500,1.000,.889)
WithinCorrL1["Outcome3",] <- c(.389,.889,1.000)

WithinCorrL2 <- declareCorrMatrix("Outcome1","Outcome2","Outcome3")
WithinCorrL2["Outcome1",] <- c(1.000,.889,.778)
WithinCorrL2["Outcome2",] <- c(.889,1.000,.889)
WithinCorrL2["Outcome3",] <- c(.778,.889,1.000)

MixedCorr <- list("Level1"=WithinCorrL1,"Level2"=WithinCorrL2)
class(MixedCorr) <- "wss"
```

### Analyses of Multiple Variables

#### Confidence Intervals for the Means

```{r}
estimateMeansBy(MixedSummary)
```

```{r}
estimateMeansBy(MixedSummary,conf.level=.99)
```

#### Plots of Confidence Intervals for the Means

```{r,MixedBy-MeansA}
plotMeansBy(MixedSummary)
```

```{r,MixedBy-MeansB}
plotMeansBy(MixedSummary,conf.level=.99,mu=5,rope=c(3,7))
```

#### Significance Tests for the Means

```{r}
testMeansBy(MixedSummary)
```

```{r}
testMeansBy(MixedSummary,mu=5)
```

#### Effect Size for the Means

```{r}
standardizeMeansBy(MixedSummary)
```

```{r}
standardizeMeansBy(MixedSummary,mu=5,conf.level=.99)
```

### Analyses of a Variable Comparison

```{r}
CompSummaryL1 <- WithinSummaryL1[c("Outcome1","Outcome2"),]
CompSummaryL2 <- WithinSummaryL2[c("Outcome1","Outcome2"),]
CompSummary <- list("Level1"=WithinSummaryL1,"Level2"=WithinSummaryL2)
class(CompSummary) <- "wss"
```

#### Confidence Interval for the Mean Difference

```{r}
estimateDifferenceBy(CompSummary,MixedCorr)
```

```{r}
estimateDifferenceBy(CompSummary,MixedCorr,conf.level=.99)
```

#### Plots of Confidence Intervals for the Mean Difference

```{r,MixedBy-DifferenceA}
plotDifferenceBy(CompSummary,MixedCorr)
```

```{r,MixedBy-DifferenceB}
plotDifferenceBy(CompSummary,MixedCorr,conf.level=.99,rope=c(-2,2))
```

#### Significance Test for the Mean Difference

```{r}
testDifferenceBy(CompSummary,MixedCorr)
```

```{r}
testDifferenceBy(CompSummary,MixedCorr,mu=-2)
```

#### Effect Size for the Mean Difference

```{r}
standardizeDifferenceBy(CompSummary,MixedCorr)
```

```{r}
standardizeDifferenceBy(CompSummary,MixedCorr,conf.level=.99)
```

### Analyses of a Variable Contrast

```{r}
O1vsOthers <- c(-1,.5,.5)
```

#### Confidence Interval for the Contrast

```{r}
estimateContrastBy(MixedSummary,MixedCorr,contrast=O1vsOthers)
```

```{r}
estimateContrastBy(MixedSummary,MixedCorr,contrast=O1vsOthers,conf.level=.99)
```

#### Plots of Confidence Intervals for a Contrast

```{r,MixedBy-ContrastA}
plotContrastBy(MixedSummary,MixedCorr,contrast=O1vsOthers)
```

```{r,MixedBy-ContrastB}
plotContrastBy(MixedSummary,MixedCorr,contrast=O1vsOthers,labels=c("Outcome1","Others"),conf.level=.99,rope=c(-2,2))
```

#### Significance Test for the Contrast

```{r}
testContrastBy(MixedSummary,MixedCorr,contrast=O1vsOthers)
```

```{r}
testContrastBy(MixedSummary,MixedCorr,contrast=O1vsOthers,mu=4)
```

#### Effect Size for the Contrast

```{r}
standardizeContrastBy(MixedSummary,MixedCorr,contrast=O1vsOthers)
```

```{r}
standardizeContrastBy(MixedSummary,MixedCorr,contrast=O1vsOthers,conf.level=.99)
```
