---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Relational Intervals - Repeated Measures (Within-Subjects) Tutorial with Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Relational Intervals - Repeated Measures (Within-Subjects) Tutorial with Data

### Enter Data

This code inputs the variable names and creates a viewable data frame.

```{r}
Outcome1 <- c(0,0,3,5)
Outcome2 <- c(4,7,4,9)
Outcome3 <- c(9,6,4,9)
RepeatedData <- data.frame(Outcome1,Outcome2,Outcome3)
```

### Relational Intervals

This code will provide a table of descriptive statistics, the confidence intervals, and the relational intervals for each level of the factor.

```{r}
estimateRelational(Outcome1,Outcome2,Outcome3)
```

This code will produce a graph of the confidence intervals for each level of the factor. It will then add relational intervals to the existing plot.

```{r,Repeated-RelationalA}
plotMeans(Outcome1,Outcome2,Outcome3)
addRelational(Outcome1,Outcome2,Outcome3)
```

Instead, this code can be used to directly create the graph of confidence intervals and relational intervals for each level of the factor.

```{r,Repeated-RelationalB}
plotRelational(Outcome1,Outcome2,Outcome3)
```

And of course, the confidence levels can be altered and a comparison line to represent a population (or test) value can be added.

```{r,Repeated-RelationalC}
plotRelational(Outcome1,Outcome2,Outcome3,conf.level=.99,mu=5)
```
