---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Relational Intervals - OneWay (Between-Subjects) Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Relational Intervals - OneWay (Between-Subjects) Tutorial with Summary Statistics

### Source the EASI Functions

### Enter Summary Statistics

This code inputs the group summaries and creates a single summary table.

```{r}
Level1 <- c(N=4,M=2.000,SD=2.449)
Level2 <- c(N=4,M=6.000,SD=2.449)
Level3 <- c(N=4,M=7.000,SD=2.449)
OneWaySummary <- rbind(Level1,Level2,Level3)
class(OneWaySummary) <- "bss"
```

### Relational Intervals

This code will provide a table of descriptive statistics, the confidence intervals, and the relational intervals for each level of the factor.

```{r}
estimateRelational(OneWaySummary)
```

This code will produce a graph of the confidence intervals for each level of the factor. It will then add relational intervals to the existing plot.

```{r,OneWay-RelationalA}
plotMeans(OneWaySummary)
addRelational(OneWaySummary)
```

Instead, this code can be used to directly create the graph of confidence intervals and relational intervals for each level of the factor.

```{r,OneWay-RelationalB}
plotRelational(OneWaySummary)
```

And of course, the confidence levels can be altered and a comparison line to represent a population (or test) value can be added.

```{r,OneWay-RelationalC}
plotRelational(OneWaySummary,conf.level=.99,mu=5)
```
