---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Relational Intervals - Repeated (Within-Subjects) Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Relational Intervals - Repeated (Within-Subjects) Tutorial with Summary Statistics

### Enter Summary Statistics

This code inputs the variable summaries and creates a summary table.

```{r}
Outcome1 <- c(N=4,M=2.000,SD=2.449)
Outcome2 <- c(N=4,M=6.000,SD=2.449)
Outcome3 <- c(N=4,M=7.000,SD=2.449)
RepeatedSummary <- rbind(Outcome1,Outcome2,Outcome3)
class(RepeatedSummary) <- "wss"
```

This code creates a correlation matrix, enters just the top triangle, and then uses a function to fill in the whole matrix.

```{r}
RepeatedCorr <- declareCorrMatrix("Outcome1","Outcome2","Outcome3")
RepeatedCorr["Outcome1","Outcome2"] <- .500
RepeatedCorr["Outcome1","Outcome3"] <- .056
RepeatedCorr["Outcome2","Outcome3"] <- .389
RepeatedCorr <- fillCorrMatrix(RepeatedCorr)
```

### Relational Intervals

This code will provide a table of descriptive statistics, the confidence intervals, and the relational intervals for each level of the factor.

```{r}
estimateRelational(RepeatedSummary,RepeatedCorr)
```

This code will produce a graph of the confidence intervals for each level of the factor. It will then add relational intervals to the existing plot.

```{r,Repeated-RelationalA}
plotMeans(RepeatedSummary)
addRelational(RepeatedSummary,RepeatedCorr)
```

Instead, this code can be used to directly create the graph of confidence intervals and relational intervals for each level of the factor.

```{r,Repeated-RelationalB}
plotRelational(RepeatedSummary,RepeatedCorr)
```

And of course, the confidence levels can be altered and a comparison line to represent a population (or test) value can be added.

```{r,Repeated-RelationalC}
plotRelational(RepeatedSummary,RepeatedCorr,conf.level=.99,mu=5)
```
