---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Correlations Tutorial with Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Correlations Tutorial with Data

### Enter Data

This code inputs the variable names and creates a viewable data frame.
```{r}
Outcome1 <- c(0,0,3,5)
Outcome2 <- c(4,7,4,9)
Outcome3 <- c(9,6,4,9)
RepeatedData <- data.frame(Outcome1,Outcome2,Outcome3)
```

### Descriptive Statistics

This code obtains the descriptive statistics for the data frame.
```{r}
describeMeans(Outcome1,Outcome2,Outcome3)
```

This code obtains a table of correlations for the entire data frame.
```{r}
describeCorrelations(Outcome1,Outcome2,Outcome3)
```

### Analyses of a Correlation

This section produces analyses of a single correlation.

#### Confidence Interval for the Correlation

This code will provide the confidence interval for the correlation.
```{r}
estimateCorrelation(Outcome1,Outcome2)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateCorrelation(Outcome1,Outcome2,conf.level=.99)
```

#### Plot of the Confidence Interval for the Correlation

This code will produce a graph of the confidence interval for the correlation.
```{r,Correlation-A}
plotCorrelation(Outcome1,Outcome2)
```

Of course, it is possible to change from the default confidence level.
```{r,Correlation-B}
plotCorrelation(Outcome1,Outcome2,conf.level=.99)
```

#### Significance Test for the Correlation

This code will produce a table of NHST for the correlation (against a value of zero).
```{r}
testCorrelation(Outcome1,Outcome2)
```

### Analyses of Several Correlations

This section extends the analyses to correlations among multiple variables.

#### Confidence Intervals for the Correlations

This code will provide the confidence intervals for the correlations.
```{r}
estimateCorrelations(Outcome1,Outcome2,Outcome3)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateCorrelations(Outcome1,Outcome2,Outcome3,conf.level=.99)
```

#### Plots of the Confidence Intervals for the Correlations

This code will produce a graph of the confidence intervals for the correlations.
```{r,Correlations-A}
plotCorrelations(Outcome1,Outcome2,Outcome3)
```

Of course, it is possible to change from the default confidence level.
```{r,Correlations-B}
plotCorrelations(Outcome1,Outcome2,Outcome3,conf.level=.99)
```

#### Significance Tests for the Correlation

This code will produce a table of NHST for the correlations (against a value of zero).
```{r}
testCorrelations(Outcome1,Outcome2,Outcome3)
```
