---
title: "Factorial (Between-Subjects) Tutorial with Data"
author: "Craig A. Wendorf"
date: "2020-10-20"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Factorial (Between-Subjects) Tutorial with Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8",filename="render_toc.R")
```

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Factorial (Between-Subjects) Tutorial with Data

### Table of Contents

```{r toc, echo=FALSE}
sourceDir <- getSrcDirectory(function(dummy) {dummy})
setwd(sourceDir)
render_toc("FactorialDataTutorial.Rmd")
```

### Data Management

#### Data Entry

This code inputs the variable names and creates a viewable data frame.
```{r}
FactorA <- c(1,1,1,1,2,2,2,2,3,3,3,3,1,1,1,1,2,2,2,2,3,3,3,3)
FactorB <- c(1,1,1,1,1,1,1,1,1,1,1,1,2,2,2,2,2,2,2,2,2,2,2,2)
Outcome <- c(0,0,3,5,4,7,4,9,4,9,6,9,3,1,6,6,2,2,5,7,2,4,7,7)
FactorA <- factor(FactorA,levels=c(1,2,3),labels=c("A1","A2","A3"))
FactorB <- factor(FactorB,levels=c(1,2),labels=c("B1","B2"))
FactorialData <- data.frame(FactorA,FactorB,Outcome)
```

This code subsets the data into two different data frames (for simple effects analysis).
```{r}
FactorialDataB1 <- subset(FactorialData,FactorB=="B1")
FactorialDataB2 <- subset(FactorialData,FactorB=="B2")
```

#### Plot of the Data

```{r,Factorial-Violins}
with(FactorialDataB1,plotViolins(Outcome~FactorA,main="Summaries of the Groups"))
with(FactorialDataB1,plotBoxes(Outcome~FactorA,add=TRUE))
with(FactorialDataB1,plotData(Outcome~FactorA,add=TRUE,method="stack",pch=16))
with(FactorialDataB2,plotViolins(Outcome~FactorA,main="Summaries of the Groups"))
with(FactorialDataB2,plotBoxes(Outcome~FactorA,add=TRUE))
with(FactorialDataB2,plotData(Outcome~FactorA,add=TRUE,method="stack",pch=16))
```

#### Descriptive Statistics

This code obtains the descriptive statistics for the two data frames.
```{r}
with(FactorialDataB1,describeMeans(Outcome~FactorA))
with(FactorialDataB2,describeMeans(Outcome~FactorA))
```

### Analyses of the Means

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

#### Confidence Intervals for the Means

This code will provide tables of confidence intervals for each level of the factor.
```{r}
with(FactorialDataB1,estimateMeans(Outcome~FactorA))
with(FactorialDataB2,estimateMeans(Outcome~FactorA))
```

This code will produce a graph of the confidence intervals for each level of the factor.
```{r,Factorial-MeansA}
with(FactorialDataB1,plotMeans(Outcome~FactorA))
with(FactorialDataB2,plotMeans(Outcome~FactorA))
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
with(FactorialDataB1,estimateMeans(Outcome~FactorA,conf.level=.99))
with(FactorialDataB2,estimateMeans(Outcome~FactorA,conf.level=.99))
```

For the graph, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence in addition to changing the confidence level.
```{r,Factorial-MeansB}
with(FactorialDataB1,plotMeans(Outcome~FactorA,conf.level=.99,mu=5,rope=c(3,7)))
with(FactorialDataB2,plotMeans(Outcome~FactorA,conf.level=.99,mu=5,rope=c(3,7)))
```

#### Significance Tests for the Means

This code will produce a table of NHST separately for each level of the factor. In this case, all the means are tested against a value of zero.
```{r}
with(FactorialDataB1,testMeans(Outcome~FactorA))
with(FactorialDataB2,testMeans(Outcome~FactorA))
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
with(FactorialDataB1,testMeans(Outcome~FactorA,mu=5))
with(FactorialDataB2,testMeans(Outcome~FactorA,mu=5))
```

#### Standardized Effect Sizes for the Means

This code will produce a table of standardized mean differences separately for each level of the factor. In this case, the mean is compared to zero to form the effect size.
```{r}
with(FactorialDataB1,estimateStandardizedMeans(Outcome~FactorA))
with(FactorialDataB2,estimateStandardizedMeans(Outcome~FactorA))
```

Here too it is possible to alter the width of the confidence intervals and to establish a more plausible comparison value for the effect size.
```{r}
with(FactorialDataB1,estimateStandardizedMeans(Outcome~FactorA,mu=5,conf.level=.99))
with(FactorialDataB1,estimateStandardizedMeans(Outcome~FactorA,mu=5,conf.level=.99))
```

### Analyses of a Comparison

This section produces analyses that are equivalent to comparisons of two levels of a factor.

This code creates a new factor that identifies the two levels for comparison.
```{r}
CompDataB1 <- with(FactorialDataB1,factor(FactorA,c("A1","A2")))
CompDataB2 <- with(FactorialDataB2,factor(FactorA,c("A1","A2")))
```

#### Confidence Interval for a Mean Difference

This code estimates the confidence interval of the difference.
```{r}
with(FactorialDataB1,estimateMeanDifference(Outcome~CompDataB1))
with(FactorialDataB2,estimateMeanDifference(Outcome~CompDataB2))
```

This code obtains and plots the confidence intervals for the mean difference in the identified comparison.
```{r,Factorial-DifferenceA}
with(FactorialDataB1,plotMeanDifference(Outcome~CompDataB1))
with(FactorialDataB2,plotMeanDifference(Outcome~CompDataB2))
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
with(FactorialDataB1,estimateMeanDifference(Outcome~CompDataB1,conf.level=.99))
with(FactorialDataB2,estimateMeanDifference(Outcome~CompDataB2,conf.level=.99))
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r,Factorial-DifferenceB}
with(FactorialDataB1,plotMeanDifference(Outcome~CompDataB1,conf.level=.99,rope=c(-2,2)))
with(FactorialDataB2,plotMeanDifference(Outcome~CompDataB2,conf.level=.99,rope=c(-2,2)))
```

#### Confidence Intervals for the Comparison

If you wish, you can get the confidence intervals for the means and the mean difference in one command.
```{r}
with(FactorialDataB1,estimateMeanComparison(Outcome~CompDataB1))
with(FactorialDataB2,estimateMeanComparison(Outcome~CompDataB2))
```

This code produces a difference plot using the confidence intervals for the means and the mean difference.
```{r,Factorial-ComparisonA}
with(FactorialDataB1,plotMeanComparison(Outcome~CompDataB1))
with(FactorialDataB2,plotMeanComparison(Outcome~CompDataB2))
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
with(FactorialDataB1,estimateMeanComparison(Outcome~CompDataB1,conf.level=.99))
with(FactorialDataB2,estimateMeanComparison(Outcome~CompDataB2,conf.level=.99))
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r,Factorial-ComparisonB}
with(FactorialDataB1,plotMeanComparison(Outcome~CompDataB1,conf.level=.99,rope=c(-2,2)))
with(FactorialDataB2,plotMeanComparison(Outcome~CompDataB2,conf.level=.99,rope=c(-2,2)))
```

#### Significance Test for the Mean Difference

This code produces NHST for the identified comparison (using a default test value of zero).
```{r}
with(FactorialDataB1,testMeanDifference(Outcome~CompDataB1))
with(FactorialDataB2,testMeanDifference(Outcome~CompDataB2))
```

If the default value of zero is not plausible, it too can be changed.
```{r}
with(FactorialDataB1,testMeanDifference(Outcome~CompDataB1,mu=-2))
with(FactorialDataB2,testMeanDifference(Outcome~CompDataB2,mu=-2))
```

#### Standardized Effect Size for the Mean Difference

This code calculates a standardized mean difference for the comparison and its confidence interval.
```{r}
with(FactorialDataB1,estimateStandardizedMeanDifference(Outcome~CompDataB1))
with(FactorialDataB2,estimateStandardizedMeanDifference(Outcome~CompDataB2))
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
with(FactorialDataB1,estimateStandardizedMeanDifference(Outcome~CompDataB1,conf.level=.99))
with(FactorialDataB2,estimateStandardizedMeanDifference(Outcome~CompDataB2,conf.level=.99))
```

### Analyses of a Contrast

This section produces analyses that are equivalent to analyses involving multiple levels of a factor.

This code identifies a contrast among the groups.
```{r}
A1vsOthers <- c(-1,.5,.5)
```

#### Confidence Interval for a Contrast

This code produces a confidence interval for that contrast.
```{r}
with(FactorialDataB1,estimateMeanContrast(Outcome~FactorA,contrast=A1vsOthers))
with(FactorialDataB2,estimateMeanContrast(Outcome~FactorA,contrast=A1vsOthers))
```

This code obtains and plots the confidence intervals for the groups and the mean difference in the identified contrast.
```{r,Factorial-ContrastA}
with(FactorialDataB1,plotMeanContrast(Outcome~FactorA,contrast=A1vsOthers))
with(FactorialDataB2,plotMeanContrast(Outcome~FactorA,contrast=A1vsOthers))
```

As in all other cases, the default value of the confidence interval can be changed.
```{r}
with(FactorialDataB1,estimateMeanContrast(Outcome~FactorA,contrast=A1vsOthers,conf.level=.99))
with(FactorialDataB2,estimateMeanContrast(Outcome~FactorA,contrast=A1vsOthers,conf.level=.99))
```

The width of the confidence interval for the contrast can be altered and a region of practical equivalence can be added to the graph.
```{r,Factorial-ContrastB}
with(FactorialDataB1,plotMeanContrast(Outcome~FactorA,contrast=A1vsOthers,conf.level=.99,rope=c(-2,2)))
with(FactorialDataB2,plotMeanContrast(Outcome~FactorA,contrast=A1vsOthers,conf.level=.99,rope=c(-2,2)))
```

#### Confidence Intervals for the Subsets

If you wish, you can get the confidence intervals for the mean subsets and the mean contrast in one command.
```{r}
with(FactorialDataB1,estimateMeanSubsets(Outcome~FactorA,contrast=A1vsOthers))
with(FactorialDataB2,estimateMeanSubsets(Outcome~FactorA,contrast=A1vsOthers))
```

This code produces a difference plot using the confidence intervals for the mean subsets and the mean contrast.
```{r,Factorial-SubsetsA}
with(FactorialDataB1,plotMeanSubsets(Outcome~FactorA,contrast=A1vsOthers))
with(FactorialDataB2,plotMeanSubsets(Outcome~FactorA,contrast=A1vsOthers))
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
with(FactorialDataB1,estimateMeanSubsets(Outcome~FactorA,contrast=A1vsOthers,conf.level=.99))
with(FactorialDataB2,estimateMeanSubsets(Outcome~FactorA,contrast=A1vsOthers,conf.level=.99))
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r,Factorial-SubsetsB}
with(FactorialDataB1,plotMeanSubsets(Outcome~FactorA,contrast=A1vsOthers,labels=c("Level1","Others"),conf.level=.99,rope=c(-2,2)))
with(FactorialDataB2,plotMeanSubsets(Outcome~FactorA,contrast=A1vsOthers,labels=c("Level1","Others"),conf.level=.99,rope=c(-2,2)))
```

#### Significance Test for a Contrast

This code produces a NHST for the identified contrast. It tests the contrast against a value of zero by default.
```{r}
with(FactorialDataB1,testMeanContrast(Outcome~FactorA,contrast=A1vsOthers))
with(FactorialDataB2,testMeanContrast(Outcome~FactorA,contrast=A1vsOthers))
```

If desired, the contrast can be tested against other values.
```{r}
with(FactorialDataB1,testMeanContrast(Outcome~FactorA,contrast=A1vsOthers,mu=4))
with(FactorialDataB2,testMeanContrast(Outcome~FactorA,contrast=A1vsOthers,mu=4))
```

#### Standardized Effect Size for a Contrast

This code calculates a standardized contrast and its confidence interval.
```{r}
with(FactorialDataB1,estimateStandardizedMeanContrast(Outcome~FactorA,contrast=A1vsOthers))
with(FactorialDataB2,estimateStandardizedMeanContrast(Outcome~FactorA,contrast=A1vsOthers))
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
with(FactorialDataB1,estimateStandardizedMeanContrast(Outcome~FactorA,contrast=A1vsOthers,conf.level=.99))
with(FactorialDataB2,estimateStandardizedMeanContrast(Outcome~FactorA,contrast=A1vsOthers,conf.level=.99))
```

### Analyses of the Pairwise Comparisons

This section provides analyses of all possible pairwise comparisons among the levels of the factor.

#### Confidence Intervals for the Pairwise Comparisons

This code will provide a table of descriptive statistics and confidence intervals for each pairwise comparison.
```{r}
with(FactorialDataB1,estimateMeansPairwise(Outcome~FactorA))
with(FactorialDataB2,estimateMeansPairwise(Outcome~FactorA))
```

This code will produce a graph of the confidence intervals for each of the pairwise comparisons.
```{r,Factorial-PairwiseA}
with(FactorialDataB1,plotMeansPairwise(Outcome~FactorA))
with(FactorialDataB2,plotMeansPairwise(Outcome~FactorA))
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
with(FactorialDataB1,estimateMeansPairwise(Outcome~FactorA,conf.level=.99))
with(FactorialDataB2,estimateMeansPairwise(Outcome~FactorA,conf.level=.99))
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added to the graph.
```{r,Factorial-PairwiseB}
with(FactorialDataB1,plotMeansPairwise(Outcome~FactorA,mu=-2,conf.level=.99,rope=c(-4,0)))
with(FactorialDataB2,plotMeansPairwise(Outcome~FactorA,mu=-2,conf.level=.99,rope=c(-4,0)))
```

#### Significance Tests of the Pairwise Comparisons

This code will produce a table of NHST for each of the pairwise comparisons. In this case, all the comparisons are tested against a value of zero.
```{r}
with(FactorialDataB1,testMeansPairwise(Outcome~FactorA))
with(FactorialDataB2,testMeansPairwise(Outcome~FactorA))
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
with(FactorialDataB1,testMeansPairwise(Outcome~FactorA,mu=-2))
with(FactorialDataB2,testMeansPairwise(Outcome~FactorA,mu=-2))
```

#### Standardized Effect Sizes for the Pairwise Comparisons

This code will produce a table of standardized mean differences for each pairwise comparison. 
```{r}
with(FactorialDataB1,estimateStandardizedMeansPairwise(Outcome~FactorA))
with(FactorialDataB2,estimateStandardizedMeansPairwise(Outcome~FactorA))
```

Here too it is possible to alter the width of the confidence intervals.
```{r}
with(FactorialDataB1,estimateStandardizedMeansPairwise(Outcome~FactorA,conf.level=.99))
with(FactorialDataB2,estimateStandardizedMeansPairwise(Outcome~FactorA,conf.level=.99))
```
