---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Independent Groups Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Independent Groups Tutorial with Summary Statistics

### Enter Summary Statistics

This code inputs the variable summaries and creates a single summary table.
```{r}
Level1 <- c(N=4,M=2.000,SD=2.449)
Level2 <- c(N=4,M=6.000,SD=2.449)
IndependentSummary <- rbind(Level1,Level2)
class(IndependentSummary) <- "bss"
IndependentSummary
```

### Analyses of Multiple Groups

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

#### Confidence Intervals for the Means

This code will provide a table of descriptive statistics and confidence intervals for each level of the factor.
```{r}
estimateMeans(IndependentSummary)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateMeans(IndependentSummary,conf.level=.99)
```

#### Plots of the Confidence Intervals for the Means

This code will produce a graph of the confidence intervals for each level of the factor.
```{r,Independent-MeansA}
plotMeans(IndependentSummary)
```

Of course, it is possible to change from the default confidence level. Additionally, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence can be added.
```{r,Independent-MeansB}
plotMeans(IndependentSummary,conf.level=.99,mu=5,rope=c(3,7))
```

#### Significance Tests for the Means

This code will produce a table of NHST separately for each level of the factor. In this case, all the means are tested against a value of zero.
```{r}
testMeans(IndependentSummary)
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
testMeans(IndependentSummary,mu=5)
```

#### Effect Sizes for the Means

This code will produce a table of standardized mean differences separately for each level of the factor. In this case, the mean is compared to zero to form the effect size.
```{r}
standardizeMeans(IndependentSummary)
```

Here too it is possible to alter the width of the confidence intervals and to establish a more plausible comparison value for the effect size.
```{r}
standardizeMeans(IndependentSummary,mu=5,conf.level=.99)
```
 
### Analyses of a Group Comparison

This section produces analyses that examine differences among the two levels of a factor.

#### Confidence Interval for a Mean Difference

This code estimates the confidence interval of the difference.
```{r}
estimateDifference(IndependentSummary)
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
estimateDifference(IndependentSummary,conf.level=.99)
```

#### Plot of the Confidence Interval for a Mean Difference

This code obtains and plots the confidence intervals for the groups and the mean difference .
```{r,Independent-DifferenceA}
plotDifference(IndependentSummary)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added.
```{r,Independent-DifferenceB}
plotDifference(IndependentSummary,conf.level=.99,rope=c(-2,2))
```

#### Significance Test for a Mean Difference

This code produces NHST for the mean difference (using a default test value of zero).
```{r}
testDifference(IndependentSummary)
```

If the default value of zero is not plausible, it too can be changed.
```{r}
testDifference(IndependentSummary,mu=2)
```

#### Effect Size for the Mean Difference

This code calculates a standardized mean difference and its confidence interval.
```{r}
standardizeDifference(IndependentSummary)
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
standardizeDifference(IndependentSummary,conf.level=.99)
```
