---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Mixed Design Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Mixed Design Tutorial with Summary Statistics

### Enter Summary Statistics

This code inputs the variable summaries and creates a summary table.
```{r}
Time1 <- c(N=4,M=2.000,SD=2.449)
Time2 <- c(N=4,M=6.000,SD=2.449)
Time3 <- c(N=4,M=7.000,SD=2.449)
WithinSummaryG1 <- rbind(Time1,Time2,Time3)
class(WithinSummaryG1) <- "wss"
```

This code creates a correlation matrix, enters just the top triangle, and then uses a function to fill in the whole matrix.
```{r}
WithinCorrG1 <- declareCorrMatrix("Time1","Time2","Time3")
WithinCorrG1["Time1",] <- c(1.000,.500,.389)
WithinCorrG1["Time2",] <- c(.500,1.000,.889)
WithinCorrG1["Time3",] <- c(.389,.889,1.000)
```

And repeat the process to create the second subset.
```{r}
Time1 <- c(N=4,M=2.000,SD=2.449)
Time2 <- c(N=4,M=6.000,SD=2.449)
Time3 <- c(N=4,M=7.000,SD=2.449)
WithinSummaryG2 <- rbind(Time1,Time2,Time3)
class(WithinSummaryG2) <- "wss"
```

And for the correlation matrix of the second subset.
```{r}
WithinCorrG2 <- declareCorrMatrix("Time1","Time2","Time3")
WithinCorrG2["Time1",] <- c(1.000,.889,.778)
WithinCorrG2["Time2",] <- c(.889,1.000,.889)
WithinCorrG2["Time3",] <- c(.778,.889,1.000)
```

### Analyses of Multiple Variables

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

#### Confidence Intervals for the Means

This code will provide a table of descriptive statistics and confidence intervals for each level of the factor.
```{r}
estimateMeans(WithinSummaryG1)
estimateMeans(WithinSummaryG2)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateMeans(WithinSummaryG1,conf.level=.99)
estimateMeans(WithinSummaryG2,conf.level=.99)
```

#### Plots of Confidence Intervals for the Means

This code will produce a graph of the confidence intervals for each level of the factor.
```{r,Mixed-MeansA}
plotMeans(WithinSummaryG1)
plotMeans(WithinSummaryG2)
```

Of course, it is possible to change from the default confidence level. Additionally, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence.
```{r,Mixed-MeansB}
plotMeans(WithinSummaryG1,conf.level=.99,mu=5,rope=c(3,7))
plotMeans(WithinSummaryG2,conf.level=.99,mu=5,rope=c(3,7))
```

#### Significance Tests for the Means

This code will produce a table of NHST separately for each level of the factor. In this case, all the means are tested against a value of zero.
```{r}
testMeans(WithinSummaryG1)
testMeans(WithinSummaryG2)
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
testMeans(WithinSummaryG1,mu=5)
testMeans(WithinSummaryG2,mu=5)
```

#### Effect Size for the Means

This code will produce a table of standardized mean differences separately for each level of the factor. In this case, the mean is compared to zero to form the effect size.
```{r}
standardizeMeans(WithinSummaryG1)
standardizeMeans(WithinSummaryG2)
```

Here too it is possible to alter the width of the confidence intervals and to establish a more plausible comparison value for the effect size.
```{r}
standardizeMeans(WithinSummaryG1,mu=5,conf.level=.99)
standardizeMeans(WithinSummaryG2,mu=5,conf.level=.99)
```

### Analyses of a Variable Comparison

This section produces analyses that are equivalent to comparisons of two levels of a factor.

This code creates a new table that identifies the two levels for comparison and repeats for the second subset.
```{r}
CompSummaryG1 <- WithinSummaryG1[c("Time1","Time2"),]
class(CompSummaryG1) <- "wss"
CompSummaryG2 <- WithinSummaryG2[c("Time1","Time2"),]
class(CompSummaryG2) <- "wss"
```

#### Confidence Interval for the Mean Difference

This code identifies the two levels for comparison and estimates the confidence interval of the difference.
```{r}
estimateDifference(CompSummaryG1,WithinCorrG1)
estimateDifference(CompSummaryG2,WithinCorrG2)
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
estimateDifference(CompSummaryG1,WithinCorrG1,conf.level=.99)
estimateDifference(CompSummaryG2,WithinCorrG2,conf.level=.99)
```

#### Plots of Confidence Intervals for the Mean Difference

This code obtains and plots the confidence intervals for the levels and the mean difference in the identified comparison.
```{r,Mixed-DifferenceA}
plotDifference(CompSummaryG1,WithinCorrG1)
plotDifference(CompSummaryG2,WithinCorrG2)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added.
```{r,Mixed-DifferenceB}
plotDifference(CompSummaryG1,WithinCorrG1,conf.level=.99,rope=c(-2,2))
plotDifference(CompSummaryG2,WithinCorrG2,conf.level=.99,rope=c(-2,2))
```

#### Significance Test for the Mean Difference

This code produces NHST for the identified comparison (using a default test value of zero).
```{r}
testDifference(CompSummaryG1,WithinCorrG1)
testDifference(CompSummaryG2,WithinCorrG2)
```

If the default value of zero is not plausible, it too can be changed.
```{r}
testDifference(CompSummaryG1,WithinCorrG1,mu=-2)
testDifference(CompSummaryG2,WithinCorrG2,mu=-2)
```

#### Effect Size for the Mean Difference

This code calculates a standardized mean difference for the comparison and its confidence interval.
```{r}
standardizeDifference(CompSummaryG1,WithinCorrG1)
standardizeDifference(CompSummaryG2,WithinCorrG2)
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
standardizeDifference(CompSummaryG1,WithinCorrG1,conf.level=.99)
standardizeDifference(CompSummaryG2,WithinCorrG2,conf.level=.99)
```

### Analyses of a Variable Contrast

This section produces analyses that are equivalent to analyses involving multiple levels of a factor.

This code identifies a contrast among the levels.
```{r}
T1vsOthers <- c(-1,.5,.5)
```

#### Confidence Interval for the Contrast

This code produces a confidence interval for that contrast.
```{r}
estimateContrast(WithinSummaryG1,WithinCorrG1,contrast=T1vsOthers)
estimateContrast(WithinSummaryG2,WithinCorrG2,contrast=T1vsOthers)
```

As in all other cases, the default value of the confidence interval can be changed.
```{r}
estimateContrast(WithinSummaryG1,WithinCorrG1,contrast=T1vsOthers,conf.level=.99)
estimateContrast(WithinSummaryG2,WithinCorrG2,contrast=T1vsOthers,conf.level=.99)
```

#### Plots of Confidence Intervals for a Contrast

This code obtains and plots the confidence intervals for the groups and the mean difference in the identified contrast.
```{r,Mixed-ContrastA}
plotContrast(WithinSummaryG1,WithinCorrG1,contrast=T1vsOthers)
plotContrast(WithinSummaryG2,WithinCorrG2,contrast=T1vsOthers)
```

The width of the confidence interval for the contrast can be altered and a region of practical equivalence can be added.
```{r,Mixed-ContrastB}
plotContrast(WithinSummaryG1,WithinCorrG1,contrast=T1vsOthers,labels=c("Time1","Others"),conf.level=.99,rope=c(-2,2))
plotContrast(WithinSummaryG2,WithinCorrG2,contrast=T1vsOthers,labels=c("Time1","Others"),conf.level=.99,rope=c(-2,2))
```

#### Significance Test for the Contrast

This code produces a NHST for the identified contrast. It tests the contrast against a value of zero by default.
```{r}
testContrast(WithinSummaryG1,WithinCorrG1,contrast=T1vsOthers)
testContrast(WithinSummaryG2,WithinCorrG2,contrast=T1vsOthers)
```

If desired, the contrast can be tested against other values.
```{r}
testContrast(WithinSummaryG1,WithinCorrG1,contrast=T1vsOthers,mu=4)
testContrast(WithinSummaryG2,WithinCorrG2,contrast=T1vsOthers,mu=4)
```

#### Effect Size for the Contrast

This code calculates a standardized contrast and its confidence interval.
```{r}
standardizeContrast(WithinSummaryG1,WithinCorrG1,contrast=T1vsOthers)
standardizeContrast(WithinSummaryG2,WithinCorrG2,contrast=T1vsOthers)
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
standardizeContrast(WithinSummaryG1,WithinCorrG1,contrast=T1vsOthers,conf.level=.99)
standardizeContrast(WithinSummaryG2,WithinCorrG2,contrast=T1vsOthers,conf.level=.99)
```
