---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{OneWay (Between-Subjects) Tutorial with Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## OneWay (Between-Subjects) Tutorial with Summary Statistics

### Enter Summary Statistics

This code inputs the variable summaries and creates a single summary table.
```{r}
Level1 <- c(N=4,M=2.000,SD=2.449)
Level2 <- c(N=4,M=6.000,SD=2.449)
Level3 <- c(N=4,M=7.000,SD=2.449)
OneWaySummary <- rbind(Level1,Level2,Level3)
class(OneWaySummary) <- "bss"
OneWaySummary
```

### Analyses of Multiple Groups

This section produces analyses that are equivalent to one-sample analyses separately for each level of a factor.

#### Confidence Intervals for the Means

This code will provide a table of descriptive statistics and confidence intervals for each level of the factor.
```{r}
estimateMeans(OneWaySummary)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
estimateMeans(OneWaySummary,conf.level=.99)
```

#### Plots of the Confidence Intervals for the Means

This code will produce a graph of the confidence intervals for each level of the factor.
```{r,OneWay-MeansA}
plotMeans(OneWaySummary)
```

Of course, it is possible to change from the default confidence level. Additionally, it is possible to add a comparison line to represent a population (or test) value and a region of practical equivalence.
```{r,OneWay-MeansB}
plotMeans(OneWaySummary,conf.level=.99,mu=5,rope=c(3,7))
```

#### Significance Tests for the Means

This code will produce a table of NHST separately for each level of the factor. In this case, all the means are tested against a value of zero.
```{r}
testMeans(OneWaySummary)
```

Often, the default test value of zero is not meaningful or plausible. This too can be altered (often in conjunction with what is presented in the plot).
```{r}
testMeans(OneWaySummary,mu=5)
```

#### Effect Sizes for the Means

This code will produce a table of standardized mean differences separately for each level of the factor. In this case, the mean is compared to zero to form the effect size.
```{r}
standardizeMeans(OneWaySummary)
```

Here too it is possible to alter the width of the confidence intervals and to establish a more plausible comparison value for the effect size.
```{r}
standardizeMeans(OneWaySummary,mu=5,conf.level=.99)
```
 
### Analyses of a Group Comparison

This section produces analyses that are equivalent to comparisons of two levels of a factor.

This code creates a new table that identifies the two levels for comparison.
```{r}
CompSummary <- OneWaySummary[c("Level1","Level2"),]
class(CompSummary) <- "bss"
```

#### Confidence Interval for a Mean Difference

This code estimates the confidence interval of the difference.
```{r}
estimateDifference(CompSummary)
```

Of course, you can change the confidence level from the default 95% if desired.
```{r}
estimateDifference(CompSummary,conf.level=.99)
```

#### Plot of the Confidence Interval for a Mean Difference

This code obtains and plots the confidence intervals for the groups and the mean difference in the identified comparison.
```{r,OneWay-DifferenceA}
plotDifference(CompSummary)
```

Once again, the confidence levels can be changed away from the default and a region of practical equivalence can be added.
```{r,OneWay-DifferenceB}
plotDifference(CompSummary,conf.level=.99,rope=c(-2,2))
```

#### Significance Test for a Mean Difference

This code produces NHST for the identified comparison (using a default test value of zero).
```{r}
testDifference(CompSummary)
```

If the default value of zero is not plausible, it too can be changed.
```{r}
testDifference(CompSummary,mu=-2)
```

#### Effect Size for the Mean Difference

This code calculates a standardized mean difference for the comparison and its confidence interval.
```{r}
standardizeDifference(CompSummary)
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
standardizeDifference(CompSummary,conf.level=.99)
```

### Analyses of a Group Contrast

This section produces analyses that are equivalent to analyses involving multiple levels of a factor.

This code identifies a contrast among the groups
```{r}
L1vsOthers <- c(-1,.5,.5)
```

#### Confidence Interval for a Contrast

This code produces a confidence interval for that contrast.
```{r}
estimateContrast(OneWaySummary,contrast=L1vsOthers)
```

As in all other cases, the default value of the confidence interval can be changed.
```{r}
estimateContrast(OneWaySummary,contrast=L1vsOthers,conf.level=.99)
```

#### Plots of Confidence Intervals for a Contrast

This code obtains and plots the confidence intervals for the groups and the mean difference in the identified contrast.
```{r,OneWay-ContrastA}
plotContrast(OneWaySummary,contrast=L1vsOthers)
````

The width of the confidence interval for the contrast can be altered and a region of practical equivalence can be added.
```{r,OneWay-ContrastB}
plotContrast(OneWaySummary,contrast=L1vsOthers,labels=c("Level1","Others"),conf.level=.99,rope=c(-2,2))
```

#### Significance Test for a Contrast

This code produces a NHST for the identified contrast. It tests the contrast against a value of zero by default.
```{r}
testContrast(OneWaySummary,contrast=L1vsOthers)
```

If desired, the contrast can be tested against other values.
```{r}
testContrast(OneWaySummary,contrast=L1vsOthers,mu=4)
```

#### Effect Size for a Contrast

This code calculates a standardized contrast and its confidence interval.
```{r}
standardizeContrast(OneWaySummary,contrast=L1vsOthers)
```

The width of the confidence interval for the effect size can be altered if desired.
```{r}
standardizeContrast(OneWaySummary,contrast=L1vsOthers,conf.level=.99)
```
