---
subtitle: "Bivariate Regression Summary Statistics Example"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Bivariate Regression Summary Statistics Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 6, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Bivariate Regression Summary Statistics Example

This page analyzes bivariate regression models using summary statistics input.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

#### Data Entry

This code inputs the variable summaries and creates a summary table.
```{r}
Predictor <- c(N = 10, M = 8.000, SD = 1.414)
Criterion <- c(N = 10, M = 11.000, SD = 2.211)
BivariateSummary <- construct(Predictor, Criterion, class = "wss")
```

This code creates a correlation matrix.
```{r}
Predictor <- c(1.000, .533)
Criterion <- c(.533, 1.000)
BivariateCorr <- construct(Predictor, Criterion, class = "corr")
```

#### Summary Statistics

This code confirms the descriptive statistics from the summary tables.
```{r}
(BivariateSummary) |> describeSummary()
(BivariateCorr) |> describeCorrelations()
```

### Analyses of Overall Model

This section produces analyses of the overall regression model.

This code will produce a source table associated with the regression model.
```{r}
(BivariateSummary) |> describeRegressionEffect(BivariateCorr)
```

#### Confidence Interval

This code will produce the confidence interval for R Squared.
```{r}
(BivariateSummary) |> estimateRegressionEffect(BivariateCorr)
```

The code defaults to 90% confidence intervals. This can be changed if desired.
```{r}
(BivariateSummary) |> estimateRegressionEffect(BivariateCorr, conf.level = .95)
```

#### Significance Test

This code will calculate NHST for the regression model.
```{r}
(BivariateSummary) |> testRegressionEffect(BivariateCorr)
```

### Analyses of the Regression Coefficients

This section analyses the regression coefficients obtained from the overall model.

#### Confidence Intervals 

This code will provide a table of confidence intervals for each of the regression coefficients.
```{r}
(BivariateSummary) |> estimateRegressionCoefficients(BivariateCorr)
```

This code will produce a graph of the confidence intervals for each of the regression coefficients.
```{r, Bivariate-Summary-CoefficientsA}
(BivariateSummary) |> plotRegressionCoefficients(BivariateCorr)
```

The code defaults to 95% confidence intervals. This can be changed if desired.
```{r}
(BivariateSummary) |> estimateRegressionCoefficients(BivariateCorr, conf.level = .99)
```

For the graph, it is possible to plot just coefficients for the predictors (minus the intercept) in addition to changing the confidence level. A comparison line and region of practical equivalence can also be added.
```{r, Bivariate-Summary-CoefficientsB}
(BivariateSummary) |> plotRegressionCoefficients(BivariateCorr, conf.level = .99, line = 0, rope = c(-.5, .5), intercept = FALSE)
```

#### Significance Tests

This code will produce a table of NHST separately for each of the regression coefficients. In this case, all the coefficients are tested against a value of zero.
```{r}
(BivariateSummary) |> testRegressionCoefficients(BivariateCorr)
```

#### Standardized Coefficient

This code will provide a table of confidence intervals for the standardized coefficient.
```{r}
(BivariateSummary) |> estimateStandardizedRegressionCoefficients(BivariateCorr)
```

This code will produce a graph of the confidence intervals for the standardized coefficient.
```{r, Bivariate-Summary-StandardizedA}
(BivariateSummary) |> plotStandardizedRegressionCoefficients(BivariateCorr)
```

As in other places, the code defaults to a 95% confidence interval. This can be changed if desired.
```{r}
(BivariateSummary) |> estimateStandardizedRegressionCoefficients(BivariateCorr, conf.level = .99)
```

For the graph, it is possible to change the confidence level.
```{r, Bivariate-Summary-StandardizedB}
(BivariateSummary) |> plotStandardizedRegressionCoefficients(BivariateCorr, conf.level = .99)
```

### Analyses of Regression Values

This section provides analyses of individual predicted values.

#### Regression Line

This code produces a plot of the regression line (with confidence and prediction intervals suppressed).
```{r, Bivariate-Summary-LineA}
(BivariateSummary) |> plotRegression(BivariateCorr, interval = "none")
```

#### Confidence and Prediction Intervals

This code provides estimates confidence and prediction limits for a specific value of the Predictor (value=4).
```{r}
(BivariateSummary) |> estimateRegression(BivariateCorr, value = 8)
```

This code plots the confidence interval associated with the regression line and labels the interval for the specific value of the Predictor.
```{r, Bivariate-Summary-ConfidenceA}
(BivariateSummary) |> plotRegression(BivariateCorr, value = 8, interval = "confidence")
```

This code plots the prediction interval associated with the regression line and labels the interval for the specific value of the Predictor.
```{r, Bivariate-Summary-ConfidenceB}
(BivariateSummary) |> plotRegression(BivariateCorr, value = 8, interval = "prediction")
```
