---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{BodyWell Two Sample Data Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## BodyWell Two Sample Data Example

This page compares a correlation between two variables in two independent samples using raw data input.

### Data Management

#### Data Entry

First, enter the data.
```{r}
Gender <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2)
BodySatisfaction <- c(4,2.4,3,3,3.1,2.4,2.9,3.1,3,3.3,2,3.1,2.4,3.1,3.3,3.4,3.3,3.6,2.7,3.3,3.6,2.3,3.7,4,2.7,3.1,3.3,3.4,4.4,3.3,3.3,4,4.1,3.3,3.6,3.9,4,5,3,3,3.3,3.9,3.9,4.7,5,2.6,2.9,3.4,3.4,3.9,4.3,2.6,3.1,3.4,3.7,4,4.1,4,5,4,2.4,3.7,3,3.6,2.9,2.7,3.3,4.3,3.1,4.3,4.4,4,3.3,3.7,2.9,3.4,3.6,4.7,4.1,3,4.1,3.7,4.1,4,3.1,3.7,3.3,4.4,4.3,4,4,4,3.4,4.9,3.7,3.3,3.9,4.6,4,3.9,4.7,4.3,4.4,4.4,4.6,4.3)
Wellbeing <- c(1,2.4,2.3,2.4,2.8,3.2,3.4,3.4,3.6,3.6,3.8,3.8,4,4,4.2,4.2,4.4,4.4,4.6,4.6,4.6,4.8,4.8,4.8,5,5,5,5,5,5.2,5.3,5.2,5.2,5.6,5.6,5.6,5.6,5.6,5.8,5.7,5.8,5.8,5.9,5.8,5.8,6,6,6,6.1,6,6,6.2,6.2,6.2,6.4,6.4,6.4,6.6,7,2.8,3,3.2,3.2,3.4,3.4,3.8,4.2,4.4,4.4,4.6,4.6,4.6,4.8,4.8,4.8,5,5,5.2,5.2,5.4,5.6,5.6,5.5,5.6,5.6,5.7,5.6,5.6,5.6,5.8,5.8,6,6,6,6,6,6,6,6.1,6.2,6.2,6.2,6.2,6.4,6.6,7)
BodyWellTwoData <- data.frame(Gender,BodySatisfaction,Wellbeing)
```

This code subsets the data into two different data frames for use in analyzing the two Gender groups separately.
```{r}
BodyWellTwoDataL1 <- subset(BodyWellTwoData,Gender=="1")
BodyWellTwoDataL2 <- subset(BodyWellTwoData,Gender=="2")
```

#### Descriptive Statistics

This code obtains the descriptive statistics for the Gender groups.
```{r}
with(BodyWellTwoDataL1,describeMeans(cbind(BodySatisfaction,Wellbeing)))
with(BodyWellTwoDataL2,describeMeans(cbind(BodySatisfaction,Wellbeing)))
```

This code obtains a table of correlations for the two groups.
```{r}
with(BodyWellTwoDataL1,describeCorrelations(cbind(BodySatisfaction,Wellbeing)))
with(BodyWellTwoDataL2,describeCorrelations(cbind(BodySatisfaction,Wellbeing)))
```

### Analyses of a Correlation Comparison

The main question is whether the correlation between Body Satisfaction and Wellbeing is different in the two groups.

First it is necessary to estimate the confidence intervals for each of the correlations.
```{r}
CorrEstimateL1 <- with(BodyWellTwoDataL1,estimateCorrelations(cbind(BodySatisfaction,Wellbeing)))
CorrEstimateL2 <- with(BodyWellTwoDataL2,estimateCorrelations(cbind(BodySatisfaction,Wellbeing)))
```

Then we can estimate the correlations and the difference in the correlations.
```{r,BodyWellTwo-Data-Comparison}
estimateCorrelationComparison(CorrEstimateL1,CorrEstimateL2,main="Correlations for the Gender Groups",labels=c("Females","Males"))
plotCorrelationComparison(CorrEstimateL1,CorrEstimateL2,main="Correlations for the Gender Groups",labels=c("Females","Males"),ylim=c(-1,1),values=FALSE)
```
