---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Correlation Example with BodyWell One Sample Summary Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Correlation Example with BodyWell One Sample Summary Statistics

### Data Management

This code inputs the variable summaries and creates a summary table.
```{r}
BodySatisfaction <- c(N=106,M=3.605,SD=0.659)
Wellbeing <- c(N=106,M=5.055,SD=1.162)
BodyWellOneSummary <- rbind(BodySatisfaction,Wellbeing)
class(BodyWellOneSummary) <- "wss"
```

This code creates a correlation matrix and enters single correlation.
```{r}
BodyWellOneCorr <- declareCorrelations("BodySatisfaction","Wellbeing")
BodyWellOneCorr["BodySatisfaction","Wellbeing"] <- .467
```

### Analyses of the Correlation

More importantly, we can get the confidence interval for the correlation.
```{r}
estimateCorrelations(BodyWellOneSummary,BodyWellOneCorr)
```

This is the plot of correlation and its confidence interval.
```{r,BodyWellOne-Correlation}
plotCorrelations(BodyWellOneSummary,BodyWellOneCorr,main="Correlation for the Entire Sample",ylim=c(-1,1))
```
