---
subtitle: "BodyWell One Sample Summary Statistics Example"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{BodyWell One Sample Summary Statistics Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## BodyWell One Sample Summary Statistics Example

This page analyzes a single correlation between two variables using summary statistics input.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

This code inputs the variable summaries and creates a summary table.
```{r}
BodySatisfaction <- c(N = 106, M = 3.605, SD = 0.659)
Wellbeing <- c(N = 106, M = 5.055, SD = 1.162)
BodyWellOneSummary <- rbind(BodySatisfaction, Wellbeing)
class(BodyWellOneSummary) <- "wss"
```

This code creates a correlation matrix and enters single correlation.
```{r}
BodyWellOneCorr <- declareCorrelations("BodySatisfaction", "Wellbeing")
BodyWellOneCorr["BodySatisfaction", "Wellbeing"] <- .467
BodyWellOneCorr <- fillCorrelations(BodyWellOneCorr)
```

### Analyses of the Correlation

We can get the confidence interval for the correlation.
```{r}
estimateCorrelations(BodyWellOneSummary, BodyWellOneCorr)
```

This is the plot of correlation and its confidence interval.
```{r,BodyWellOne-Summary-Correlation}
plotCorrelations(BodyWellOneSummary, BodyWellOneCorr, main = "Correlation for the Entire Sample", ylim = c(-1, 1), values = FALSE, line = 0)
```
