---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Correlation Example with BodyWell One Sample Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Correlation Example with BodyWell One Sample Data

### Data Management

#### Data Entry

First, enter the data.
```{r}
BodySatisfaction <- c(4,2.4,3,3,3.1,2.4,2.9,3.1,3,3.3,2,3.1,2.4,3.1,3.3,3.4,3.3,3.6,2.7,3.3,3.6,2.3,3.7,4,2.7,3.1,3.3,3.4,4.4,3.3,3.3,4,4.1,3.3,3.6,3.9,4,5,3,3,3.3,3.9,3.9,4.7,5,2.6,2.9,3.4,3.4,3.9,4.3,2.6,3.1,3.4,3.7,4,4.1,4,5,4,2.4,3.7,3,3.6,2.9,2.7,3.3,4.3,3.1,4.3,4.4,4,3.3,3.7,2.9,3.4,3.6,4.7,4.1,3,4.1,3.7,4.1,4,3.1,3.7,3.3,4.4,4.3,4,4,4,3.4,4.9,3.7,3.3,3.9,4.6,4,3.9,4.7,4.3,4.4,4.4,4.6,4.3)
Wellbeing <- c(1,2.4,2.3,2.4,2.8,3.2,3.4,3.4,3.6,3.6,3.8,3.8,4,4,4.2,4.2,4.4,4.4,4.6,4.6,4.6,4.8,4.8,4.8,5,5,5,5,5,5.2,5.3,5.2,5.2,5.6,5.6,5.6,5.6,5.6,5.8,5.7,5.8,5.8,5.9,5.8,5.8,6,6,6,6.1,6,6,6.2,6.2,6.2,6.4,6.4,6.4,6.6,7,2.8,3,3.2,3.2,3.4,3.4,3.8,4.2,4.4,4.4,4.6,4.6,4.6,4.8,4.8,4.8,5,5,5.2,5.2,5.4,5.6,5.6,5.5,5.6,5.6,5.7,5.6,5.6,5.6,5.8,5.8,6,6,6,6,6,6,6,6.1,6.2,6.2,6.2,6.2,6.4,6.6,7)
BodyWellOneData <- data.frame(BodySatisfaction,Wellbeing)
```

#### Descriptive Statistics

First, it's useful to get the means and standard deviations for the variables.
```{r}
describeMeans(BodySatisfaction,Wellbeing)
```

Next, we can get the correlation among the variables.
```{r}
describeCorrelations(BodySatisfaction,Wellbeing)
```

### Analyses of a Correlation

More importantly, we can get the confidence interval for the correlation.
```{r}
estimateCorrelations(BodySatisfaction,Wellbeing)
```

This is the plot of correlation and its confidence interval.
```{r,BodyWellOne-Correlation}
plotCorrelations(BodySatisfaction,Wellbeing,main="Correlation for the Entire Sample",ylim=c(-1,1))
```
