---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{BodyWell Regression Summary Statistics Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## BodyWell Regression Summary Statistics Example

This page analyzes bivariate regression models using summary statistics input.

### Data Management

This code inputs the variable summaries and creates a summary table.
```{r}
BodySatisfaction <- c(N=106,M=3.605,SD=0.659)
Wellbeing <- c(N=106,M=5.055,SD=1.162)
BodyWellOneSummary <- rbind(BodySatisfaction,Wellbeing)
class(BodyWellOneSummary) <- "wss"
```

This code creates a correlation matrix and enters single correlation.
```{r}
BodyWellOneCorr <- declareCorrelations("BodySatisfaction","Wellbeing")
BodyWellOneCorr["BodySatisfaction","Wellbeing"] <- .467
BodyWellOneCorr <- fillCorrelations(BodyWellOneCorr)
```

### Analyses of the Regression Line

Importantly, we can get a display of the regression line (with the confidence interval suppressed).
```{r,Regression-Summary-Model}
plotRegression(BodyWellOneSummary,BodyWellOneCorr,interval="none",xlim=c(1,5),ylim=c(1,7),cross=TRUE)
```

We can then determine the slope and intercept of the line and get confidence intervals for them.
```{r,Regression-Summary-Coefficients}
estimateRegressionCoefficients(BodyWellOneSummary,BodyWellOneCorr)
plotRegressionCoefficients(BodyWellOneSummary,BodyWellOneCorr)
```

### Analyses of Regression Values

Finally, we get the confidence and prediction intervals of Wellbeing at a BodySatisfaction score of 2.
```{r,Regression-Summary-Value}
estimateRegression(BodyWellOneSummary,BodyWellOneCorr,value=2)
plotRegression(BodyWellOneSummary,BodyWellOneCorr,interval="both",value=2,xlim=c(1,5),ylim=c(1,7),values=FALSE)
```