---
subtitle: "Donohue Summary Statistics Example"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Donohue Summary Statistics Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7",filename='revised_toc.R')
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Donohue Summary Statistics Example

This page analyzes a single-factor within-subjects (repeated measures) design using summary statistics input.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile,base_level=3,toc_depth=4)
```

---

### Data Management

Prior to analyses, enter the tables of summary statistics.

```{r}
Pretest <- c(N=20,M=19.300,SD=5.904)
Posttest <- c(N=20,M=23.600,SD=4.762)
Followup <- c(N=20,M=23.400,SD=4.616)
DonohueSummary <- rbind(Pretest,Posttest,Followup)
class(DonohueSummary) <- "wss"

DonohueCorr <- declareCorrelations("Pretest","Posttest","Followup")
DonohueCorr["Pretest","Posttest"] <- .493
DonohueCorr["Pretest","Followup"] <- .536
DonohueCorr["Posttest","Followup"] <- .743
DonohueCorr <- fillCorrelations(DonohueCorr)
```

### Analyses of the Different Variables

With multiple variables, it is useful to get descriptive statistics and confidence intervals for each variable.

```{r,Donohue-Summary-Means}
estimateMeans(DonohueSummary)
plotMeans(DonohueSummary,main="Critical Thinking Scores at Pretest, Posttest, and Followup",ylim=c(0,30),values=FALSE)
```
 
### Analysis of a Variable Difference

The first research question is whether there is a difference between the posttest and followup occasions.

First, set the comparison and obtain the difference plot for that comparison.

```{r,Donohue-Summary-Comparison}
PostvsFollowup <- DonohueSummary[c(2,3),]
class(PostvsFollowup) <- "wss"
estimateMeanComparison(PostvsFollowup,DonohueCorr)
plotMeanComparison(PostvsFollowup,DonohueCorr,main="Critical Thinking Scores of Posttest vs Followup",ylim=c(0,30),values=FALSE)
```

Then, obtain the standardized effect size for that comparison.

```{r}
estimateStandardizedMeanDifference(PostvsFollowup,DonohueCorr)
```

### Analysis of a Variable Contrast

The second research question is whether the pretest differs from the posttest and followup combined.

First, set the contrast and obtain a difference plot for the contrast.

```{r,Donohue-Summary-Contrast}
PrevsPostFollow <- c(-1,.5,.5)
estimateMeanSubsets(DonohueSummary,DonohueCorr,contrast=PrevsPostFollow)
plotMeanSubsets(DonohueSummary,DonohueCorr,contrast=PrevsPostFollow,labels=c("Pretest","Post&Follow"),main="Critical Thinking Scores of Prestest vs Posttest and Followup Combined",ylab="Critical Thinking",ylim=c(0,30),values=FALSE)
```

Then, estimate the standardized contrast.

```{r}
estimateStandardizedMeanContrast(DonohueSummary,DonohueCorr,contrast=PrevsPostFollow)
```
