---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "2021-03-16"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Repeated Measures (Within-Subjects) Example with Donohue Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## Repeated Measures (Within-Subjects) Example with Donohue Data

### Data Management

Prior to analyses, enter the data.

```{r}
Pretest <- c(7,11,11,13,15,17,18,18,19,19,19,19,21,22,25,25,25,26,27,29)
Posttest <- c(16,20,25,22,28,12,16,26,21,22,26,30,23,27,23,27,28,24,28,28)
Followup <- c(16,18,23,21,27,21,18,21,24,21,27,28,18,27,23,28,31,18,31,27)
DonohueData <- data.frame(Pretest,Posttest,Followup)
```

### Analyses of the Different Variables

With multiple variables, it is useful to get descriptive statistics and confidence intervals for each variable.

```{r}
estimateMeans(Pretest,Posttest,Followup)
```

It is also useful to view the means and confidence intervals of the groups in a plot.

```{r,Donohue-Means}
plotMeans(Pretest,Posttest,Followup,main="Critical Thinking Scores at Pretest, Posttest, and Followup",ylab="Critical Thinking Score")
```
 
### Analysis of a Variable Difference

The first research question is whether there is a difference between the posttest and followup occasions.

First, set the comparison and obtain the difference plot for that comparison.

```{r,Donohue-Comparison}
plotMeanComparison(Posttest,Followup,main="Critical Thinking Scores of Posttest vs Followup",ylab="Critical Thinking Score")
```

Then, obtain the standardized effect size for that comparison.

```{r}
estimateStandardizedMeanDifference(Posttest,Followup)
```

### Analysis of a Variable Contrast

The second research question is whether the pretest differs from the posttest and followup combined.

First, set the contrast and obtain a difference plot for the contrast.

```{r,Donohue-Contrast}
PrevsPostFollow <- c(-1,.5,.5)
plotMeanSubsets(Pretest,Posttest,Followup,contrast=PrevsPostFollow,labels=c("Pretest","Post&Follow"),main="Critical Thinking Scores of Prestest vs Posttest and Followup Combined",ylab="Critical Thinking Score")
```

then, estimate the standardized contrast.

```{r}
estimateStandardizedMeanContrast(Pretest,Posttest,Followup,contrast=PrevsPostFollow)
```
