---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Frenda Summary Statistics Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## Frenda Summary Statistics Example

### Data Management

Create a table of summary statistics for the study. Though the study is a factorial design, treat each level of the two factors as independent groups in a single factor.

```{r}
EveningSleep <- c(N=26,M=1.50,SD=1.38)
EveningNosleep <- c(N=26,M=1.14,SD=0.96)
MorningSleep <- c(N=25,M=1.38,SD=1.50)
MorningNosleep <- c(N=26,M=2.22,SD=1.68)
FrendaSummary <- rbind(EveningSleep,EveningNosleep,MorningSleep,MorningNosleep)
class(FrendaSummary) <- "bss"
```

### Analyses of the Different Groups

First, estimate the descriptive statistics and confidence intervals for all levels.

```{r,Frenda-Summary-Means}
estimateMeans(FrendaSummary)
plotMeans(FrendaSummary,ylab="False Memory",ylim=c(0,4),values=FALSE)
```

### Analyses of the Marginal Means

Then, use contrast codes to estimate the marginal means for each factor.

First, for the Evening condition:

```{r}
Evening <- c(.5,.5,0,0)
estimateMeanContrast(FrendaSummary,contrast=Evening)
```

Then for the Morning condition:

```{r}
Morning <- c(0,0,.5,.5)
estimateMeanContrast(FrendaSummary,contrast=Morning)
```

Then for the Sleep condition:

```{r}
Sleep <- c(.5,0,.5,0)
estimateMeanContrast(FrendaSummary,contrast=Sleep)
```

Finally for the NoSleep condition:

```{r}
Nosleep <- c(0,.5,0,.5)
estimateMeanContrast(FrendaSummary,contrast=Nosleep)
```

### Analyses of Main Effects 

#### Analyses of the Factor A (Evening vs Morning) Main Effect

To analyze the main effect of Factor A, set a contrast code and plot the marginal means and the difference between them.

```{r,Frenda-Summary-MainA}
mainFactorA <- c(-.5,-.5,.5,.5)
estimateMeanSubsets(FrendaSummary,contrast=mainFactorA)
plotMeanSubsets(FrendaSummary,contrast=mainFactorA,labels=c("Evening","Morning"),main="Factor A Main Effect",ylab="False Memory",ylim=c(0,4),values=FALSE)
```

Then estimate the standardized effect size for the main effect.

```{r}
estimateStandardizedMeanContrast(FrendaSummary,contrast=mainFactorA)
```

#### Analyses of the Factor B (Sleep vs NoSleep) Main Effect

To analyze the main effect of Factor B, set a contrast code and plot the marginal means and the difference between them.

```{r,Frenda-Summary-MainB}
mainFactorB <- c(-.5,.5,-.5,.5)
estimateMeanSubsets(FrendaSummary,contrast=mainFactorB)
plotMeanSubsets(FrendaSummary,contrast=mainFactorB,labels=c("Sleep","NoSleep"),main="Factor B Main Effect",ylab="False Memory",ylim=c(0,4),values=FALSE)
```

Then estimate the standardized effect size for the main effect.

```{r}
estimateStandardizedMeanContrast(FrendaSummary,contrast=mainFactorB)
```

### Analyses of the Interaction

To analyze the interaction, set a contrast code and estimate the effect.

```{r}
Interaction <- c(1,-1,-1,1)
estimateMeanContrast(FrendaSummary,contrast=Interaction)
```

#### Analyses of the Factor B (Sleep vs NoSleep) at A1 (Evening) Simple Effect

More helpfully, analyze the simple effect by setting the appropriate contrast and plotting.

```{r,Frenda-Summary-SimpleA1}
simpleBatA1 <- c(-1,1,0,0)
estimateMeanSubsets(FrendaSummary,contrast=simpleBatA1)
plotMeanSubsets(FrendaSummary,contrast=simpleBatA1,labels=c("Sleep","NoSleep"),main="Simple Effect of B at A1",ylab="False Memory",ylim=c(0,4),values=FALSE)
```

Then estimate the standardized effect size for the simple effect.

```{r}
estimateStandardizedMeanContrast(FrendaSummary,contrast=simpleBatA1)
```

#### Analyses of the Factor B (Sleep vs NoSleep) at A2 (Morning) Simple Effect

Next, analyze the other simple effect by setting the appropriate contrast and plotting.

```{r,Frenda-Summary-SimpleA2}
simpleBatA2 <- c(0,0,-1,1)
estimateMeanSubsets(FrendaSummary,contrast=simpleBatA2)
plotMeanSubsets(FrendaSummary,contrast=simpleBatA2,labels=c("Sleep","NoSleep"),main="Simple Effect of B at A2",ylab="False Memory",ylim=c(0,4),values=FALSE)
```

Then estimate the standardized effect size for the simple effect.

```{r}
estimateStandardizedMeanContrast(FrendaSummary,contrast=simpleBatA2)
```
