---
subtitle: "Holzel Summary Statistics Example"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Holzel Summary Statistics Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Holzel Summary Statistics Example

This page analyzes a two-factor mixed design (one between-subjects and one within-subjects factor) using summary statistics input.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Data Management

Create two tables of summary statistics for the first simple effect of interest.

```{r}
PretestControl <- c(N = 17, M = 43.815, SD = 4.910)
PosttestControl <- c(N = 17, M = 43.932, SD = 5.507)
HolzelSummaryControl <- rbind(PretestControl, PosttestControl)
class(HolzelSummaryControl) <- "wss"

HolzelCorrControl <- declareCorrelations("PretestControl", "PosttestControl")
HolzelCorrControl["PretestControl", "PosttestControl"] <- .970
HolzelCorrControl <- fillCorrelations(HolzelCorrControl)
```

Create two tables of summary statistics for the second simple effect of interest.

```{r}
PretestMeditation <- c(N = 16, M = 43.705, SD = 6.427)
PosttestMeditation <- c(N = 16, M = 44.666, SD = 6.303)
HolzelSummaryMeditation <- rbind(PretestMeditation, PosttestMeditation)
class(HolzelSummaryMeditation) <- "wss"

HolzelCorrMeditation <- declareCorrelations("PretestMeditation", "PosttestMeditation")
HolzelCorrMeditation["PretestMeditation", "PosttestMeditation"] <- .993
HolzelCorrMeditation <- fillCorrelations(HolzelCorrMeditation)
```

### Analyses of the Differences within Conditions

For each subset, obtain a difference plot comparing pretest and posttest.

```{r,Holzel-Summary-Comparison}
estimateMeanComparison(HolzelSummaryControl, HolzelCorrControl)
plotMeanComparison(HolzelSummaryControl, HolzelCorrControl, main = "Pretest vs Posttest for the Control Group", ylab = "Gray Matter", values = FALSE)
estimateMeanComparison(HolzelSummaryMeditation, HolzelCorrMeditation)
plotMeanComparison(HolzelSummaryMeditation, HolzelCorrMeditation, main = "Pretest vs Posttest for the Meditation Group", ylab = "Gray Matter", values = FALSE)
```

Then for each subset, obtain the standardized effect size comparing pretest to posttest.

```{r}
estimateStandardizedMeanDifference(HolzelSummaryControl, HolzelCorrControl)
estimateStandardizedMeanDifference(HolzelSummaryMeditation, HolzelCorrMeditation)
```
