---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{PenLaptop Summary Statistics Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## PenLaptop Summary Statistics Example

### PenLaptop1 Sample

PenLaptop1 focuses on the difference between two groups in the first sample. First, create a table of summary statistics.

```{r}
Pen <- c(N=34,M=8.812,SD=4.749)
Laptop <- c(N=31,M=14.519,SD=7.286)
PenLaptop1Summary <- rbind(Pen,Laptop)
class(PenLaptop1Summary) <- "bss"
```

The primary emphasis of the analysis is to estimate and represent the difference between the two conditions.

```{r,PenLaptop1-Summary-Comparison}
estimateMeanComparison(PenLaptop1Summary)
plotMeanComparison(PenLaptop1Summary,main="Transcription as a Function of Note Taking",ylab="Transcription %",ylim=c(0,20),values=FALSE)
```

The secondary emphasis of the analysis is provide a standardized effect size for the difference.

```{r}
estimateStandardizedMeanDifference(PenLaptop1Summary)
```

### PenLaptop2 Sample

PenLaptop2 focuses on the difference between two groups in the second sample. Thus, create a table of summary statistics.

```{r}
Pen <- c(N=48,M=6.881,SD=4.219)
Laptop <- c(N=103,M=12.088,SD=5.525)
PenLaptop2Summary <- rbind(Pen,Laptop)
class(PenLaptop2Summary) <- "bss"
```

The primary emphasis of the analysis is to estimate and represent the difference between the two conditions.

```{r,PenLaptop2-Summary-Comparison}
estimateMeanComparison(PenLaptop2Summary)
plotMeanComparison(PenLaptop2Summary,main="Transcription as a Function of Note Taking",ylab="Transcription %",ylim=c(0,20),values=FALSE)
```

The secondary emphasis of the analysis is provide a standardized effect size for the difference.

```{r}
estimateStandardizedMeanDifference(PenLaptop2Summary)
```

### PenLaptop3 Sample

PenLaptop3 focuses on the difference between two groups in the third sample. Thus, create a table of summary statistics.

```{r}
Pen <- c(N=54,M=4.178,SD=2.549)
Laptop <- c(N=55,M=11.622,SD=5.681)
PenLaptop3Summary <- rbind(Pen,Laptop)
class(PenLaptop3Summary) <- "bss"
```

The primary emphasis of the analysis is to estimate and represent the difference between the two conditions.

```{r,PenLaptop3-Summary-Comparison}
estimateMeanComparison(PenLaptop3Summary)
plotMeanComparison(PenLaptop3Summary,main="Transcription as a Function of Note Taking",ylab="Transcription %",ylim=c(0,20),values=FALSE)
```

The secondary emphasis of the analysis is provide a standardized effect size for the difference.

```{r}
estimateStandardizedMeanDifference(PenLaptop3Summary)
```
