---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "2020-11-20"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{OneWay (Between-Subjects) Example with Rattan Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
library(EASI)
```

## OneWay (Between-Subjects) Example with Rattan Data

### Data Management

Prior to analyses, enter the data.

```{r}
Feedback <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3)
Motivation <- c(5.5,5,5.5,6,1,2.5,4.5,1,3.5,1.5,5.5,6,1.5,1,3.5,2.5,3,1,2,6,4.5,4.5,6,7,3,7,3.5,5,4.5,5.5,6.5,6,6,7,5.5,6,2.5,4.5,3.5,6,5,6,3.5,4,3,5.5,3,6,3,5,6,6.5,3.5,2)
Feedback <- factor(Feedback,levels=c(1,2,3),labels=c("Comfort","Challenge","Control"))
RattanData <- data.frame(Feedback,Motivation)
```

### Analyses of the Different Groups

With multiple groups, it is useful to get descriptive statistics and confidence intervals for each group.

```{r}
estimateMeans(Motivation~Feedback)
```

It is also useful to view the means and confidence intervals of the groups in a plot.

```{r,Rattan-Means}
plotMeans(Motivation~Feedback,main="Motivation as a Function of Feedback Type",ylab="Motivation")
```

### Analysis of a Group Difference

The first research question is whether there is a difference between the two non-control groups.

First, set the comparison and obtain the difference plot for that comparison.

```{r,Rattan-Comparison}
Comparison <- factor(Feedback,c("Comfort","Challenge"))
plotMeanComparison(Motivation~Comparison,main="Influence of Comfort vs Challenge Feedback on Motivation",ylab="Motivation")
```

Then, obtain the standardized effect size for that comparison.

```{r}
estimateStandardizedMeanDifference(Motivation~Comparison)
```

### Analysis of a Group Contrast

The second research question is whether the Comfort group differs from the other two groups.

First, set the contrast and obtain a difference plot for the contrast.

```{r,Rattan-Contrast}
ComfortvsOthers <- c(-1,.5,.5)
plotMeanSubsets(Motivation~Feedback,contrast=ComfortvsOthers,labels=c("Comfort","Others"),main="Influence of Comfort Feedback vs Other Types of Feedback on Motivation",ylab="Motivation")
```

Then, estimate the standardized contrast.

```{r}
estimateStandardizedMeanContrast(Motivation~Feedback,contrast=ComfortvsOthers)
```
