---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{OneWay (Rattan Summary Statistics Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Rattan Summary Statistics Example

This page analyzes a single-factor between-subjects (one-way) design using summary statistics input.

### Data Management

Prior to analyses, enter a table of summary statistics.

```{r}
Comfort <- c(N=18,M=3.333,SD=1.917)
Challenge <- c(N=17,M=5.265,SD=1.448)
Control <- c(N=19,M=4.447,SD=1.433)
RattanSummary <- rbind(Comfort,Challenge,Control)
class(RattanSummary) <- "bss"
```

### Analyses of the Different Groups

With multiple groups, it is useful to get descriptive statistics and confidence intervals for each group.

```{r,Rattan-Summary-Means}
estimateMeans(RattanSummary)
plotMeans(RattanSummary,main="Motivation as a Function of Feedback Type",ylab="Motivation",ylim=c(0,7),values=FALSE)
```

### Analysis of a Group Difference

The first research question is whether there is a difference between the two non-control groups.

First, set the comparison and obtain the difference plot for that comparison.

```{r,Rattan-Summary-Comparison}
ComfortvsChallenge <- rbind(Comfort,Challenge)
class(ComfortvsChallenge) <- "bss"
estimateMeanComparison(ComfortvsChallenge)
plotMeanComparison(ComfortvsChallenge,main="Influence of Comfort vs Challenge Feedback on Motivation",ylab="Motivation",ylim=c(0,7),values=FALSE)
```

Then, obtain the standardized effect size for that comparison.

```{r}
estimateStandardizedMeanDifference(ComfortvsChallenge)
```

### Analysis of a Group Contrast

The second research question is whether the Comfort group differs from the other two groups.

First, set the contrast and obtain a difference plot for the contrast.

```{r,Rattan-Summary-Contrast}
ComfortvsOthers <- c(-1,.5,.5)
estimateMeanSubsets(RattanSummary,contrast=ComfortvsOthers)
plotMeanSubsets(RattanSummary,contrast=ComfortvsOthers,labels=c("Comfort","Others"),main="Influence of Comfort Feedback vs \n Other Types of Feedback on Motivation",ylab="Motivation",ylim=c(0,7),values=FALSE)
```

Then, estimate the standardized contrast.

```{r}
estimateStandardizedMeanContrast(RattanSummary,contrast=ComfortvsOthers)
```
