---
subtitle: "Thomason Data Example"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Thomason Data Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r,include=FALSE}
if (!require(EASI)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/EASI")
}
library(EASI)
```

## Thomason Data Example

This page analyzes a within-subjects (paired samples) design for two time points using raw data input.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Thomason1 Sample

Thomason1 focuses on the difference between pretest and posttest in the first sample. First, enter the data.

```{r}
Pretest <- c(13, 12, 12, 9, 14, 17, 14, 9, 6, 7, 11, 15)
Posttest <- c(14, 13, 16, 12, 15, 18, 13, 10, 10, 8, 14, 16)
Thomason1Data <- data.frame(Pretest, Posttest)
```

The primary emphasis of the analysis is to estimate and represent the difference between the two conditions.

```{r,Thomason1-Data-Comparison}
estimateMeanComparison(Thomason1Data)
plotMeanComparison(Thomason1Data, main = "LSAT Score Before and After Mapping", ylab = "LSAT Score", ylim = c(0, 20), values = FALSE)
```

The secondary emphasis of the analysis is provide a standardized effect size for the difference.

```{r}
estimateStandardizedMeanDifference(Thomason1Data)
```

### Thomason2 Sample

Thomason2 focuses on the difference between pretest and posttest in the second sample. Thus, enter the data.

```{r}
Pretest <- c(10, 14, 7, 12, 11, 11, 15, 14, 9, 16, 10, 11, 13, 19, 19, 15)
Posttest <- c(12, 19, 6, 9, 15, 13, 17, 14, 10, 17, 9, 14, 15, 22, 18, 18)
Thomason2Data <- data.frame(Pretest, Posttest)
```

The primary emphasis of the analysis is to estimate and represent the difference between the two conditions.

```{r,Thomason2-Data-Comparison}
estimateMeanComparison(Thomason2Data)
plotMeanComparison(Thomason2Data, main = "LSAT Score Before and After Mapping", ylab = "LSAT Score", ylim = c(0, 20), values = FALSE)
```

The secondary emphasis of the analysis is provide a standardized effect size for the difference.

```{r}
estimateStandardizedMeanDifference(Thomason2Data)
```

### Thomason3 Sample

Thomason3 focuses on the difference between pretest and posttest in the third sample. Thus, enter the data.

```{r}
Pretest <- c(41, 50, 71, 70, 74, 75, 64, 72, 77, 53, 60, 73, 72, 62, 68, 63, 69, 71, 70, 70, 75, 71, 76, 64, 70, 65, 75, 66, 70, 70, 64, 72, 63, 68, 64, 61, 63, 76, 71)
Posttest <- c(52, 63, 69, 71, 80, 80, 69, 76, 78, 77, 67, 76, 69, 73, 73, 68, 70, 81, 70, 76, 77, 75, 69, 77, 70, 76, 65, 64, 72, 71, 63, 78, 71, 77, 67, 66, 73, 75, 75)
Thomason3Data <- data.frame(Pretest, Posttest)
```

The primary emphasis of the analysis is to estimate and represent the difference between the two conditions.

```{r,Thomason3-Data-Comparison}
estimateMeanComparison(Thomason3Data)
plotMeanComparison(Thomason3Data, main = "LSAT Score Before and After Mapping", ylab = "LSAT Score", values = FALSE)
```

The secondary emphasis of the analysis is provide a standardized effect size for the difference.

```{r}
estimateStandardizedMeanDifference(Thomason3Data)
```
