---
title: "Estimation Approach to Statistical Inference"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    collapse: true
    theme: cerulean
    highlight: tango
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Thomason Data Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(devtools)) install.packages('devtools')
devtools::install_github("cwendorf/EASI")}
library(EASI)
```

## Thomason Data Example

### Thomason1 Sample

Thomason1 focuses on the difference between pretest and posttest in the first sample. First, enter the data.

```{r}
Pretest <- c(13,12,12,9,14,17,14,9,6,7,11,15)
Posttest <- c(14,13,16,12,15,18,13,10,10,8,14,16)
Thomason1Data <- data.frame(Pretest,Posttest)
```

The primary emphasis of the analysis is to estimate and represent the difference between the two conditions.

```{r,Thomason1-Data-Comparison}
estimateMeanComparison(Thomason1Data)
plotMeanComparison(Thomason1Data,main="LSAT Score Before and After Mapping",ylab="LSAT Score",ylim=c(0,20),values=FALSE)
```

The secondary emphasis of the analysis is provide a standardized effect size for the difference.

```{r}
estimateStandardizedMeanDifference(Thomason1Data)
```

### Thomason2 Sample

Thomason2 focuses on the difference between pretest and posttest in the second sample. Thus, enter the data.

```{r}
Pretest <- c(10,14,7,12,11,11,15,14,9,16,10,11,13,19,19,15)
Posttest <- c(12,19,6,9,15,13,17,14,10,17,9,14,15,22,18,18)
Thomason2Data <- data.frame(Pretest,Posttest)
```

The primary emphasis of the analysis is to estimate and represent the difference between the two conditions.

```{r,Thomason2-Data-Comparison}
estimateMeanComparison(Thomason2Data)
plotMeanComparison(Thomason2Data,main="LSAT Score Before and After Mapping",ylab="LSAT Score",ylim=c(0,20),values=FALSE)
```

The secondary emphasis of the analysis is provide a standardized effect size for the difference.

```{r}
estimateStandardizedMeanDifference(Thomason2Data)
```

### Thomason3 Sample

Thomason3 focuses on the difference between pretest and posttest in the third sample. Thus, enter the data.

```{r}
Pretest <- c(41,50,71,70,74,75,64,72,77,53,60,73,72,62,68,63,69,71,70,70,75,71,76,64,70,65,75,66,70,70,64,72,63,68,64,61,63,76,71)
Posttest <- c(52,63,69,71,80,80,69,76,78,77,67,76,69,73,73,68,70,81,70,76,77,75,69,77,70,76,65,64,72,71,63,78,71,77,67,66,73,75,75)
Thomason3Data <- data.frame(Pretest,Posttest)
```

The primary emphasis of the analysis is to estimate and represent the difference between the two conditions.

```{r,Thomason3-Data-Comparison}
estimateMeanComparison(Thomason3Data)
plotMeanComparison(Thomason3Data,main="LSAT Score Before and After Mapping",ylab="LSAT Score",values=FALSE)
```

The secondary emphasis of the analysis is provide a standardized effect size for the difference.

```{r}
estimateStandardizedMeanDifference(Thomason3Data)
```
