---
subtitle: "Thomason Summary Statistics Example"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Thomason Summary Statistics Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7",filename='revised_toc.R')
```

```{r,include=FALSE}
if(!require(EASI)) {
if(!require(remotes)) install.packages('remotes')
remotes::install_github("cwendorf/EASI")}
library(EASI)
```

## Thomason Summary Statistics Example

This page analyzes a within-subjects (paired samples) design for two time points using summary statistics input.

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile,base_level=3,toc_depth=4)
```

---

### Thomason1 Sample

Thomason1 focuses on the difference between pretest and posttest in the first sample. First, create the tables of summary statistics.

```{r}
Pretest <- c(N=12,M=11.583,SD=3.315)
Posttest <- c(N=12,M=13.250,SD=2.896)
Thomason1Summary <- rbind(Pretest,Posttest)
class(Thomason1Summary) <- "wss"
Thomason1Corr <- data.frame()
Thomason1Corr["Pretest","Posttest"] <- .892
```

The primary emphasis of the analysis is to estimate and represent the difference between the two conditions.

```{r,Thomason1-Summary-Comparison}
estimateMeanComparison(Thomason1Summary,Thomason1Corr)
plotMeanComparison(Thomason1Summary,Thomason1Corr,main="LSAT Score Before and After Mapping",ylab="LSAT Score",ylim=c(0,20),values=FALSE)
```

The secondary emphasis of the analysis is provide a standardized effect size for the difference.

```{r}
estimateStandardizedMeanDifference(Thomason1Summary,Thomason1Corr)
```

### Thomason2 Sample

Thomason2 focuses on the difference between pretest and posttest in the second sample. Thus, create the tables of summary statistics.

```{r}
Pretest <- c(N=16,M=12.875,SD=3.403)
Posttest <- c(N=16,M=14.250,SD=4.282)
Thomason2Summary <- rbind(Pretest,Posttest)
class(Thomason2Summary) <- "wss"
Thomason2Corr <- data.frame()
Thomason2Corr["Pretest","Posttest"] <- .871
```

The primary emphasis of the analysis is to estimate and represent the difference between the two conditions.

```{r,Thomason2-Summary-Comparison}
estimateMeanComparison(Thomason2Summary,Thomason2Corr)
plotMeanComparison(Thomason2Summary,Thomason2Corr,main="LSAT Score Before and After Mapping",ylab="LSAT Score",ylim=c(0,20),values=FALSE)
```

The secondary emphasis of the analysis is provide a standardized effect size for the difference.

```{r}
estimateStandardizedMeanDifference(Thomason2Summary,Thomason2Corr)
```

### Thomason3 Sample

Thomason3 focuses on the difference between pretest and posttest in the third sample. Thus, create the tables of summary statistics.

```{r}
Pretest <- c(N=39,M=67.410,SD=7.419)
Posttest <- c(N=39,M=71.769,SD=5.851)
Thomason3Summary <- rbind(Pretest,Posttest)
class(Thomason3Summary) <- "wss"
Thomason3Corr <- data.frame()
Thomason3Corr["Pretest","Posttest"] <- .601
```

The primary emphasis of the analysis is to estimate and represent the difference between the two conditions.

```{r,Thomason3-Summary-Comparison}
estimateMeanComparison(Thomason3Summary,Thomason3Corr)
plotMeanComparison(Thomason3Summary,Thomason3Corr,main="LSAT Score Before and After Mapping",ylab="LSAT Score",values=FALSE)
```

The secondary emphasis of the analysis is provide a standardized effect size for the difference.

```{r}
estimateStandardizedMeanDifference(Thomason3Summary,Thomason3Corr)
```
